### 2019-11-20 paper/paper.tex
Initial commit of 'paper.tex'.

\documentclass[aps,prb,reprint,groupedaddress,showpacs,amsfonts,amsmath,amssymb,superscriptaddress]{revtex4-1}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{color}
\usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}

\begin{document}

\title{Global phase diagram and possible quantum spin liquid in the extended triangular lattice model}

\author{Shi Wang}
\affiliation{National Laboratory of Solid State Microstructures and School of Physics, Nanjing University, Nanjing 210093, China}
\author{Shun-Li Yu}
\email{slyu@nju.edu.cn}
\affiliation{National Laboratory of Solid State Microstructures and School of Physics, Nanjing University, Nanjing 210093, China}
\affiliation{Collaborative Innovation Center of Advanced Microstructures, Nanjing University, Nanjing 210093, China}
\author{Jian-Xin Li}
\email{jxli@nju.edu.cn}
\affiliation{National Laboratory of Solid State Microstructures and School of Physics, Nanjing University, Nanjing 210093, China}
\affiliation{Collaborative Innovation Center of Advanced Microstructures, Nanjing University, Nanjing 210093, China}

\date{\today}

\begin{abstract}
The abstract of this article. Left blank currently.
\end{abstract}

\maketitle

\section{Introduction}
The spin-1/2 Kitaev model on honeycomb lattice, which has both gapped and gapless quantum spin liquid(QSL) ground state (GS) supporting fractionalized excitations, is of central interest in condensed matter physics (and beyond) over the last few years. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model. As pointed out by Jackeli and Khaliullin, the elementary ingredients for realizing this highly anisotropic spin model is the interplay of the strong relativistic spin-orbit coupling (SOC) and electron interactions. Indeed, the interplay of SOC and electron interactions gives rise to many novel phases, especially for the so called relativistic Mott insulators (RMIs) whose physics may drastically differ from that of Mott insulators with weak SOC (e.g., cuprates). Of particular interest are 4d and 5d transition metal oxides, such as $\alpha$-RuCl$_3$ and iridates A$_2$IrO$_3$ (A=Na, Li).
In 2009, Jackeli and Khaliullin laid out in remarkably precise terms what the elementary ingredients for a succussful Kitaev material serach strategy are. They not only explained the microscopic origin of Kitaev-type bond-directional exchange interactions in certain (edge sharing) 4d$^5$ and 5d$^5$ transition metal compounds, they also proposed the Kitaev-Heisenberg model to describe the physics in iridates of the form A$_2$IrO$_3$ such as Na$_2$IrO$_3$.

\end{document}

### 2019-12-04 paper/paper.tex
20191204 10:58

@@
 \section{Introduction}
-The spin-1/2 Kitaev model on honeycomb lattice, which has both gapped and gapless quantum spin liquid(QSL) ground state (GS) supporting fractionalized excitations, is of central interest in condensed matter physics (and beyond) over the last few years.
-Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model.
-As pointed out by Jackeli and Khaliullin, the elementary ingredients for realizing this highly anisotropic spin model is the interplay of the strong relativistic spin-orbit coupling (SOC) and electron interactions.
-Indeed, the interplay of SOC and electron interactions gives rise to many novel phases, especially for the so called relativistic Mott insulators (RMIs) whose physics may drastically differ from that of Mott insulators with weak SOC (e.g., cuprates).
-Of particular interest are 4d and 5d transition metal oxides, such as $\alpha$-RuCl$_3$ and iridates A$_2$IrO$_3$ (A=Na, Li).
-In 2009, Jackeli and Khaliullin laid out in remarkably precise terms what the elementary ingredients for a succussful Kitaev material serach strategy are.
-They not only explained the microscopic origin of Kitaev-type bond-directional exchange interactions in certain (edge sharing) 4d$^5$ and 5d$^5$ transition metal compounds, they also proposed the Kitaev-Heisenberg model to describe the physics in iridates of the form A$_2$IrO$_3$ such as Na$_2$IrO$_3$.
+Geometrical frustration, which arises when the lattice geometry gives rise to constraints on the system Hamiltonian that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
+In particular, antiferromagnets on the triangular lattice is a typcial example of such geomtrical frustrated spin systems.
+Anderson proposed that a fully disordered resonating-valence-bond (RVB) state may be the ground state of the antiferromagnetic Heisenberg model on triangular lattice.
+However, exchange frustation in systems with strongly anisotropic magnetic exchange has been shown  tobe another avenue to explore the QSL state.
 

### 2019-12-04 paper/paper.tex
20191204 22:06

@@
 \section{Introduction}
-Geometrical frustration, which arises when the lattice geometry gives rise to constraints on the system Hamiltonian that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
-In particular, antiferromagnets on the triangular lattice is a typcial example of such geomtrical frustrated spin systems.
-Anderson proposed that a fully disordered resonating-valence-bond (RVB) state may be the ground state of the antiferromagnetic Heisenberg model on triangular lattice.
-However, exchange frustation in systems with strongly anisotropic magnetic exchange has been shown  tobe another avenue to explore the QSL state.
+Geometric frustration, which arises when the lattice geometry gives rise to constraints on the system Hamiltonian that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
+In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interest in condensed matter physics.
+For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, Anderson proposed that a fully disordered resonating-valence-bond (RVB) state may be the ground state.
+However, lots of studies point to a 120$^\circ$ N\'{e}el-ordered ground state.
+It is thus desirable to include next-nearest-neighbor interactions to introduce further frustration.
+After considering the next-nearest-neighbor interactions, the system has a much richer phase diagram incluing a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order.
+All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.
+\textcolor{red}{$\cdots\cdots$}
+
+Recently however, exchange frustation in systems with strongly anisotropic magnetic exchange has been shown to be another promising approach to explore exotic quantum spin states.
+Like Geometrical frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy.
+\textcolor{red}{$\cdots\cdots$}
+
+On the experimental side, a variety of triangular magnets such YbMgGaO$_2$, \emph{AReCh}$_2$ (A=alkali or monovalent ions, Re=rare-earth, Ch=O, S,Se) have been synthesized and explored by magnetic susceptibility and heat capacity measurements.
+The lack of signature for long-range magnetic order and spin freezing down to very low temperature implies their candidacy for quantum spin liquid state.
+\textcolor{red}{$\cdots\cdots$}
+
+Inspired by previous theoretical and experimental works, we study the J-K-$\Gamma$ model Hamiltonian on the triangular lattice.
+To the best of our knowledge, no exact solution of the spin-$1/2$ Kitaev or $\Gamma$ model on the triangular lattice has been obtained so far.
+Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular J-K-$\Gamma$ model.
+\textcolor{red}{$\cdots\cdots$}
+
+In this paper, be combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the J-K-$\Gamma$ model.
+\textcolor{red}{$\cdots\cdots$}
+
+The rest of the paper is organized as follows: \textcolor{red}{$\cdots\cdots$}
 

### 2019-12-05 paper/paper.tex
20191205 17:14

@@
 \begin{abstract}
-The abstract of this article. Left blank currently.
+\textcolor{red}{Abstract of this article.}
+
+\textcolor{red}{Left blank currently.}
 \end{abstract}
@@
 \section{Introduction}
-Geometric frustration, which arises when the lattice geometry gives rise to constraints on the system Hamiltonian that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
+Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
 In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interest in condensed matter physics.
 For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, Anderson proposed that a fully disordered resonating-valence-bond (RVB) state may be the ground state.
-However, lots of studies point to a 120$^\circ$ N\'{e}el-ordered ground state.
-It is thus desirable to include next-nearest-neighbor interactions to introduce further frustration.
-After considering the next-nearest-neighbor interactions, the system has a much richer phase diagram incluing a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order.
+However, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state.
+When the next-nearest-neighbor interactions are included which introduce further frustration, the system has a much richer phase diagram incluing a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order.
 All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.
@@
 Like Geometrical frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy.
+The spin-1/2 Kitaev model on honeycomb lattice, which has both gapped and gapless quantum spin liquid(QSL) ground state (GS) supporting fractionalized excitations, is of central interest in condensed matter physics (and beyond) over the last few years.
+Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model.
+As pointed out by Jackeli and Khaliullin, the elementary ingredients for realizing this highly anisotropic spin model is the interplay of the strong relativistic spin-orbit coupling (SOC) and electron interactions.
+Indeed, the interplay of SOC and electron interactions gives rise to many novel phases, especially for the so called relativistic Mott insulators (RMIs) whose physics may drastically differ from that of Mott insulators with weak SOC (e.g., cuprates).
+Of particular interest are 4d and 5d transition metal oxides, such as $\alpha$-RuCl$_3$ and iridates A$_2$IrO$_3$ (A=Na, Li).
+In 2009, Jackeli and Khaliullin laid out in remarkably precise terms what the elementary ingredients for a succussful Kitaev material serach strategy are.
+They not only explained the microscopic origin of Kitaev-type bond-directional exchange interactions in certain (edge sharing) 4d$^5$ and 5d$^5$ transition metal compounds, they also proposed the Kitaev-Heisenberg model to describe the physics in iridates of the form A$_2$IrO$_3$ such as Na$_2$IrO$_3$.
 \textcolor{red}{$\cdots\cdots$}
@@
 Inspired by previous theoretical and experimental works, we study the J-K-$\Gamma$ model Hamiltonian on the triangular lattice.
-To the best of our knowledge, no exact solution of the spin-$1/2$ Kitaev or $\Gamma$ model on the triangular lattice has been obtained so far.
+To the best of our knowledge, no exact solution has been reported so far for the spin-$1/2$ Kitaev and/or $\Gamma$ model on the triangular lattice.
 Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular J-K-$\Gamma$ model.

### 2019-12-06 paper/paper.tex
20191206 15:21

@@
 \usepackage{color}
+\usepackage{changes}
+    \definechangesauthor[name={Wang Shi}, color=orange]{swang}
+
 \usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}
@@
 \begin{abstract}
-\textcolor{red}{Abstract of this article.}
-
-\textcolor{red}{Left blank currently.}
+    The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization.
+\textcolor{red}{$\cdots \cdots$}
 \end{abstract}
@@
 Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
-In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interest in condensed matter physics.
-For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, Anderson proposed that a fully disordered resonating-valence-bond (RVB) state may be the ground state.
-However, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state.
+%
+\replaced[id=swang]{In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interest in condensed matter physics.
+For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) state was proposed as the possible ground state in the early years, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter.
+}{The nearest-neighbor spin-$1/2$ antiferromagetic Heisenberg model on triangular lattice is a typical example of such geometric frustrated spin systems and have attracted numerous interest in condensed matter physics.
+Though a fully disordered resonating-valence-bond (RVB) state was proposed as the possible ground state in the early years, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter.}
+%
 When the next-nearest-neighbor interactions are included which introduce further frustration, the system has a much richer phase diagram incluing a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order.

### 2019-12-09 paper/paper.tex
20191209 10:41

--- 2019-12-05 paper/paper.tex
@@
 \usepackage{color}
+% \usepackage{changes}
+    % \definechangesauthor[name={Wang Shi}, color=orange]{swang}
+
 \usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}
@@
 In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interest in condensed matter physics.
-For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, Anderson proposed that a fully disordered resonating-valence-bond (RVB) state may be the ground state.
-However, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state.
+For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) state was proposed as the possible ground state in the early years, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter.
 When the next-nearest-neighbor interactions are included which introduce further frustration, the system has a much richer phase diagram incluing a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order.
@@
 Recently however, exchange frustation in systems with strongly anisotropic magnetic exchange has been shown to be another promising approach to explore exotic quantum spin states.
-Like Geometrical frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy.
+Like geometrical frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy.
 The spin-1/2 Kitaev model on honeycomb lattice, which has both gapped and gapless quantum spin liquid(QSL) ground state (GS) supporting fractionalized excitations, is of central interest in condensed matter physics (and beyond) over the last few years.
 Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model.
-As pointed out by Jackeli and Khaliullin, the elementary ingredients for realizing this highly anisotropic spin model is the interplay of the strong relativistic spin-orbit coupling (SOC) and electron interactions.
+As pointed out by Jackeli and Khaliullin, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles.
 Indeed, the interplay of SOC and electron interactions gives rise to many novel phases, especially for the so called relativistic Mott insulators (RMIs) whose physics may drastically differ from that of Mott insulators with weak SOC (e.g., cuprates).
 Of particular interest are 4d and 5d transition metal oxides, such as $\alpha$-RuCl$_3$ and iridates A$_2$IrO$_3$ (A=Na, Li).
-In 2009, Jackeli and Khaliullin laid out in remarkably precise terms what the elementary ingredients for a succussful Kitaev material serach strategy are.
-They not only explained the microscopic origin of Kitaev-type bond-directional exchange interactions in certain (edge sharing) 4d$^5$ and 5d$^5$ transition metal compounds, they also proposed the Kitaev-Heisenberg model to describe the physics in iridates of the form A$_2$IrO$_3$ such as Na$_2$IrO$_3$.
 \textcolor{red}{$\cdots\cdots$}
 
-On the experimental side, a variety of triangular magnets such YbMgGaO$_2$, \emph{AReCh}$_2$ (A=alkali or monovalent ions, Re=rare-earth, Ch=O, S,Se) have been synthesized and explored by magnetic susceptibility and heat capacity measurements.
+On the experimental side, a variety of triangular magnets such YbMgGaO$_2$, ErMgGaO$_2$, TmMgGaO$_2$ and \emph{AReCh}$_2$ (A=alkali or monovalent ions, Re=rare-earth, Ch=O, S, Se) hav e been synthesized and explored by magnetic susceptibility and heat capacity measurements.
 The lack of signature for long-range magnetic order and spin freezing down to very low temperature implies their candidacy for quantum spin liquid state.
+The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.
 \textcolor{red}{$\cdots\cdots$}
 
-Inspired by previous theoretical and experimental works, we study the J-K-$\Gamma$ model Hamiltonian on the triangular lattice.
+Inspired by previous theoretical and experimental works, we study the Heisenberg-Kitaev-$\Gamma$ (JK$\Gamma$) model Hamiltonian on the triangular lattice.
 To the best of our knowledge, no exact solution has been reported so far for the spin-$1/2$ Kitaev and/or $\Gamma$ model on the triangular lattice.
@@
 
-In this paper, be combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the J-K-$\Gamma$ model.
+In this manuscript, by combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the J-K-$\Gamma$ model.
 \textcolor{red}{$\cdots\cdots$}

### 2019-12-09 paper/paper.tex
20191209 21:33

@@
 
-\title{Global phase diagram and possible quantum spin liquid in the extended triangular lattice model}
+\title{Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model}
 
@@
 Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
-In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interest in condensed matter physics.
-For nearest-neighbor antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) state was proposed as the possible ground state in the early years, several theoretical and numerical studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter.
-When the next-nearest-neighbor interactions are included which introduce further frustration, the system has a much richer phase diagram incluing a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order.
+In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics.
+For nearest-neighbor (NN) spin-$1/2$ antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
+When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order \cite{PhysRevB.42.4800,PhysRevB.46.11137}.
 All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.
-\textcolor{red}{$\cdots\cdots$}
 
-Recently however, exchange frustation in systems with strongly anisotropic magnetic exchange has been shown to be another promising approach to explore exotic quantum spin states.
-Like geometrical frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy.
-The spin-1/2 Kitaev model on honeycomb lattice, which has both gapped and gapless quantum spin liquid(QSL) ground state (GS) supporting fractionalized excitations, is of central interest in condensed matter physics (and beyond) over the last few years.
+On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states.
+Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy.
+The spin-$1/2$ Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration.
+As pointed out by Jackeli and Khaliullin \cite{Khaliullin2005, PhysRevLett.102.017205}, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles.
 Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model.
-As pointed out by Jackeli and Khaliullin, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles.
-Indeed, the interplay of SOC and electron interactions gives rise to many novel phases, especially for the so called relativistic Mott insulators (RMIs) whose physics may drastically differ from that of Mott insulators with weak SOC (e.g., cuprates).
-Of particular interest are 4d and 5d transition metal oxides, such as $\alpha$-RuCl$_3$ and iridates A$_2$IrO$_3$ (A=Na, Li).
-\textcolor{red}{$\cdots\cdots$}
+It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}=1/2$ moments.
+In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
+Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=$1/2$ models with edge sharing octahedra \cite {PhysRevLett.112.077204}.
+Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liqiud (SL) as well as four magnetically ordered phases has been obtained.
+However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.
 
-On the experimental side, a variety of triangular magnets such YbMgGaO$_2$, ErMgGaO$_2$, TmMgGaO$_2$ and \emph{AReCh}$_2$ (A=alkali or monovalent ions, Re=rare-earth, Ch=O, S, Se) hav e been synthesized and explored by magnetic susceptibility and heat capacity measurements.
-The lack of signature for long-range magnetic order and spin freezing down to very low temperature implies their candidacy for quantum spin liquid state.
+On the experimental side, the discovery of YbMgGaO$_4$ has invoked increasing interest in searching for rare-earth based spin-frustrated materials \cite{srep16419,PhysRevLett.115.167203,PhysRevB.94.035107,PhysRevB.96.054445,PhysRevB.97.184413,PhysRevB.97.125105,PhysRevB.96.075105,PhysRevLett.119.157201}.
+The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}.
+Extensive studies of magnetic properties using neutron scattering \cite{Nature20614,nphys3971,PhysRevLett.117.267202,PhysRevX.8.031001}, muon spin relaxation ($\mu$SR) \cite{PhysRevLett.117.097201}, electron spin resonance (ESR) \cite{PhysRevLett.115.167203} reveal a possible gapless quantum spin liquid (QSL) ground state.
+More recently, a class of compounds \emph{AReCh}$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
+The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,arXiv1911.12712}.
 The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.
-\textcolor{red}{$\cdots\cdots$}
 
-Inspired by previous theoretical and experimental works, we study the Heisenberg-Kitaev-$\Gamma$ (JK$\Gamma$) model Hamiltonian on the triangular lattice.
+Inspired by previous theoretical and experimental works, we study the Heisenberg-Kitaev-$\Gamma$ ($J-K-\Gamma$) model on the triangular lattice. The $J-K-\Gamma$ model Hamiltonian is given by
+\begin{equation}
+    H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack
+\end{equation}
+where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.
+1, and $\alpha$, $\beta$ are the remaining directions.
+$J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges.
 To the best of our knowledge, no exact solution has been reported so far for the spin-$1/2$ Kitaev and/or $\Gamma$ model on the triangular lattice.
-Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular J-K-$\Gamma$ model.
-\textcolor{red}{$\cdots\cdots$}
+Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular $J-K-\Gamma$ model.
 
-In this manuscript, by combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the J-K-$\Gamma$ model.
+In this manuscript, by combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the $J-K-\Gamma$ model.
 \textcolor{red}{$\cdots\cdots$}
@@
 
+\section{Methods}
+
+The ground state of the full anisotropic Hamiltonian is no longer solvable in closed analytical form, even in the classical case.
+One, therefore, either has to rely on approximate analytical method or on numerical techniques.
+Here, we briefly describe the methods we used.
+\textcolor{red}{$\cdots\cdots$}
+
+\subsection{Dual Transformation}
+\textcolor{red}{A introduction to dual transformation. Left blank currently.}
+
+\subsection{Classical Monte Carlo}
+\textcolor{red}{A introduction to classical Monte Carlo. Left blank currently.}
+
+\subsection{Exact Diagonalization}
+\textcolor{red}{A introduction to exact diagonalization. Left blank currently.}
+
+\section{Phase Diagram and Analysis}
+\textcolor{red}{Global phase diagram of the $J-K-\Gamma$ model. Left blank currently.}
+
+\section{Discussion}
+\textcolor{red}{A discussion of our results. Left blank currently.}
+
+\section{Acknowledgements}
+\textcolor{red}{Acknowledgements. Left blank currently.}
+
+\bibliography{ref}
+
 \end{document}

### 2019-12-10 paper/paper.tex
20191210 8:56

@@
 Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model.
-It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}=1/2$ moments.
+It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}=1/2$ moments.
 In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
@@
 Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liqiud (SL) as well as four magnetically ordered phases has been obtained.
-However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.
+However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.
 

### 2019-12-22 FiguresForPaper/ShowStructureFactor.py
Add `ShowStructureFactor.py`.

@@ -1,0 +1,69 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from HamiltonianPy import  TRIANGLE_CELL_KS
+
+
+numx = 4
+numy = 6
+alpha = 0.05
+beta = 0.02
+J = np.sin(alpha * np.pi) * np.sin(beta * np.pi)
+K = np.sin(alpha * np.pi) * np.cos(beta * np.pi)
+G = np.cos(alpha * np.pi)
+sub_fig_tag = "(f)"
+params = r"$\alpha={0:.2f}\pi, \beta={1:.2f}\pi$".format(alpha, beta)
+# params = r"$J={0:.0f},K={1:.0f},\Gamma={2:.0f}$".format(J, K, G)
+
+step = 0.005
+kx_ratios = np.arange(-0.7, 0.7 + step, step)
+ky_ratios = np.arange(-0.7 + step, 0.7, step)
+kpoints = np.matmul(
+    np.stack(np.meshgrid(kx_ratios, ky_ratios, indexing="ij"), axis=-1),
+    4 * np.pi * np.identity(2) / np.sqrt(3)
+)
+BZBoundary = TRIANGLE_CELL_KS[[*range(6), 0]]
+
+sf_file_name = "SF_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}".format(
+    numx, numy, alpha, beta
+)
+factors = np.load("data/" + sf_file_name + ".npy")
+
+fig, ax = plt.subplots(num=sf_file_name)
+im = ax.pcolormesh(
+    kpoints[:, :, 0], kpoints[:, :, 1], factors, zorder=0,
+    cmap="Reds", shading="gouraud",
+)
+fig.colorbar(im, ax=ax, format="%.1f")
+
+ax.plot(
+    BZBoundary[:, 0], BZBoundary[:, 1], zorder=1,
+    lw=3, ls="dashed", color="tab:blue", alpha=1.0,
+)
+ax.text(
+    0.0, 1.0, sub_fig_tag,
+    fontsize="xx-large", ha="left", va="top", transform=ax.transAxes
+)
+ax.text(
+    0.5, 0.96, params,
+    fontsize="xx-large", ha="center", va="top", transform=ax.transAxes
+)
+
+ticks = np.array([-1, 0, 1], dtype=np.int64)
+ax.set_xticks(ticks * np.pi)
+ax.set_yticks(ticks * np.pi)
[…]

### 2019-12-22 FiguresForPaper/ShowStructureFactor.py
Redesign `ShowStructureFactor.py`.

@@ -1,69 +1,76 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
-from HamiltonianPy import  TRIANGLE_CELL_KS
 
+NUMX = 4
+NUMY = 6
+DATA_PATH = "data/"
+DATA_NAME_TEMP = "SF_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.npz"
 
-numx = 4
-numy = 6
-alpha = 0.05
-beta = 0.02
-J = np.sin(alpha * np.pi) * np.sin(beta * np.pi)
-K = np.sin(alpha * np.pi) * np.cos(beta * np.pi)
-G = np.cos(alpha * np.pi)
-sub_fig_tag = "(f)"
-params = r"$\alpha={0:.2f}\pi, \beta={1:.2f}\pi$".format(alpha, beta)
-# params = r"$J={0:.0f},K={1:.0f},\Gamma={2:.0f}$".format(J, K, G)
-
-step = 0.005
-kx_ratios = np.arange(-0.7, 0.7 + step, step)
-ky_ratios = np.arange(-0.7 + step, 0.7, step)
-kpoints = np.matmul(
-    np.stack(np.meshgrid(kx_ratios, ky_ratios, indexing="ij"), axis=-1),
-    4 * np.pi * np.identity(2) / np.sqrt(3)
+fig, axes = plt.subplots(
+    nrows=2, ncols=3, sharex="all", sharey="all", num="StructureFactors",
 )
-BZBoundary = TRIANGLE_CELL_KS[[*range(6), 0]]
+sub_fig_tags = ["(a)", "(b)", "(c)", "(d)", "(e)", "(f)"]
+params = [
+    (0.00, 0.00), (1.00, 0.00), (0.50, 0.00),
+    (0.30, 0.25), (0.75, 0.25), (0.05, 0.02),
+]
+for index, (tag, (alpha, beta)) in enumerate(zip(sub_fig_tags, params)):
+    data_file_name = DATA_PATH + DATA_NAME_TEMP.format(NUMX, NUMY, alpha, beta)
+    with np.load(data_file_name) as ld:
+        kpoints = ld["kpoints"]
+        factors = ld["factors"]
+        BZBoundary = ld["BZBoundary"]
 
-sf_file_name = "SF_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}".format(
-    numx, numy, alpha, beta
-)
[…]

### 2019-12-22 utilities.py
Add numba accelerated version of `np.kron` for 1D complex array.

@@ -8,6 +8,7 @@ __all__ = [
     "derivation",
     "ShowVectorField2D",
     "ShowVectorField3D",
+    "mykron0", "mykron1",
 ]
 
 
@@ -15,6 +16,7 @@ from mpl_toolkits.mplot3d import Axes3D
 import matplotlib.pyplot as plt
 import numpy as np
 
+from numba import complex128, jit, void
 from HamiltonianPy import lattice_generator
 
 
@@ -330,6 +332,33 @@ def ShowVectorField3D(ax, points, vectors, title="", markersize=10, **kwargs):
     )
     ax.set_title(title, fontsize="xx-large")
     return ax
+
+
+@jit(
+    void(complex128[:], complex128[:], complex128[:]),
+    nopython=True, cache=True
+)
+def mykron0(a, b, out):
+    num_a = a.shape[0]
+    num_b = b.shape[0]
+    for i in range(num_a):
+        ai = a[i]
+        index = i * num_b
+        for j in range(num_b):
+            out[index + j] = ai * b[j]
+
+
+@jit(complex128[:](complex128[:], complex128[:]), nopython=True, cache=True)
+def mykron1(a, b):
+    num_a = a.shape[0]
+    num_b = b.shape[0]
+    out = np.zeros(num_a * num_b, dtype=np.complex128)
+    for i in range(num_a):
+        ai = a[i]
+        index = i * num_b
+        for j in range(num_b):
+            out[index + j] = ai * b[j]
+    return out
 
 
 if __name__ == "__main__":

### 2019-12-24 FiguresForPaper/ShowStructureFactor.py
Change the used model parameters.

@@ -13,7 +13,7 @@ fig, axes = plt.subplots(
 sub_fig_tags = ["(a)", "(b)", "(c)", "(d)", "(e)", "(f)"]
 params = [
     (0.00, 0.00), (1.00, 0.00), (0.50, 0.00),
-    (0.30, 0.25), (0.75, 0.25), (0.05, 0.02),
+    (0.30, 0.25), (0.70, 0.66), (0.05, 0.02),
 ]
 for index, (tag, (alpha, beta)) in enumerate(zip(sub_fig_tags, params)):
     data_file_name = DATA_PATH + DATA_NAME_TEMP.format(NUMX, NUMY, alpha, beta)
@@ -59,7 +59,7 @@ for j, (J, K, G) in enumerate(tmp):
         fontsize="large", ha="center", va="top",
         transform=axes[0, j].transAxes
     )
-tmp = [(0.30, 0.25), (0.75, 0.25), (0.05, 0.02)]
+tmp = [(0.30, 0.25), (0.70, 0.66), (0.05, 0.02)]
 for j, (alpha, beta) in enumerate(tmp):
     axes[1, j].text(
         0.5, 0.96, r"$\alpha={0:.2f}\pi,\beta={1:.2f}\pi$".format(alpha, beta),

### 2019-12-24 FiguresForPaper/ModelDefinition.py
Change the "a", "x", "y" tag position; Change the x, y limit; Change the default figure size.

@@ -50,12 +50,12 @@ ax.plot(point5[0], point5[1], ls="", marker="o", ms=MS, color="tab:pink")
 ax.plot(point6[0], point6[1], ls="", marker="o", ms=MS, color="tab:cyan")
 
 ax.text(
-    0.50, 0.0, "x",
+    -0.50, 0.0, "x",
     fontsize="xx-large", ha="center", va="bottom", color="tab:red",
 )
 ax.text(
-    0.75, np.sqrt(3)/4, "y",
-    fontsize="xx-large", ha="right", va="top", color="tab:green",
+    0.25, -np.sqrt(3)/4, "y",
+    fontsize="xx-large", ha="left", va="bottom", color="tab:green",
 )
 ax.text(
     0.25, np.sqrt(3)/4, "z",
@@ -63,18 +63,17 @@ ax.text(
 )
 
 ax.text(
-    0, 1, "(a)",
+    0, 0.98, "(b)",
     fontsize="xx-large", ha="left", va="top", transform=ax.transAxes
 )
 
-ax.set_xlim(-1.05, 1.05)
-ax.set_ylim(-0.95, 0.95)
+ax.set_xlim(-1.1, 1.1)
+ax.set_ylim(-1.0, 1.0)
 ax.set_aspect("equal")
-fig.set_size_inches(8, 7.4)
+fig.set_size_inches(4, 4)
 ax.set_axis_off()
 plt.show()
 # fig.savefig("figures/ModelDefinition.pdf", dpi=200)
 # fig.savefig("figures/ModelDefinition.png", dpi=200)
 # fig.savefig("figures/ModelDefinition.jpg", dpi=200)
-# fig.savefig("figures/ModelDefinition.eps", dpi=200)
 plt.close("all")

### 2019-12-24 FiguresForPaper/ShowSingleOctahedral.py
Add `ShowSingleOctahedral.py`.

@@ -1,0 +1,163 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from matplotlib.patches import Polygon
+from matplotlib.collections import PatchCollection
+
+
+def Rotation2D(theta=0.0, deg=True):
+    """
+    Rotation about the axis perpendicular to the plane by theta angle.
+
+    Parameters
+    ----------
+    theta : float, optional
+        The angle to rotate.
+        Default: 0.0.
+    deg : bool, optional
+        Whether the given theta is in degree or radian.
+        Default: True.
+
+    Returns
+    -------
+    RZ : array with shape (2, 2)
+        The corresponding rotation matrix.
+    """
+
+    if deg:
+        theta = np.pi * theta / 180
+    sin_theta = np.sin(theta)
+    cos_theta = np.cos(theta)
+    return np.array([[cos_theta, -sin_theta], [sin_theta, cos_theta]])
+
+
+SQRT3 = np.sqrt(3)
+# Points on the bottom layer
+POINTS_BOTTOM = np.array(
+    [[-0.5, SQRT3 / 6], [0.5, SQRT3 / 6], [0.0, -SQRT3 / 3]], dtype=np.float64
+)
+
+# Points on the middle layer
+POINTS_MIDDLE = np.array([[0.0, 0.0]], dtype=np.float64)
+
+# Points on the top layer
+POINTS_TOP = np.array(
+    [[0.0, SQRT3 / 3], [-0.5, -SQRT3 / 6], [0.5, -SQRT3 / 6]], dtype=np.float64
+)
+
+# Points' coordinates actually used.
+# Rotate the system about z-axis by theta degree
+theta = 90
+points_bottom = np.dot(Rotation2D(theta), POINTS_BOTTOM.T).T
+points_middle = np.dot(Rotation2D(theta), POINTS_MIDDLE.T).T
+points_top = np.dot(Rotation2D(theta), POINTS_TOP.T).T
+arrows = points_top - points_middle[0]
+
+LW = 2
+MS = 10
+FACECOLOR = "orangered"
+fig, ax = plt.subplots()
+
+# Draw points on the bottom layer
+ax.plot(
+    points_bottom[:, 0], points_bottom[:, 1], zorder=6,
+    ls="", marker="o", ms=MS, color="gray", alpha=1.0,
+)
+# Draw points on the middle layer
+ax.plot(
+    points_middle[:, 0], points_middle[:, 1], zorder=2,
[…]

### 2019-12-24 FiguresForPaper/ShowEdgeSharingOctahedral.py
Add `ShowEdgeSharingOctahedral.py`.

@@ -1,0 +1,199 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from matplotlib.patches import Polygon
+from matplotlib.collections import PatchCollection
+
+
+def Rotation2D(theta=0.0, deg=True):
+    """
+    Rotation about the axis perpendicular to the plane by theta angle.
+
+    Parameters
+    ----------
+    theta : float, optional
+        The angle to rotate.
+        Default: 0.0.
+    deg : bool, optional
+        Whether the given theta is in degree or radian.
+        Default: True.
+
+    Returns
+    -------
+    RZ : array with shape (2, 2)
+        The corresponding rotation matrix.
+    """
+
+    if deg:
+        theta = np.pi * theta / 180
+    sin_theta = np.sin(theta)
+    cos_theta = np.cos(theta)
+    return np.array([[cos_theta, -sin_theta], [sin_theta, cos_theta]])
+
+
+SQRT3 = np.sqrt(3)
+# Points on the bottom layer
+POINTS_BOTTOM = np.array(
+    [
+        [-1.0, 2 * SQRT3 / 3], [0.0, 2 * SQRT3 / 3], [1.0, 2 * SQRT3 / 3],
+        [-1.5, SQRT3 / 6], [-0.5, SQRT3 / 6],
+        [0.5, SQRT3 / 6], [1.5, SQRT3 / 6],
+        [-1.0, -SQRT3 / 3], [0.0, -SQRT3 / 3], [1.0, -SQRT3 / 3],
+        [-0.5, -5 * SQRT3 / 6], [0.5, -5 * SQRT3 / 6],
+    ], dtype=np.float64,
+)
+
+# Points on the middle layer
+POINTS_MIDDLE = np.array(
+    [
+        [-0.5, SQRT3 / 2], [0.5, SQRT3 / 2],
+        [-1.0, 0.0], [0.0, 0.0], [1.0, 0.0],
+        [-0.5, -SQRT3 / 2], [0.5, -SQRT3 / 2],
+    ], dtype=np.float64
+)
+
+# Points on the top layer
+POINTS_TOP = np.array(
+    [
+        [-0.5, 5 * SQRT3 / 6], [0.5, 5 * SQRT3 / 6],
+        [-1.0, SQRT3 / 3], [0.0, SQRT3 / 3], [1.0, SQRT3 / 3],
[…]

### 2019-12-25 FiguresForPaper/ShowStructureFactor.py
Change the method for tagging the model parameters.

@@ -52,19 +52,14 @@ axes[1, 2].set_xlabel(r"$k_x/\pi$", fontsize="large")
 axes[0, 0].set_ylabel(r"$k_y/\pi$", fontsize="large")
 axes[1, 0].set_ylabel(r"$k_y/\pi$", fontsize="large")
 
-tmp = [(0, 0, 1), (0, 0, -1), (0, 1, 0)]
-for j, (J, K, G) in enumerate(tmp):
-    axes[0, j].text(
-        0.5, 0.96, r"$J={0:d},K={1:d},\Gamma={2:d}$".format(J, K, G),
-        fontsize="large", ha="center", va="top",
-        transform=axes[0, j].transAxes
-    )
+titles = [r"$J=K=0,\Gamma=1$", r"$J=K=0,\Gamma=-1$", r"$J=\Gamma=0,K=1$"]
+for j, title in enumerate(titles):
+    axes[0, j].set_title(title, fontsize="large")
 tmp = [(0.30, 0.25), (0.70, 0.66), (0.05, 0.02)]
 for j, (alpha, beta) in enumerate(tmp):
-    axes[1, j].text(
-        0.5, 0.96, r"$\alpha={0:.2f}\pi,\beta={1:.2f}\pi$".format(alpha, beta),
-        fontsize="large", ha="center", va="top",
-        transform=axes[1, j].transAxes
+    axes[1, j].set_title(
+        r"$\alpha={0:.2f}\pi,\beta={1:.2f}\pi$".format(alpha, beta),
+        fontsize="large",
     )
 
 fig.set_size_inches(18, 9)

### 2019-12-25 FiguresForPaper/ShowProbabilities.py
Add `ShowProbabilities.py`.

@@ -1,0 +1,133 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+
+NUMX = 4
+NUMY = 6
+LW = 4
+MS = 10
+INDICATOR_COLOR = "green"
+INDICATOR_ALPHA = 1.0
+COLORMAP = "hot_r"
+DATA_PATH = "data/"
+DATA_NAME_TEMP = "PS_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.npz"
+
+
+fig, axes = plt.subplots(
+    nrows=2, ncols=3,
+    subplot_kw={"polar": True}, num="Probabilities",
+)
+sub_fig_tags = ["(a)", "(b)", "(c)", "(d)", "(e)", "(f)"]
+params = [
+    (0.30, 1.30), (0.70, 1.65), (0.50, 0.75),
+    (0.30, 0.25), (0.70, 0.66), (0.50, 0.00),
+]
+phi_ticks = np.array([0.0, 0.5, 1.0, 1.5])
+theta_ticks = np.array([0.0, 0.25, 0.50])
+
+for index, (tag, (alpha, beta)) in enumerate(zip(sub_fig_tags, params)):
+    data_file_name = DATA_PATH + DATA_NAME_TEMP.format(NUMX, NUMY, alpha, beta)
+    with np.load(data_file_name) as ld:
+        thetas = ld["thetas"][0:51]
+        phis = ld["phis"]
+        probabilities = ld["probabilities"][0:51, :]
+
+    i, j = divmod(index, 3)
+    cs_ij = axes[i, j].pcolormesh(
+        phis, thetas, probabilities, zorder=0,
+        cmap=COLORMAP, shading="gouraud", vmin=0.0,
+    )
+    colorbar = fig.colorbar(cs_ij, ax=axes[i, j], pad=0.06)
+    colorbar_ticks = np.linspace(0.0, np.max(probabilities), 5, endpoint=True)
+    colorbar.set_ticks(colorbar_ticks)
+    colorbar.set_ticklabels(
+        ["{0:.1f}".format(tick * 100) for tick in colorbar_ticks],
+    )
+    colorbar.ax.tick_params(labelsize="medium")
+    colorbar.ax.set_title("P[%]", pad=10, fontsize="medium")
+
+    axes[i, j].set_aspect("equal")
+    axes[i, j].set_ylim(0, 0.5 * np.pi)
[…]

### 2019-12-25 FiguresForPaper/ShowMagneticOrder.py
Change the magnetic orders to draw. Originally, the module draws FM, stripe-x, Neel and Dual Neel, now it draws stripe-x, stripe-y, stripe-z, Neel and Dual Neel.

@@ -14,29 +14,25 @@ def Show2DVectors(ax, xs, ys, vectors, colors):
 
 fig, ax = plt.subplots(num="MagneticOrder")
 
+NUM = 4
 # The clusters on which the spin vectors are plotted
-FMCluster = lattice_generator("triangle", num0=4, num1=4)
-StripeXCluster = lattice_generator("triangle", num0=4, num1=4)
-NeelCluster = lattice_generator("triangle", num0=4, num1=4)
-DualNeelCluster = lattice_generator("triangle", num0=8, num1=4)
+StripeXCluster = lattice_generator("triangle", num0=NUM, num1=NUM)
+StripeYCluster = lattice_generator("triangle", num0=NUM, num1=NUM)
+StripeZCluster = lattice_generator("triangle", num0=NUM, num1=NUM)
+NeelCluster = lattice_generator("triangle", num0=NUM, num1=NUM)
+DualNeelCluster = lattice_generator("triangle", num0=2 * NUM, num1=NUM)
 
 # Draw the clusters
-x_deltas = (0.0, 4.0, 8.0, 12.0)
-clusters = (FMCluster, StripeXCluster, NeelCluster, DualNeelCluster)
+x_deltas = (0.0, 4.0, 8.0, 12.0, 16.0)
+clusters = (
+    StripeXCluster, StripeYCluster, StripeZCluster,
+    NeelCluster, DualNeelCluster
+)
 for x_delta, clusters in zip(x_deltas, clusters):
     intra_bonds, inter_bonds = clusters.bonds(nth=1)
     for bond in intra_bonds:
         (x0, y0), (x1, y1) = bond.endpoints
         ax.plot([x0 + x_delta, x1 + x_delta], [y0, y1], color="black", zorder=0)
-
-# Draw the FM order
-x_delta = x_deltas[0]
-points = FMCluster.points
-spin_colors = ["tab:orange" for point in points]
-spin_vectors = np.array([[0.0, 1.0] for point in points])
-Show2DVectors(
-    ax, points[:, 0] + x_delta, points[:, 1], spin_vectors, spin_colors
-)
 
 # Draw the StripeX order
 StripeXCell = Lattice(
@@ -46,7 +42,7 @@ StripeXCell = Lattice(
 StripeXCellSpinColors = ("tab:orange", "tab:purple")
[…]

### 2019-12-25 paper/paper.tex
20191225 14:26

@@
 \usepackage{graphicx}
+% \usepackage{subfigure}
 \usepackage{bm}
@@
 Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=$1/2$ models with edge sharing octahedra \cite {PhysRevLett.112.077204}.
-Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liqiud (SL) as well as four magnetically ordered phases has been obtained.
+Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained.
 However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.
@@
 
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{Fig1.pdf}
+    \caption{(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedral.
+(b) Three different direction of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue respectively.
+The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation.
+(c) The orientation of the cubic $x$, $y$, $z$ with respect to the octahedral.
+The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.}
+     \label{fig:ModelDefinition}
+\end{figure}
+
 \section{Methods}
@@
 
+\begin{figure*}
+    \centering
+    % \subfigure{\includegraphics[width=0.96\textwidth]{Fig2_a.pdf}}\\
+    % \subfigure{\includegraphics[width=0.96\textwidth]{Fig2_b_f.pdf}}\\
+    \includegraphics[width=0.96\textwidth]{Fig2.pdf}
+    \caption{(Color online) (a) Global phase diagram of the triangular lattice J-K-$\Gamma$ model.
+The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
+There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase.
+(b) Illustration of the FM order.
+All spins along the same direction.
+(c) Illustation of the stripe order of the $x$ type.
+That is the spins along the x-bond direction are parallel and adjacent chains are antiparallel.
+There are also stripe order of the $y$ or $z$ type, which are degenerate with the $x$ type stripe order.
+(d) Illustration of the 120$^\circ$ N\'{e}el order.
+All spins are coplanar and the angles between nearest-neighbor spins are 120$^\circ$.
+(e) Illustration of the Dual N\'{e}el order.
+The magnetic unit cell include 12 lattice sites as marked by the green dashed parallelogram.}
+     \label{fig:PhaseDiagram}
+\end{figure*}
+
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
+    \caption{(Color online) Static structure factors for different model paramters.}
+     \label{fig:StructureFactors}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
+    \caption{(Color online) Map of the probabilities.}
+     \label{fig:StructureFactors}
+\end{figure}
+
 \section{Discussion}

### 2019-12-25 utilities.py
A new design of the `TriangularLattice.__init__`. It now can initialize different clusters; Add a `which` and `identity` properties; Add `ShowNNBonds` method.

@@ -17,7 +17,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 
 from numba import complex128, jit, void
-from HamiltonianPy import lattice_generator
+from HamiltonianPy import Lattice
 
 
 class TriangularLattice:
@@ -38,26 +38,55 @@ class TriangularLattice:
         "J": -1.0, "K": 0.0, "G": 0.0, "GP": 0.0,
     }
 
-    def __init__(self, numx, numy=None):
+    def __init__(self, num1, num2=None, which="xz"):
         """
         Customize the newly created instance.
 
+        On triangular lattice, the nearest-neighbor (NN) bonds along the
+        zero-degree direction is defined as the x-type bond (x-bond); NN bonds
+        along the 120-degree direction is defined as the y-type bond (y-bond);
+        NN bonds along the 60-degree direction is defined as the z-type bond
+        (z-bond). The definition of the x, y, z bond is counterclockwise.
+
         Parameters
         ----------
-        numx : int
+        num1 : int
             The number of lattice site along the 1st translation vector.
-        numy : int or None, optional
+        num2 : int or None, optional
             The number of lattice site along the 2nd translation vector.
-            The default value `None` implies that `numy` takes the same value
-            as `numx`.
+            The default value `None` implies that `num2` takes the same value
+            as `num1`.
+        which : ["xy" | "yz" | "zx" | "yx" | "zy" | "xz"], optional
+            Define the direction of the cluster. This parameter determine the
+            interpretation of the `num1` and `num2` parameters. For example,
+            if `which` is set to "xy", then there are `num1` lattice sites
+            along the x-bond direction and `num2` lattice sites along the
+            y-bond direction.
+            Default: "xz".
         """
 
-        assert isinstance(numx, int) and numx > 0
-        assert (numy is None) or (isinstance(numy, int) and numy > 0)
-        if numy is None:
-            numy = numx
+        assert isinstance(num1, int) and num1 > 0
+        assert (num2 is None) or (isinstance(num2, int) and num2 > 0)
+        assert which in ("xy", "yz", "zx", "yx", "zy", "xz")
+        if num2 is None:
+            num2 = num1
 
-        cluster = lattice_generator("triangle", num0=numx, num1=numy)
[…]

### 2019-12-25 SpinModel.py
Modify `SpinModel.py` according to the changes in `utilities.py`; Change the rules for saving and loading data.

@@ -37,12 +37,12 @@ class JKGModelEDSolver(TriangularLattice):
         # directory relative CWD, the "tmp/" directory is created if necessary.
 
         directory = Path("tmp/")
-        name_template = "TRIANGLE_NUMX={0}_NUMY={1}_H{2}.npz"
+        name_template = "TRIANGLE_" + self.identity.upper() + "_H{0}.npz"
 
         # The slash operator helps create child paths
-        file_HJ = directory / name_template.format(self.numx, self.numy, "J")
-        file_HK = directory / name_template.format(self.numx, self.numy, "K")
-        file_HG = directory / name_template.format(self.numx, self.numy, "G")
+        file_HJ = directory / name_template.format("J")
+        file_HK = directory / name_template.format("K")
+        file_HG = directory / name_template.format("G")
 
         logger = logging.getLogger(__name__).getChild(
             ".".join([self.__class__.__name__, "TermMatrix"])
@@ -84,40 +84,48 @@ class JKGModelEDSolver(TriangularLattice):
         return HJ, HK, HG
 
     def GS(
-            self, gs_path="data/QuantumSpinModel/GS/",
-            v0=None, tol=0.0, **model_params,
+            self, es_path="data/QuantumSpinModel/ES/",
+            k=6, v0=None, tol=0.0, **model_params,
     ):
         """
-        Calculate the ground state energy and vector of the J-K-G model.
+        Find the smallest `kth` eigenvalues and eigenvectors of the J-K-G
+        model Hamiltonian.
 
-        This method saves the ground state data into a single file in
+        This method saves the eigenvalues and eigenvectors into a single file in
         compressed `.npz` format. The `.npz` files will be saved into the given
-        `gs_path` and the names of the `.npz` files have the following pattern:
-            "GS_numx={numx}_numy={numy}_alpha={alpha:.4f}_beta={beta:.4f}.npz"
+        `es_path` and the names of the `.npz` files have the following pattern:
+            "ES_num1={num1}_num2={num2}_which={which}_
+            alpha={alpha:.4f}_beta={beta:.4f}.npz"
         The variables in the "{}"s are replaced with the actual variables.
-        The lattice size `numx` and `numy` are stored with keyword name: `size`;
+        The lattice size `num1` and `num2` are stored with keyword name: `size`;
+        The lattice type `which` is stored with keyword name: `which`;
         The model parameters `alpha` and `beta` are stored with keyword
         name: `parameters`;
-        The ground state energy is stored with keyword name: `gse`;
[…]

### 2019-12-25 ClassicalModel.py
Modify `ClassicalModel.py` according to the changes in `utilities.py`.

@@ -14,7 +14,7 @@ import numpy as np
 import tables as tb
 from scipy.optimize import basinhopping
 
-from utilities import *
+from utilities import TriangularLattice, ShowVectorField3D
 
 
 __all__ = [
@@ -89,11 +89,11 @@ class JKGModelClassicalSolver(TriangularLattice):
             [sin_phis * sin_thetas, sin_phis * cos_thetas, cos_phis],
             dtype=np.float64
         ).T
-        energy_per_site = res.fun / self._site_num
+        energy_per_site = res.fun / self.site_num
 
         Path(data_path).mkdir(exist_ok=True, parents=True)
         h5f_name = "OSC_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.h5".format(
-            self.numx, self.numy, alpha, beta
+            self.num1, self.num2, alpha, beta
         )
         h5f = tb.open_file(data_path + h5f_name, mode="a")
         try:
@@ -101,8 +101,8 @@ class JKGModelClassicalSolver(TriangularLattice):
         except AttributeError:
             current_count = 0
             h5f.set_node_attr("/", "count", current_count)
-            h5f.set_node_attr("/", "numx", self.numx)
-            h5f.set_node_attr("/", "numy", self.numy)
+            h5f.set_node_attr("/", "numx", self.num1)
+            h5f.set_node_attr("/", "numy", self.num2)
             h5f.set_node_attr("/", "alpha", alpha)
             h5f.set_node_attr("/", "beta", beta)
 

### 2019-12-25 run/ClassicalFMEnergyVsSpinDirection.py
Add `ClassicalFMEnergyVsSpinDirection.py`.

@@ -1,0 +1,55 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+
+def FMEnergies(thetas, phis, J=-1.0, K=0.0, G=0.0):
+    sin_thetas = np.sin(thetas)
+    cos_thetas = np.cos(thetas)
+    sin_phis = np.sin(phis)
+    cos_phis = np.cos(phis)
+    num_thetas = thetas.shape[0]
+    num_phis = phis.shape[0]
+    energies = np.zeros((num_thetas, num_phis), dtype=np.float64)
+    for i in range(num_thetas):
+        for j in range(num_phis):
+            sx = sin_thetas[i] * cos_phis[j]
+            sy = sin_thetas[i] * sin_phis[j]
+            sz = cos_thetas[i]
+            energies[i, j] = 3 * J + K + 2 * G * (sx * sy + sx * sz + sy * sz)
+    return energies
+
+
+if __name__ == "__main__":
+    alpha = 0.0
+    beta = 1.3
+    J = np.sin(alpha * np.pi) * np.sin(beta * np.pi)
+    K = np.sin(alpha * np.pi) * np.cos(beta * np.pi)
+    G = np.cos(alpha * np.pi)
+
+    step = 0.005
+    thetas = np.arange(0, 1 + step, step)
+    phis = np.arange(-1, 1 + step, step)
+
+    energies = FMEnergies(thetas * np.pi, phis * np.pi, J, K, G)
+
+    fig, ax = plt.subplots()
+    cs = ax.pcolormesh(phis, thetas, energies, cmap="hot", shading="gouraud")
+    fig.colorbar(cs, ax=ax, shrink=0.85)
+    ax.plot(
+        np.arctan2(-1, -1) / np.pi, np.arctan2(np.sqrt(2), -1) / np.pi,
+        ls="", marker="o", color="tab:blue", alpha=0.75,
+    )
+    ax.plot(
+        np.arctan2(1, 1) / np.pi, np.arctan2(np.sqrt(2), 1) / np.pi,
+        ls="", marker="o", color="tab:blue", alpha=0.75,
+    )
+    tmp = np.arctan2(1, -np.sin(phis * np.pi) - np.cos(phis * np.pi)) / np.pi
+    ax.plot(phis, tmp, color="tab:green", alpha=0.75)
+    ax.set_title(r"$\alpha={0:.3f}\pi, \beta={1:.3f}\pi$".format(alpha, beta))
[…]

### 2019-12-25 run/ClassicalStripeEnergyVsSpinDirection.py
Add `ClassicalStripeEnergyVsSpinDirection.py`.

@@ -1,0 +1,125 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+
+def _StripeXEnergy(sx, sy, sz, J, K, G):
+    return -J - K + 2 * K * sx * sx + 2 * G * (sy * sz - sx * sy - sx * sz)
+
+def _StripeYEnergy(sx, sy, sz, J, K, G):
+    return -J - K + 2 * K * sy * sy + 2 * G * (sx * sz - sx * sy - sy * sz)
+
+def _StripeZEnergy(sx, sy, sz, J, K, G):
+    return -J - K + 2 * K * sz * sz + 2 * G * (sx * sy - sx * sz - sy * sz)
+
+
+def ExtremePoint(K, G, which="x"):
+    tmp = np.sqrt(9 * G * G - 4 * K * G + 4 * K * K)
+    lambda_b = -(G + 2 * K - tmp) / 4
+    lambda_c = -(G + 2 * K + tmp) / 4
+
+    x_a = 0.0
+    y_a = -1.0 / np.sqrt(2)
+    z_a = 1.0 / np.sqrt(2)
+
+    y_b = z_b = np.sqrt(G * G / (4 * lambda_b * (lambda_b + G) + 3 * G * G))
+    x_b = y_b * (2 * lambda_b + G) / G
+
+    y_c = z_c = np.sqrt(G * G / (4 * lambda_c * (lambda_c + G) + 3 * G * G))
+    x_c = y_c * (2 * lambda_c + G) / G
+
+    if which == "x":
+        x0, y0, z0 = x_a, y_a, z_a
+        x1, y1, z1 = x_b, y_b, z_b
+        x2, y2, z2 = x_c, y_c, z_c
+    elif which == "y":
+        x0, y0, z0 = z_a, x_a, y_a
+        x1, y1, z1 = z_b, x_b, y_b
+        x2, y2, z2 = z_c, x_c, y_c
+    elif which == "z":
+        x0, y0, z0 = y_a, z_a, x_a
+        x1, y1, z1 = y_b, z_b, x_b
+        x2, y2, z2 = y_c, z_c, x_c
+    else:
+        raise ValueError("Invalid `which` parameter: {0}".format(which))
+
+    phi0 = np.arctan2(y0, x0)
+    phi1 = np.arctan2(y1, x1)
+    phi2 = np.arctan2(y2, x2)
[…]

### 2019-12-25 run/ExtractGE.py
Add `ExtractGE.py`.

@@ -1,0 +1,29 @@
+from pathlib import Path
+from time import time
+import numpy as np
+
+
+# gs_data_path = "data/QuantumSpinModel/GS/"
+gs_data_path = "D:/JKGModel/data/QuantumSpinModel/GS/"
+# gs_data_path = "E:/JKGModel/data/QuantumSpinModel/GS/"
+
+ge_data_path = "data/QuantumSpinModel/GE/"
+ge_name_temp = "GE_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.npz"
+Path(ge_data_path).mkdir(parents=True, exist_ok=True)
+
+count = 0
+t0 = time()
+for gs_name in Path(gs_data_path).iterdir():
+    with np.load(gs_name) as ld:
+        numx, numy = ld["size"]
+        alpha, beta = ld["parameters"]
+        gse = ld["gse"]
+    ge_full_name = ge_data_path + ge_name_temp.format(numx, numy, alpha, beta)
+    np.savez(
+        ge_full_name, size=[numx, numy], parameters=[alpha, beta], gse=gse
+    )
+    count += 1
+    print(ge_full_name)
+t1 = time()
+print("The total number: {0}".format(count))
+print("The time spend on extract ge info: {0:.4f}s".format(t1 - t0))

### 2019-12-25 run/FourierTransformationOfSpinConfig.py
Add `FourierTransformationOfSpinConfig.py`.

@@ -1,0 +1,84 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import tables as tb
+
+from time import time
+
+from HamiltonianPy import lattice_generator, TRIANGLE_CELL_KS
+from DualTransformation import *
+from utilities import ShowVectorField3D
+
+
+def DFT(kpoints, points, vectors):
+    numkx, numky, space_dim = kpoints.shape
+    dft = np.zeros((numkx, numky, 3), dtype=np.complex128)
+    for i in range(numkx):
+        for j in range(numky):
+            tmp = np.exp(1j * np.dot(points, kpoints[i, j])).reshape((-1, 1))
+            dft[i, j] = np.sum(vectors * tmp, axis=0)
+    return dft
+
+
+numx = numy = 12
+cell = lattice_generator("triangle", num0=1, num1=1)
+cluster = lattice_generator("triangle", num0=numx, num1=numy)
+ratio_x = np.arange(-2 * numx, 2 * numx) / numx
+ratio_y = np.arange(-2 * numy, 2 * numy) / numy
+kpoints = np.matmul(
+    np.stack(np.meshgrid(ratio_x, ratio_y, indexing="ij"), axis=-1), cell.bs,
+)
+BZBoundary = TRIANGLE_CELL_KS[[*range(6), 0]]
+
+# vectors = GenerateFMOrder(cluster.points)
+# vectors = T4(cluster.points, GenerateFMOrder(cluster.points))
+# vectors = T1T4(cluster.points, GenerateFMOrder(cluster.points))
+# vectors = GenerateNeelOrder(cluster.points)
+# vectors = T4(cluster.points, GenerateNeelOrder(cluster.points))
+# vectors = T1T4(cluster.points, GenerateNeelOrder(cluster.points))
+
+alpha = 0.5
+beta = 1.5
+index = 10
+data_path = "data/ClassicalSpinModel/OptimizedSpinConfig/"
+h5f_name_temp = "OSC_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.h5"
+h5f_full_name = data_path + h5f_name_temp.format(numx, numy, alpha, beta)
+h5f = tb.open_file(h5f_full_name, mode="r")
+vectors = h5f.get_node("/", "Run{0:0>4d}".format(index)).read()
+h5f.close()
+
+fig_spin_config = plt.figure("SpinConfiguration")
[…]

### 2019-12-25 run/PlotGSEs.py
Add `PlotGSEs.py`.

@@ -1,0 +1,166 @@
+"""
+Plot the ground state energy versus model parameter.
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+from scipy.signal import find_peaks
+
+from utilities import derivation
+
+
+GE_FILE_NAME_TEMP = "GE_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.npz"
+GS_FILE_NAME_TEMP = "GS_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.npz"
+
+
+def ShowGEs(
+        params, gses, fix_which, fixed_param, *,
+        line_width=4, show_marker=False, marker_size=6
+):
+    if fix_which == "alpha":
+        title = r"$\alpha={0:.4f}\pi$".format(fixed_param)
+        xlabel = r"$\beta/\pi$"
+        d2gses_ylabel = r"$-\frac{d^2E}{d\beta^2}$"
+    elif fix_which == "beta":
+        title = r"$\beta={0:.4f}\pi$".format(fixed_param)
+        xlabel = r"$\alpha/\pi$"
+        d2gses_ylabel = r"$-\frac{d^2E}{d\alpha^2}$"
+    else:
+        raise ValueError("Invalid `fix_which` parameter!")
+
+    d2params, d2gses = derivation(params, gses, nth=2)
+    peaks, properties = find_peaks(-d2gses)
+    print("The peak positions of second derivatives:")
+    print(", ".join("{0:.4f}".format(param) for param in d2params[peaks]))
+
+    fig, ax_gses = plt.subplots()
+    ax_d2gses = ax_gses.twinx()
+    color_gses = "tab:blue"
+    color_d2gses = "tab:red"
+    if show_marker:
+        marker_props = {"marker": "o", "markersize": marker_size}
+    else:
+        marker_props = {}
+
+    ax_gses.plot(
+        params, gses, lw=line_width, color=color_gses, **marker_props
+    )
+    ax_d2gses.plot(
+        d2params, -d2gses, lw=line_width, color=color_d2gses, **marker_props
+    )
+    ax_gses.set_xlim(params[0], params[-1])
+    ax_gses.set_title(title, fontsize="xx-large")
+    ax_gses.set_xlabel(xlabel, fontsize="large")
+    ax_gses.set_ylabel("$E$", rotation=0, fontsize="large", color=color_gses)
+    ax_d2gses.set_ylabel(
[…]

### 2019-12-25 run/RunClassicalModel.py
Add `RunClassicalModel.py`.

@@ -1,0 +1,21 @@
+import logging
+import sys
+from time import time
+
+from ClassicalModel import JKGModelClassicalSolver
+
+logging.basicConfig(
+    stream=sys.stdout, level=logging.INFO,
+    format="%(asctime)s - %(message)s",
+)
+logging.info("Program start running")
+
+max_run = 10
+numx = numy = 6
+solver = JKGModelClassicalSolver(numx, numy)
+for i in range(1, max_run+1):
+    t0 = time()
+    solver.MinimizeGeneralSpinConfig(alpha=0.5, beta=0.5)
+    t1 = time()
+    logging.info("%d/%d, dt=%.4fs", i, max_run, t1 - t0)
+logging.info("Program stop running")

### 2019-12-25 run/RunQuantumSpinStructureFactor.py
Add `RunQuantumSpinStructureFactor.py`.

@@ -1,0 +1,87 @@
+import logging
+import sys
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+from HamiltonianPy import lattice_generator, TRIANGLE_CELL_KS
+
+from StructureFactor import QuantumSpinStructureFactor
+
+
+logging.basicConfig(
+    level=logging.INFO, stream=sys.stdout,
+    format="%(asctime)s - %(levelname)s - %(name)s - %(message)s"
+)
+logging.info("Program start running")
+LOG_MSG = "SFs for alpha=%.4f, beta=%.4f: dt=%.4fs"
+
+# GS_DATA_PATH = "data/QuantumSpinModel/GS/"
+GS_DATA_PATH = "E:/JKGModel/data/QuantumSpinModel/GS/"
+# GS_DATA_PATH = "C:/Users/swang/Desktop/Eigenstates/"
+GS_DATA_NAME_TEMP = "GS_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.npz"
+SF_DATA_NAME_TEMP = "SF_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.npz"
+################################################################################
+
+# Prepare k-points and boundary of first Brillouin Zone
+numx = 4
+numy = 6
+cluster = lattice_generator("triangle", num0=numx, num1=numy)
+bs = 4 * np.pi * np.identity(2) / np.sqrt(3)
+step = 0.01
+kx_ratios = np.arange(-0.7, 0.7 + step, step)
+ky_ratios = np.arange(-0.7 + step, 0.7, step)
+kpoints = np.matmul(
+    np.stack(np.meshgrid(kx_ratios, ky_ratios, indexing="ij"), axis=-1), bs
+)
+BZBoundary = TRIANGLE_CELL_KS[[*range(6), 0]]
+
+# Load ground state data
+alpha = 0.70
+beta = 0.66
+gs_data_name = GS_DATA_NAME_TEMP.format(numx, numy, alpha, beta)
+with np.load(GS_DATA_PATH + gs_data_name) as ld:
+    ket = ld["ket"][:, 0]
+
+# Calculate and save static structure factors
+t0 = time()
+factors = QuantumSpinStructureFactor(kpoints, cluster.points, ket)
+assert np.all(np.abs(factors.imag) < 1E-12)
[…]

### 2019-12-25 run/RunSpinModel.py
Add `RunSpinModel.py`.

@@ -1,0 +1,61 @@
+import logging
+import sys
+import matplotlib.pyplot as plt
+import numpy as np
+
+from SpinModel import *
+from utilities import derivation
+
+
+logging.basicConfig(
+    level=logging.INFO,
+    stream=sys.stdout,
+    format="%(asctime)s - %(levelname)s - %(name)s - %(message)s",
+)
+logging.info("Program start running")
+
+num1 = 3
+num2 = 4
+which = "xz"
+alpha = 0.5
+betas = np.arange(0, 2, 0.01)
+
+solver = JKGModelEDSolver(num1, num2, which=which)
+for beta in betas:
+    solver.GS(alpha=alpha, beta=beta)
+
+gses = []
+es_path = "data/QuantumSpinModel/ES/"
+es_name_temp = "ES_" + solver.identity + "_alpha={0:.4f}_beta={1:.4f}.npz"
+for beta in betas:
+    es_full_name = es_path + es_name_temp.format(alpha, beta)
+    with np.load(es_full_name) as ld:
+        gses.append(np.sort(ld["values"])[0])
+gses = np.array(gses, dtype=np.float64)
+d2betas, d2gses = derivation(betas, gses, nth=2)
+
+fig, ax_gses = plt.subplots(num=solver.identity)
+ax_d2gses = ax_gses.twinx()
+color_gses = "tab:blue"
+color_d2gses = "tab:orange"
+ax_gses.plot(betas, gses, color=color_gses)
+ax_d2gses.plot(d2betas, -d2gses / (np.pi ** 2), color=color_d2gses)
+
+ax_gses.set_xlim(betas[0], betas[-1])
+ax_gses.set_title(r"$\alpha={0:.4f}\pi$".format(alpha), fontsize="xx-large")
+ax_gses.set_xlabel(r"$\beta/\pi$", fontsize="xx-large")
+ax_gses.set_ylabel("E", rotation=0, fontsize="xx-large", color=color_gses)
+ax_gses.tick_params("y", colors=color_gses)
+ax_gses.grid(ls="dashed", axis="x", color="gray")
+ax_gses.grid(ls="dashed", axis="y", color=color_gses)
+
+ax_d2gses.set_ylabel(
+    r"$E^{''}$", rotation=0, fontsize="xx-large", color=color_d2gses
+)
+ax_d2gses.tick_params("y", colors=color_d2gses)
+ax_d2gses.grid(ls="dashed", axis="y", color=color_d2gses)
[…]

### 2019-12-25 run/ShowOptimizedSpinConfig.py
Add `ShowOptimizedSpinConfig.py`.

@@ -1,0 +1,40 @@
+from mpl_toolkits.mplot3d import Axes3D
+import matplotlib.pyplot as plt
+import tables as tb
+
+from HamiltonianPy import lattice_generator
+from utilities import ShowVectorField3D
+
+
+data_path = "data/ClassicalSpinModel/OptimizedSpinConfig/"
+h5f_name_temp = "OSC_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.h5"
+
+alpha = 0.5
+beta = 1.85
+numx = numy = 12
+cluster = lattice_generator("triangle", num0=numx, num1=numy)
+
+h5f_name = h5f_name_temp.format(numx, numy, alpha, beta)
+h5f = tb.open_file(data_path + h5f_name, mode="r")
+for carray in h5f.iter_nodes("/"):
+    energy = h5f.get_node_attr(carray, "energy")
+    spin_vectors = carray.read()
+    print(spin_vectors)
+
+    fig = plt.figure()
+    ax = fig.add_subplot(111, projection="3d")
+    title = "{0}\n".format(carray.name)
+    title += r"$\alpha={0:.4f}\pi,\beta={1:.4f}\pi,E_{{min}}={2:.8f}$".format(
+        alpha, beta, energy
+    )
+    ShowVectorField3D(
+        ax, cluster.points, spin_vectors, title=title
+    )
+    ax.set_zlim(-0.5, 0.5)
+    ax.set_xlabel("X")
+    ax.set_ylabel("Y")
+    ax.set_zlabel("Z")
+    plt.get_current_fig_manager().window.showMaximized()
+    plt.show()
+    plt.close("all")
+h5f.close()

### 2019-12-25 run/StructureFactorForDualOrders.py
Add `StructureFactorForDualOrders.py`.

@@ -1,0 +1,85 @@
+import logging
+import sys
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+from HamiltonianPy import lattice_generator, TRIANGLE_CELL_KS
+from HamiltonianPy.rotation3d import RotationGeneral
+
+from StructureFactor import ClassicalSpinStructureFactor
+from DualTransformation import *
+
+logging.basicConfig(
+    level=logging.INFO, stream=sys.stdout,
+    format="%(asctime)s - %(levelname)s - %(name)s - %(message)s"
+)
+logging.info("Program start running")
+
+
+bs = 4 * np.pi * np.identity(2) / np.sqrt(3)
+step = 0.01
+kx_ratios = np.arange(-0.7, 0.7 + step, step)
+ky_ratios = np.arange(-0.7 + step, 0.7, step)
+kpoints = np.matmul(
+    np.stack(np.meshgrid(kx_ratios, ky_ratios, indexing="ij"), axis=-1), bs
+)
+BZBoundary = TRIANGLE_CELL_KS[[*range(6), 0]]
+
+num = 16
+cluster = lattice_generator("triangle", num0=num, num1=num)
+points = cluster.points
+vx, vy, vz = 2 * np.random.random(3) - 1
+FMCellVectors = np.array([vx, vy, vz], dtype=np.float64)
+NeelCellVectors = np.array(
+    [
+        np.array([vx, vy, vz]),
+        np.dot(RotationGeneral((0, -vz, vy), 120, deg=True), [vx, vy, vz]),
+        np.dot(RotationGeneral((0, -vz, vy), 240, deg=True), [vx, vy, vz]),
+    ], dtype=np.float64
+)
+
+FMSpinConfig = GenerateFMOrder(points, FMCellVectors)
+T1FMSpinConfig = T1(points, FMSpinConfig)
+T4FMSpinConfig = T4(points, FMSpinConfig)
+T1T4FMSpinConfig = T1T4(points, FMSpinConfig)
+# ShowFMT1T4(points, FMCellVectors)
+
+NeelSpinConfig = GenerateNeelOrder(points, NeelCellVectors)
+T1NeelSpinConfig = T1(points, NeelSpinConfig)
+T4NeelSpinConfig = T4(points, NeelSpinConfig)
+T1T4NeelSpinConfig = T1T4(points, NeelSpinConfig)
[…]

### 2019-12-25 run/StructureFactorForFourSublatticeOrder.py
Add `StructureFactorForFourSublatticeOrder.py`.

@@ -1,0 +1,71 @@
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+from HamiltonianPy import lattice_generator, TRIANGLE_CELL_KS
+
+from StructureFactor import ClassicalSpinStructureFactor
+from utilities import ShowVectorField3D
+
+
+bs = 4 * np.pi * np.identity(2) / np.sqrt(3)
+step = 0.01
+kx_ratios = np.arange(-0.7, 0.7 + step, step)
+ky_ratios = np.arange(-0.7 + step, 0.7, step)
+kpoints = np.matmul(
+    np.stack(np.meshgrid(kx_ratios, ky_ratios, indexing="ij"), axis=-1), bs
+)
+BZBoundary = TRIANGLE_CELL_KS[[*range(6), 0]]
+
+numx_cell = numy_cell = 2
+numx_cluster = numy_cluster = 16
+cell = lattice_generator("triangle", num0=numx_cell, num1=numy_cell)
+cluster = lattice_generator("triangle", num0=numx_cluster, num1=numy_cluster)
+
+thetas = np.pi * np.random.random(numx_cell * numy_cell)
+phis = 2 * np.pi * np.random.random(numx_cell * numy_cell)
+vxs = np.sin(thetas) * np.cos(phis)
+vys = np.sin(thetas) * np.sin(phis)
+vzs = np.cos(thetas)
+spin_vectors = []
+for point in cluster.points:
+    index = cell.getIndex(site=point, fold=True)
+    spin_vectors.append([vxs[index], vys[index], vzs[index]])
+spin_vectors = np.array(spin_vectors, dtype=np.float64)
+
+t0 = time()
+factors = ClassicalSpinStructureFactor(kpoints, cluster.points, spin_vectors)
+assert np.all(np.abs(factors.imag) < 1E-12)
+t1 = time()
+print("The time spend on SF: {0:.4f}s".format(t1 - t0))
+
+fig0 = plt.figure("original")
+ax0 = fig0.add_subplot(111, projection="3d")
+ShowVectorField3D(ax0, cluster.points, spin_vectors)
+ax0.set_xlabel("X", fontsize="xx-large")
+ax0.set_ylabel("Y", fontsize="xx-large")
+ax0.set_zlabel("Z", fontsize="xx-large")
+ax0.set_zlim(-0.5, 0.5)
+
[…]

### 2019-12-25 run/StructureFactorForOptimizedSpinConfig.py
Add `StructureFactorForOptimizedSpinConfig.py`.

@@ -1,0 +1,72 @@
+import logging
+import sys
+
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+import tables as tb
+from HamiltonianPy import lattice_generator, TRIANGLE_CELL_KS
+
+from StructureFactor import ClassicalSpinStructureFactor
+
+
+logging.basicConfig(
+    level=logging.INFO, stream=sys.stdout,
+    format="%(asctime)s - %(levelname)s - %(name)s - %(message)s"
+)
+logging.info("Program start running")
+
+
+bs = 4 * np.pi * np.identity(2) / np.sqrt(3)
+step = 0.01
+kx_ratios = np.arange(-0.7, 0.7 + step, step)
+ky_ratios = np.arange(-0.7 + step, 0.7, step)
+kpoints = np.matmul(
+    np.stack(np.meshgrid(kx_ratios, ky_ratios, indexing="ij"), axis=-1), bs
+)
+BZBoundary = TRIANGLE_CELL_KS[[*range(6), 0]]
+
+data_path = "data/ClassicalSpinModel/OptimizedSpinConfig/"
+data_name_temp = "OSC_numx={0}_numy={1}_alpha={2:.4f}_beta={3:.4f}.h5"
+
+alpha = 0.05
+beta = 0.05
+numx = 12
+numy = 12
+cluster = lattice_generator("triangle", num0=numx, num1=numy)
+data_full_name = data_path + data_name_temp.format(numx, numy, alpha, beta)
+h5_file = tb.open_file(data_full_name, mode="r")
+for carray in h5_file.iter_nodes("/"):
+    vectors = carray.read()
+    t0 = time()
+    factors = ClassicalSpinStructureFactor(kpoints, cluster.points, vectors)
+    assert np.all(np.abs(factors.imag) < 1E-12)
+    t1 = time()
+    logging.info("The time spend: %.4fs", t1 - t0)
+
+    # Plot the static structure factors
+    fig, ax = plt.subplots()
+    im = ax.pcolormesh(
+        kpoints[:, :, 0], kpoints[:, :, 1], factors.real, zorder=0,
+        cmap="Reds", shading="gouraud",
+    )
+    fig.colorbar(im, ax=ax)
+    ax.plot(
+        BZBoundary[:, 0], BZBoundary[:, 1], zorder=1,
+        lw=3, ls="dashed", color="tab:blue", alpha=1.0,
+    )
[…]

### 2019-12-25 run/StructureFactorForStripeOrder.py
Add `StructureFactorForStripeOrder.py`.

@@ -1,0 +1,92 @@
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+from HamiltonianPy import lattice_generator, Lattice
+from HamiltonianPy import TRIANGLE_CELL_KS
+
+from StructureFactor import ClassicalSpinStructureFactor
+from utilities import ShowVectorField3D
+
+
+bs = 4 * np.pi * np.identity(2) / np.sqrt(3)
+step = 0.01
+kx_ratios = np.arange(-0.7, 0.7 + step, step)
+ky_ratios = np.arange(-0.7 + step, 0.7, step)
+kpoints = np.matmul(
+    np.stack(np.meshgrid(kx_ratios, ky_ratios, indexing="ij"), axis=-1), bs
+)
+BZBoundary = TRIANGLE_CELL_KS[[*range(6), 0]]
+
+numx = numy = 8
+cluster = lattice_generator("triangle", num0=numx, num1=numy)
+
+which = "z"
+if which == "x":
+    # FM along x-bond
+    cell_points = np.array([[0, 0], [0.5, np.sqrt(3)/2]], dtype=np.float64)
+    cell_vectors = np.array([[1, 0], [1, np.sqrt(3)]], dtype=np.float64)
+elif which == "y":
+    # FM along y-bond
+    cell_points = np.array([[0, 0], [1, 0]], dtype=np.float64)
+    cell_vectors = np.array([[2, 0], [-0.5, np.sqrt(3)/2]], dtype=np.float64)
+elif which == "z":
+    # FM along z-bond
+    cell_points = np.array([[0, 0], [1, 0]], dtype=np.float64)
+    cell_vectors = np.array([[2, 0], [0.5, np.sqrt(3)/2]], dtype=np.float64)
+else:
+    raise ValueError("Invalid `which` variable!")
+cell = Lattice(points=cell_points, vectors=cell_vectors)
+
+theta = np.pi * np.random.random()
+phi = 2 * np.pi * np.random.random()
+vx = np.sin(theta) * np.cos(phi)
+vy = np.sin(theta) * np.sin(phi)
+vz = np.cos(theta)
+spin_vectors = []
+for point in cluster.points:
+    index = cell.getIndex(site=point, fold=True)
+    if index == 0:
+        spin_vectors.append([vx, vy, vz])
+    elif index == 1:
[…]

### 2019-12-25 run/TestFMDirection.py
Add `TestFMDirection.py`.

@@ -1,0 +1,113 @@
+import logging
+import sys
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+from utilities import mykron0
+
+
+def ProbabilitiesOnFM24(thetas, phis, ket):
+    num_thetas = thetas.shape[0]
+    num_phis = phis.shape[0]
+    sin_half_thetas = np.sin(thetas / 2)
+    cos_half_thetas = np.cos(thetas / 2)
+    exp_1j_half_phis = np.exp(1j * phis / 2)
+    exp_1j_half_phis_conj = exp_1j_half_phis.conjugate()
+    probabilities = np.zeros((num_thetas, num_phis), dtype=np.float64)
+
+    spinor2 = np.zeros(2 ** 2, dtype=np.complex128)
+    spinor4 = np.zeros(2 ** 4, dtype=np.complex128)
+    spinor8 = np.zeros(2 ** 8, dtype=np.complex128)
+    spinor16 = np.zeros(2 ** 16, dtype=np.complex128)
+    spinor24 = np.zeros(2 ** 24, dtype=np.complex128)
+    for i in range(num_thetas):
+        t0 = time()
+        for j in range(num_phis):
+            spinor1 = np.array(
+                [
+                    cos_half_thetas[i] * exp_1j_half_phis_conj[j],
+                    sin_half_thetas[i] * exp_1j_half_phis[j],
+                ], dtype=np.complex128,
+            )
+
+            mykron0(spinor1, spinor1, spinor2)
+            mykron0(spinor2, spinor2, spinor4)
+            mykron0(spinor4, spinor4, spinor8)
+            mykron0(spinor8, spinor8, spinor16)
+            mykron0(spinor8, spinor16, spinor24)
+
+            inner = np.vdot(spinor24, ket)
+            probabilities[i, j] = (inner * inner.conjugate()).real
+        t1 = time()
+        logging.info("%03dth theta, dt=%.4fs", i, t1 - t0)
+    return probabilities
+
+
+if __name__ == "__main__":
+    logging.basicConfig(
+        stream=sys.stdout, level=logging.INFO,
+        format="%(asctime)s - %(message)s",
+    )
+    logging.info("Program start running")
+
+    # GS_DATA_PATH = "data/QuantumSpinModel/GS/"
[…]

### 2019-12-25 run/TestStripeDirection.py
Add `TestStripeDirection.py`.

@@ -1,0 +1,201 @@
+import logging
+import sys
+from time import time
+
+import matplotlib.pyplot as plt
+import numpy as np
+from utilities import mykron0
+
+
+def ProbabilitiesOnStripe24(thetas, phis, ket, which="x"):
+    num_thetas = thetas.shape[0]
+    num_phis = phis.shape[0]
+    sin_half_thetas_up = np.sin(thetas / 2)
+    cos_half_thetas_up = np.cos(thetas / 2)
+    exp_1j_half_phis_up = np.exp(1j * phis / 2)
+    exp_1j_half_phis_conj_up = exp_1j_half_phis_up.conjugate()
+
+    sin_half_thetas_down = np.sin((np.pi - thetas) / 2)
+    cos_half_thetas_down = np.cos((np.pi - thetas) / 2)
+    exp_1j_half_phis_down = np.exp(1j * (phis + np.pi) / 2)
+    exp_1j_half_phis_conj_down = exp_1j_half_phis_down.conjugate()
+
+    probabilities = np.zeros((num_thetas, num_phis), dtype=np.float64)
+    if which == "x":
+        spinor2 = np.zeros(2 ** 2, dtype=np.complex128)
+        spinor4 = np.zeros(2 ** 4, dtype=np.complex128)
+        spinor8 = np.zeros(2 ** 8, dtype=np.complex128)
+        spinor16 = np.zeros(2 ** 16, dtype=np.complex128)
+        spinor24 = np.zeros(2 ** 24, dtype=np.complex128)
+        for i in range(num_thetas):
+            t0 = time()
+            for j in range(num_phis):
+                spinor1_up = np.array(
+                    [
+                        cos_half_thetas_up[i] * exp_1j_half_phis_conj_up[j],
+                        sin_half_thetas_up[i] * exp_1j_half_phis_up[j],
+                    ], dtype=np.complex128,
+                )
+                spinor1_down = np.array(
+                    [
+                        cos_half_thetas_down[i] * exp_1j_half_phis_conj_down[j],
+                        sin_half_thetas_down[i] * exp_1j_half_phis_down[j],
+                    ], dtype=np.complex128,
+                )
+                mykron0(spinor1_down, spinor1_up, spinor2)
+                mykron0(spinor2, spinor2, spinor4)
+                mykron0(spinor4, spinor4, spinor8)
+                mykron0(spinor8, spinor8, spinor16)
+                mykron0(spinor16, spinor8, spinor24)
+
[…]

### 2019-12-25 PlotGE.py
Delete `PlotGE.py`.

@@ -1,205 +1,0 @@
-"""
-Plot the ground state energy versus model parameter
-"""
-
-
-from pathlib import Path
-
-import matplotlib.pyplot as plt
-import numpy as np
-
-from ProjectDataBase.PhaseData import Phase_Transition_Points_Fixed_Alpha
-from ProjectDataBase.PhaseData import Phase_Transition_Points_Fixed_Beta
-
-
-# Useful data for plotting GEs versus alphas or betas
-fontsize = 15
-linewidth = 5
-spinewidth = 3
-title_pad = 15
-tick_params = {
-    "labelsize": 12,
-    "which": "both",
-    "length": 6,
-    "width": spinewidth,
-    "direction": "in",
-}
-color_map = plt.get_cmap("tab10")
-colors = color_map(range(color_map.N))
-
-xlabel_template = r"$\{var}(/\pi)$"
-second_derivative = r"$-\frac{{d^2E}}{{d\{var}^2}}$"
-title_template = r"E and -$\frac{{d^2E}}{{d\{var}^2}}$ vs $\{var}$ " \
-                 r"at $\{fixed_which}={fixed_param:.3f}\pi$"
-
-
-def derivation(xs, ys, nth=1):
-    """
-    Calculate the nth derivatives of `ys` versus `xs` discretely
-
-    The derivatives are calculated using the following formula:
-        dy/dx = (ys[i+1] - ys[i]) / (xs[i+1] - xs[i])
-
-    Parameters
-    ----------
-    xs : 1-D array
-        The independent variables
-        `xs` is assumed to be sorted in ascending order and there are no
-        identical values in `xs`.
-    ys : 1-D array
-        The dependent variables
-        `ys` should be of the same length as `xs`.
-    nth : int, optional
-        The nth derivatives
-        default: 1
-
-    Returns
-    -------
-    xs : 1-D array
-        The independent variables
-    ys : 1-D array
-        The nth derivatives corresponding to the returned `xs`
-    """
-
-    assert isinstance(nth, int) and nth >= 0
-    assert isinstance(xs, np.ndarray) and xs.ndim == 1
-    assert isinstance(ys, np.ndarray) and ys.shape == xs.shape
-
-    for i in range(nth):
-        ys = (ys[1:] - ys[:-1]) / (xs[1:] - xs[:-1])
-        xs = (xs[1:] + xs[:-1]) / 2
-    return xs, ys
-
-
-def GEsVsParams(fixed_param, fixed_which="alpha", step=0.01, numx=3, numy=4,
[…]

### 2019-12-25 ProjectDataBase/LatticeData.py
Delete the `ProjectDataBase` directory and its contents.

@@ -1,30 +1,0 @@
-"""
-This module provides the lattice information of the triangular lattice
-
-
-AS : 2-D array
-    The real space translation vectors
-BS : 2-D array
-    The reciprocal space (k space) translation vectors
-RS : 2-D array
-    The displaces to three nonequivalent nearest neighbors on triangular lattice
-"""
-
-
-import numpy as np
-
-
-__all__ = [
-    "AS",
-    "BS",
-    "RS",
-]
-
-
-AS = np.array([[1, 0], [0.5, np.sqrt(3) / 2]], dtype=np.float64)
-RS = np.array(
-    [[1, 0], [0.5, np.sqrt(3) / 2], [-0.5, np.sqrt(3) / 2]], dtype=np.float64
-)
-BS = 2 * np.pi * np.array(
-    [[1, -1 / np.sqrt(3)], [0, 2 / np.sqrt(3)]], dtype=np.float64
-)

### 2019-12-25 ProjectDataBase/SigmaMatrix.py

@@ -1,20 +1,0 @@
-"""
-This module defines the commonly used sigma matrices
-"""
-
-
-import numpy as np
-
-
-# sigma matrices
-SIGMA0 = np.array([[1, 0], [0, 1]], dtype=np.float64)
-SIGMAX = np.array([[0, 1], [1, 0]], dtype=np.float64)
-SIGMAY = np.array([[0, -1j], [1j, 0]], dtype=np.complex128)
-SIGMAZ = np.array([[1, 0], [0, -1]], dtype=np.float64)
-SIGMAS = np.array([SIGMA0, SIGMAX, SIGMAY, SIGMAZ])
-
-# sigmay * 1j
-ISIGMAY = np.array([[0, 1], [-1, 0]], dtype=np.float64)
-
-# pairing matrices
-PMS = np.matmul(ISIGMAY, SIGMAS) / np.sqrt(2)

### 2019-12-25 ProjectDataBase/__init__.py

@@ -1,10 +1,0 @@
-"""
-This package defines the commonly used data in this project
-
-Available modules
------------------
-LatticeData
-    This module provides the lattice information of the triangular lattice
-SigmaMatrix
-    This module defines the commonly used sigma matrices
-"""

### 2019-12-30 paper/paper.tex
20191230 18:53:30

@@
 \documentclass[aps,prb,reprint,groupedaddress,showpacs,amsfonts,amsmath,amssymb,superscriptaddress]{revtex4-1}
+\usepackage{IEEEtrantools}
 \usepackage{graphicx}
@@
 It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}=1/2$ moments.
-In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
+In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.
+\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
 Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=$1/2$ models with edge sharing octahedra \cite {PhysRevLett.112.077204}.
@@
     H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack
+    \label{eq:Hamiltonian}
 \end{equation}
-where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.
-1, and $\alpha$, $\beta$ are the remaining directions.
+where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.\ref{fig:ModelDefinition}(b), and $\alpha$, $\beta$ are the remaining directions.
 $J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges.
@@
 Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular $J-K-\Gamma$ model.
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{Fig1.pdf}
+    \caption{(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron.
+(b) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively.
+The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation.
+(c) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron.
+The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.}
+    \label{fig:ModelDefinition}
+\end{figure}
 
@@
 
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig1.pdf}
-    \caption{(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedral.
-(b) Three different direction of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue respectively.
-The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation.
-(c) The orientation of the cubic $x$, $y$, $z$ with respect to the octahedral.
-The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.}
-     \label{fig:ModelDefinition}
-\end{figure}
-
 \section{Methods}
-
-The ground state of the full anisotropic Hamiltonian is no longer solvable in closed analytical form, even in the classical case.
+The full anisotropic Hamiltonian \eqref{eq:Hamiltonian} is no longer exactly solvable, even for the classical case.
 One, therefore, either has to rely on approximate analytical method or on numerical techniques.
+To determine the ground state of the Hamiltonian \eqref{eq:Hamiltonian}, we employ a combination of classical Monte Cralo simulation and ED calculation.
 Here, we briefly describe the methods we used.
-\textcolor{red}{$\cdots\cdots$}
-
-\subsection{Dual Transformation}
-\textcolor{red}{A introduction to dual transformation. Left blank currently.}
+For convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchanges using angles $\alpha$ and $\beta$
+\begin{equation}
+    J=\sin\alpha \sin\beta, \quad K=\sin\alpha \cos\beta, \quad \Gamma=\cos\alpha
+    \label{eq:Parameters}
+\end{equation}
+where $\alpha \in [0, \pi]$ and $\beta \in [0, 2\pi]$ to cover the global phase diagram.
 
@@
 \subsection{Exact Diagonalization}
-\textcolor{red}{A introduction to exact diagonalization. Left blank currently.}
+We perform a Lanczos ED calculation of the GS energy of the Hamiltonian \eqref{eq:Hamiltonian} on a 24-site cluster with periodic boundary conditions.
+To detect quantum phase transitions, the second derivatives of the ground-state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the groun-state characteristics.
+Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified.
+The remaining phases were identified mainly by examining the static structure factor
+\begin{equation}
+    S(\mathbf{Q}) = \frac{1}{N} \sum_{ij}e^{i\mathbf{Q}\cdot(\mathbf{r}_i - \mathbf{r}_j)} \langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle
+    \label{eq:StaticStructureFactor}
+\end{equation}
 
-\section{Phase Diagram and Analysis}
-\textcolor{red}{Global phase diagram of the $J-K-\Gamma$ model. Left blank currently.}
+To extract the moment direction of a magnetic ordered phase from a cluster ground state, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}.
+The basic idea of this method is to measure the probabilities of the exact cluster ground state $|GS\rangle$ on cluster spin-coherent states with varying moment directions.
+The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
+\begin{equation}
+    |\Psi\rangle = \prod_{i=1}^N|\theta_i,\phi_i\rangle
+    \label{eq:ClusterCoherentState}
+\end{equation}
+where the spin-1/2 coherent state
+\begin{equation}
+    |\theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) |\uparrow \rangle = e^{-i\phi S^z} e^{-i\theta S^y} |\uparrow\rangle
+    \label{eq:Spin-1/2CoherentState}
+\end{equation}
+is fully polaried along the $(\theta, \phi)$ direction.
+Here the cubic axes are used (see Fig.
+\ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z |\uparrow \rangle = \frac{1}{2}|\uparrow \rangle$.
+By calculating the overlap with the exact cluster GS from ED, and maximizing the probability $P = |\langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.
 
+\section{Classical Analysis}
+To understand the effects of inculding this off-diagonal $\Gamma$ term, we first study the classical $J-K-\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension.
+On our proceeding, we note that the global phase diagram has been obtained previously by using a combination of Luttinger-Tsiza (LT) and classical Monte Carlo simulations \cite{PhysRevB.92.165108}.
+Six different magnetic orderings: ferromagnet (FM), stripe, 120$^\circ$ N\'{e}el order, nematic, $\mathbb{Z}_2$ and dual-$\mathbb{Z}_2$ vortex crystal phases were found, see Fig.
+2 in Ref \onlinecite{PhysRevB.92.165108}.
+Our classical Monte Carlo study give qualitatively the same phase diagram.
+
+\subsection{Moment direction of the classcial FM order}
+For the classical FM order, the energy of the $J-K-\Gamma$ model per lattice site is given by
+\begin{equation}
+    E_{FM}^{c} = (3J + K) + 2\Gamma(S^xS^y + S^yS^z + S^zS^x)
+    \label{eq:EcFM}
+\end{equation}
+On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\mathbf{S}| = 1$.
+$f(S^x, S^y, S^z)$ takes maximum value $f_{max}=1$ at $S^x=S^y=S^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $S^x + S^y + S^z = 0$ and $|\mathbf{S}| = 1$ are fulfilled.
+That is to say, for $\Gamma > 0$ the moment of the classcial FM state prefers to lie in the plane that is perpendicular to the $[111]$ direction and when $\Gamma$ is negative, the moment would along the $[111]$ or $[\bar{1}\bar{1}\bar{1}]$ direction.
+
+\subsection{Moment direction of the classcial stripe order}
+
+In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig.
+\ref{fig:PhaseDiagram}(b)-(d).
+For the spin configuration shown in Fig.
+\ref{fig:PhaseDiagram}(b), the energy of the $J-K-\Gamma$ model Hamiltonian is
+\begin{IEEEeqnarray}{rCl}
+    E_{StripeX}^{c} & = & -(J + K) + 2KS^xS^x \nonumber \\
+        && + 2\Gamma(S^yS^z - S^xS^y - S^zS^x)
+    \label{eq:EcStripeX}
+\end{IEEEeqnarray}
+and the energy for spin configuration in Fig.
+\ref{fig:PhaseDiagram}(c) and \ref{fig:PhaseDiagram}(d) can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$.
+The moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$.
+In general, $E_{StripeX}^{c}$ has three extreme points where the first derivatives equal zero
+\begin{align}
+    &\mathbf{S}_0: \quad S_{0}^{y}=-S_{0}^{z} = \pm1/\sqrt{2}, \quad S_{0}^{x} = 0\\
+    &\mathbf{S}_1: \quad S_{1}^{y}=S_{1}^{z} = f_{1}(K, \Gamma), \quad S_{1}^{x} = g_{1}(K, \Gamma) S_{1}^{y}\\
+    &\mathbf{S}_2: \quad S_{2}^{y}=S_{2}^{z} = f_{2}(K, \Gamma), \quad S_{2}^{x} = g_{2}(K, \Gamma) S_{2}^{y}
+\end{align}
+see Appendix A for their explicit expressions.
+
+For $\Gamma=0, K>0$, the stripe order shown in Fig.
+\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
+A definite positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction and negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction.
+When $\Gamma=0, K<0$, the moment would along the $x$ axis to have lowest energy and both positive and negative $\Gamma$ make it deviate from the $x$ axis and point the $\mathbf{S}_1$ direction.
+
+\textcolor{red}{$\cdots \cdots$}
+
+\section{Global Phase Diagram}
 \begin{figure*}
     \centering
-    % \subfigure{\includegraphics[width=0.96\textwidth]{Fig2_a.pdf}}\\
-    % \subfigure{\includegraphics[width=0.96\textwidth]{Fig2_b_f.pdf}}\\
     \includegraphics[width=0.96\textwidth]{Fig2.pdf}
@@
     \caption{(Color online) Map of the probabilities.}
-     \label{fig:StructureFactors}
+     \label{fig:Proabilities}
 \end{figure}
+
+\textcolor{red}{Global phase diagram of the $J-K-\Gamma$ model. Left blank currently.}
 

### 2019-12-30 paper/paper.tex
20191230 22:37

@@
 \subsection{Exact Diagonalization}
-We perform a Lanczos ED calculation of the GS energy of the Hamiltonian \eqref{eq:Hamiltonian} on a 24-site cluster with periodic boundary conditions.
+We perform a Lanczos ED calculation of the GS energy of the Hamiltonian \eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC).
 To detect quantum phase transitions, the second derivatives of the ground-state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the groun-state characteristics.
 Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified.
-The remaining phases were identified mainly by examining the static structure factor
+The remaining phases were identified mainly by examining the static magnetic structure factor (SMSF)
 \begin{equation}
-    S(\mathbf{Q}) = \frac{1}{N} \sum_{ij}e^{i\mathbf{Q}\cdot(\mathbf{r}_i - \mathbf{r}_j)} \langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle
+    S(\mathbf{Q}) = \frac{1}{N} \sum_{ij}e^{i\mathbf{Q}\cdot(\mathbf{R}_i - \mathbf{R}_j)} \langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle
     \label{eq:StaticStructureFactor}
 \end{equation}
+where N is the total number of spins, $\mathbf{R}_i$ is the position of site $i$ and $\langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle$ is the average over the ground state.
 
@@
 \section{Classical Analysis}
-To understand the effects of inculding this off-diagonal $\Gamma$ term, we first study the classical $J-K-\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension.
+To understand the effects of inculding the off-diagonal $\Gamma$ term, we first study the classical $J-K-\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension.
 On our proceeding, we note that the global phase diagram has been obtained previously by using a combination of Luttinger-Tsiza (LT) and classical Monte Carlo simulations \cite{PhysRevB.92.165108}.
@@
 \end{equation}
-On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\mathbf{S}| = 1$.
+On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\mathbf{S}| = 1$.
 $f(S^x, S^y, S^z)$ takes maximum value $f_{max}=1$ at $S^x=S^y=S^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $S^x + S^y + S^z = 0$ and $|\mathbf{S}| = 1$ are fulfilled.
@@
 For the spin configuration shown in Fig.
-\ref{fig:PhaseDiagram}(b), the energy of the $J-K-\Gamma$ model Hamiltonian is
+\ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian \eqref{eq:Hamiltonian} is
 \begin{IEEEeqnarray}{rCl}
@@
 There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase.
-(b) Illustration of the FM order.
-All spins along the same direction.
-(c) Illustation of the stripe order of the $x$ type.
-That is the spins along the x-bond direction are parallel and adjacent chains are antiparallel.
-There are also stripe order of the $y$ or $z$ type, which are degenerate with the $x$ type stripe order.
-(d) Illustration of the 120$^\circ$ N\'{e}el order.
+The three FM phases different from each other in the direction of the ordered moment, and also the four stripe phases are distinguished by their moment directions, see main text for details.
+(b)-(d) Illustation of the three degenerate spin configurations for all stripe orders.
+(e) Illustration of the 120$^\circ$ N\'{e}el order.
 All spins are coplanar and the angles between nearest-neighbor spins are 120$^\circ$.
-(e) Illustration of the Dual N\'{e}el order.
+(f) Illustration of the Dual N\'{e}el order.
 The magnetic unit cell include 12 lattice sites as marked by the green dashed parallelogram.}
@@
 
+In this section, we turn to study the quantum phases in the $J-K-\Gamma$ model Hamiltonian.
+We consider a $4 \times 6$ cluster with PBC that has been used previously to study the HK model on triangular lattice \cite{KaiLi2015}.
+The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.
+\ref{fig:PhaseDiagram}(a).
+The phase boundaries are obtained from the location of singular features in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
+The quantum phase diagrams is closely resemble to the classical results in Ref.
+\onlinecite{PhysRevB.92.165108} except for the small green area near $\Gamma=1$ which does not appear in the classical phase diagram.
+
+In the HK limit, by virtue of the existence of the so-called four-sublattice-transformation (FST), two more magnetic ordered phases were identified in addition to the well-understood FM and 120$^\circ$ N\'{e}el phases.
+Under the transformation, we obtain a collinear stripe order (see Fig.
+\ref{fig:PhaseDiagram}(b)-(d)) from the original FM order and a noncollinear spiral order (dual N\'{e}el) from the 120$^\circ$ N\'{e}el order (see Fig.
+\ref{fig:PhaseDiagram}(e) and (f)).
+The transformation is no longer valid when $\Gamma$ is included, but the phases surrounding these spcial points can still be identified with each respective limit.
+
+To identify the remaining phases and providing more information of these phase, we calculate the SMSF for some representative model paramters, as shown in Fig.
+\ref{fig:StructureFactors}.
+For pure $\Gamma$ model, see Fig.
+\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
+Take into account of the classical results, we propose the three blue areas with different shadings to be FM ordered phases and they different from each other in the direction of the ordered moment which will be discussed in the next section.
+In Fig.
+\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the GS of the $J-K-\Gamma$ model around these model parameters could be stripe ordered.
+
 \begin{figure}
     \includegraphics[width=0.45\textwidth]{Fig3.pdf}
-    \caption{(Color online) Static structure factors for different model paramters.}
+    \caption{(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
      \label{fig:StructureFactors}
@@
 
-\textcolor{red}{Global phase diagram of the $J-K-\Gamma$ model. Left blank currently.}
+\textcolor{red}{$\cdots \cdots$}
 
-\section{Discussion}
-\textcolor{red}{A discussion of our results. Left blank currently.}
+\section{Summary}
+\textcolor{red}{Summary of our work. Left blank currently.}
 

### 2019-12-31 paper/paper.tex
20191231 12:18:40

@@
 \affiliation{National Laboratory of Solid State Microstructures and School of Physics, Nanjing University, Nanjing 210093, China}
+
+\author{\textcolor{cyan}{XXX}}
+\affiliation{\textcolor{cyan}{XXX}}
+\author{\textcolor{cyan}{XXX}}
+\affiliation{\textcolor{cyan}{XXX}}
+
 \author{Shun-Li Yu}
@@
 \begin{abstract}
-    The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization.
-\textcolor{red}{$\cdots \cdots$}
+\textcolor{red}{The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization. $\cdots \cdots$}
 \end{abstract}
@@
 We perform a Lanczos ED calculation of the GS energy of the Hamiltonian \eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC).
-To detect quantum phase transitions, the second derivatives of the ground-state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the groun-state characteristics.
+To detect quantum phase transitions, the second derivatives of the ground-state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground-state characteristics.
 Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified.
@@
 $f(S^x, S^y, S^z)$ takes maximum value $f_{max}=1$ at $S^x=S^y=S^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $S^x + S^y + S^z = 0$ and $|\mathbf{S}| = 1$ are fulfilled.
-That is to say, for $\Gamma > 0$ the moment of the classcial FM state prefers to lie in the plane that is perpendicular to the $[111]$ direction and when $\Gamma$ is negative, the moment would along the $[111]$ or $[\bar{1}\bar{1}\bar{1}]$ direction.
+The condition $S^x + S^y + S^z = 0$ specify a plane that is perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.
+\ref{fig:ModelDefinition}(c) this is actually the plane of the triangular lattice.
+That is to say, for $\Gamma > 0$ the moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the moment would perpendicular to the lattice plane.
+
+Our classical Monte Carlo simulation found FM ordered state with the right moment direction for majority of the area marked as FM phase (see Fig.
+2 in Ref \onlinecite{PhysRevB.92.165108}) except for the pure $\Gamma$ term.
+For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found.
+When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix A for details).
+Based on these observation, it is reasonable to say that the ground state of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions.
+For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM order as the ground state which was verified by our Monte Carlo simulation.
+On the other hand, when both positive Heisenberg and Kitaev interactions are included, which introduces further frustation to the system, the FM order is unlikely to be selected.
+For $\Gamma < 0$, the spins form stripe order and for positive $\Gamma$ the system remains disordered.
+
+\textcolor{red}{$\cdots \cdots$}
 
@@
 \begin{IEEEeqnarray}{rCl}
-    E_{StripeX}^{c} & = & -(J + K) + 2KS^xS^x \nonumber \\
-        && + 2\Gamma(S^yS^z - S^xS^y - S^zS^x)
+    E_{StripeX}^{c} & = & -(J + K) + 2 K S^x S^x \nonumber \\
+        && \negmedspace {} + 2 \Gamma (S^y S^z - S^z S^x - S^x S^y)
     \label{eq:EcStripeX}
@@
 
-For $\Gamma=0, K>0$, the stripe order shown in Fig.
+For $\Gamma=0, K>0$, it can be clearly seen from Eq\eqref{eq:EcStripeX} that the stripe order shown in Fig.
 \ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
-A definite positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction and negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction.
-When $\Gamma=0, K<0$, the moment would along the $x$ axis to have lowest energy and both positive and negative $\Gamma$ make it deviate from the $x$ axis and point the $\mathbf{S}_1$ direction.
+A definite positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction.
+When $\Gamma=0, K<0$, the moment would along the $x$ axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$ axis and point the $\mathbf{S}_1$ direction.
 
@@
 
+\textcolor{red}{$\cdots \cdots$}
+
+\section{Moment Direction-Exact Diagonalization Results}
 \begin{figure}
@@
 
-\textcolor{red}{$\cdots \cdots$}
+\textcolor{red}{Exact diagonalization results of the moment direction for FM and stripe phases. Left blank currently.}
 

### 2019-12-31 paper/paper.tex
20191231 18:23:40

@@
 \end{equation}
+where $S^x$, $S^y$, $S^z$ are the corresponding components of the classical moment vector.
 On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\mathbf{S}| = 1$.
@@
 For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM order as the ground state which was verified by our Monte Carlo simulation.
-On the other hand, when both positive Heisenberg and Kitaev interactions are included, which introduces further frustation to the system, the FM order is unlikely to be selected.
-For $\Gamma < 0$, the spins form stripe order and for positive $\Gamma$ the system remains disordered.
-
-\textcolor{red}{$\cdots \cdots$}
+On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS.
+In fact, the classical GS were found to be disordered for $0 < J \ll \Gamma$ and stripe ordered for $0 < J \ll -\Gamma$.
+As for the disordered phase, when quantum flucations are involved, a quantum spin liquid state may emerge.
 
 \subsection{Moment direction of the classcial stripe order}
-
 In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig.
@@
 \begin{align}
-    &\mathbf{S}_0: \quad S_{0}^{y}=-S_{0}^{z} = \pm1/\sqrt{2}, \quad S_{0}^{x} = 0\\
-    &\mathbf{S}_1: \quad S_{1}^{y}=S_{1}^{z} = f_{1}(K, \Gamma), \quad S_{1}^{x} = g_{1}(K, \Gamma) S_{1}^{y}\\
-    &\mathbf{S}_2: \quad S_{2}^{y}=S_{2}^{z} = f_{2}(K, \Gamma), \quad S_{2}^{x} = g_{2}(K, \Gamma) S_{2}^{y}
+    &\mathbf{S}_0: \quad S_{0}^{y}=-S_{0}^{z} = \pm1/\sqrt{2}, \quad S_{0}^{x} = 0 \label{eq:S0} \\
+    &\mathbf{S}_1: \quad S_{1}^{y}=S_{1}^{z} = f_{1}(K, \Gamma), \quad S_{1}^{x} = g_{1}(K, \Gamma) S_{1}^{y} \label{eq:S1} \\
+    &\mathbf{S}_2: \quad S_{2}^{y}=S_{2}^{z} = f_{2}(K, \Gamma), \quad S_{2}^{x} = g_{2}(K, \Gamma) S_{2}^{y} \label{eq:S2}
 \end{align}
-see Appendix A for their explicit expressions.
+see Appendix B for their explicit expressions.
 
@@
 \ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
-A definite positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction.
-When $\Gamma=0, K<0$, the moment would along the $x$ axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$ axis and point the $\mathbf{S}_1$ direction.
-
+An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction.
+When $\Gamma=0, K<0$, the moment would along the $x$ axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$ axis to point the $\mathbf{S}_1$ direction.
+All these stripe orders with the specific moment direction were found in our Monte Carlo simulation.
+However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found for a range of $J$ and $K$.
+Both positive and negative $\Gamma$ lift the degeneracy and drive the moment direction of stripe order to specific direction.
 \textcolor{red}{$\cdots \cdots$}
@@
 
-To identify the remaining phases and providing more information of these phase, we calculate the SMSF for some representative model paramters, as shown in Fig.
+To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig.
 \ref{fig:StructureFactors}.

### 2020-01-02 paper/paper.tex
20200102 13:21:00

@@
-\documentclass[aps,prb,reprint,groupedaddress,showpacs,amsfonts,amsmath,amssymb,superscriptaddress]{revtex4-1}
+\documentclass[aps,prb,reprint,amsfonts,amsmath,amssymb,showpacs,groupedaddress,superscriptaddress]{revtex4-1}
 \usepackage{IEEEtrantools}
 \usepackage{graphicx}
-% \usepackage{subfigure}
 \usepackage{bm}
@@
 To extract the moment direction of a magnetic ordered phase from a cluster ground state, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}.
-The basic idea of this method is to measure the probabilities of the exact cluster ground state $|GS\rangle$ on cluster spin-coherent states with varying moment directions.
+The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions.
 The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
 \begin{equation}
-    |\Psi\rangle = \prod_{i=1}^N|\theta_i,\phi_i\rangle
+    |\Psi\rangle = \bigotimes_{i=1}^N|\theta_i,\phi_i\rangle
     \label{eq:ClusterCoherentState}
@@
 \ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z |\uparrow \rangle = \frac{1}{2}|\uparrow \rangle$.
-By calculating the overlap with the exact cluster GS from ED, and maximizing the probability $P = |\langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.
+By calculating the overlap with the exact cluster GS, and maximizing the probability $P = |\langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.
 
@@
 The moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$.
-In general, $E_{StripeX}^{c}$ has three extreme points where the first derivatives equal zero
+In general ($J,K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has three extreme points where the first derivatives equal zero
 \begin{align}
@@
 An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction.
-When $\Gamma=0, K<0$, the moment would along the $x$ axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$ axis to point the $\mathbf{S}_1$ direction.
-All these stripe orders with the specific moment direction were found in our Monte Carlo simulation.
-However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found for a range of $J$ and $K$.
-Both positive and negative $\Gamma$ lift the degeneracy and drive the moment direction of stripe order to specific direction.
-\textcolor{red}{$\cdots \cdots$}
+When $\Gamma=0, K<0$, the moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{S}_1$ direction.
+All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation.
+However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$.
 
@@
 The phase boundaries are obtained from the location of singular features in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
-The quantum phase diagrams is closely resemble to the classical results in Ref.
+The quantum phase diagram is closely resemble to the classical result in Ref.
 \onlinecite{PhysRevB.92.165108} except for the small green area near $\Gamma=1$ which does not appear in the classical phase diagram.
 
-In the HK limit, by virtue of the existence of the so-called four-sublattice-transformation (FST), two more magnetic ordered phases were identified in addition to the well-understood FM and 120$^\circ$ N\'{e}el phases.
+In the HK limit, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified in addition to the well-understood FM ($J=-1$)and 120$^\circ$ N\'{e}el ($J=1$) phases.
 Under the transformation, we obtain a collinear stripe order (see Fig.
@@
 \ref{fig:PhaseDiagram}(e) and (f)).
-The transformation is no longer valid when $\Gamma$ is included, but the phases surrounding these spcial points can still be identified with each respective limit.
+The phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.
 
+When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid.
 To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig.
@@
 \ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
-Take into account of the classical results, we propose the three blue areas with different shadings to be FM ordered phases and they different from each other in the direction of the ordered moment which will be discussed in the next section.
+Take into account of the classical results, we propose the three blue areas with different shadings in the global phase diagram (see Fig.
+\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the next section.
 In Fig.
 \ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the GS of the $J-K-\Gamma$ model around these model parameters could be stripe ordered.
+For the model parameters shown in Fig.
+\ref{fig:StructureFactors}(d) and (e), the GS of the classical model is stripe ordered, and our ED results suggest the stripe state persist in the quantum limit.
 

### 2020-01-02 paper/paper.tex
20200102 14:14:20

@@
 
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
+    \caption{(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
+     \label{fig:StructureFactors}
+\end{figure}
+
 When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid.
@@
 Take into account of the classical results, we propose the three blue areas with different shadings in the global phase diagram (see Fig.
-\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the next section.
+\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., \emph{FM-A}, \emph{FM-B}, \emph{FM-C}) and they different from each other in the direction of the ordered moment which will be discussed in the next section.
 In Fig.
-\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the GS of the $J-K-\Gamma$ model around these model parameters could be stripe ordered.
-For the model parameters shown in Fig.
-\ref{fig:StructureFactors}(d) and (e), the GS of the classical model is stripe ordered, and our ED results suggest the stripe state persist in the quantum limit.
-
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
-    \caption{(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
-     \label{fig:StructureFactors}
-\end{figure}
-
+\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit.
+It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state.
+The four stripe phases designated as \emph{Stripe-A}, \emph{-B}, \emph{-C}, \emph{-D} in Fig.
+\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction.
+Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.
+\ref{fig:PhaseDiagram}(a).
+For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig.
+\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.
 \textcolor{red}{$\cdots \cdots$}
@@
 \section{Moment Direction-Exact Diagonalization Results}
+\textcolor{red}{Exact diagonalization results of the moment direction for FM and stripe phases. Left blank currently.}
+
 \begin{figure}
@@
 \end{figure}
-
-\textcolor{red}{Exact diagonalization results of the moment direction for FM and stripe phases. Left blank currently.}
 

### 2020-01-02 paper/paper.tex
20200102 14:49:10

@@
     \includegraphics[width=0.45\textwidth]{Fig4.pdf}
-    \caption{(Color online) Map of the probabilities.}
+    \caption{(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
+The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.
+\ref{fig:ModelDefinition}(c).
+The green dashed lines and solid circles mark the ordered moment direction determined for the classical states, see main text for details.
+(a)-(b) Probability maps for the FM states in the \emph{FM-A} and \emph{FM-C} phase, respectively.
+(c)-{f} Proability maps for the stripe states in the \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C}, \emph{Stripe-D}, resepctively.}
      \label{fig:Proabilities}

### 2020-01-02 paper/paper.tex
20200102 19:11:10

@@
 \subsection{Classical Monte Carlo}
-\textcolor{red}{A introduction to classical Monte Carlo. Left blank currently.}
+\textcolor{red}{A introduction to classical Monte Carlo.  To be accomplished $\cdots \cdots$}
 
@@
 \section{Moment Direction-Exact Diagonalization Results}
-\textcolor{red}{Exact diagonalization results of the moment direction for FM and stripe phases. Left blank currently.}
-
 \begin{figure}
@@
 
+Having map out the global phase diagram of the $J-K-\Gamma$ model, we now move to the moment direction of these FM and stripe phases which provides key characteristic to distinguish them.
+Since the cluster spin-coherent state is captured by only a single pair ($\theta$, $\phi$) for collinear phases (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2.$
+
+\subsection{Moment direction of the FM phases}
+For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction.
+The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction(i.e., \textit{x}, \textit{y}, \textit{z} direction).
+However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction.
+To extract the moment direction of the \emph{FM-A} and \emph{FM-C} phases, we construct the following cluster spin-coherent state
+\begin{equation}
+    |\Psi(\theta, \phi) \rangle = \bigotimes_{i=1}^N|\theta,\phi \rangle
+\end{equation}
+and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$. The resulting probability maps are shown in Fig. \ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).
+
+\textcolor{red}{Moment direction of the FM phases. To be accomplished $\cdots \cdots$}
+
+\subsection{Moment direction of the stripe phases}
+\textcolor{red}{Moment direction of the stripe phases. To be accomplished $\cdots \cdots$}
+
 \section{Summary}
-\textcolor{red}{Summary of our work. Left blank currently.}
+\textcolor{red}{Summary of our work. To be accomplished $\cdots \cdots$}
 
-\section{Acknowledgements}
-\textcolor{red}{Acknowledgements. Left blank currently.}
+\begin{acknowledgments}
+    \textcolor{red}{Acknowledgements.  To be accomplished $\cdots \cdots$}
+\end{acknowledgments}
+
+% The following are the Appendixes of this article
+\appendix
+
+\section{Analysis of the classical energy and moment direction}
+
+\textcolor{red}{Analysis of the classical energy and moment direction. To be accomplished $\cdots \cdots$}
+
+\newpage
 

### 2020-01-02 paper/paper.tex
20200102 22:22:00

@@
 \end{equation}
-and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$. The resulting probability maps are shown in Fig. \ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).
-
-\textcolor{red}{Moment direction of the FM phases. To be accomplished $\cdots \cdots$}
+and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$.
+The resulting probability maps are shown in Fig.
+\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).
+For the \emph{FM-A} phase, the probability map reveals the moment being constrained to the lattice plane with all directions degenerate, as expected from classical considerations (see the green dashed line).
+As for the \emph{FM-C} phase, the probability is clearly peaked at the direction perpendicular to the lattice plane which is also consistent with our classical analysis (marked by the green solid circle).
 
 \subsection{Moment direction of the stripe phases}
-\textcolor{red}{Moment direction of the stripe phases. To be accomplished $\cdots \cdots$}
+The stripe phases have three degenerate patterns as shown in Fig.
+\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern.
+For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.
+\ref{fig:PhaseDiagram}(b) and present the probability maps in Fig.
+\ref{fig:Proabilities}(c)-(f) for \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C}, \emph{Stripe-D} respectively.
+In the HK limit, the \emph{Stripe-A} phase is connected to the \emph{FM-B} phase through FST and the spins are supposed to along the \emph{x}-axis for stripe pattern in Fig.
+\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit (see Fig.
+\ref{fig:Proabilities}(c)).
+As for the \emph{Stripe-D} phase near the AF Kitaev point, the probability map Fig.
+\ref{fig:Proabilities}(f) reveals the moment being constrained to the vicinity of the \emph{yz} plane, as predicted by classical analysis.
+Within this plane, the order-from-disorder mechanism selects the cubic axes \emph{y} and \emph{z} where the probability reaches its maxima.
+The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of six possible classical stripe states, more importantly it a signature of large quantum flucations in the ground state.
+
+The main effect of $\Gamma$ term on \emph{Stripe-A} and \emph{Stripe-D} is tilting the moment orientation away from the cubic axes directions, yielding \emph{Stripe-B} and \emph{Stripe-C}.
+Fig.
+\ref{fig:Proabilities}(e) is a representative probability map for \emph{Stripe-B}.
+The probability takes maximum value at the directions determined by Eq.\eqref{eq:S1}.
+\textcolor{red}{$\cdots \cdots$}
 

### 2020-01-03 paper/paper.tex
20200103 10:45:50

@@
 
-In this manuscript, by combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the $J-K-\Gamma$ model.
-\textcolor{red}{$\cdots\cdots$}
-
-The rest of the paper is organized as follows: \textcolor{red}{$\cdots\cdots$}
+The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization methods are introduced in Section II.
+Section III discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states.
+The global phase diagram of the quantum model is presented in Section IV along with a discussion of its phases.
+In Section V, we study the moment direction of the quantum FM and stripe states, which provide characteristics to distinguish these phases.
 
@@
     \includegraphics[width=0.45\textwidth]{Fig4.pdf}
-    \caption{(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
+    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
 The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.
 \ref{fig:ModelDefinition}(c).
-The green dashed lines and solid circles mark the ordered moment direction determined for the classical states, see main text for details.
+The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.
 (a)-(b) Probability maps for the FM states in the \emph{FM-A} and \emph{FM-C} phase, respectively.
-(c)-{f} Proability maps for the stripe states in the \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C}, \emph{Stripe-D}, resepctively.}
-     \label{fig:Proabilities}
+(c)-(f) Proability maps for the stripe states in the \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C} and \emph{Stripe-D} phase, respectively.}
 \end{figure}
@@
 
-The main effect of $\Gamma$ term on \emph{Stripe-A} and \emph{Stripe-D} is tilting the moment orientation away from the cubic axes directions, yielding \emph{Stripe-B} and \emph{Stripe-C}.
+The main effect of $\Gamma$ term on the \emph{Stripe-A} and \emph{Stripe-D} phase is tilting the moment orientation away from the cubic axes directions, yielding the \emph{Stripe-B} and \emph{Stripe-C} phase.
 Fig.
-\ref{fig:Proabilities}(e) is a representative probability map for \emph{Stripe-B}.
-The probability takes maximum value at the directions determined by Eq.\eqref{eq:S1}.
-\textcolor{red}{$\cdots \cdots$}
+\ref{fig:Proabilities}(e) is a representative probability map for the \emph{Stripe-B} phase.
+The probability takes maximum value at the direction determined by Eq.\eqref{eq:S1}, which means that the moment direction changes with the model parameters $K$ and $\Gamma$.
+On the other hand, the case of the \emph{Stripe-C} phase is rather different.
+The probability is clearly peaked at the direction given by Eq.\eqref{eq:S0} with the maximum value $P_{max}$ considerably less than $\frac{1}{6}$ (see Fig.
+\ref{fig:Proabilities}(d)).
+Apart from the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the cluster GS, quantum flucations may take responsibilities for the reduced probability.
 

### 2020-01-03 paper/paper.tex
20200103 15:46:50

--- 2020-01-02 paper/paper.tex
@@
 \affiliation{\textcolor{cyan}{XXX}}
+
 \author{\textcolor{cyan}{XXX}}
@@
 \affiliation{Collaborative Innovation Center of Advanced Microstructures, Nanjing University, Nanjing 210093, China}
+
 \author{Jian-Xin Li}
@@
 
-\section{Introduction}
+\section{\label{sec:SectionI}Introduction}
 Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
 In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics.
-For nearest-neighbor (NN) spin-$1/2$ antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
+For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
 When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order \cite{PhysRevB.42.4800,PhysRevB.46.11137}.
@@
 Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy.
-The spin-$1/2$ Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration.
+The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration.
 As pointed out by Jackeli and Khaliullin \cite{Khaliullin2005, PhysRevLett.102.017205}, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles.
 Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model.
-It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}=1/2$ moments.
-In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.
-\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
-Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=$1/2$ models with edge sharing octahedra \cite {PhysRevLett.112.077204}.
+It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}$=1/2 moments.
+In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
+Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}.
 Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained.
@@
 Extensive studies of magnetic properties using neutron scattering \cite{Nature20614,nphys3971,PhysRevLett.117.267202,PhysRevX.8.031001}, muon spin relaxation ($\mu$SR) \cite{PhysRevLett.117.097201}, electron spin resonance (ESR) \cite{PhysRevLett.115.167203} reveal a possible gapless quantum spin liquid (QSL) ground state.
-More recently, a class of compounds \emph{AReCh}$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
+More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
 The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,arXiv1911.12712}.
@@
 \begin{equation}
-    H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack
-    \label{eq:Hamiltonian}
+    H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack \label{eq:Hamiltonian}
 \end{equation}
-where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.\ref{fig:ModelDefinition}(b), and $\alpha$, $\beta$ are the remaining directions.
+where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(b), and $\alpha$, $\beta$ are the remaining directions.
 $J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges.
-To the best of our knowledge, no exact solution has been reported so far for the spin-$1/2$ Kitaev and/or $\Gamma$ model on the triangular lattice.
+To the best of our knowledge, no exact solution has been reported so far for the spin-1/2 Kitaev and/or $\Gamma$ model on the triangular lattice.
 Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular $J-K-\Gamma$ model.
@@
     \includegraphics[width=\columnwidth]{Fig1.pdf}
-    \caption{(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron.
+    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron.
 (b) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively.
@@
 The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.}
-    \label{fig:ModelDefinition}
 \end{figure}
 
-In this manuscript, by combining the classical Monte Carlo simulation and exact diagonalization (ED) calculation, we map out the global phase diagram of the $J-K-\Gamma$ model.
-\textcolor{red}{$\cdots\cdots$}
+The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization methods are introduced in Sec.~\ref{sec:SectionII}.
+Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states.
+The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a discussion of its phases.
+In Sec.~\ref{sec:SectionV}, we study the moment direction of the quantum FM and stripe states, which provide characteristics to distinguish these phases.
 
-The rest of the paper is organized as follows: \textcolor{red}{$\cdots\cdots$}
-
-\section{Methods}
-The full anisotropic Hamiltonian \eqref{eq:Hamiltonian} is no longer exactly solvable, even for the classical case.
+\section{\label{sec:SectionII}Methods}
+The full anisotropic Hamiltonian~\eqref{eq:Hamiltonian} is no longer exactly solvable, even for the classical case.
 One, therefore, either has to rely on approximate analytical method or on numerical techniques.
-To determine the ground state of the Hamiltonian \eqref{eq:Hamiltonian}, we employ a combination of classical Monte Cralo simulation and ED calculation.
+To determine the ground state of the Hamiltonian~\eqref{eq:Hamiltonian}, we employ a combination of classical Monte Cralo simulation and ED calculation.
 Here, we briefly describe the methods we used.
-For convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchanges using angles $\alpha$ and $\beta$
+For convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchanges using spherical angles $\alpha$ and $\beta$
 \begin{equation}
-    J=\sin\alpha \sin\beta, \quad K=\sin\alpha \cos\beta, \quad \Gamma=\cos\alpha
-    \label{eq:Parameters}
+    J = \sin\alpha \sin\beta, \quad
+    K = \sin\alpha \cos\beta, \quad
+    \Gamma = \cos\alpha \label{eq:Parameters}
 \end{equation}
@@
 
-\subsection{Classical Monte Carlo}
+\subsection{\label{sec:SectionIIA}Classical Monte Carlo}
 \textcolor{red}{A introduction to classical Monte Carlo. To be accomplished $\cdots \cdots$}
 
-\subsection{Exact Diagonalization}
-We perform a Lanczos ED calculation of the GS energy of the Hamiltonian \eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC).
-To detect quantum phase transitions, the second derivatives of the ground-state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground-state characteristics.
+\subsection{\label{sec:SectionIIB}Exact Diagonalization}
+We perform a Lanczos ED calculation of the GS energy of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC).
+To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics.
 Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified.
@@
 \begin{equation}
-    S(\mathbf{Q}) = \frac{1}{N} \sum_{ij}e^{i\mathbf{Q}\cdot(\mathbf{R}_i - \mathbf{R}_j)} \langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle
-    \label{eq:StaticStructureFactor}
+    S(\bm{Q}) = \frac{1}{N} \sum_{ij} e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \langle \bm{S}_i \bm{\cdot} \bm{S}_j \rangle \label{eq:SMSF}
 \end{equation}
-where N is the total number of spins, $\mathbf{R}_i$ is the position of site $i$ and $\langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle$ is the average over the ground state.
+where N is the total number of spins, $\bm{R}_i$ is the position of site $i$ and $\langle \bm{S}_i \bm{\cdot} \bm{S}_j \rangle$ is the average over the ground state.
 
@@
 \begin{equation}
-    |\Psi\rangle = \bigotimes_{i=1}^N|\theta_i,\phi_i\rangle
-    \label{eq:ClusterCoherentState}
+    | \Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle \label{eq:ClusterCoherentState}
 \end{equation}
@@
 \begin{equation}
-    |\theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) |\uparrow \rangle = e^{-i\phi S^z} e^{-i\theta S^y} |\uparrow\rangle
-    \label{eq:Spin-1/2CoherentState}
+    | \theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle \label{eq:Spin-1/2CoherentState}
 \end{equation}
 is fully polaried along the $(\theta, \phi)$ direction.
-Here the cubic axes are used (see Fig.
-\ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z |\uparrow \rangle = \frac{1}{2}|\uparrow \rangle$.
-By calculating the overlap with the exact cluster GS, and maximizing the probability $P = |\langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.
+Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$.
+By calculating the overlap with the exact cluster GS, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.
 
-\section{Classical Analysis}
+\section{\label{sec:SectionIII}Classical Analysis}
 To understand the effects of inculding the off-diagonal $\Gamma$ term, we first study the classical $J-K-\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension.
 On our proceeding, we note that the global phase diagram has been obtained previously by using a combination of Luttinger-Tsiza (LT) and classical Monte Carlo simulations \cite{PhysRevB.92.165108}.
-Six different magnetic orderings: ferromagnet (FM), stripe, 120$^\circ$ N\'{e}el order, nematic, $\mathbb{Z}_2$ and dual-$\mathbb{Z}_2$ vortex crystal phases were found, see Fig.
-2 in Ref \onlinecite{PhysRevB.92.165108}.
+Six different magnetic orderings: ferromagnet (FM), stripe, 120$^\circ$ N\'{e}el order, nematic, $\mathbb{Z}_2$ and dual-$\mathbb{Z}_2$ vortex crystal phases were found, see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}.
 Our classical Monte Carlo study give qualitatively the same phase diagram.
 
-\subsection{Moment direction of the classcial FM order}
+\subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
 For the classical FM order, the energy of the $J-K-\Gamma$ model per lattice site is given by
 \begin{equation}
-    E_{FM}^{c} = (3J + K) + 2\Gamma(S^xS^y + S^yS^z + S^zS^x)
-    \label{eq:EcFM}
+    E_{FM}^{c} = (3J + K) + 2 \Gamma (S^x S^y + S^y S^z + S^z S^x) \label{eq:EcFM}
 \end{equation}
 where $S^x$, $S^y$, $S^z$ are the corresponding components of the classical moment vector.
-On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\mathbf{S}| = 1$.
-$f(S^x, S^y, S^z)$ takes maximum value $f_{max}=1$ at $S^x=S^y=S^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $S^x + S^y + S^z = 0$ and $|\mathbf{S}| = 1$ are fulfilled.
-The condition $S^x + S^y + S^z = 0$ specify a plane that is perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.
-\ref{fig:ModelDefinition}(c) this is actually the plane of the triangular lattice.
+On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\bm{S}| = 1$.
+$f(S^x, S^y, S^z)$ takes maximum value $f_{max}=1$ at $S^x=S^y=S^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $S^x + S^y + S^z = 0$ and $|\bm{S}| = 1$ are fulfilled.
+The condition $S^x + S^y + S^z = 0$ specify a plane that is perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c) this is actually the plane of the triangular lattice.
 That is to say, for $\Gamma > 0$ the moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the moment would perpendicular to the lattice plane.
 
-Our classical Monte Carlo simulation found FM ordered state with the right moment direction for majority of the area marked as FM phase (see Fig.
-2 in Ref \onlinecite{PhysRevB.92.165108}) except for the pure $\Gamma$ term.
+Our classical Monte Carlo simulation found FM ordered state with the right moment direction for majority of the area marked as FM phase (see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}) except for the pure $\Gamma$ term.
 For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found.
@@
 
-\subsection{Moment direction of the classcial stripe order}
-In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig.
-\ref{fig:PhaseDiagram}(b)-(d).
-For the spin configuration shown in Fig.
-\ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian \eqref{eq:Hamiltonian} is
-\begin{IEEEeqnarray}{rCl}
+\subsection{\label{sec:SectionIIIB}Moment direction of the classcial stripe order}
+In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig.~\ref{fig:PhaseDiagram}(b)-(d).
+For the spin configuration shown in Fig.~\ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} is
+\begin{eqnarray}
     E_{StripeX}^{c} & = & -(J + K) + 2 K S^x S^x \nonumber \\
-        && \negmedspace {} + 2 \Gamma (S^y S^z - S^z S^x - S^x S^y)
-    \label{eq:EcStripeX}
-\end{IEEEeqnarray}
-and the energy for spin configuration in Fig.
-\ref{fig:PhaseDiagram}(c) and \ref{fig:PhaseDiagram}(d) can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$.
+        & & +\: 2 \Gamma (S^y S^z - S^z S^x - S^x S^y) \label{eq:EcStripeX}
+\end{eqnarray}
+and the energy for spin configuration in Fig.~\ref{fig:PhaseDiagram}(c) and \ref{fig:PhaseDiagram}(d) can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$.
 The moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$.
 In general ($J,K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has three extreme points where the first derivatives equal zero
+\begin{subequations}
+    \label{eq:whole}
     \begin{align}
-    &\mathbf{S}_0: \quad S_{0}^{y}=-S_{0}^{z} = \pm1/\sqrt{2}, \quad S_{0}^{x} = 0 \label{eq:S0} \\
-    &\mathbf{S}_1: \quad S_{1}^{y}=S_{1}^{z} = f_{1}(K, \Gamma), \quad S_{1}^{x} = g_{1}(K, \Gamma) S_{1}^{y} \label{eq:S1} \\
-    &\mathbf{S}_2: \quad S_{2}^{y}=S_{2}^{z} = f_{2}(K, \Gamma), \quad S_{2}^{x} = g_{2}(K, \Gamma) S_{2}^{y} \label{eq:S2}
+        & \mathbf{S}_0: \quad S_{0}^{y}=-S_{0}^{z} = \pm1/\sqrt{2}, \quad S_{0}^{x} = 0 \label{eq:S0} \\
+        & \mathbf{S}_1: \quad S_{1}^{y}=S_{1}^{z} = f_{1}(K, \Gamma), \quad S_{1}^{x} = g_{1}(K, \Gamma) S_{1}^{y} \label{eq:S1} \\
+        & \mathbf{S}_2: \quad S_{2}^{y}=S_{2}^{z} = f_{2}(K, \Gamma), \quad S_{2}^{x} = g_{2}(K, \Gamma) S_{2}^{y} \label{eq:S2}
     \end{align}
+\end{subequations}
 see Appendix B for their explicit expressions.
 
-For $\Gamma=0, K>0$, it can be clearly seen from Eq\eqref{eq:EcStripeX} that the stripe order shown in Fig.
-\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
+For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
 An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction.
@@
 
-\section{Global Phase Diagram}
+\section{\label{sec:SectionIV}Global Phase Diagram}
 \begin{figure*}
@@
     \includegraphics[width=0.96\textwidth]{Fig2.pdf}
-    \caption{(Color online) (a) Global phase diagram of the triangular lattice J-K-$\Gamma$ model.
+    \caption{\label{fig:PhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J-K-\Gamma$ model.
 The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
@@
 The magnetic unit cell include 12 lattice sites as marked by the green dashed parallelogram.}
-     \label{fig:PhaseDiagram}
 \end{figure*}
@@
 We consider a $4 \times 6$ cluster with PBC that has been used previously to study the HK model on triangular lattice \cite{KaiLi2015}.
-The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.
-\ref{fig:PhaseDiagram}(a).
+The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:PhaseDiagram}(a).
 The phase boundaries are obtained from the location of singular features in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
-The quantum phase diagram is closely resemble to the classical result in Ref.
-\onlinecite{PhysRevB.92.165108} except for the small green area near $\Gamma=1$ which does not appear in the classical phase diagram.
+The quantum phase diagram is closely resemble to the classical result in Ref~\onlinecite{PhysRevB.92.165108} except for the small green area near $\Gamma=1$ which does not appear in the classical phase diagram.
 
 In the HK limit, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified in addition to the well-understood FM ($J=-1$)and 120$^\circ$ N\'{e}el ($J=1$) phases.
-Under the transformation, we obtain a collinear stripe order (see Fig.
-\ref{fig:PhaseDiagram}(b)-(d)) from the original FM order and a noncollinear spiral order (dual N\'{e}el) from the 120$^\circ$ N\'{e}el order (see Fig.
-\ref{fig:PhaseDiagram}(e) and (f)).
+Under the transformation, we obtain a collinear stripe order (see Fig.~\ref{fig:PhaseDiagram}(b)-(d)) from the original FM order and a noncollinear spiral order (dual N\'{e}el) from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)).
 The phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.
@@
     \includegraphics[width=0.45\textwidth]{Fig3.pdf}
-    \caption{(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
-     \label{fig:StructureFactors}
+    \caption{\label{fig:StructureFactors}(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
 \end{figure}
@@
 When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid.
-To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig.
-\ref{fig:StructureFactors}.
-For pure $\Gamma$ model, see Fig.
-\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
-Take into account of the classical results, we propose the three blue areas with different shadings in the global phase diagram (see Fig.
-\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., \emph{FM-A}, \emph{FM-B}, \emph{FM-C}) and they different from each other in the direction of the ordered moment which will be discussed in the next section.
-In Fig.
-\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit.
+To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}.
+For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
+Take into account of the classical results, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}.
+In Fig.~\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit.
 It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state.
-The four stripe phases designated as \emph{Stripe-A}, \emph{-B}, \emph{-C}, \emph{-D} in Fig.
-\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction.
-Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.
-\ref{fig:PhaseDiagram}(a).
-For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig.
-\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.
+The four stripe phases designated as Stripe-A, Stripe-B, Stripe-C, Stripe-D in Fig.~\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction.
+Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:PhaseDiagram}(a).
+For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.
 \textcolor{red}{$\cdots \cdots$}
 
-\section{Moment Direction-Exact Diagonalization Results}
+\section{\label{sec:SectionV}Moment Direction-Exact Diagonalization Results}
 \begin{figure}
     \includegraphics[width=0.45\textwidth]{Fig4.pdf}
-    \caption{(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
-The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.
-\ref{fig:ModelDefinition}(c).
-The green dashed lines and solid circles mark the ordered moment direction determined for the classical states, see main text for details.
-(a)-(b) Probability maps for the FM states in the \emph{FM-A} and \emph{FM-C} phase, respectively.
-(c)-{f} Proability maps for the stripe states in the \emph{Stripe-A}, \emph{Stripe-B}, \emph{Stripe-C}, \emph{Stripe-D}, resepctively.}
-     \label{fig:Proabilities}
+    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
+The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c).
+The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.
+(a)-(b) Probability maps for the FM states in the FM-A and FM-C phase, respectively.
+(c)-(f) Proability maps for the stripe states in the Stripe-A, Stripe-B, Stripe-C and Stripe-D phase, respectively.}
 \end{figure}
@@
 Having map out the global phase diagram of the $J-K-\Gamma$ model, we now move to the moment direction of these FM and stripe phases which provides key characteristic to distinguish them.
-Since the cluster spin-coherent state is captured by only a single pair ($\theta$, $\phi$) for collinear phases (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2.$
+Since the cluster spin-coherent state is captured by only a single pair ($\theta$, $\phi$) for collinear phases (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
 
-\subsection{Moment direction of the FM phases}
+\subsection{\label{sec:SectionVA}Moment direction of the FM phases}
 For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction.
-The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction(i.e., \textit{x}, \textit{y}, \textit{z} direction).
+The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction(i.e., $x$, $y$, $z$ direction).
 However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction.
-To extract the moment direction of the \emph{FM-A} and \emph{FM-C} phases, we construct the following cluster spin-coherent state
+To extract the moment direction of the FM-A and FM-C phases, we construct the following cluster spin-coherent state
 \begin{equation}
@@
 \end{equation}
-and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$. The resulting probability maps are shown in Fig. \ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).
+and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$.
+The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).
+For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane with all directions degenerate, as expected from classical considerations (see the green dashed line).
+As for the FM-C phase, the probability is clearly peaked at the direction perpendicular to the lattice plane which is also consistent with our classical analysis (marked by the green solid circle).
 
-\textcolor{red}{Moment direction of the FM phases. To be accomplished $\cdots \cdots$}
+\subsection{\label{sec:SectionVB}Moment direction of the stripe phases}
+The stripe phases have three degenerate patterns as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern.
+For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and present the probability maps in Fig.~\ref{fig:Proabilities}(c)-(f) for Stripe-A, Stripe-B, Stripe-C, Stripe-D respectively.
+In the HK limit, the Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit (see Fig.~\ref{fig:Proabilities}(c)).
+As for the Stripe-D phase near the AF Kitaev point, the probability map Fig.~\ref{fig:Proabilities}(f) reveals the moment being constrained to the vicinity of the $yz$ plane, as predicted by classical analysis.
+Within this plane, the order-from-disorder mechanism selects the cubic axes $y$ and $z$ where the probability reaches its maxima.
+The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of six possible classical stripe states, more importantly it a signature of large quantum flucations in the ground state.
 
-\subsection{Moment direction of the stripe phases}
-\textcolor{red}{Moment direction of the stripe phases. To be accomplished $\cdots \cdots$}
+The main effect of $\Gamma$ term on the Stripe-A and Stripe-D phase is tilting the moment orientation away from the cubic axes directions, yielding the Stripe-B and Stripe-C phase.
+Fig.~\ref{fig:Proabilities}(e) is a representative probability map for the Stripe-B phase.
+The probability takes maximum value at the direction determined by Eq.~\eqref{eq:S1}, which means that the moment direction changes with the model parameters $K$ and $\Gamma$.
+On the other hand, the case of the Stripe-C phase is rather different.
+The probability is clearly peaked at the direction given by Eq.~\eqref{eq:S0} with the maximum value $P_{max}$ considerably less than $\frac{1}{6}$ (see Fig.~\ref{fig:Proabilities}(d)).
+Apart from the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the cluster GS, quantum flucations may take responsibilities for the reduced probability.
 
-\section{Summary}
+\section{\label{sec:SectionVI}Summary}
 \textcolor{red}{Summary of our work. To be accomplished $\cdots \cdots$}
@@
 \section{Analysis of the classical energy and moment direction}
-
 \textcolor{red}{Analysis of the classical energy and moment direction. To be accomplished $\cdots \cdots$}

### 2020-03-23 paper/paper.tex
20200323 14:41

@@
 For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
-When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including a N\'{e}el phase, a phase with spin-wave selection of nontrivial ground states and a phase with incommensurate long-range order \cite{PhysRevB.42.4800,PhysRevB.46.11137}.
+When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a spin liquid state \cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111}.
 All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.
@@
 The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration.
-As pointed out by Jackeli and Khaliullin \cite{Khaliullin2005, PhysRevLett.102.017205}, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles.
-Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model.
-It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}$=1/2 moments.
+Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model.
+Khaliullin \emph{et al.,} \cite{Khaliullin2005, PhysRevLett.102.017205} proposed to realized this highly anisotropic spin model in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates $A_2$IrO$_3$ (A = Na, Li).
+In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra.
+The resulting Hamiltonian is the Kitaev-Heisenberg (KH) model.
+It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}.
 In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
 Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}.
-Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained.
+Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the KH model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained.
 However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.
@@
 The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}.
-Extensive studies of magnetic properties using neutron scattering \cite{Nature20614,nphys3971,PhysRevLett.117.267202,PhysRevX.8.031001}, muon spin relaxation ($\mu$SR) \cite{PhysRevLett.117.097201}, electron spin resonance (ESR) \cite{PhysRevLett.115.167203} reveal a possible gapless quantum spin liquid (QSL) ground state.
 More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
@@
 
-The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization methods are introduced in Sec.~\ref{sec:SectionII}.
+The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization (ED) methods are introduced in Sec.~\ref{sec:SectionII}.
 Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states.
@@
 \subsection{\label{sec:SectionIIB}Exact Diagonalization}
-We perform a Lanczos ED calculation of the GS energy of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC).
+We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC).
 To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics.
 Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified.
-The remaining phases were identified mainly by examining the static magnetic structure factor (SMSF)
-\begin{equation}
-    S(\bm{Q}) = \frac{1}{N} \sum_{ij} e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \langle \bm{S}_i \bm{\cdot} \bm{S}_j \rangle \label{eq:SMSF}
-\end{equation}
-where N is the total number of spins, $\bm{R}_i$ is the position of site $i$ and $\langle \bm{S}_i \bm{\cdot} \bm{S}_j \rangle$ is the average over the ground state.
+The remaining phases were identified mainly by examining the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$
+\begin{subequations}
+    \begin{align}
+        & S(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \bm{\cdot} \bm{S}_j | \Omega \rangle e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \label{eq:SMSF} \\
+        & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} G(\bm{k}, \omega) \label{eq:Akomega} \\
+        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j}) \\
+        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle
+    \end{align}
+\end{subequations}
+where $| \Omega \rangle$ and $E_0$ are the GS and ground state energy respectively, N is the total number of spins, $\bm{R}_i$ the position of site $i$, and $\eta = 0^+$.
 
-To extract the moment direction of a magnetic ordered phase from a cluster ground state, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}.
+To extract the moment direction of a magnetic ordered phase from a cluster GS, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}.
 The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions.
@@
 Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$.
-By calculating the overlap with the exact cluster GS, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.
+By calculating the overlap between the exact cluster GS and cluster spin-conherent states, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.
 
@@
 
-For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
+For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $S^x = 0$ which means that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
 An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction.
@@
 In this section, we turn to study the quantum phases in the $J-K-\Gamma$ model Hamiltonian.
-We consider a $4 \times 6$ cluster with PBC that has been used previously to study the HK model on triangular lattice \cite{KaiLi2015}.
+We consider a $4 \times 6$ cluster with PBC that has been used previously to study the KH model on triangular lattice \cite{KaiLi2015}.
 The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:PhaseDiagram}(a).
@@
 
-In the HK limit, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified in addition to the well-understood FM ($J=-1$)and 120$^\circ$ N\'{e}el ($J=1$) phases.
-Under the transformation, we obtain a collinear stripe order (see Fig.~\ref{fig:PhaseDiagram}(b)-(d)) from the original FM order and a noncollinear spiral order (dual N\'{e}el) from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)).
+For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$.
+As for the KH ($\Gamma=0$) mode, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified.
+Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(b)) and introduce the rotated spin operators $\bm{S}^{'}$: $\bm{S}_{0}^{'} = \bm{S}_0$ for sublattice 0, $\bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)$ for sublattice 1, $\bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)$ for sublattice 2, and $\bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)$ for sublattice 3.
+The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$.
+For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $\alpha^{'}=\alpha=\pi/2, tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$.
+When $\alpha=\pi/2, \beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$.
+Thus, transformating back to the original spin basis, a collinear stripe order can be obtained.
+Similarly, a noncollinear spiral order (dual N\'{e}el) at $\alpha=\pi/2, \beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)).
 The phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.
@@
 For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
-Take into account of the classical results, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}.
+Based on this observation, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}.
 In Fig.~\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit.
@@
 For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.
-\textcolor{red}{$\cdots \cdots$}
 
@@
 For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction.
-The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction(i.e., $x$, $y$, $z$ direction).
+The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction).
 However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction.
-To extract the moment direction of the FM-A and FM-C phases, we construct the following cluster spin-coherent state
-\begin{equation}
-    |\Psi(\theta, \phi) \rangle = \bigotimes_{i=1}^N|\theta,\phi \rangle
-\end{equation}
-and calculate the probabilities $P(\theta, \phi)$ with varying $\theta$ and $\phi$.
+To extract the moment direction of the FM-A and FM-C phases, we calculate the probabilities $P(\theta, \phi)$ with varying $\theta$s and $\phi$s.
 The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).
-For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane with all directions degenerate, as expected from classical considerations (see the green dashed line).
-As for the FM-C phase, the probability is clearly peaked at the direction perpendicular to the lattice plane which is also consistent with our classical analysis (marked by the green solid circle).
+For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.
+The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(b)).
 

### 2020-03-25 paper/paper.tex
20200325 15:34

@@
     \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron.
-(b) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively.
-The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation.
-(c) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron.
-The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.}
+(b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron.
+The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.
+(c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively.
+The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see tha main text for detailed information.
+(d) The k-points in the first Brillouin zone corresponding to a 4 $\times$ 6 cluster with 4 lattice sites along the $x$-bond direction and 6 lattice sites along the $y$-bond direction.}
 \end{figure}
@@
 Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified.
-The remaining phases were identified mainly by examining the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$
+To have a better understanding of the characteristics of the remaining phases, we examine the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$ of these phases.
+$S(\bm{Q})$ and $A(\bm{k}, \omega)$ are defined as follow:
 \begin{subequations}
@@
         & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} G(\bm{k}, \omega) \label{eq:Akomega} \\
-        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j}) \\
-        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle
+        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)} \\
+        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle \label{eq:GreenFunction}
     \end{align}
@@
 is fully polaried along the $(\theta, \phi)$ direction.
-Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(c)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$.
+Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$.
 By calculating the overlap between the exact cluster GS and cluster spin-conherent states, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.
@@
 \begin{equation}
-    E_{FM}^{c} = (3J + K) + 2 \Gamma (S^x S^y + S^y S^z + S^z S^x) \label{eq:EcFM}
+    E_{FM}^{c} = (3J + K) + 2 \Gamma (v^x v^y + v^y v^z + v^z v^x) \label{eq:EcFM}
 \end{equation}
-where $S^x$, $S^y$, $S^z$ are the corresponding components of the classical moment vector.
-On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(S^x, S^y, S^z) = S^xS^y + S^yS^z + S^zS^x$ with the constraint $|\bm{S}| = 1$.
-$f(S^x, S^y, S^z)$ takes maximum value $f_{max}=1$ at $S^x=S^y=S^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $S^x + S^y + S^z = 0$ and $|\bm{S}| = 1$ are fulfilled.
-The condition $S^x + S^y + S^z = 0$ specify a plane that is perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c) this is actually the plane of the triangular lattice.
-That is to say, for $\Gamma > 0$ the moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the moment would perpendicular to the lattice plane.
+where $v^x$, $v^y$, $v^z$ are the corresponding components of the classical moment vector.
+On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(v^x, v^y, v^z) = v^x v^y + v^y v^z + v^z v^x$ with the constraint $|\bm{v}| = 1$.
+$f(v^x, v^y, v^z)$ takes maximum value $f_{max}=1$ at $v^x=v^y=v^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $v^x + v^y + v^z = 0$ and $|\bm{v}| = 1$ are fulfilled.
+The condition $v^x + v^y + v^z = 0$ specifies a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction.
+Considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) this is actually the plane of the triangular lattice.
+That is to say, for $\Gamma > 0$ the ordered moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the ordered moment would perpendicular to the lattice plane.
 
@@
 When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix A for details).
-Based on these observation, it is reasonable to say that the ground state of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions.
-For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM order as the ground state which was verified by our Monte Carlo simulation.
+Based on these observation, it is reasonable to say that the GS of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions.
+For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM ordered state as the GS.
 On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS.
@@
 \begin{eqnarray}
-    E_{StripeX}^{c} & = & -(J + K) + 2 K S^x S^x \nonumber \\
-        & & +\: 2 \Gamma (S^y S^z - S^z S^x - S^x S^y) \label{eq:EcStripeX}
+    E_{StripeX}^{c} & = & -(J + K) + 2 K v^x v^x \nonumber \\
+        & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y) \label{eq:EcStripeX}
 \end{eqnarray}
 and the energy for spin configuration in Fig.~\ref{fig:PhaseDiagram}(c) and \ref{fig:PhaseDiagram}(d) can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$.
-The moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$.
-In general ($J,K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has three extreme points where the first derivatives equal zero
+The ordered moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$.
+In general ($J,K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has three extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ equal zero
 \begin{subequations}
@@
     \begin{align}
-        & \mathbf{S}_0: \quad S_{0}^{y}=-S_{0}^{z} = \pm1/\sqrt{2}, \quad S_{0}^{x} = 0 \label{eq:S0} \\
-        & \mathbf{S}_1: \quad S_{1}^{y}=S_{1}^{z} = f_{1}(K, \Gamma), \quad S_{1}^{x} = g_{1}(K, \Gamma) S_{1}^{y} \label{eq:S1} \\
-        & \mathbf{S}_2: \quad S_{2}^{y}=S_{2}^{z} = f_{2}(K, \Gamma), \quad S_{2}^{x} = g_{2}(K, \Gamma) S_{2}^{y} \label{eq:S2}
+        & \mathbf{v}_0: \quad v_{0}^{y}=-v_{0}^{z} = \pm1/\sqrt{2}, \quad v_{0}^{x} = 0 \label{eq:v0} \\
+        & \mathbf{v}_1: \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), \quad v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y} \label{eq:v1} \\
+        & \mathbf{v}_2: \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), \quad v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y} \label{eq:v2}
     \end{align}
@@
 
-For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $S^x = 0$ which means that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
-An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{S}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{S}_1$ direction.
-When $\Gamma=0, K<0$, the moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{S}_1$ direction.
+For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $v^x = 0$ which means that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
+An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{v}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{v}_1$ direction.
+When $\Gamma=0, K<0$, the ordered moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{v}_1$ direction.
 All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation.
 However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$.
+The GS of the classical HK model near the antiferromagetic Kitaev point ($K=1$) is high degenerate and both positive and negative $\Gamma$ interactions select specific stripe ordered state as the GS.
 
@@
 As for the KH ($\Gamma=0$) mode, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified.
-Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(b)) and introduce the rotated spin operators $\bm{S}^{'}$: $\bm{S}_{0}^{'} = \bm{S}_0$ for sublattice 0, $\bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)$ for sublattice 1, $\bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)$ for sublattice 2, and $\bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)$ for sublattice 3.
+Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and introduce the rotated spin operators $\bm{S}^{'}$: $\bm{S}_{0}^{'} = \bm{S}_0$ for sublattice 0, $\bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)$ for sublattice 1, $\bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)$ for sublattice 2, and $\bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)$ for sublattice 3.
 The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$.
@@
 Similarly, a noncollinear spiral order (dual N\'{e}el) at $\alpha=\pi/2, \beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)).
-The phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.
+Apart from these well-established phases, the phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.
 
@@
 \end{figure}
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
+    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for different model parameters.
+The $A(\bm{k}, \omega)$ is draw along the $M-\Gamma-M$ path in the first BZ.
+For the 4 $\times$ 6 cluster we use, there are 24 nonequivalent k-points in the first BZ, and 7 k-points on the $M-\Gamma-M$ path, see Fig.~\ref{fig:ModelDefinition}(d)}
+\end{figure}
 
 When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid.
-To identify the remaining phases and providing more information of these phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}.
+To identify the remaining phases, we calculate the SMSF and spin excitation spectrum for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors} and Fig.~\ref{fig:Spectrum}.
 For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
 Based on this observation, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}.
+The ground states of the quantum model in these area are similar to their classical analogue except for the pure $\Gamma$ model.
+For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order.
+However, for the quantum model, quantum flucations select the FM ordered states as GS out of an otherwise infinitely degenerate manifold of classical states.
+This selection of states among a continuum is the so called "order-from-disorder" mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.
+
 In Fig.~\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit.
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
+    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
     \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS.

### 2020-03-26 paper/paper.tex
20200326 12:43
Signed-off-by: wangshiphys <wangshiphys@gmail.com>

@@
 (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively.
-The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see tha main text for detailed information.
-(d) The k-points in the first Brillouin zone corresponding to a 4 $\times$ 6 cluster with 4 lattice sites along the $x$-bond direction and 6 lattice sites along the $y$-bond direction.}
+The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see tha main text for detailed information.}
 \end{figure}
@@
 \end{figure}
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
-    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for different model parameters.
-The $A(\bm{k}, \omega)$ is draw along the $M-\Gamma-M$ path in the first BZ.
-For the 4 $\times$ 6 cluster we use, there are 24 nonequivalent k-points in the first BZ, and 7 k-points on the $M-\Gamma-M$ path, see Fig.~\ref{fig:ModelDefinition}(d)}
-\end{figure}
 
 When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid.
-To identify the remaining phases, we calculate the SMSF and spin excitation spectrum for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors} and Fig.~\ref{fig:Spectrum}.
+To identify the remaining phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}.
 For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
@@
 This selection of states among a continuum is the so called "order-from-disorder" mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.
+Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM ordered state is selected as the GS.
 
-In Fig.~\ref{fig:StructureFactors}(c)-(e), the SMSF peaked at the M-points indicating that the stripe ordered GS of the classical model persist in the quantum limit.
+For these areas marked as Stripe-A, Stripe-B, Stripe-C and Stripe-D in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(c)-(e).
+For all of these model parameters, the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) indicating that the stripe ordered GS of the classical model persist in the quantum limit.
 It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state.
 The four stripe phases designated as Stripe-A, Stripe-B, Stripe-C, Stripe-D in Fig.~\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction.
+
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
+    \caption{\label{fig:Spectrum}(Color online) (a) The k-points in the first Brillouin zone corresponding to a 4 $\times$ 6 cluster with 4 lattice sites along the $x$-bond direction and 6 lattice sites along the $y$-bond direction.
+(b) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$.
+The $A(\bm{k}, \omega)$ is draw along the path shown in (a).}
+\end{figure}
+
 Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:PhaseDiagram}(a).
-For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ and Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.
+For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ.
+Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.
+To have further understanding of the characteristics of this phase, we also calculate the spin excitation spectrum and a typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}(b).
+The high intensities at both the center and M-points of the first BZ is consistent with SMSF data.
+Moreover, there are continuum spectrum at high energy which is a characteristic of QSL.
+However, the $A(\mathbf{k}, \omega)$ does not have intensities at $\omega = 0$ which indicates the system described by the corresponding model Hamiltonian is gapped.
+Combined with all of the above results, we propose the GS of quantum $J-K-\Gamma$ model at the green area is a gapped QSL.
 

### 2020-03-26 paper/paper.tex
20200326 13:51
Signed-off-by: wangshiphys <wangshiphys@gmail.com>

@@
 Fig.~\ref{fig:Proabilities}(e) is a representative probability map for the Stripe-B phase.
-The probability takes maximum value at the direction determined by Eq.~\eqref{eq:S1}, which means that the moment direction changes with the model parameters $K$ and $\Gamma$.
+The probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, which means that the moment direction changes with the model parameters $K$ and $\Gamma$.
 On the other hand, the case of the Stripe-C phase is rather different.
-The probability is clearly peaked at the direction given by Eq.~\eqref{eq:S0} with the maximum value $P_{max}$ considerably less than $\frac{1}{6}$ (see Fig.~\ref{fig:Proabilities}(d)).
+The probability is clearly peaked at the direction given by Eq.~\eqref{eq:v0} with the maximum value $P_{max}$ considerably less than $\frac{1}{6}$ (see Fig.~\ref{fig:Proabilities}(d)).
 Apart from the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the cluster GS, quantum flucations may take responsibilities for the reduced probability.
@@
 \section{\label{sec:SectionVI}Summary}
-\textcolor{red}{Summary of our work. To be accomplished $\cdots \cdots$}
+In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model.
+The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the antiferromagetic $\Gamma$ point.
+We propose the QSL to be gapped based on the spin excitation spectrum.
+Apart from this QSL phase, we also provide detailed description of the distinctions between those collinear phases.
+Especially, we propose the GS of the antiferromagetic Kitaev model to be a stripe ordered state and the ordered moment along the $x, y, z$-axis direction.
 

### 2020-03-28 paper/paper.tex
20200328 23:21
Signed-off-by: wangshiphys <wangshiphys@gmail.com>

@@
 % The following are the Appendixes of this article
+\newpage
 \appendix
 
-\section{Analysis of the classical energy and moment direction}
-\textcolor{red}{Analysis of the classical energy and moment direction. To be accomplished $\cdots \cdots$}
+\section{Classical energy and moment direction of the stripe ordered states}
+For classical stripe ordered states, all the spins are collinear and there are three degenerate spin configurations as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) in the main text.
+The corresponding energies of the classical $J-K-\Gamma$ model for these spin configurations are
+\begin{subequations}
+    \begin{eqnarray}
+        E_{StripeX}^{c} & = & -(J + K) + 2 K v^x v^x \nonumber \\
+            & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y)
+            \label{eq:AEcStripeX} \\
+        E_{StripeY}^{c} & = & -(J + K) + 2 K v^y v^y \nonumber \\
+            & & +\: 2 \Gamma (v^z v^x - v^x v^y - v^y v^z)
+            \label{eq:AEcStripeY} \\
+        E_{StripeZ}^{c} & = & -(J + K) + 2 K v^z v^z \nonumber \\
+            & & +\: 2 \Gamma (v^x v^y - v^y v^z - v^z v^x)
+            \label{eq:AEcStripeZ}
+    \end{eqnarray}
+\end{subequations}
+where $v^x$, $v^y$, $v^z$ are the corresponding components of the classical spin vector.
+The ordered moment direction of the classical stripe order is determined by the anisotropic parameters $K$ and $\Gamma$ and can be obtained by finding the global minimum of $E_{StripeX}^{c}$, $E_{StripeY}^{c}$ and $E_{StripeZ}^{c}$ with the constraint $|\bm{v}|=1$.
+It is clear from Eq.~\eqref{eq:AEcStripeX}, Eq.~\eqref{eq:AEcStripeY} and Eq.~\eqref{eq:AEcStripeZ}, if $\bm{v}_{min}$ minimize the energy, then $-\bm{v}_{min}$ also minimize the energy.
+Here we only consider one of the direction.
+
+When $\Gamma=0$, it can be clearly seen from Eq.~\eqref{eq:AEcStripeX}, $E_{StripeX}^c$ takes minimum value at $v^x=0$ for positive $K$ and $v^x=1$ for negative $K$.
+When the $\Gamma$ interaction is included, the problem becomes a little more complex.
+To find the unit vector $\bm{v}_{min}$ that minimize $E_{StripeX}^{c}$, we use the Lagrange multiplier method.
+For $\Gamma>0, K=0$, $E_{StripeX}^{c}$ takes minimum value when the condition $v^x=v^y+v^z$ is fulfilled.
+On the other hand, when $\Gamma<0, K=0$, there are only two vectors that minimize $E_{StripeX}^{c}$, i.e., $v^y=v^z=-v^x=\pm 1/\sqrt{3}$.
+
+More generally, if both $K, \Gamma \neq 0$, $E_{StripeX}^{c}$ has six extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ equal zero.
+Here we give three of them explicitly and the other three are opposite to the given ones
+\begin{subequations}
+    \begin{eqnarray}
+        & \bm{v}_0: \quad v_{0}^{y}=-v_{0}^{z} = 1/\sqrt{2}, & v_{0}^{x} = 0 \\
+        & \bm{v}_1: \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), & v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y} \\
+        & \bm{v}_2: \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), & v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y}
+    \end{eqnarray}
+\end{subequations}
+and
+\begin{subequations}
+    \begin{eqnarray}
+        \lambda_{1} & = &- (\Gamma +2 K - \sqrt{9\Gamma^2 - 4 \Gamma K + 4 K^2}) / 4 \nonumber \\
+        \lambda_{2} & = & -(\Gamma +2 K + \sqrt{9\Gamma^2 + 4 \Gamma K + 4 K^2}) / 4 \nonumber \\
+        f_{1,2}(K, \Gamma) & = & \frac{|\Gamma|}{\sqrt{4 \lambda_{1,2} (\lambda_{1,2} + \Gamma) + 3 \Gamma^{2}}} \\
+        g_{1,2}(K, \Gamma) & = & (2 \lambda_{1,2} + \Gamma) / \Gamma
+    \end{eqnarray}
+\end{subequations}
+For a specific $K$ and $\Gamma$, by comparing the values of $E_{StripeX}^{c}$ at $\bm{v}_0$, $\bm{v}_1$ and $\bm{v}_2$ we can determine the global minimum of $E_{StripeX}^{c}$ and the corresponding $\bm{v}_{min}$.
+When both $\Gamma$ and $K$ are positive, $E_{StripeX}^{c}$ takes minimum value at the direction determined by $\bm{v}_0$.
+Otherwise, $\bm{v}_1$ specifies the direction where $E_{StripeX}^{c}$ has lowest energy.
+
+The similar analysis can be applied to $E_{StripeY}^{c}$ and $E_{StripeZ}^{c}$ and the ordered moment direction that minimize the classical energy can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$ of the results for $E_{StripeX}^{c}$.
+
+\section{Classical ground states for some special model parameters}
+
+\subsection{$J=K=0, \Gamma=1$}
+For pure antiferromagetic $\Gamma$ model, the classical ground state is highly degenerate including FM state as well as states with no long range order.
+The ordered moment of the FM state lie in a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction.
+Fig.~\ref{fig:SpinConfig}(a) show a typical spin configuration of those disordered states that have the same energy as the FM state.
+
+\subsection{$J=K=0, \Gamma=-1$}
+For pure ferromagnetic $\Gamma$ model, we found several energetically degenerate states as the classcial ground state, including FM state, stripe states and a noncollinear state.
+The FM state is shown in Fig.~\ref{fig:SpinConfig}(b) and the ordered moment is along the $[111]$ direction.
+As for the stripe states, there are three degenerate spin configurations as shown in Fig.~\ref{fig:SpinConfig}(c)-(e) and the directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively.
+Apart from these collinear states, a noncollinear state exist as the classical ground state.
+The magnetic unit-cell contains four lattice sites.
+The directions for the yellow, gray, pink, cyan arrows in Fig.~\ref{fig:SpinConfig}(f) are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.
+
+\subsection{$J=\Gamma=0, K=1$}
+The ground state for the classical antiferromagetic Kitaev model is also degenerate involving three nematic ordered states and three stripe ordered states.
+For the nematic ordered state shown in Fig.~\ref{fig:SpinConfig}(g), the spins on the chains along the $x$-bond direction form antiferromagetic chains and the direction for the orange arrow is $[100]$.
+There is no association between different chains.
+Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:SpinConfig}(h) and Fig.~\ref{fig:SpinConfig}(i) respectively.
+The direction for the orange arrow in Fig.~\ref{fig:SpinConfig}(h) is $[010]$ and in Fig.~\ref{fig:SpinConfig}(i) is $[001]$.
+In addition to these nematic ordered states, there are stripe ordered states that have the same energy as the nematic ordered states.
+They have the same pattern as that is shown in Fig.~\ref{fig:SpinConfig}(c)-(e), but with different ordered moment directions.
+For the stripe ordered states shown in Fig.~\ref{fig:SpinConfig}(c)-(e) the ordered moment lie in the $yz$, $xz$ and $xy$ plane, respectively.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.96\textwidth]{FigA4.pdf}
+    \caption{\label{fig:SpinConfig}(Color online) Classical ground state spin configurations for some special model parameters.
+For subfigure (a)-(f), the spin vectors were projected to the $xy$ plane and different spin vectors were represented by different colors.
+(a) Typical disordered spin configuration for $J=K=0,\Gamma=1$.
+(b)-(f) Spin configurations for $J=K=0,\Gamma=-1$.
+(g)-(i) Nematic ordered spin configurations for $J=\Gamma=0, K=1$.}
+\end{figure*}
 

### 2020-03-29 paper/paper.tex
20200329 11:17
Signed-off-by: wangshiphys <wangshiphys@gmail.com>

@@
 \subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
-For the classical FM order, the energy of the $J-K-\Gamma$ model per lattice site is given by
+For the classical FM order, all spins are aligned in parallel and the energy of the $J-K-\Gamma$ model per lattice site is given by
 \begin{equation}
@@
 For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found.
-When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix A for details).
+When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix~\ref{apx:AppendixA} for details).
 Based on these observation, it is reasonable to say that the GS of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions.
@@
 In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig.~\ref{fig:PhaseDiagram}(b)-(d).
-For the spin configuration shown in Fig.~\ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} is
+For the spin configuration shown in Fig.~\ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} per lattice site is
 \begin{eqnarray}
@@
 The ordered moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$.
-In general ($J,K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has three extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ equal zero
+In general ($K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has six extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ equal zero.
+Here we give three of them explicitly and the other three are opposite to the given ones
 \begin{subequations}
     \label{eq:whole}
-    \begin{align}
-        & \mathbf{v}_0: \quad v_{0}^{y}=-v_{0}^{z} = \pm1/\sqrt{2}, \quad v_{0}^{x} = 0 \label{eq:v0} \\
-        & \mathbf{v}_1: \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), \quad v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y} \label{eq:v1} \\
-        & \mathbf{v}_2: \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), \quad v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y} \label{eq:v2}
-    \end{align}
+    \begin{eqnarray}
+        & \bm{v}_0:& \quad v_{0}^{y}=-v_{0}^{z} = 1/\sqrt{2}, \quad v_{0}^{x} = 0 \label{eq:v0} \\
+        & \bm{v}_1:& \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), \quad v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y} \label{eq:v1} \\
+        & \bm{v}_2:& \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), \quad v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y} \label{eq:v2}
+    \end{eqnarray}
 \end{subequations}
-see Appendix B for their explicit expressions.
+see Appendix~\ref{apx:AppendixB} for their explicit expressions.
 
 For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $v^x = 0$ which means that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
-An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\mathbf{v}_0$ direction whereas negative $\Gamma$ drives it to the $\mathbf{v}_1$ direction.
-When $\Gamma=0, K<0$, the ordered moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\mathbf{v}_1$ direction.
+An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction whereas negative $\Gamma$ drives it to the $\bm{v}_1$ direction.
+When $\Gamma=0, K<0$, the ordered moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\bm{v}_1$ direction.
 All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation.
-However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$.
+However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$ (see Appendix~\ref{apx:AppendixA} for details).
 The GS of the classical HK model near the antiferromagetic Kitaev point ($K=1$) is high degenerate and both positive and negative $\Gamma$ interactions select specific stripe ordered state as the GS.
@@
 
-\section{Classical energy and moment direction of the stripe ordered states}
+\section{\label{apx:AppendixA}Classical ground states for some special model parameters}
+
+\subsection{$J=K=0, \Gamma=1$}
+For pure antiferromagetic $\Gamma$ model, the classical ground state is highly degenerate including FM state as well as states with no long range order.
+The ordered moment of the FM state lie in a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction.
+Fig.~\ref{fig:GSForPositiveGamma} show a typical spin configuration of those disordered states that have the same energy as the FM state.
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{FigA1.pdf}
+    \caption{\label{fig:GSForPositiveGamma}(Color online) Typical disordered ground state for $J=K=0, \Gamma=1$.
+The 3D unit spin vectors were projected to the $xy$ plane and different vectors were represented by different colors.}
+\end{figure}
+
+\subsection{$J=K=0, \Gamma=-1$}
+For pure ferromagnetic $\Gamma$ model, we found several energetically degenerate states as the classcial ground state, including FM state, stripe states and a noncollinear state.
+The ordered moment of the FM state along the $[111]$ direction.
+As for the stripe states, there are three degenerate spin configurations as shown in Fig.~\ref{fig:GSForNegativeGamma}(a)-(c) and the directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively.
+Apart from these collinear states, a noncollinear state exist as the classical ground state.
+The magnetic unit-cell contains four lattice sites.
+The directions for the yellow, gray, pink, cyan arrows in Fig.~\ref{fig:GSForNegativeGamma}(d) are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{FigA2.pdf}
+    \caption{\label{fig:GSForNegativeGamma}(Color online) Typical ground state spin configurations for $J=K=0, \Gamma=-1$.
+The 3D unit spin vectors were projected to the $xy$ plane and different vectors were represented by different colors.
+(a)-(c) Stripe ordered states.
+The directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively.
+(d) Noncollinear state.
+The directions for the yellow, gray, pink, cyan arrows are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.}
+\end{figure}
+
+\subsection{$J=\Gamma=0, K=1$}
+The ground state for the classical antiferromagetic Kitaev model is also degenerate involving three nematic ordered states and three stripe ordered states.
+For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(a), the spins on the chains along the $x$-bond direction form antiferromagetic chains and the direction for the orange arrow is $[100]$.
+There is no association between different chains.
+Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(b) and Fig.~\ref{fig:GSForPositiveK}(c) respectively.
+The direction for the orange arrow in Fig.~\ref{fig:GSForPositiveK}(b) is $[010]$ and in Fig.~\ref{fig:GSForPositiveK}(c) is $[001]$.
+In addition to these nematic ordered states, there are stripe ordered states that have the same energy as the nematic ordered states.
+For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(d)-(f), the corresponding ordered moment lie in the $yz$, $xz$ and $xy$ plane, respectively.
+\begin{figure}
+    \includegraphics[width=0.5\textwidth]{FigA3.pdf}
+    \caption{\label{fig:GSForPositiveK}(Color online) Nematic and stripe ground state spin configurations for $J=\Gamma=0, K=1$.}
+\end{figure}
+
+\section{\label{apx:AppendixB}Classical energy and moment direction of the stripe ordered states}
 For classical stripe ordered states, all the spins are collinear and there are three degenerate spin configurations as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) in the main text.
@@
 
-\section{Classical ground states for some special model parameters}
-
-\subsection{$J=K=0, \Gamma=1$}
-For pure antiferromagetic $\Gamma$ model, the classical ground state is highly degenerate including FM state as well as states with no long range order.
-The ordered moment of the FM state lie in a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction.
-Fig.~\ref{fig:SpinConfig}(a) show a typical spin configuration of those disordered states that have the same energy as the FM state.
-
-\subsection{$J=K=0, \Gamma=-1$}
-For pure ferromagnetic $\Gamma$ model, we found several energetically degenerate states as the classcial ground state, including FM state, stripe states and a noncollinear state.
-The FM state is shown in Fig.~\ref{fig:SpinConfig}(b) and the ordered moment is along the $[111]$ direction.
-As for the stripe states, there are three degenerate spin configurations as shown in Fig.~\ref{fig:SpinConfig}(c)-(e) and the directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively.
-Apart from these collinear states, a noncollinear state exist as the classical ground state.
-The magnetic unit-cell contains four lattice sites.
-The directions for the yellow, gray, pink, cyan arrows in Fig.~\ref{fig:SpinConfig}(f) are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.
-
-\subsection{$J=\Gamma=0, K=1$}
-The ground state for the classical antiferromagetic Kitaev model is also degenerate involving three nematic ordered states and three stripe ordered states.
-For the nematic ordered state shown in Fig.~\ref{fig:SpinConfig}(g), the spins on the chains along the $x$-bond direction form antiferromagetic chains and the direction for the orange arrow is $[100]$.
-There is no association between different chains.
-Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:SpinConfig}(h) and Fig.~\ref{fig:SpinConfig}(i) respectively.
-The direction for the orange arrow in Fig.~\ref{fig:SpinConfig}(h) is $[010]$ and in Fig.~\ref{fig:SpinConfig}(i) is $[001]$.
-In addition to these nematic ordered states, there are stripe ordered states that have the same energy as the nematic ordered states.
-They have the same pattern as that is shown in Fig.~\ref{fig:SpinConfig}(c)-(e), but with different ordered moment directions.
-For the stripe ordered states shown in Fig.~\ref{fig:SpinConfig}(c)-(e) the ordered moment lie in the $yz$, $xz$ and $xy$ plane, respectively.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.96\textwidth]{FigA4.pdf}
-    \caption{\label{fig:SpinConfig}(Color online) Classical ground state spin configurations for some special model parameters.
-For subfigure (a)-(f), the spin vectors were projected to the $xy$ plane and different spin vectors were represented by different colors.
-(a) Typical disordered spin configuration for $J=K=0,\Gamma=1$.
-(b)-(f) Spin configurations for $J=K=0,\Gamma=-1$.
-(g)-(i) Nematic ordered spin configurations for $J=\Gamma=0, K=1$.}
-\end{figure*}
-
 \newpage

### 2020-03-30 paper/paper.tex
20200330 20:30
Signed-off-by: wangshiphys <wangshiphys@gmail.com>

@@
 
+\subsection{\label{subsec:HKLimit}Phases in the HK limit ($\Gamma=0$)}
 For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$.
-As for the KH ($\Gamma=0$) mode, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases were identified.
-Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and introduce the rotated spin operators $\bm{S}^{'}$: $\bm{S}_{0}^{'} = \bm{S}_0$ for sublattice 0, $\bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)$ for sublattice 1, $\bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)$ for sublattice 2, and $\bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)$ for sublattice 3.
+As for the HK ($\Gamma=0$) model, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases can be identified.
+Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and introduce the rotated spin operators $\bm{S}^{'}$
+\begin{align*}
+    & \bm{S}_{0}^{'} = \bm{S}_{0}& \quad \text{for sublattice 0} \\
+    & \bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1} \\
+    & \bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2} \\
+    & \bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}
+\end{align*}
 The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$.
-For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $\alpha^{'}=\alpha=\pi/2, tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$.
-When $\alpha=\pi/2, \beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$.
+For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$.
+When $\beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$.
 Thus, transformating back to the original spin basis, a collinear stripe order can be obtained.
-Similarly, a noncollinear spiral order (dual N\'{e}el) at $\alpha=\pi/2, \beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)).
+Similarly, a noncollinear spiral order (dual N\'{e}el) at $\beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)).
+
 Apart from these well-established phases, the phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.
+To determine the GS of HK model in this area, we calculate the SMSF at $K=1$ and the resulting profile is shown in Fig.~\ref{fig:StructureFactors}(c).
+It is clear from Fig.~\ref{fig:StructureFactors}(c) that the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) which is a typical characteristic of stripe ordered states.
+
+To have further insight into these phases, we adopt the method introduced in Ref~\onlinecite{PhysRevB.94.064435} to extract the moment directions for some of these phases.
+For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction.
+The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction).
+In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis.
+As for stripe ordered states, there are three degenerate patterns in real space as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern.
+Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
+For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps for the representative model parameters of the Stripe-A and Stripe-D phase are shown in Fig.~\ref{fig:Proabilities}(c) and Fig.~\ref{fig:Proabilities}(f).
+The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction.
+The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit.
+On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(f) indicates that the ordered moment pointing to the $y$ and $z$-axis direction.
+The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it a signature of large quantum flucations in the ground state.
+It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states.
+This selection of states among a continuum is the so called "order-from-disorder" mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.
+
+In a word, for the HK model, apart from these well established phases, our ED calculations provide evidence that the GS of the model near the AF Kitaev point is stripe ordered states.
+However, Stripe-D different from Stripe-A in the direction of the ordered moment direction.
+To be specific, for a certain spin pattern, the ordered moment would along only one of the $x, y, z$-axis direction in the Stripe-A phase and point to the other two axes directions for the Stripe-D phase.
 
@@
 \end{figure}
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
+    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
+The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c).
+The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.
+(a)-(b) Probability maps for the FM states in the FM-A and FM-C phase, respectively.
+(c)-(f) Proability maps for the stripe states in the Stripe-A, Stripe-B, Stripe-C and Stripe-D phase, respectively.}
+\end{figure}
 
-When the off-diagonal $\Gamma$ term is included, the transforamtion is no longer valid.
-To identify the remaining phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}.
+\subsection{\label{subsec:GammaEffects}Effects of the $\Gamma$ term}
+When the off-diagonal $\Gamma$ term is included, the FST is no longer valid.
+To study the nature of these remaining phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}.
 For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
-Based on this observation, we propose the three blue areas with different shadings in the global phase diagram (see Fig.~\ref{fig:PhaseDiagram}) to be FM ordered phases (i.e., FM-A, FM-B, FM-C) and they different from each other in the direction of the ordered moment which will be discussed in the Sec.~\ref{sec:SectionV}.
-The ground states of the quantum model in these area are similar to their classical analogue except for the pure $\Gamma$ model.
+Bases on this observation, we propose the areas containing the $\Gamma=\pm 1$ points in the global phase diagram to be FM ordered phases (i.e., FM-A, FM-C).
+To further confirm our hypothesis, we construct cluster spin-coherent states with all the spins are polarized along the $(\theta, \phi)$ direction.
+By inspecting the probability map $P(\theta, \phi)$, we can measure the presence of the cluster spin-coherent states in the exact cluster GS.
+The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).
+The large overlap between the exact cluster GS and FM ordered cluster spin-coherent state provides solid evidence that the corresponding areas are FM phases.
+For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.
+The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(b)).
+The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model.
 For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order.
-However, for the quantum model, quantum flucations select the FM ordered states as GS out of an otherwise infinitely degenerate manifold of classical states.
-This selection of states among a continuum is the so called "order-from-disorder" mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.
-Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM ordered state is selected as the GS.
+However, for the quantum model, quantum flucations select the FM ordered states lie in the lattice plane as GS out of an otherwise infinitely degenerate manifold of classical states.
+Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM state perpendicular to the lattice plane is selected as the GS.
+In the HK limit, the GS of the model near the $J=-1$ point is FM state and the ordered moment is fixed to the $x,y,z$-axis direction by the Kitaev interaction.
+When an infinitesimal $\Gamma$ interaction is introduced, positive couplings drive the ordered moment to the lattice plane and negative couplings pinning the ordered moment to be perpendicular to the lattice plane.
 
-For these areas marked as Stripe-A, Stripe-B, Stripe-C and Stripe-D in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(c)-(e).
-For all of these model parameters, the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) indicating that the stripe ordered GS of the classical model persist in the quantum limit.
-It is worth to note that even the GS of the classical model near the AF Kitaev point was identified to be nematic ordered which is energetically degenerate with the stripe state, our ED results favor the idea that quantum flucations would select a stripe state.
-The four stripe phases designated as Stripe-A, Stripe-B, Stripe-C, Stripe-D in Fig.~\ref{fig:PhaseDiagram}(a) different from each other only in the moment direction.
+For these areas marked as Stripe-B and Stripe-C in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(e) and Fig.~\ref{fig:StructureFactors}(d).
+For all of these model parameters, the SMSF peaked at the M-points indicating stripe ordered GS in these areas.
+To test the presence of the classical stripe ordered states, we construct cluster spin-coherent states based on the spin pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(d) and Fig.~\ref{fig:Proabilities}(e).
+When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$.
+Considering the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the exact cluster GS, it is reasonable to say that the stripe ordered ground states for the classical $J-K-\Gamma$ model in these areas persist in the quantum limit and the ordered moments of the quantum states coincide with their classical analogue.
+The reduced probabilities $P_{max} < \frac{1}{6}$ may be attributed to quantum flucations.
+In the HK limit, there exist a stripe phase (i.e., Stripe-A) when $J>0, K<0$ and the ordered moment along the $x,y,z$-axis direction.
+When an infinitesimal $\Gamma$ interaction is included, both positive and negative couplings tilting the ordered moment orientation away from the cubic axes directions, yielding the Stripe-B phase.
+The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
+%When $\Gamma \rightarrow 0^{+}$ or $\Gamma \rightarrow 0^{-}$, the direction determined by Eq.~\eqref{eq:v1} tend to be the same as the $x$-axis direction which means the phase transition from positive $\Gamma$ to negative $\Gamma$ is continuous.%
+As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different.
+An infinitesimal positive $\Gamma$ interaction changes the ordered moment orientation from the cubic axes directions to the direction specified by Eq.~\eqref{eq:v0} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
+On the other hand, when an infinitesimal negative $\Gamma$ interaction is introduced, the ordered moment is rotated to the direction determined by Eq.~\eqref{eq:v1} and its equivalents.
 
@@
 To have further understanding of the characteristics of this phase, we also calculate the spin excitation spectrum and a typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}(b).
-The high intensities at both the center and M-points of the first BZ is consistent with SMSF data.
+The high intensities at both the center and M-points of the first BZ is consistent with the SMSF data.
 Moreover, there are continuum spectrum at high energy which is a characteristic of QSL.
@@
 
-\section{\label{sec:SectionV}Moment Direction-Exact Diagonalization Results}
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
-    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
-The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c).
-The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.
-(a)-(b) Probability maps for the FM states in the FM-A and FM-C phase, respectively.
-(c)-(f) Proability maps for the stripe states in the Stripe-A, Stripe-B, Stripe-C and Stripe-D phase, respectively.}
-\end{figure}
-
-Having map out the global phase diagram of the $J-K-\Gamma$ model, we now move to the moment direction of these FM and stripe phases which provides key characteristic to distinguish them.
-Since the cluster spin-coherent state is captured by only a single pair ($\theta$, $\phi$) for collinear phases (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
-
-\subsection{\label{sec:SectionVA}Moment direction of the FM phases}
-For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction.
-The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction).
-However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction.
-To extract the moment direction of the FM-A and FM-C phases, we calculate the probabilities $P(\theta, \phi)$ with varying $\theta$s and $\phi$s.
-The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).
-For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.
-The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(b)).
-
-\subsection{\label{sec:SectionVB}Moment direction of the stripe phases}
-The stripe phases have three degenerate patterns as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern.
-For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and present the probability maps in Fig.~\ref{fig:Proabilities}(c)-(f) for Stripe-A, Stripe-B, Stripe-C, Stripe-D respectively.
-In the HK limit, the Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit (see Fig.~\ref{fig:Proabilities}(c)).
-As for the Stripe-D phase near the AF Kitaev point, the probability map Fig.~\ref{fig:Proabilities}(f) reveals the moment being constrained to the vicinity of the $yz$ plane, as predicted by classical analysis.
-Within this plane, the order-from-disorder mechanism selects the cubic axes $y$ and $z$ where the probability reaches its maxima.
-The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of six possible classical stripe states, more importantly it a signature of large quantum flucations in the ground state.
-
-The main effect of $\Gamma$ term on the Stripe-A and Stripe-D phase is tilting the moment orientation away from the cubic axes directions, yielding the Stripe-B and Stripe-C phase.
-Fig.~\ref{fig:Proabilities}(e) is a representative probability map for the Stripe-B phase.
-The probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, which means that the moment direction changes with the model parameters $K$ and $\Gamma$.
-On the other hand, the case of the Stripe-C phase is rather different.
-The probability is clearly peaked at the direction given by Eq.~\eqref{eq:v0} with the maximum value $P_{max}$ considerably less than $\frac{1}{6}$ (see Fig.~\ref{fig:Proabilities}(d)).
-Apart from the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the cluster GS, quantum flucations may take responsibilities for the reduced probability.
-
-\section{\label{sec:SectionVI}Summary}
+\section{\label{sec:SectionV}Summary}
 In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model.

### 2020-03-31 paper/paper.tex
20200331 13:33
Signed-off-by: wangshiphys <wangshiphys@gmail.com>

@@
 \begin{abstract}
-\textcolor{red}{The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization. $\cdots \cdots$}
+The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization.
+The quantum phase diagram is quite similar to the classical case except for a small area of possible QSL near the $\Gamma=1$ point.
+The continuum in the spin excitation spectrum and no spectrum intensity at zero energy indicates that the ground state of the model in this area is gapped QSL.
+As for the exotic phase near the antiferromagetic Kitaev point, our exact diagnoalization results provide evidence that it is stripe phase and the ordered moment along the cubic axes direction.
+In adition to the identification of these novel phases, we made a detailed distinction between these FM and stripe phases which occupy the majority area of the global phase diagram.
 \end{abstract}
@@
 For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
-When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a spin liquid state \cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111}.
+When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a spin liquid state \cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}.
 All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.
@@
 On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states.
-Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy.
+Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy.
 The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration.
@@
 In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra.
-The resulting Hamiltonian is the Kitaev-Heisenberg (KH) model.
+The resulting Hamiltonian is the Heisenberg-Kitaev (HK) model.
 It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}.
@@
 Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}.
-Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the KH model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained.
+Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the HK model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained.
 However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.
@@
 More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
-The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,arXiv1911.12712}.
+The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}.
 The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.
@@
 Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states.
-The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a discussion of its phases.
-In Sec.~\ref{sec:SectionV}, we study the moment direction of the quantum FM and stripe states, which provide characteristics to distinguish these phases.
+The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a detailed discussion of its phases.
 
@@
 \subsection{\label{sec:SectionIIB}Exact Diagonalization}
-We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on several $4 \times 6$ clusters with periodic boundary conditions (PBC).
+We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with periodic boundary conditions (PBC).
 To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics.
@@
 \subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
-For the classical FM order, all spins are aligned in parallel and the energy of the $J-K-\Gamma$ model per lattice site is given by
+For classical FM states, all spins are aligned in parallel and the energy of the $J-K-\Gamma$ model per lattice site is given by
 \begin{equation}
@@
 In this section, we turn to study the quantum phases in the $J-K-\Gamma$ model Hamiltonian.
-We consider a $4 \times 6$ cluster with PBC that has been used previously to study the KH model on triangular lattice \cite{KaiLi2015}.
+We consider a $4 \times 6$ cluster with PBC that has been used previously to study the HK model on triangular lattice \cite{KaiLi2015}.
 The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:PhaseDiagram}(a).
@@
 Thus, transformating back to the original spin basis, a collinear stripe order can be obtained.
-Similarly, a noncollinear spiral order (dual N\'{e}el) at $\beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and (f)).
+Similarly, a noncollinear spiral order (Dual N\'{e}el) at $\beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and Fig.~\ref{fig:PhaseDiagram}(f)).
 
 Apart from these well-established phases, the phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.
-To determine the GS of HK model in this area, we calculate the SMSF at $K=1$ and the resulting profile is shown in Fig.~\ref{fig:StructureFactors}(c).
-It is clear from Fig.~\ref{fig:StructureFactors}(c) that the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) which is a typical characteristic of stripe ordered states.
+To determine the GS of HK model in this area, we calculate the SMSF at $K=1$ and the resulting profile is shown in Fig.~\ref{fig:StructureFactors}(a).
+It is clear from Fig.~\ref{fig:StructureFactors}(a) that the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) which is a typical characteristic of stripe ordered states.
 
@@
 Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
-For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps for the representative model parameters of the Stripe-A and Stripe-D phase are shown in Fig.~\ref{fig:Proabilities}(c) and Fig.~\ref{fig:Proabilities}(f).
+For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps for the representative model parameters of the Stripe-A and Stripe-D phase are shown in Fig.~\ref{fig:Proabilities}(a) and Fig.~\ref{fig:Proabilities}(b).
 The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction.
 The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit.
-On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(f) indicates that the ordered moment pointing to the $y$ and $z$-axis direction.
-The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it a signature of large quantum flucations in the ground state.
+On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(b) indicates that the ordered moment pointing to the $y$ and $z$-axis direction.
+The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it is a signature of large quantum flucations in the GS.
 It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states.
-This selection of states among a continuum is the so called "order-from-disorder" mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.
+This selection of states among a continuum is the so called \emph{order-from-disorder} mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.
 
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
+    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
     \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
-The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(c).
-The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.
-(a)-(b) Probability maps for the FM states in the FM-A and FM-C phase, respectively.
-(c)-(f) Proability maps for the stripe states in the Stripe-A, Stripe-B, Stripe-C and Stripe-D phase, respectively.}
+The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b).
+The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.}
 \end{figure}
@@
 To study the nature of these remaining phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}.
-For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(a) and (b), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
+For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(b) and (c), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
 Bases on this observation, we propose the areas containing the $\Gamma=\pm 1$ points in the global phase diagram to be FM ordered phases (i.e., FM-A, FM-C).
@@
 By inspecting the probability map $P(\theta, \phi)$, we can measure the presence of the cluster spin-coherent states in the exact cluster GS.
-The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(a) and \ref{fig:Proabilities}(b).
+The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(c) and \ref{fig:Proabilities}(d).
 The large overlap between the exact cluster GS and FM ordered cluster spin-coherent state provides solid evidence that the corresponding areas are FM phases.
-For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.
-The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(b)).
+For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(c)) with all directions degenerate.
+The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(d)).
 The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model.
@@
 
-For these areas marked as Stripe-B and Stripe-C in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(e) and Fig.~\ref{fig:StructureFactors}(d).
+For these areas marked as Stripe-B and Stripe-C in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(d) and Fig.~\ref{fig:StructureFactors}(e).
 For all of these model parameters, the SMSF peaked at the M-points indicating stripe ordered GS in these areas.
-To test the presence of the classical stripe ordered states, we construct cluster spin-coherent states based on the spin pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(d) and Fig.~\ref{fig:Proabilities}(e).
+To test the presence of the classical stripe ordered states, we construct cluster spin-coherent states based on the spin pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(e) and Fig.~\ref{fig:Proabilities}(f).
 When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$.
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
+    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
     \caption{\label{fig:Spectrum}(Color online) (a) The k-points in the first Brillouin zone corresponding to a 4 $\times$ 6 cluster with 4 lattice sites along the $x$-bond direction and 6 lattice sites along the $y$-bond direction.

### 2020-06-22 paper/paper.tex
20200622 10:57:00

@@
 \affiliation{\textcolor{cyan}{XXX}}
+
+\author{Wei Wang}
+\affiliation{School of Science, Nanjing University of Posts and Telecommunications (NUPT), Nanjing 210023, China}
 
@@
 It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}.
-In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a))and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
+In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)) and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
 Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}.
@@
 \end{equation}
-where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(b), and $\alpha$, $\beta$ are the remaining directions.
+where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(c), and $\alpha$, $\beta$ are the remaining directions.
 $J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges.
@@
 (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively.
-The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see tha main text for detailed information.}
+The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see the main text for detailed information.}
 \end{figure}
@@
 On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(b) indicates that the ordered moment pointing to the $y$ and $z$-axis direction.
-The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it is a signature of large quantum flucations in the GS.
+The small $P_{max}$ of about 2\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it is a signature of large quantum flucations in the GS.
 It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states.
@@
 The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
-%When $\Gamma \rightarrow 0^{+}$ or $\Gamma \rightarrow 0^{-}$, the direction determined by Eq.~\eqref{eq:v1} tend to be the same as the $x$-axis direction which means the phase transition from positive $\Gamma$ to negative $\Gamma$ is continuous.%
+
 As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different.
@@
     \includegraphics[width=0.45\textwidth]{Fig5.pdf}
-    \caption{\label{fig:Spectrum}(Color online) (a) The k-points in the first Brillouin zone corresponding to a 4 $\times$ 6 cluster with 4 lattice sites along the $x$-bond direction and 6 lattice sites along the $y$-bond direction.
-(b) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$.
-The $A(\bm{k}, \omega)$ is draw along the path shown in (a).}
+    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$. $A(\bm{k}, \omega)$ is draw along the path $M-\Gamma-M-\Gamma$.}
 \end{figure}
@@
 
-\section{\label{sec:SectionV}Summary}
+\section{\label{sec:SectionV}Classical Monte Carlo Phase Diagram}
+We begin with paralleling-tempering Monte Carlo \cite{JPSJ.65.1604} on 40 replicas with temperature $T/J$ ranging from 0.001 to 1.0.
+For each replica, we sample it with a combination of heat-bath \cite{Miyatake_1986} and over-relaxation method \cite{Berg2004MarkovCM} mainly on a $24 \times 24$ triangle lattice with periodic boundary contitions.
+A whole MC step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice.
+We perform $10^6$ MC steps per replica, then, we copy out the spin configuration from the lowest-T replcia, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the ground state.
+The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
+\begin{equation}
+    \mathbf{S}_i = \frac{\mathbf{h}_i^{loc}}{|\mathbf{h}_i^{loc}|}S
+\end{equation}
+with
+\begin{equation}
+    \mathbf{h}_i^{loc} = \sum_{<j>} JS_j + KS_j^{\gamma}\hat{e}^{\gamma} + \Gamma (S_j^{\alpha}\hat{e}^{\beta} + S_j^{\beta}\hat{e}^{\alpha})
+\end{equation}
+For some competing states, we start from several different initial configurations in order to obtain the correct classical ground state.
+
+From the magnetic configuration of ground state, we compute the spin structure factor given by:
+\begin{equation}
+    \mathbf{S}_k = \frac{1}{N} \sum_{ij} \langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle e^{i \mathbf{k} \cdot (\mathbf{r}_i - \mathbf{r}_j)}
+\end{equation}
+which is one of the key character to identify magnetic phases.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.96\textwidth]{Fig6.pdf}
+    \caption{\label{fig:ClassicalPhaseDiagram}(Color online) Classical global phase diagram of the triangular lattice $J-K-\Gamma$ model from Monte Carlo simuations.}
+\end{figure*}
+
+\section{\label{sec:SectionVI}Summary}
 In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model.
@@
 The ground state for the classical antiferromagetic Kitaev model is also degenerate involving three nematic ordered states and three stripe ordered states.
-For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(a), the spins on the chains along the $x$-bond direction form antiferromagetic chains and the direction for the orange arrow is $[100]$.
-There is no association between different chains.
-Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(b) and Fig.~\ref{fig:GSForPositiveK}(c) respectively.
-The direction for the orange arrow in Fig.~\ref{fig:GSForPositiveK}(b) is $[010]$ and in Fig.~\ref{fig:GSForPositiveK}(c) is $[001]$.
-In addition to these nematic ordered states, there are stripe ordered states that have the same energy as the nematic ordered states.
-For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(d)-(f), the corresponding ordered moment lie in the $yz$, $xz$ and $xy$ plane, respectively.
+For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(a)-(c), the corresponding ordered moment lie in the $yz$, $xz$ and $xy$ plane, respectively.
+In addition to these stripe ordered states, there are nematic ordered states that have the same energy as the stripe ordered states.
+For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(d), the spins on the chains along the $x$-bond direction form antiferromagetic chains and the direction for the pink arrows are $[100]$.
+There are no association between different chains.
+Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(e) and Fig.~\ref{fig:GSForPositiveK}(f) respectively.
+The direction for the lightgreen arrows in Fig.~\ref{fig:GSForPositiveK}(e) and lightyellow arrows in Fig.~\ref{fig:GSForPositiveK}(f) are $[010]$ and $[001]$, respectively.
 \begin{figure}

### 2020-07-29 paper/paper.tex
20200729 9:25

@@
 \documentclass[aps,prb,reprint,amsfonts,amsmath,amssymb,showpacs,groupedaddress,superscriptaddress]{revtex4-1}
-\usepackage{IEEEtrantools}
-\usepackage{graphicx}
 \usepackage{bm}
 \usepackage{color}
-% \usepackage{changes}
-    % \definechangesauthor[name={Wang Shi}, color=orange]{swang}
-
+\usepackage{graphicx}
 \usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}
@@
 
-\title{Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model}
+\title{Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model}
 
@@
 \begin{abstract}
-The global ground state phase diagram of the Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice is studied using classical Monte Carlo and exact diagonalization.
-The quantum phase diagram is quite similar to the classical case except for a small area of possible QSL near the $\Gamma=1$ point.
-The continuum in the spin excitation spectrum and no spectrum intensity at zero energy indicates that the ground state of the model in this area is gapped QSL.
-As for the exotic phase near the antiferromagetic Kitaev point, our exact diagnoalization results provide evidence that it is stripe phase and the ordered moment along the cubic axes direction.
-In adition to the identification of these novel phases, we made a detailed distinction between these FM and stripe phases which occupy the majority area of the global phase diagram.
+The celebrated Kitaev honeycomb model provides an analytically tractable example with an exact quantum spin liquid ground state.
+While in real materials, other types of interactions besides the Kitaev coupling are present and these models can also be generalized to a triangular lattice.
+Here, we study the classical and quantum Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice using the classical Monte Carlo and exact diagonalization.
+We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit.
+Near the antiferromagetic (AF) Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism.
+Around the AF $\Gamma$ point, we find a possible quantum spin liquid in a noticeable region with a continuum in spin excitations.
 \end{abstract}
@@
 
-\section{\label{sec:SectionI}Introduction}
-Geometric frustration, which arises when the lattice geometry gives rise to constraints that cannot be simultaneously satisfied, plays an important role in various kinds of magnetic systems.
-In particluar, antiferromagnets on the triangular lattice are typical examples of such geometric frustated spin systems and have attracted numerous interests in condensed matter physics.
-For nearest-neighbor (NN) spin-1/2 antiferromagetic Heisenberg model on triangular lattice, though a fully disordered resonating-valence-bond (RVB) \cite{Anderson1973} state was proposed as the possible ground state in the early years, several studies point to a 120$^\circ$ N\'{e}el-ordered ground state thereafter \cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
-When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a spin liquid state \cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}.
+\section{\label{sec:Introduction}Introduction}
+Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems.
+The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins.
+In particular, the special case where spins are $S=1/2$ has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a "quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
+When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}.
 All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.
@@
 Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy.
-The spin-1/2 Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration.
+The spin-$1/2$ Kitaev model~\cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless QSL states supporting fractionalized excitations, is a celebrated example of a model with exchange frustration.
+In this model, the spins subject to the Kitaev interactions consisting of nearest neighbor Ising-type interactions, with the quantization axis depending on the spatial orientation of an exchange bond.
 Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model.
-Khaliullin \emph{et al.,} \cite{Khaliullin2005, PhysRevLett.102.017205} proposed to realized this highly anisotropic spin model in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates $A_2$IrO$_3$ (A = Na, Li).
+G.
+Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li).
 In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra.
-The resulting Hamiltonian is the Heisenberg-Kitaev (HK) model.
-It was later extended to contains more terms such as the off-diagonal $\Gamma$ term \cite{PhysRevLett.112.077204}.
-In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)) and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}.
-Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=1/2 models with edge sharing octahedra \cite {PhysRevLett.112.077204}.
-Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the HK model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained.
-However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.
+However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases.
+The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204}, in which the NN Heisenberg interaction is also taken into account.
+This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripy, and zigzag types, besides extended spin-liquid phases near the Kitaev limits.
+Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e.
+bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.
+Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included.
+Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204}.
+Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.
 
-On the experimental side, the discovery of YbMgGaO$_4$ has invoked increasing interest in searching for rare-earth based spin-frustrated materials \cite{srep16419,PhysRevLett.115.167203,PhysRevB.94.035107,PhysRevB.96.054445,PhysRevB.97.184413,PhysRevB.97.125105,PhysRevB.96.075105,PhysRevLett.119.157201}.
-The Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra \cite{srep16419,PhysRevLett.115.167203}.
-More recently, a class of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
-The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state \cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}.
-The novel magnetic properties of these triangluar magnets may be attributed to the interplay of geometric frustation and exchange frustration induces by spin-orbit coupling.
-
-Inspired by previous theoretical and experimental works, we study the Heisenberg-Kitaev-$\Gamma$ ($J-K-\Gamma$) model on the triangular lattice. The $J-K-\Gamma$ model Hamiltonian is given by
-\begin{equation}
-    H=\sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \bm{\cdot} \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack \label{eq:Hamiltonian}
-\end{equation}
-where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(c), and $\alpha$, $\beta$ are the remaining directions.
-$J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions and $\Gamma$ the symmetric off-diagonal exchanges.
-To the best of our knowledge, no exact solution has been reported so far for the spin-1/2 Kitaev and/or $\Gamma$ model on the triangular lattice.
-Therefore, it remains conceptually interesting to investigate whether the QSL could exist as a possible ground state of the triangular $J-K-\Gamma$ model.
+In fact, magnetic ions located at the center of edge-shared octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}.
+The HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization~\cite{KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}.
+All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripy types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types.
+Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,JPSJ.85.114710}.
+However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate.
+The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}.
+When the symmetric off-diagonal exchange interaction $\Gamma$ is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}.
+However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce.
+In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.
 
 \begin{figure}
-    \includegraphics[width=\columnwidth]{Fig1.pdf}
+    \centering
+    \begin{minipage}{0.6\columnwidth}
+        \includegraphics[width=\linewidth]{fig/EdgeSharingOctahedrons.pdf}
+    \end{minipage}\hspace{0pt}
+    \begin{minipage}{0.3\columnwidth}
+        \includegraphics[width=\linewidth]{fig/SingleOctahedron.pdf}\vspace{0pt}
+        \includegraphics[width=\linewidth]{fig/ModelDefinition.pdf}
+    \end{minipage}
     \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron.
@@
 
-The rest of the paper is organized as follows: The classical Monte Carlo and exact diagnoalization (ED) methods are introduced in Sec.~\ref{sec:SectionII}.
-Section~\ref{sec:SectionIII} discusses the phases of the classical $J-K-\Gamma$ model with the main focus on the direction of the ordered moment of the FM and stripe states.
-The global phase diagram of the quantum model is presented in Sec.~\ref{sec:SectionIV} along with a detailed discussion of its phases.
+On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments.
+In particular, due to their possible Kramers doublets and spin-orbital coupling, the $4f$ electrons can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbit entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms.
+A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614,PhysRevLett.117.267202,PhysRevLett.120.087201,PhysRevLett.122.137201,LiAdroja-398}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra~\cite{srep16419,PhysRevLett.115.167203}.
+At low temperatures, QSL states have been proposed due to its lack of long-range magnetic order and the observation of a continuum of magnetic excitations~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614}, but the exchange disorder induced by the intermixture of Mg$^{2+}$ and Ga$^{3+}$ may lead to a spin glass state~\cite{PhysRevLett.120.087201} or a random valence bond state~\cite{PhysRevLett.122.137201,LiAdroja-398}.
+More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
+The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}.
+These triangluar magnets of rare-earth ions provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbit coupling.
 
-\section{\label{sec:SectionII}Methods}
-The full anisotropic Hamiltonian~\eqref{eq:Hamiltonian} is no longer exactly solvable, even for the classical case.
-One, therefore, either has to rely on approximate analytical method or on numerical techniques.
-To determine the ground state of the Hamiltonian~\eqref{eq:Hamiltonian}, we employ a combination of classical Monte Cralo simulation and ED calculation.
-Here, we briefly describe the methods we used.
-For convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchanges using spherical angles $\alpha$ and $\beta$
+{
+    \color{red}The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK model.
+The exact diagonalization and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}.
+Section~\ref{sec:Results} disscuss the main results of this paper.
+}
+
+\section{\label{sec:Model}Model}
+
+The $J$-$K$-$\Gamma$ model Hamiltonian on the triangular lattice is given by
+\begin{equation}
+    H = \sum_{\langle i,j \rangle \in \alpha \beta (\gamma)} \lbrack J \bm{S}_i \cdot \bm{S}_j + K S_i^{\gamma} S_j^{\gamma} + \Gamma (S_i^{\alpha} S_j^{\beta} + S_i^{\beta} S_j^{\alpha}) \rbrack,
+    \label{eq:Hamiltonian}
+\end{equation}
+where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(c), and $\alpha$, $\beta$ are the remaining directions.
+$J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions, and $\Gamma$ the symmetric off-diagonal exchanges.
+
+In the followings, for convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchange interactions using spherical angles $\alpha$ and $\beta$
 \begin{equation}
@@
     K = \sin\alpha \cos\beta, \quad
-    \Gamma = \cos\alpha \label{eq:Parameters}
+    \Gamma = \cos\alpha
+    \label{eq:Parameters}
 \end{equation}
-where $\alpha \in [0, \pi]$ and $\beta \in [0, 2\pi]$ to cover the global phase diagram.
+where $\alpha \in [0, \pi]$ and $\beta \in [0, 2\pi]$ to cover the global parameter space.
 
-\subsection{\label{sec:SectionIIA}Classical Monte Carlo}
-\textcolor{red}{A introduction to classical Monte Carlo. To be accomplished $\cdots \cdots$}
+In the HK limit ($\Gamma=0$), the model~\eqref{eq:Hamiltonian} admits an exact duality transformation, i.e., the so-called four-sublattice-transformation (FST)~\cite{PhysRevB.89.014414}.
+The FST is a spin rotation transformation which divides the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and performs the following rotations of the spins on the four sublattices to map the spin $\bm{S}_{i}$ to $\bm{S}_{i}^{\prime}$,
+\begin{align*}
+    & \bm{S}_{0}^{\prime} = \bm{S}_{0}& \quad \text{for sublattice 0}, \\
+    & \bm{S}_{1}^{\prime} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1}, \\
+    & \bm{S}_{2}^{\prime} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2}, \\
+    & \bm{S}_{3}^{\prime} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}.
+\end{align*}
+This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the sublattices $1$, $2$, and $3$, respectively.
+The resulting Hamiltonian $H^{\prime}(\bm{S}^{\prime})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{\prime} = -J$ and $K^{\prime} = 2J + K$.
+For the spherical angles defined in Eq.~\eqref{eq:Parameters}, the mapping takes the form
+\begin{align}
+    \tan\beta^{\prime} = -\sin\beta / (2\sin\beta + \cos\beta).
+    \label{eq:FST}
+\end{align}
+This special property of the model can help us to identify some exotic magnetically ordered phases from the well established simple counterparts.
 
-\subsection{\label{sec:SectionIIB}Exact Diagonalization}
-We perform Lanczos ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with periodic boundary conditions (PBC).
-To detect quantum phase transitions, the second derivatives of the ground state energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and looked for singular features that indicate changes in the ground state characteristics.
-Phases containing exactly solvable or well-understood points, such as the FM, 120$^\circ$ N\'{e}el, stripe and Dual N\'{e}el can be readily identified.
-To have a better understanding of the characteristics of the remaining phases, we examine the static magnetic structure factor (SMSF) $S(\bm{Q})$ and dynamic spin excitation spectrum $A(\bm{k}, \omega)$ of these phases.
-$S(\bm{Q})$ and $A(\bm{k}, \omega)$ are defined as follow:
-\begin{subequations}
+\section{\label{sec:Methods}Methods}
+
+\subsection{\label{subsec:MethodED}Exact Diagonalization}
+
+To obtain the quantum phase diagram of the model~\eqref{eq:Hamiltonian}, we perform exact-diagonalization calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with the periodic boundary condition.
+To detect quantum phase transitions, the second derivatives of the GS energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and its singularities are used to identify possible phase transtions.
+
+To identify the ground-state properties, we first examine the static structure factor (SSF),
 \begin{align}
-        & S(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \bm{\cdot} \bm{S}_j | \Omega \rangle e^{i \bm{Q} \bm{\cdot} (\bm{R}_i - \bm{R}_j)} \label{eq:SMSF} \\
-        & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} G(\bm{k}, \omega) \label{eq:Akomega} \\
-        & G(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} G_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)} \\
-        & G_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i\eta - H + E_0} S_j^{-} | \Omega \rangle \label{eq:GreenFunction}
+    \mathcal{S}(\bm{Q}) = \frac{1}{N} \sum_{ij} \langle \Omega | \bm{S}_i \cdot \bm{S}_j | \Omega \rangle e^{i \bm{Q} \cdot (\bm{R}_i - \bm{R}_j)},
+    \label{eq:SSF}
 \end{align}
-\end{subequations}
-where $| \Omega \rangle$ and $E_0$ are the GS and ground state energy respectively, N is the total number of spins, $\bm{R}_i$ the position of site $i$, and $\eta = 0^+$.
+from which we can find the wave vectors of the ordered phases and distinguish possible QSL states.
+Here, $|\Omega\rangle$ is the GS, $N$ is the total number of lattice sites, and $\bm{R}_i$ the position of site $i$.
 
-To extract the moment direction of a magnetic ordered phase from a cluster GS, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435}.
+To further determine the magnetic configurations of the magnetically ordered phases, we employ a method by studying the projections of the exact GSs of the finite cluster to the classical states~\cite{PhysRevB.94.064435}.
 The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions.
-The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$
-\begin{equation}
-    | \Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle \label{eq:ClusterCoherentState}
-\end{equation}
+The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$, i.e.,
+\begin{align}
+    |\Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle,
+    \label{eq:ClusterCoherentState}
+\end{align}
 where the spin-1/2 coherent state
-\begin{equation}
-    | \theta, \phi \rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle \label{eq:Spin-1/2CoherentState}
-\end{equation}
-is fully polaried along the $(\theta, \phi)$ direction.
-Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles, and $S^z | \uparrow \rangle = \frac{1}{2} | \uparrow \rangle$.
-By calculating the overlap between the exact cluster GS and cluster spin-conherent states, and maximizing the probability $P = | \langle \Psi | GS \rangle|^2$ with respect to $\theta$s and $\phi$s, we can then identify the classical pattern that best fits the exact GS.
+\begin{align}
+    |\theta, \phi\rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle
+    \label{eq:Spin-1/2CoherentState}
+\end{align}
+is fully polaried state along the $(\theta, \phi)$ direction.
+Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles.
+By calculating the overlap between the exact cluster GS and cluster spin-conherent states, $P = | \langle \Psi | GS \rangle|^2$, and maximizing its value with respect to $\theta$'s and $\phi$'s, we can then identify the classical spin pattern that best fits the exact quantum GS.
 
-\section{\label{sec:SectionIII}Classical Analysis}
-To understand the effects of inculding the off-diagonal $\Gamma$ term, we first study the classical $J-K-\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension.
-On our proceeding, we note that the global phase diagram has been obtained previously by using a combination of Luttinger-Tsiza (LT) and classical Monte Carlo simulations \cite{PhysRevB.92.165108}.
-Six different magnetic orderings: ferromagnet (FM), stripe, 120$^\circ$ N\'{e}el order, nematic, $\mathbb{Z}_2$ and dual-$\mathbb{Z}_2$ vortex crystal phases were found, see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}.
-Our classical Monte Carlo study give qualitatively the same phase diagram.
+Since one of the key characteristics of QSL is the fractional excitation, which can lead to a continuous spectrum, so we study the dynamic structure factor (DSF) $A(\bm{k}, \omega)$ to search for the possible QSLs.
+$A(\bm{k}, \omega)$ is given by
+\begin{align}
+    & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} \mathcal{S}(\bm{k}, \omega), \label{eq:Akomega} \\
+    & \mathcal{S}(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} \mathcal{S}_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)}, \\
+    & \mathcal{S}_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i0^{+} - H + E_0} S_j^{-} | \Omega \rangle, \label{eq:GreenFunction}
+\end{align}
+where $E_0$ is the ground state energy.
 
-\subsection{\label{sec:SectionIIIA}Moment direction of the classcial FM order}
+\subsection{\label{subsec:MethodMC}Classical Monte Carlo}
+
+In order to better understand the quantum phases identified by the exact diagonalization method, we also perform classical Monte Carlo simulations.
+We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$.
+For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24\times 24$ triangle lattice with periodic boundary conditions.
+A whole MC step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice.
+We perform $10^6$ MC steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS.
+The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
+\begin{align}
+    \bm{S}_i = \frac{\bm{h}_i^{loc}}{|\bm{h}_i^{loc}|} S,
+\end{align}
+with
+\begin{align}
+    \bm{h}_i^{loc} = \sum_{\langle j \rangle} J \bm{S}_j + K {S}^{\gamma}_j \hat{e}^{\gamma} + \Gamma (S^\alpha_j \hat{e}^{\beta} + S^\beta_j \hat{e}^\alpha),
+\end{align}
+For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.
+
+From the magnetic configuration of GS, we compute the spin structure factor given by
+\begin{align}
+    \mathcal{S}_{\bm{k}} = \frac{1}{N} \sum_{ij} \left \langle \bm{S}_i \cdot \bm{S}_j \right \rangle e^{i \bm{k} \cdot (\bm{r}_i-\bm{r}_j)},
+\end{align}
+which is a key characterizes to identify magnetic phases.
+
+\section{\label{sec:Results}Results}
+
+\subsection{\label{subsec:GlobalPhaseDiagram}Global Phase Diagram}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
+    \includegraphics[width=\linewidth]{fig/SecondDerivatives.pdf}
+    \caption{\label{fig:QuantumPhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
+The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
+There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase.
+The three FM phases different from each other in the direction of the ordered moment, and also the four stripe phases are distinguished by their moment directions, see main text for details.
+(b) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=1.5\pi$.
+(c) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=0$.
+(d) The red (blue) line is $-\partial^2E_0/\partial\beta^2$ ($E_0$) versus $\beta$ with $\alpha=0.3\pi$.}
+\end{figure*}
+
+The quantum phase diagrams obtained by the exact-diagonalization method for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:QuantumPhaseDiagram}(a).
+The phase boundaries are obtained from the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
+
+In the HK limit ($\Gamma=0$), as with the previous study~\cite{KaiLi2015}, we find five quantum phases.
+For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$.
+As mentioned in Sec.~\ref{sec:Model}, the form of the HK model ($\Gamma=0$) is invariant under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions.
+Thus, by virtue of the FST, two more magnetic ordered phases can be identified.
+When $\beta=\pi - \arctan\frac{1}{2}$ in Eq.~\eqref{eq:FST}, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$, whose GS is a FM state.
+Thus, transformating back to the original spin basis, a collinear stripe order can be obtained.
+Similarly, a noncollinear spiral order (dual N\'{e}el) is obtained from the 120$^\circ$ N\'{e}el order for $\beta=-\arctan\frac{1}{2}$.
+However, for the phase near the AFM Kitaev point ($J=\Gamma=0$, $K>0$), it is mapped to itself under FST, so we can not identify its magnetic properties with the FST.
+
+When the $\Gamma$ term is included, we find that the stripe phase, the FM phase and the phase near the AFM Kitaev point in the HK model are actually phase boundaries in the global phase diagram of the $J$-$K$-$\Gamma$ model.
+Moreover, except the 120$^\circ$ N\'{e}el state and the dual N\'{e}el state, which already exist in the HK limit, there are six other new phases.
+
+To reveal the natures of these new phases, we perform the classical MC calculations as described in Sec.~\ref{subsec:MethodMC}.
+For convenience of comparison between the quantum and classical results, we also present the classical phase diagram obtained from the MC simulations in Fig.~\ref{fig:ClassicalPhaseDiagram}, which is consistent with the phase diagram reported in Ref.~\onlinecite{PhysRevB.92.165108}.
+According to the classical MC results, we can identify that the three new phases with large areas mainly located in the $J>0$ region have stripe orders (i.e., the stripe-B and stripe-C phases), while the two new phases mainly located in the $J<0$ region are FM (i.e., the FM-A and FM-C phases).
+In addition, we find that the area of the 120$^\circ$ N\'{e}el state in the quantum phase diagram is greatly reduced, and more importantly the extra phase near $\Gamma=1$ that does not exist in the classical phase diagram.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/ClassicalGlobalPhaseDiagram.pdf}
+    \caption{\label{fig:ClassicalPhaseDiagram}(Color online) Classical global phase diagram of the $J$-$K$-$\Gamma$ model obtained from classical Monte Carlo simulation.}
+\end{figure}
+
+The properties of each quantum phases, especially the spin configuration of the ordered phases, can also be inferred from the SSF in~\eqref{eq:SSF},  so we illustrate the results for some typical parameters in Fig.~\ref{fig:StructureFactors}.
+The results in Fig.~\ref{fig:StructureFactors}(d) and (e) show the SSFs in the stripe-B and stripe-C phases, respectively.
+It is clear that the SSFs are peaked at the $\tilde{M}$ points of the first Brillouin zone (BZ), which is a typical characteristic of stripe ordered states.
+For the case of pure AFM Kitev limit ($J=\Gamma=0$, $K=1$), the SSF in Fig.~\ref{fig:StructureFactors}(a) shows the same structure as those in Fig.~\ref{fig:StructureFactors}(d) and (e), so the GSs around the AFM Kitev point also belongs to a stripe phase, which we label the stripe-D phase.
+In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the results of two other special points with $\Gamma=\pm1$ and $J=K=0$, i.e., the pure $\Gamma$ models.
+We find that the GSs of both models have ferromagnetic order, as the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ.
+The ferromagnetic phases contains these two specail points are denoted with FM-A and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}(a).
+The SSF for the quantum phase that does not exist in the classical phase diagram in a small region around the point with $J=K=0$ and $\Gamma=1$ is illustrated in Fig.~\ref{fig:StructureFactors}(f), which exhibits high intensities at both $\tilde{\Gamma}$ and $\tilde{M}$.
+{\color{red}It seems impossible for a classical magnetically ordering state to satisfy these two wave vectors simultaneously, so we infer that this quantum phase is a QSL.}
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
+    \caption{\label{fig:StructureFactors}(Color online) SSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
+\end{figure}
+
+According the above analysis, we find that, unlike the case for the honeycomb lattice, the Kitaev interactions on the triangular lattice do not give rise to QSL states, so the quantum phase diagram is similar to its classic counterpart.
+Here, the large coordination number plays a key role to stabilize the classical magnetic order, although the geometric and exchange frustrations coexist in the triangular lattice $J$-$K$-$\Gamma$ model.
+Although we have basically determine the nature of each phase, there are still two problems should be explained: first, why there are phase transitions between the phases with the same type of classical order, suas the phase transitions between FM phases and stripe phases; second, what other important characteristics of the QSL phase in the phase diagram can be used to help us understand its properties more deeply.
+In the followings, we will address these problems.
+
+\subsection{\label{subsec:FMPhases}FM Phases}
+
+To have a better understanding of the phase transitions between these FM phases, we first study the classical $J$-$K$-$\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension.
 For classical FM states, all spins are aligned in parallel and the energy of the $J-K-\Gamma$ model per lattice site is given by
@@
 
-Our classical Monte Carlo simulation found FM ordered state with the right moment direction for majority of the area marked as FM phase (see Fig.~2 in Ref~\onlinecite{PhysRevB.92.165108}) except for the pure $\Gamma$ term.
+Our classical Monte Carlo simulation found FM ordered states with the right moment direction for majority of the area marked as FM phase (see Fig.~\ref{fig:ClassicalPhaseDiagram}) except for the pure $\Gamma$ term.
 For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found.
@@
 On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS.
-In fact, the classical GS were found to be disordered for $0 < J \ll \Gamma$ and stripe ordered for $0 < J \ll -\Gamma$.
-As for the disordered phase, when quantum flucations are involved, a quantum spin liquid state may emerge.
 
-\subsection{\label{sec:SectionIIIB}Moment direction of the classcial stripe order}
-In the case of stripe order, there are three degenerate spin configurations as illustrated in Fig.~\ref{fig:PhaseDiagram}(b)-(d).
-For the spin configuration shown in Fig.~\ref{fig:PhaseDiagram}(b), the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} per lattice site is
+In light of the classical analysis, we conjecture the main differences between these FM phases lies in the ordered moment direction.
+To further confirm our hypothesis, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435} to extract the moment direction of these FM phases from our ED cluster ground state.
+Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (such as FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
+The resulting probability maps for representive model parameters of FM-A and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(c) and (d).
+It is worth to note that the large overlap between the exact cluster GS and FM ordered cluster spin-coherent state again provides solid evidence that the corresponding areas are FM phases.
+For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction.
+The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction).
+In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis.
+However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction.
+For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(c)) with all directions degenerate.
+The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(d)).
+The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model.
+For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order.
+However, for the quantum model, quantum flucations select the FM ordered states lie in the lattice plane as GS out of an otherwise infinitely degenerate manifold of classical states.
+Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM state perpendicular to the lattice plane is selected as the GS.
+This selection of states among degenerate classical ground states is the so called \emph{order-from-disorder} mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.
+
+In the HK limit, the GS of the model near the $J=-1$ point is FM state and the ordered moment is fixed to the $x,y,z$-axis direction by the Kitaev interaction.
+When an infinitesimal $\Gamma$ interaction is introduced, positive couplings drive the ordered moment to the lattice plane and negative couplings pinning the ordered moment to be perpendicular to the lattice plane.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
+    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
+The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b).
+The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.}
+\end{figure}
+
+\subsection{\label{subsec:StripePhases}Stripe Phases}
+
+Inspired by the previous discussion of those FM phases, we perform the same analysis for these stripe phases.
+For stripe order, there are three degenerated spin configurations in real-space, designated as \emph{config-x}, \emph{config-y} and \emph{config-z} respectively.
+For \emph{configx}, the spins on the chains along the $x$-bond direction form ferromagnetic chains and adjacent chains are anti-parallel.
+Similarly, the ferromagnetic chains along the $y$-bond and $z$-bond direction for \emph{config-y} and \emph{config-z} respectively.
+For \emph{config-x}, the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} per lattice site is
 \begin{eqnarray}
     E_{StripeX}^{c} & = & -(J + K) + 2 K v^x v^x \nonumber \\
-        & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y) \label{eq:EcStripeX}
+        & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y)
+        \label{eq:EcStripeX}
 \end{eqnarray}
-and the energy for spin configuration in Fig.~\ref{fig:PhaseDiagram}(c) and \ref{fig:PhaseDiagram}(d) can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$.
+and the energy for \emph{config-y} and \emph{config-z} can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$.
 The ordered moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$.
@@
 
-For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $v^x = 0$ which means that the stripe order shown in Fig.~\ref{fig:PhaseDiagram}(b) prefers to lie in the $yz$ plane.
+For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $v^x = 0$ which means that \emph{config-x} prefers to lie in the $yz$ plane.
 An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction whereas negative $\Gamma$ drives it to the $\bm{v}_1$ direction.
@@
 
-\section{\label{sec:SectionIV}Global Phase Diagram}
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.96\textwidth]{Fig2.pdf}
-    \caption{\label{fig:PhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J-K-\Gamma$ model.
-The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
-There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase.
-The three FM phases different from each other in the direction of the ordered moment, and also the four stripe phases are distinguished by their moment directions, see main text for details.
-(b)-(d) Illustation of the three degenerate spin configurations for all stripe orders.
-(e) Illustration of the 120$^\circ$ N\'{e}el order.
-All spins are coplanar and the angles between nearest-neighbor spins are 120$^\circ$.
-(f) Illustration of the Dual N\'{e}el order.
-The magnetic unit cell include 12 lattice sites as marked by the green dashed parallelogram.}
-\end{figure*}
-
-In this section, we turn to study the quantum phases in the $J-K-\Gamma$ model Hamiltonian.
-We consider a $4 \times 6$ cluster with PBC that has been used previously to study the HK model on triangular lattice \cite{KaiLi2015}.
-The resulting phase diagrams for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:PhaseDiagram}(a).
-The phase boundaries are obtained from the location of singular features in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
-The quantum phase diagram is closely resemble to the classical result in Ref~\onlinecite{PhysRevB.92.165108} except for the small green area near $\Gamma=1$ which does not appear in the classical phase diagram.
-
-\subsection{\label{subsec:HKLimit}Phases in the HK limit ($\Gamma=0$)}
-For pure Heisenberg model ($K=\Gamma=0$), the GS is ferromagnet for $J<0$ and 120$^\circ$ N\'{e}el state for $J>0$.
-As for the HK ($\Gamma=0$) model, by virtue of the existence of the so-called four-sublattice-transformation (FST) \cite{PhysRevB.89.014414}, two more magnetic ordered phases can be identified.
-Specifically, FST is a spin rotation transformation which divide the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and introduce the rotated spin operators $\bm{S}^{'}$
-\begin{align*}
-    & \bm{S}_{0}^{'} = \bm{S}_{0}& \quad \text{for sublattice 0} \\
-    & \bm{S}_{1}^{'} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1} \\
-    & \bm{S}_{2}^{'} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2} \\
-    & \bm{S}_{3}^{'} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}
-\end{align*}
-The resulting Hamiltonian $H^{'}(\bm{S}^{'})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{'} = -J$ and $K^{'} = 2J + K$.
-For the spherical angles defined in Eq~\eqref{eq:Parameters}, the mapping takes the form $tan\beta^{'}=-sin\beta/(2sin\beta + cos\beta)$.
-When $\beta=\pi - arctan\frac{1}{2}$, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{'}$.
-Thus, transformating back to the original spin basis, a collinear stripe order can be obtained.
-Similarly, a noncollinear spiral order (Dual N\'{e}el) at $\beta=-arctan\frac{1}{2}$ can be obtained from the 120$^\circ$ N\'{e}el order (see Fig.~\ref{fig:PhaseDiagram}(e) and Fig.~\ref{fig:PhaseDiagram}(f)).
-
-Apart from these well-established phases, the phase near the AF Kitaev point (i.e., $K=1$) has been proposed to be a chiral SL at the mean field level \cite{KaiLi2015} or a nematic phase in the quantum limit from DMRG calculation \cite{PhysRevB.91.155135}, however, a more recent study suggests that a stripe state is more likely to be the GS \cite{PhysRevX.9.021017}.
-To determine the GS of HK model in this area, we calculate the SMSF at $K=1$ and the resulting profile is shown in Fig.~\ref{fig:StructureFactors}(a).
-It is clear from Fig.~\ref{fig:StructureFactors}(a) that the SMSF peaked at the midpoints of the first BZ boundary (i.e., M-points) which is a typical characteristic of stripe ordered states.
-
-To have further insight into these phases, we adopt the method introduced in Ref~\onlinecite{PhysRevB.94.064435} to extract the moment directions for some of these phases.
-For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction.
-The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction).
-In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis.
-As for stripe ordered states, there are three degenerate patterns in real space as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) and the ordered moment is locked to the orientation of the stripe pattern.
-Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (in our case, these are FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
-For brevity, we only construct cluster spin-coherent state based on the stripe pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps for the representative model parameters of the Stripe-A and Stripe-D phase are shown in Fig.~\ref{fig:Proabilities}(a) and Fig.~\ref{fig:Proabilities}(b).
+To determined the ordered moment direction of those stripe phases in the quantum phase diagram, we construct stripe ordered cluster spin-coherent states and calculate their probabilities in the ED ground state.
+For brevity, we only construct cluster spin-coherent state based on \emph{config-x} and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(a), (e), (f), (b) for Stripe-A, Stripe-B, Stripe-C, Stripe-D respectively.
 The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction.
-The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for stripe pattern in Fig.~\ref{fig:PhaseDiagram}(b) from classical considerations, our ED results show that this situation also applies at quantum limit.
+The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for \emph{config-x} from classical considerations, our ED results show that this situation also applies at quantum limit.
 On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(b) indicates that the ordered moment pointing to the $y$ and $z$-axis direction.
-The small $P_{max}$ of about 2\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(b), $\pm x$, $\pm z$ for Fig.~\ref{fig:PhaseDiagram}(c), $\pm x$, $\pm y$ for Fig.~\ref{fig:PhaseDiagram}(d)), more importantly it is a signature of large quantum flucations in the GS.
+The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for \emph{config-x}, $\pm x$, $\pm z$ for \emph{config-y}, $\pm x$, $\pm y$ for \emph{config-z}), more importantly it is a signature of large quantum flucations in the GS.
 It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states.
-This selection of states among a continuum is the so called \emph{order-from-disorder} mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.
-
-In a word, for the HK model, apart from these well established phases, our ED calculations provide evidence that the GS of the model near the AF Kitaev point is stripe ordered states.
-However, Stripe-D different from Stripe-A in the direction of the ordered moment direction.
-To be specific, for a certain spin pattern, the ordered moment would along only one of the $x, y, z$-axis direction in the Stripe-A phase and point to the other two axes directions for the Stripe-D phase.
-
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
-    \caption{\label{fig:StructureFactors}(Color online) SMSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
-\end{figure}
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
-    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
-The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b).
-The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.}
-\end{figure}
-
-\subsection{\label{subsec:GammaEffects}Effects of the $\Gamma$ term}
-When the off-diagonal $\Gamma$ term is included, the FST is no longer valid.
-To study the nature of these remaining phases, we calculate the SMSF for some representative model paramters, as shown in Fig.~\ref{fig:StructureFactors}.
-For pure $\Gamma$ model, see Fig.~\ref{fig:StructureFactors}(b) and (c), the peak of the SMSF locates at the center of first Brillouin Zone (BZ) which is a typical characteristic of the FM order.
-Bases on this observation, we propose the areas containing the $\Gamma=\pm 1$ points in the global phase diagram to be FM ordered phases (i.e., FM-A, FM-C).
-To further confirm our hypothesis, we construct cluster spin-coherent states with all the spins are polarized along the $(\theta, \phi)$ direction.
-By inspecting the probability map $P(\theta, \phi)$, we can measure the presence of the cluster spin-coherent states in the exact cluster GS.
-The resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(c) and \ref{fig:Proabilities}(d).
-The large overlap between the exact cluster GS and FM ordered cluster spin-coherent state provides solid evidence that the corresponding areas are FM phases.
-For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(c)) with all directions degenerate.
-The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(d)).
-The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model.
-For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order.
-However, for the quantum model, quantum flucations select the FM ordered states lie in the lattice plane as GS out of an otherwise infinitely degenerate manifold of classical states.
-Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM state perpendicular to the lattice plane is selected as the GS.
-In the HK limit, the GS of the model near the $J=-1$ point is FM state and the ordered moment is fixed to the $x,y,z$-axis direction by the Kitaev interaction.
-When an infinitesimal $\Gamma$ interaction is introduced, positive couplings drive the ordered moment to the lattice plane and negative couplings pinning the ordered moment to be perpendicular to the lattice plane.
-
-For these areas marked as Stripe-B and Stripe-C in the global phase diagram, the representative SMSF profiles are shown in Fig.~\ref{fig:StructureFactors}(d) and Fig.~\ref{fig:StructureFactors}(e).
-For all of these model parameters, the SMSF peaked at the M-points indicating stripe ordered GS in these areas.
-To test the presence of the classical stripe ordered states, we construct cluster spin-coherent states based on the spin pattern shown in Fig.~\ref{fig:PhaseDiagram}(b) and the resulting probability maps are shown in Fig.~\ref{fig:Proabilities}(e) and Fig.~\ref{fig:Proabilities}(f).
-When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$.
+Stripe-D different from Stripe-A in the direction of the ordered moment direction.
+To be specific, for a certain spin configuration, the ordered moment would along only one of the $x, y, z$-axis direction in the Stripe-A phase and point to the other two axes directions for the Stripe-D phase.
+When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$ (See the green solid circle in \ref{fig:Proabilities}(e) and (f)).
 Considering the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the exact cluster GS, it is reasonable to say that the stripe ordered ground states for the classical $J-K-\Gamma$ model in these areas persist in the quantum limit and the ordered moments of the quantum states coincide with their classical analogue.
 The reduced probabilities $P_{max} < \frac{1}{6}$ may be attributed to quantum flucations.
+
 In the HK limit, there exist a stripe phase (i.e., Stripe-A) when $J>0, K<0$ and the ordered moment along the $x,y,z$-axis direction.
@@
 The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
-
 As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different.
@@
 
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{Fig5.pdf}
-    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$. $A(\bm{k}, \omega)$ is draw along the path $M-\Gamma-M-\Gamma$.}
-\end{figure}
+\subsection{\label{subsec:QSL}Quantum Spin Liquid}
 
-Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:PhaseDiagram}(a).
+Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:QuantumPhaseDiagram}.
 For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ.
@@
 Combined with all of the above results, we propose the GS of quantum $J-K-\Gamma$ model at the green area is a gapped QSL.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
+    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$. $A(\bm{k}, \omega)$ is draw along the path $M-\Gamma-M-\Gamma$.}
+\end{figure}
 
-\section{\label{sec:SectionV}Classical Monte Carlo Phase Diagram}
-We begin with paralleling-tempering Monte Carlo \cite{JPSJ.65.1604} on 40 replicas with temperature $T/J$ ranging from 0.001 to 1.0.
-For each replica, we sample it with a combination of heat-bath \cite{Miyatake_1986} and over-relaxation method \cite{Berg2004MarkovCM} mainly on a $24 \times 24$ triangle lattice with periodic boundary contitions.
-A whole MC step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice.
-We perform $10^6$ MC steps per replica, then, we copy out the spin configuration from the lowest-T replcia, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the ground state.
-The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
-\begin{equation}
-    \mathbf{S}_i = \frac{\mathbf{h}_i^{loc}}{|\mathbf{h}_i^{loc}|}S
-\end{equation}
-with
-\begin{equation}
-    \mathbf{h}_i^{loc} = \sum_{<j>} JS_j + KS_j^{\gamma}\hat{e}^{\gamma} + \Gamma (S_j^{\alpha}\hat{e}^{\beta} + S_j^{\beta}\hat{e}^{\alpha})
-\end{equation}
-For some competing states, we start from several different initial configurations in order to obtain the correct classical ground state.
-
-From the magnetic configuration of ground state, we compute the spin structure factor given by:
-\begin{equation}
-    \mathbf{S}_k = \frac{1}{N} \sum_{ij} \langle \mathbf{S}_i \cdot \mathbf{S}_j \rangle e^{i \mathbf{k} \cdot (\mathbf{r}_i - \mathbf{r}_j)}
-\end{equation}
-which is one of the key character to identify magnetic phases.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.96\textwidth]{Fig6.pdf}
-    \caption{\label{fig:ClassicalPhaseDiagram}(Color online) Classical global phase diagram of the triangular lattice $J-K-\Gamma$ model from Monte Carlo simuations.}
-\end{figure*}
-
-\section{\label{sec:SectionVI}Summary}
+\section{\label{sec:Summary}Summary}
 In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model.
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{FigA1.pdf}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveGamma.pdf}
     \caption{\label{fig:GSForPositiveGamma}(Color online) Typical disordered ground state for $J=K=0, \Gamma=1$.
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{FigA2.pdf}
+    \includegraphics[width=\columnwidth]{fig/SpinConfigForNegativeGamma.pdf}
     \caption{\label{fig:GSForNegativeGamma}(Color online) Typical ground state spin configurations for $J=K=0, \Gamma=-1$.
@@
 \begin{figure}
-    \includegraphics[width=0.5\textwidth]{FigA3.pdf}
+    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveKitaev.pdf}
     \caption{\label{fig:GSForPositiveK}(Color online) Nematic and stripe ground state spin configurations for $J=\Gamma=0, K=1$.}
@@
 \section{\label{apx:AppendixB}Classical energy and moment direction of the stripe ordered states}
-For classical stripe ordered states, all the spins are collinear and there are three degenerate spin configurations as shown in Fig.~\ref{fig:PhaseDiagram}(b)-(d) in the main text.
+
+For classical stripe ordered states, all the spins are collinear and there are three degenerate spin configurations designated as \emph{config-x}, \emph{config-y} and \emph{config-z} respectively.
 The corresponding energies of the classical $J-K-\Gamma$ model for these spin configurations are

### 2020-08-01 FiguresForPaper/ShowStructureFactor.py
A new design of `ShowStructureFactor.py`.

@@ -3,43 +3,36 @@ Show the static magnetic structure factors (SMSF) for some representative model
 parameters.
 """
 
-
+from pathlib import Path
 import matplotlib.pyplot as plt
 import numpy as np
 from HamiltonianPy import TRIANGLE_CELL_MS as MS
+from HamiltonianPy import TRIANGLE_CELL_KS as KS
 
 from FontSize import *
 
 BZLW = 5
+MARKERSIZE = 16
 COLORMAP = "hot_r"
 BZCOLOR = "tab:green"
-SF_DATA_NAME_TEMP = "data/SF_num1=4_num2=6_direction=avg_" \
+FIG_Path = "figures/StructureFactors/"
+Path(FIG_Path).mkdir(exist_ok=True, parents=True)
+SF_DATA_PATH = "data/"
+SF_DATA_NAME_TEMP = "SF_num1=4_num2=6_direction=avg_" \
                     "alpha={0:.4f}_beta={1:.4f}.npz"
 
 params = [
-    (0.50, 0.00), (0.00, 0.00), (1.00, 0.00),
-    (0.70, 0.66), (0.30, 0.25), (0.05, 0.10),
+    (0.50, 0.00), (0.30, 0.80), (0.70, 0.66), (0.30, 0.00),
+    (0.00, 0.00), (1.00, 0.00), (0.05, 0.10), (0.30, 0.50),
 ]
-sub_fig_tags = ["(a)", "(b)", "(c)", "(d)", "(e)", "(f)"]
-titles = [
-    r"$J=\Gamma=0,K=1$",
-    r"$J=K=0,\Gamma=1$",
-    r"$J=K=0,\Gamma=-1$",
-    r"$\alpha={0:.2f}\pi,\beta={1:.2f}\pi$".format(*params[3]),
-    r"$\alpha={0:.2f}\pi,\beta={1:.2f}\pi$".format(*params[4]),
-    r"$\alpha={0:.2f}\pi,\beta={1:.2f}\pi$".format(*params[5]),
-]
-
-fig, axes = plt.subplots(
-    nrows=2, ncols=3, sharex="all", sharey="all", num="StructureFactors",
-)
+sub_fig_tags = ["(a)", "(b)", "(c)", "(d)", "(e)", "(f)", "(g)", "(h)"]
 for index in range(len(params)):
-    title = titles[index]
     alpha, beta = params[index]
-    ax = axes[divmod(index, 3)]
     sub_fig_tag = sub_fig_tags[index]
[…]

### 2020-08-01 FiguresForPaper/ShowSixSitesOrder.py
Add `ShowSixSitesOrder.py`.

@@ -1,0 +1,121 @@
+from pathlib import Path
+
+import HamiltonianPy as HP
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.optimize import basinhopping
+
+from ClassicalModel import *
+from FontSize import *
+from StructureFactor import ClassicalSpinStructureFactor
+
+POINTS = np.array(
+    [
+        [0.0, 0.0], [1.0, 0.0], [0.5, np.sqrt(3) / 2],
+        [1.5, np.sqrt(3) / 2], [1.0, np.sqrt(3)], [2.0, np.sqrt(3)],
+    ]
+)
+VECTORS = np.array([[1.5, -np.sqrt(3) / 2], [1.5, 1.5 * np.sqrt(3)]])
+CELL = HP.Lattice(POINTS, VECTORS)
+
+num0 = 7
+num1 = 4
+alpha = 0.30
+beta = 0.50
+
+step = 0.01
+ratios = np.arange(-0.7, 0.7 + step, step)
+kpoints = np.matmul(
+    np.stack(np.meshgrid(ratios, ratios, indexing="ij"), axis=-1),
+    4 * np.pi * np.identity(2) / np.sqrt(3)
+)
+BZBoundary = HP.TRIANGLE_CELL_KS[[*range(6), 0]]
+
+Hx, Hy, Hz = HMatrixGenerator(alpha, beta)
+cluster, category, x_bonds, y_bonds, z_bonds = ClusterGenerator(
+    num0=num0, num1=num1, cell=CELL
+)
+args = (cluster.point_num, category, x_bonds, y_bonds, z_bonds, Hx, Hy, Hz)
+
+res = basinhopping(
+    EnergyCore0, np.pi * np.random.random(2 * len(category)),
+    niter=200, minimizer_kwargs={"args": args}
+)
+phis = res.x[0::2]
+thetas = res.x[1::2]
+sin_phis = np.sin(phis)
+cos_phis = np.cos(phis)
+sin_thetas = np.sin(thetas)
+cos_thetas = np.cos(thetas)
+
+cell_vectors = np.array(
+    [sin_phis * cos_thetas, sin_phis * sin_thetas, cos_phis]
+)
+cluster_vectors = np.empty((cluster.point_num, 3), dtype=np.float64)
+for cell_index, cluster_indices in category.items():
+    cluster_vectors[cluster_indices] = cell_vectors[:, cell_index]
+
[…]

### 2020-08-01 FiguresForPaper/ShowAppendixSSF.py
Add `ShowAppendixSSF.py`.

@@ -1,0 +1,78 @@
+"""
+Show the static magnetic structure factors (SMSF) for some representative model
+parameters.
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+from HamiltonianPy import TRIANGLE_CELL_MS as MS
+
+from FontSize import *
+
+BZLW = 5
+COLORMAP = "hot_r"
+BZCOLOR = "tab:green"
+SF_DATA_NAME_TEMP = "data/SF_num1=4_num2=6_which=avg_" \
+                    "alpha={0:.4f}_beta={1:.4f}.npz"
+
+sub_fig_tags = ["(a)", "(b)", "(c)", "(d)"]
+params = [(0.50, 0.50), (0.50, 1.86), (0.30, 1.30), (0.7, 1.65)]
+
+fig, axes = plt.subplots(nrows=2, ncols=2, sharex="all", sharey="all")
+for index in range(len(params)):
+    alpha, beta = params[index]
+    ax = axes[divmod(index, 2)]
+    sub_fig_tag = sub_fig_tags[index]
+    title = r"$\alpha={0:.2f}\pi,\beta={1:.2f}\pi$".format(alpha, beta)
+
+    sf_data_name = SF_DATA_NAME_TEMP.format(alpha, beta)
+    with np.load(sf_data_name) as ld:
+        BZBoundary = ld["BZBoundary"]
+        factors = ld["factors"][0::5, 0::5]
+        kpoints = ld["kpoints"][0::5, 0::5, :]
+    vmin = np.min(factors)
+    vmax = np.max(factors)
+
+    im = ax.pcolormesh(
+        kpoints[:, :, 0], kpoints[:, :, 1], factors,
+        cmap=COLORMAP, shading="gouraud", zorder=0,
+    )
+    im.set_edgecolor("face")
+
+    colorbar = fig.colorbar(im, ax=ax, pad=0.01, format="%.1f")
+    colorbar.ax.tick_params(axis="y", labelsize="large")
+    colorbar.set_ticks(np.linspace(vmin, vmax, 5, endpoint=True))
+    colorbar.ax.tick_params(axis="y", labelsize=SMALL)
+
+    ax.plot(
+        BZBoundary[:, 0], BZBoundary[:, 1], zorder=1,
+        ls="dashed", lw=BZLW, color=BZCOLOR, alpha=1.0,
+    )
+
+    ax.text(
+        0.0, 0.98, sub_fig_tag,
[…]

### 2020-08-01 paper/paper.tex
20200801 20:05

@@
     \includegraphics[width=\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
-    \includegraphics[width=\linewidth]{fig/SecondDerivatives.pdf}
     \caption{\label{fig:QuantumPhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
@@
     \caption{\label{fig:ClassicalPhaseDiagram}(Color online) Classical global phase diagram of the $J$-$K$-$\Gamma$ model obtained from classical Monte Carlo simulation.}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/SixSitesOrder.pdf}
+    \caption{\label{fig:SixSitesOrder}(Color online) Spin configuration and spin structure factor for \emph{six-chains stripe order}. The green dashed line in (b) marks the first Brillouin Zone.}
 \end{figure}
@@
 
-\section{\label{apx:AppendixA}Classical ground states for some special model parameters}
+\section{\label{apx:AppendixA}Phase Boundaries in the Quantum Phase Diagram}
+
+To obtain the quantum phase diagram of the model \eqref{eq:Hamiltonian}, we perform exact-diagnoalization calculations of the GS of the Hamiltonian\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with the periodic boundary conditions.
+The phase boundaries are obtained from the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
+Some representive curves are shown in Fig.~\ref{fig:SecondDerivatives}.
+For Fig.~\ref{fig:SecondDerivatives}(a), $\alpha=0.05\pi$, the second derivative of $E_0$ versus $\beta$ has two peaks located at $\beta=-0.01\pi$ and $\beta=0.81\pi$, which are the phase boundaries between the FM-A and QSL phase.
+As we increase $\alpha$ to $0.3\pi$, there are three singularities in the second derivatives, see Fig.~\ref{fig:SecondDerivatives}(b).
+The small peak at $\beta=0.62\pi$ indicates the phase transition from Stripe-C to Stripe-B and the other two sharp peaks at $\beta=0.94\pi$ and $\beta=1.87\pi$ originate from the phase transitions from Stripe-B to FM-A and from FM-A to Stripe-C.
+Fig~\ref{fig:SecondDerivatives}(c) show the case for $\alpha=0.75\pi$, the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signifying the phase transitions between Stripe-B and FM-C.
+On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$'s and the corresponding results are shown in Fig.~\ref{fig:SecondDerivatives}(d)-(f).
+In Fig.~\ref{fig:SecondDerivatives}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$and $\alpha=0.097\pi$ reveal the phase transitions from FM-A to QSL and further to Stripe-C.
+The broad peak at about $\alpha=0.5\pi$ is due to the phase transitions from Stripe-C to Stripe-D to Stripe-B.
+The last singularity at $\alpha=0.93\pi$ marks the phase boundary between Stripe-B and FM-C.
+In Fig.~\ref{fig:SecondDerivatives}(e) we show the phase transition between \emph{modulated six chains stripe} and 120$^\circ$ N\'{e}el as well as the phase transition from 120$^\circ$ N\'{e}el to Stripe-B.
+$\beta$ is fixed to $0.5\pi$ and transitions occur at $\alpha=0.32\pi$ and $\alpha=0.62\pi$ respectively.
+Last but not least, we show there are phase transitions between these different FM phases.
+See Fig.~\ref{fig:SecondDerivatives}(f) where $\beta=1.5\pi$, the sharp peak at $\alpha=0.5\pi$ shows that the FM-A phase for the HK model is a cirtical point, infinitesimal $\Gamma$ interaction will cause phase transition to other FM phases which have different moment direction from FM-A phase.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/SecondDerivatives.pdf}
+    \caption{\label{fig:SecondDerivatives}Second derivatives of ground state energies versus $\alpha$ or $\beta$.
+The blue lines are the ground state energies and the red lines are the second derivatives.
+(a)-(c) $-\partial^2E_0/\partial\beta^2$ with $\alpha$ fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively.
+(d)-(f) $-\partial^2E_0/\partial\alpha^2$ with $\beta$ fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively.}
+\end{figure}
+
+\section{\label{apx:AppendixB}Quantum Static Spin Structure Factors}
+
+Here we provide additional spin structure factor profiles as a supplement to these profiles shown in the main text.
+For classical 120$^\circ$ N\'{e}el state, the SSF has high intensity at the corner of the first BZ, i.e., $\tilde{K}$ points and the SSF peaked at the middle points of $\tilde{\Gamma}$ and $\tilde{K}$'s for classical Dual N\'{e}el state.
+Fig.~\ref{fig:AppendixSSF}(a) and (b) show the SSF profiles calculated from our exact diagnoalization ground state at $\alpha=0.5\pi, \beta=0.5\pi$ and $\alpha=0.5\pi, \beta=1.85\pi$ which belong the 120$^\circ$ N\'{e}el phase and Dual N\'{e}el phase respectively.
+For both profile, though the SSF intensity is diffusive in the reciprocal space, the points with highest intensity are consistent with the classical states.
+
+In the main text, we show the SSF profiles for $alpha=0$ and $\alpha=\pi$, which provide evidence that the ground state for the pure $\Gamma$ model is FM ordered.
+However, these two points are too close to the phase boundary.
+One might question whether the SSF profiles of these two points are typical for the whole region.
+Here we show another two SSF profiles with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ which belong to FM-A phase and FM-C phase respectively.
+Both SSF profile has high intensity at $\tilde{\Gamma}$ point, which is a typical characteristic of FM ordered state.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/AppendixSSF.pdf}
+    \caption{\label{fig:AppendixSSF}(Color online) Static spin structure factors for some representative model parameters.}
+\end{figure}
+
+\section{\label{apx:AppendixC}Classical ground states for some special model parameters}
 
@@
 
-\section{\label{apx:AppendixB}Classical energy and moment direction of the stripe ordered states}
+\section{\label{apx:AppendixD}Classical energy and moment direction of the stripe ordered states}
 

### 2020-08-03 FiguresForPaper/QuantumPhaseDiagramDataBase.py
Minor changes to `QuantumPhaseDiagramDataBase.py`.

@@ -32,53 +32,53 @@ PhaseTransitionPointsWithFixedAlpha = {
     "alpha=0.080": [0.850, 1.940],
     "alpha=0.085": [0.854, 1.940],
     "alpha=0.090": [0.500, 0.858, 1.940],
-    "alpha=0.095": [0.500, 0.502, 0.862, 1.935],
-    "alpha=0.100": [0.500, 0.504, 0.866, 1.930],
-    "alpha=0.105": [0.500, 0.506, 0.870, 1.925],
-    "alpha=0.110": [0.500, 0.508, 0.876, 1.923],
-    "alpha=0.115": [0.500, 0.510, 0.882, 1.921],
-    "alpha=0.120": [0.500, 0.512, 0.890, 1.919],
-    "alpha=0.125": [0.500, 0.514, 0.893, 1.917],
-    "alpha=0.130": [0.500, 0.516, 0.896, 1.916],
-    "alpha=0.135": [0.500, 0.518, 0.899, 1.913],
-    "alpha=0.140": [0.500, 0.520, 0.902, 1.910],
-    "alpha=0.145": [0.500, 0.522, 0.905, 1.910],
-    "alpha=0.150": [0.500, 0.524, 0.908, 1.910],
-    "alpha=0.155": [0.500, 0.526, 0.911, 1.910],
-    "alpha=0.160": [0.500, 0.528, 0.913, 1.908],
-    "alpha=0.165": [0.500, 0.530, 0.915, 1.906],
-    "alpha=0.170": [0.500, 0.532, 0.920, 1.904],
-    "alpha=0.175": [0.500, 0.534, 0.920, 1.902],
-    "alpha=0.180": [0.500, 0.536, 0.920, 1.900],
-    "alpha=0.185": [0.500, 0.538, 0.923, 1.900],
-    "alpha=0.190": [0.500, 0.540, 0.924, 1.900],
-    "alpha=0.195": [0.500, 0.542, 0.924, 1.900],
-    "alpha=0.200": [0.500, 0.544, 0.925, 1.900],
-    "alpha=0.205": [0.500, 0.546, 0.925, 1.895],
-    "alpha=0.210": [0.500, 0.548, 0.926, 1.890],
-    "alpha=0.215": [0.500, 0.550, 0.926, 1.890],
-    "alpha=0.220": [0.500, 0.552, 0.927, 1.890],
-    "alpha=0.225": [0.500, 0.554, 0.928, 1.890],
[…]

### 2020-08-03 FiguresForPaper/QuantumGlobalPhaseDiagram.py
Minor changes to `QuantumGlobalPhaseDiagram.py`.

@@ -15,7 +15,6 @@ EXTRA_HEIGHT = HEIGHT / 5
 yticks = np.array([0.00, 0.25, 0.50])
 xticks = np.array([0.00, 0.50, 1.00, 1.50])
 xtick_labels = ["K = 1", "J = 1", "K = -1", "J = -1"]
-# xtick_labels = [r"${0:.0f}^\circ$".format(beta * 180) for beta in xticks]
 fig, (ax_north, ax_south) = plt.subplots(
     nrows=1, ncols=2, subplot_kw={"polar": True},
     num="QuantumGlobalPhaseDiagram",
@@ -40,6 +39,10 @@ for alpha in np.arange(0.000, 0.505, ALPHA_STEP):
         bottom=bottom, height=height, color=colors, align="edge",
     )
     radius += HEIGHT
+ax_north.plot(
+    [0.26 * np.pi, 0.26 * np.pi], [0.09, 0.44],
+    ls="dashed", color="black", lw=2, alpha=0.70,
+)
 
 # Draw the south hemisphere
 radius = 0.00
@@ -66,7 +69,7 @@ ax_north.set_yticks(yticks)
 ax_north.set_xticks(xticks * np.pi)
 ax_north.set_xticklabels(xtick_labels, ha="center", va="center", fontsize=SMALL)
 ax_north.set_yticklabels(
-    [r"$\alpha={0:.0f}^\circ$".format(alpha * 180) for alpha in yticks],
+    [r"$\alpha=0$", r"$\alpha=\frac{\pi}{4}$", r"$\alpha=\frac{\pi}{2}$"],
     ha="center", va="center", fontsize=SMALL, x=1.15 * np.pi,
 )
 ax_north.annotate(
@@ -86,7 +89,8 @@ ax_south.set_yticks(yticks)
 ax_south.set_xticks(xticks * np.pi)
 ax_south.set_xticklabels(xtick_labels, ha="center", va="center", fontsize=SMALL)
 ax_south.set_yticklabels(
-    [r"$\alpha={0:.0f}^\circ$".format(alpha * 180) for alpha in (1 - yticks)],
+    # [r"$\alpha={0:.0f}^\circ$".format(alpha * 180) for alpha in (1 - yticks)],
+    [r"$\alpha=\pi$", r"$\alpha=\frac{3}{4}\pi$", r"$\alpha=\frac{\pi}{2}$"],
[…]

### 2020-08-06 paper/paper.tex
20200806 13:50

@@
     \includegraphics[width=\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
-    \caption{\label{fig:QuantumPhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
+    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
 The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
-There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase.
-The three FM phases different from each other in the direction of the ordered moment, and also the four stripe phases are distinguished by their moment directions, see main text for details.
-(b) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=1.5\pi$.
-(c) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=0$.
-(d) The red (blue) line is $-\partial^2E_0/\partial\beta^2$ ($E_0$) versus $\beta$ with $\alpha=0.3\pi$.}
+There are in total nine phases including three different FM phases denoted as FM-A, FM-B and FM-C, three different stripe phases designated as Stripe-A, Stripe-B and Stripe-C, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase.
+The three FM phases different from each other in the direction of the ordered moment, and also the three stripe phases are distinguished by their moment directions, see main text for details.}
 \end{figure*}
 
-The quantum phase diagrams obtained by the exact-diagonalization method for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:QuantumPhaseDiagram}(a).
+The quantum phase diagrams obtained by the exact-diagonalization method for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:QuantumPhaseDiagram}.
 The phase boundaries are obtained from the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
@@
 For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found.
-When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix~\ref{apx:AppendixA} for details).
+When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix~\ref{apx:DegeneratedStates} for details).
 Based on these observation, it is reasonable to say that the GS of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions.
@@
 Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (such as FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
-The resulting probability maps for representive model parameters of FM-A and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(c) and (d).
+The resulting probability maps for representive model parameters of FM-A and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(a) and (b).
 It is worth to note that the large overlap between the exact cluster GS and FM ordered cluster spin-coherent state again provides solid evidence that the corresponding areas are FM phases.
@@
 However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction.
-For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(c)) with all directions degenerate.
-The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(d)).
+For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.
+The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(b)).
 The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model.
@@
 \end{subequations}
-see Appendix~\ref{apx:AppendixB} for their explicit expressions.
+see Appendix~\ref{apx:StripeMomentDirection} for their explicit expressions.
 
@@
 All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation.
-However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$ (see Appendix~\ref{apx:AppendixA} for details).
+However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$ (see Appendix~\ref{apx:DegeneratedStates} for details).
 The GS of the classical HK model near the antiferromagetic Kitaev point ($K=1$) is high degenerate and both positive and negative $\Gamma$ interactions select specific stripe ordered state as the GS.
@@
 To determined the ordered moment direction of those stripe phases in the quantum phase diagram, we construct stripe ordered cluster spin-coherent states and calculate their probabilities in the ED ground state.
-For brevity, we only construct cluster spin-coherent state based on \emph{config-x} and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(a), (e), (f), (b) for Stripe-A, Stripe-B, Stripe-C, Stripe-D respectively.
+For brevity, we only construct cluster spin-coherent state based on \emph{config-x} and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(c), (d), (e), (f) for Stripe-A, Stripe-D, Stripe-B, Stripe-C respectively.
 The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction.
 The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for \emph{config-x} from classical considerations, our ED results show that this situation also applies at quantum limit.
-On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(b) indicates that the ordered moment pointing to the $y$ and $z$-axis direction.
+On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(d) indicates that the ordered moment pointing to the $y$ and $z$-axis direction.
 The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for \emph{config-x}, $\pm x$, $\pm z$ for \emph{config-y}, $\pm x$, $\pm y$ for \emph{config-z}), more importantly it is a signature of large quantum flucations in the GS.
@@
 When an infinitesimal $\Gamma$ interaction is included, both positive and negative couplings tilting the ordered moment orientation away from the cubic axes directions, yielding the Stripe-B phase.
-The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
+The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:StripeMomentDirection} for details).
 As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different.
-An infinitesimal positive $\Gamma$ interaction changes the ordered moment orientation from the cubic axes directions to the direction specified by Eq.~\eqref{eq:v0} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
+An infinitesimal positive $\Gamma$ interaction changes the ordered moment orientation from the cubic axes directions to the direction specified by Eq.~\eqref{eq:v0} and its equivalents (see Appendix~\ref{apx:StripeMomentDirection} for details).
 On the other hand, when an infinitesimal negative $\Gamma$ interaction is introduced, the ordered moment is rotated to the direction determined by Eq.~\eqref{eq:v1} and its equivalents.
@@
 Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.
-To have further understanding of the characteristics of this phase, we also calculate the spin excitation spectrum and a typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}(b).
+To have further understanding of the characteristics of this phase, we also calculate the spin excitation spectrum and a typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}.
 The high intensities at both the center and M-points of the first BZ is consistent with the SMSF data.
@@
 
-\section{\label{apx:AppendixA}Phase Boundaries in the Quantum Phase Diagram}
+\section{\label{apx:PhaseBoundary}Phase Boundaries in the Quantum Phase Diagram}
 
@@
 
-\section{\label{apx:AppendixB}Quantum Static Spin Structure Factors}
+\section{\label{apx:SSF}Quantum Static Spin Structure Factors}
 
@@
 
-\section{\label{apx:AppendixC}Classical ground states for some special model parameters}
+\section{\label{apx:DegeneratedStates}Classical ground states for some special model parameters}
 
@@
 
-\section{\label{apx:AppendixD}Classical energy and moment direction of the stripe ordered states}
+\section{\label{apx:StripeMomentDirection}Classical energy and moment direction of the stripe ordered states}
 

### 2020-08-11 paper/paper.tex
20200811 9:24

--- 2020-07-29 paper/paper.tex
@@
 
-\author{\textcolor{cyan}{XXX}}
-\affiliation{\textcolor{cyan}{XXX}}
+\author{Zhongyuan Qi}
+\affiliation{College of Physics Science and Technology, Yangzhou University, Yangzhou 225002, China}
 
-\author{\textcolor{cyan}{XXX}}
-\affiliation{\textcolor{cyan}{XXX}}
+\author{Bin Xi}
+\affiliation{College of Physics Science and Technology, Yangzhou University, Yangzhou 225002, China}
 
@@
 \section{\label{sec:Introduction}Introduction}
+
 Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems.
 The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins.
-In particular, the special case where spins are $S=1/2$ has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a "quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
+In particular, the special case where spins are $S=1/2$ has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
 When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}.
@@
 The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204}, in which the NN Heisenberg interaction is also taken into account.
-This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripy, and zigzag types, besides extended spin-liquid phases near the Kitaev limits.
+This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripe, and zigzag types, besides extended spin-liquid phases near the Kitaev limits.
 Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e.
@@
 In fact, magnetic ions located at the center of edge-shared octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}.
-The HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization~\cite{KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}.
-All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripy types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types.
+The HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}.
+All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types.
 Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,JPSJ.85.114710}.
@@
 More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
-The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}.
+The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,PhysRevB.100.241116,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}.
 These triangluar magnets of rare-earth ions provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbit coupling.
 
-{
-    \color{red}The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK model.
-The exact diagonalization and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}.
-Section~\ref{sec:Results} disscuss the main results of this paper.
-}
+In this paper, we study the global phase diagram and the phase transitions of the triangular-lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses.
+We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations.
+In the HK limit ($\Gamma=0$), there are five classical phases: one FM, two stripe, one $120^{\circ}$ N\'{e}el and its dual phases.
+For the pure AFM Kitaev model, although the system has highly degenerate classical GSs composed of the stripe and nematic states, the order-by-disorder mechanism caused by quantum fluctuations makes the system select the stripe state to be the GS.
+When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases.
+With the aid of classical analysis, we determine the spin directions for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders.
+On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate.
+For the possible QSL phase, based on the investigation of the spin excitation spectrum, we find that the GS is probably a gapped $Z_{2}$ QSL.
+
+The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK limit.
+The ED and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}.
+Section~\ref{sec:Results} gives the main results of this paper.
 
@@
 
-To obtain the quantum phase diagram of the model~\eqref{eq:Hamiltonian}, we perform exact-diagonalization calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with the periodic boundary condition.
+To obtain the quantum phase diagram of the model~\eqref{eq:Hamiltonian}, we perform ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with the periodic boundary condition.
 To detect quantum phase transitions, the second derivatives of the GS energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and its singularities are used to identify possible phase transtions.
@@
 To further determine the magnetic configurations of the magnetically ordered phases, we employ a method by studying the projections of the exact GSs of the finite cluster to the classical states~\cite{PhysRevB.94.064435}.
-The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions.
-The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$, i.e.,
+The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin coherent states with varying moment directions.
+The cluster spin coherent state is a direct product of spin-1/2 coherent states on each site $i$, i.e.,
 \begin{align}
-    |\Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle,
+    | \Psi \rangle = \bigotimes_{i=1}^{N} | \theta_{i}, \phi_{i} \rangle,
     \label{eq:ClusterCoherentState}
@@
 \begin{align}
-    |\theta, \phi\rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle
+    | \theta, \phi \rangle = \mathcal{R}_{z}(\phi) \mathcal{R}_{y}(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle
     \label{eq:Spin-1/2CoherentState}
@@
 Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles.
-By calculating the overlap between the exact cluster GS and cluster spin-conherent states, $P = | \langle \Psi | GS \rangle|^2$, and maximizing its value with respect to $\theta$'s and $\phi$'s, we can then identify the classical spin pattern that best fits the exact quantum GS.
+By calculating the overlap between the exact cluster GS and cluster spin conherent states, $P = | \langle \Psi | GS \rangle |^2$, and maximizing its value with respect to $\theta$'s and $\phi$'s, we can then identify the classical spin pattern that best fits the exact quantum GS.
 
@@
 
-In order to better understand the quantum phases identified by the exact diagonalization method, we also perform classical Monte Carlo simulations.
+In order to better understand the quantum phases identified by the ED method, we also perform classical Monte Carlo simulations.
 We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$.
-For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24\times 24$ triangle lattice with periodic boundary conditions.
-A whole MC step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice.
-We perform $10^6$ MC steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS.
+For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24 \times 24$ triangle lattice with periodic boundary conditions.
+A whole Monte Carlo step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice.
+We perform $10^6$ Monte Carlo steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS.
 The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
 \begin{align}
-    \bm{S}_i = \frac{\bm{h}_i^{loc}}{|\bm{h}_i^{loc}|} S,
+    \bm{S}_{i} = \frac{\bm{h}_{i}^{loc}}{|\bm{h}_{i}^{loc}|} S,
 \end{align}
@@
 \begin{align}
-    \bm{h}_i^{loc} = \sum_{\langle j \rangle} J \bm{S}_j + K {S}^{\gamma}_j \hat{e}^{\gamma} + \Gamma (S^\alpha_j \hat{e}^{\beta} + S^\beta_j \hat{e}^\alpha),
+    \bm{h}_{i}^{loc} = \sum_{\langle j \rangle} J \bm{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
 \end{align}
@@
 
-From the magnetic configuration of GS, we compute the spin structure factor given by
+From the magnetic configuration of GS, we compute the SSF given by
 \begin{align}
@@
     \centering
-    \includegraphics[width=\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
-    \includegraphics[width=\linewidth]{fig/SecondDerivatives.pdf}
-    \caption{\label{fig:QuantumPhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
+    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
+    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
 The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
-There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase.
-The three FM phases different from each other in the direction of the ordered moment, and also the four stripe phases are distinguished by their moment directions, see main text for details.
-(b) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=1.5\pi$.
-(c) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=0$.
-(d) The red (blue) line is $-\partial^2E_0/\partial\beta^2$ ($E_0$) versus $\beta$ with $\alpha=0.3\pi$.}
+There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, three different stripe phases designated as Stripe-A, Stripe-B and Stripe-C, Modulated Stripe, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase.
+The three FM phases different from each other in the direction of the ordered moment, and also the three stripe phases are distinguished by their moment directions, see main text for details.}
 \end{figure*}
 
-The quantum phase diagrams obtained by the exact-diagonalization method for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:QuantumPhaseDiagram}(a).
-The phase boundaries are obtained from the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
+The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}.
+The phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).
 
 In the HK limit ($\Gamma=0$), as with the previous study~\cite{KaiLi2015}, we find five quantum phases.
-For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$.
-As mentioned in Sec.~\ref{sec:Model}, the form of the HK model ($\Gamma=0$) is invariant under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions.
+For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively.
+As mentioned in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions.
 Thus, by virtue of the FST, two more magnetic ordered phases can be identified.
 When $\beta=\pi - \arctan\frac{1}{2}$ in Eq.~\eqref{eq:FST}, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$, whose GS is a FM state.
-Thus, transformating back to the original spin basis, a collinear stripe order can be obtained.
-Similarly, a noncollinear spiral order (dual N\'{e}el) is obtained from the 120$^\circ$ N\'{e}el order for $\beta=-\arctan\frac{1}{2}$.
-However, for the phase near the AFM Kitaev point ($J=\Gamma=0$, $K>0$), it is mapped to itself under FST, so we can not identify its magnetic properties with the FST.
+Therefore, transformating back to the original spin basis, a collinear stripe order can be obtained.
+Similarly, a noncollinear spiral order (Dual N\'{e}el) is obtained from the 120$^\circ$ N\'{e}el order for $\beta=-\arctan\frac{1}{2}$.
+However, for the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since it is mapped to itself under FST, we can not identify its magnetic properties with the FST.
 
-When the $\Gamma$ term is included, we find that the stripe phase, the FM phase and the phase near the AFM Kitaev point in the HK model are actually phase boundaries in the global phase diagram of the $J$-$K$-$\Gamma$ model.
-Moreover, except the 120$^\circ$ N\'{e}el state and the dual N\'{e}el state, which already exist in the HK limit, there are six other new phases.
+The properties of each quantum phases, especially the spin configuration of the ordered phases, can be inferred from the SSF defined in Eq.~\eqref{eq:SSF}, so we calculate the SSF for the case of pure AFM Kitaev limit ($J=\Gamma=0$, $K=1$) and present the result in Fig.~\ref{fig:StructureFactors}(a).
+We find that the SSF shows obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i).
+For the sake of clarity, we further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters.
+The stripe orders are indeed possible GS spin configurations, but there are also many nematic states with the same energy as it at the classical level since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details).
+When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order.
+Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
+Moreover, every stripe order in this phase can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.
 
-To reveal the natures of these new phases, we perform the classical MC calculations as described in Sec.~\ref{subsec:MethodMC}.
-For convenience of comparison between the quantum and classical results, we also present the classical phase diagram obtained from the MC simulations in Fig.~\ref{fig:ClassicalPhaseDiagram}, which is consistent with the phase diagram reported in Ref.~\onlinecite{PhysRevB.92.165108}.
-According to the classical MC results, we can identify that the three new phases with large areas mainly located in the $J>0$ region have stripe orders (i.e., the stripe-B and stripe-C phases), while the two new phases mainly located in the $J<0$ region are FM (i.e., the FM-A and FM-C phases).
-In addition, we find that the area of the 120$^\circ$ N\'{e}el state in the quantum phase diagram is greatly reduced, and more importantly the extra phase near $\Gamma=1$ that does not exist in the classical phase diagram.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{fig/ClassicalGlobalPhaseDiagram.pdf}
-    \caption{\label{fig:ClassicalPhaseDiagram}(Color online) Classical global phase diagram of the $J$-$K$-$\Gamma$ model obtained from classical Monte Carlo simulation.}
-\end{figure}
+When the $\Gamma$ term is included, we find that the FM phase and the stripe-C phase in the HK model are actually phase boundaries in the global phase diagram of the $J$-$K$-$\Gamma$ model.
+Moreover, except the 120$^\circ$ N\'{e}el state and the dual N\'{e}el state, which already exist in the HK limit, there are five other new phases according to the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
 
-The properties of each quantum phases, especially the spin configuration of the ordered phases, can also be inferred from the SSF in~\eqref{eq:SSF},  so we illustrate the results for some typical parameters in Fig.~\ref{fig:StructureFactors}.
-The results in Fig.~\ref{fig:StructureFactors}(d) and (e) show the SSFs in the stripe-B and stripe-C phases, respectively.
-It is clear that the SSFs are peaked at the $\tilde{M}$ points of the first Brillouin zone (BZ), which is a typical characteristic of stripe ordered states.
-For the case of pure AFM Kitev limit ($J=\Gamma=0$, $K=1$), the SSF in Fig.~\ref{fig:StructureFactors}(a) shows the same structure as those in Fig.~\ref{fig:StructureFactors}(d) and (e), so the GSs around the AFM Kitev point also belongs to a stripe phase, which we label the stripe-D phase.
-In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the results of two other special points with $\Gamma=\pm1$ and $J=K=0$, i.e., the pure $\Gamma$ models.
-We find that the GSs of both models have ferromagnetic order, as the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ.
-The ferromagnetic phases contains these two specail points are denoted with FM-A and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}(a).
-The SSF for the quantum phase that does not exist in the classical phase diagram in a small region around the point with $J=K=0$ and $\Gamma=1$ is illustrated in Fig.~\ref{fig:StructureFactors}(f), which exhibits high intensities at both $\tilde{\Gamma}$ and $\tilde{M}$.
-{\color{red}It seems impossible for a classical magnetically ordering state to satisfy these two wave vectors simultaneously, so we infer that this quantum phase is a QSL.}
+To reveal the natures of these new phases, we further study the SSFs in these new phases.
+Since the stripe phase for $K<0$ in the HK limit is located inside a phase of the global phase diagram, we infer this phase to have a stripe order and denote it as the stripe-A phase in Fig.~\ref{fig:QuantumPhaseDiagram}.
+To confirm this, we present the SSFs for two typical points, i.e.
+$\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$, in the $\Gamma>0$ and $\Gamma<0$ regions in Fig.~\ref{fig:StructureFactors}(b) and (c), respectively.
+Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a signature feature of the stripe phase.
+In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-B in the phase diagram.
+
+When we carefully examine the SSF near $\beta=0.5\pi$, we find that the SSF is obviously different from those of the stripe phases.
+As shown in Fig.~\ref{fig:StructureFactors}(e) for $\alpha=0.3\pi$ and $\beta=0.5\pi$, besides the peaks at the $\tilde{M}$ points, the SSF also shows significant intensities along the boundary of the BZ.
+In order to clarify whether there is another magnetic ordering phase near $\beta=0.5\pi$, we use the ``basin-hopping" technique again to search for the possible spin order for $\alpha=0.3\pi$ and $\beta=0.5\pi$ on a $12 \times 12$ lattice.
+The spin configuration is depicted in Fig.~\ref{fig:ModulatedStripe}(a), which exhibits a modulated stripe order.
+For this modulated stripe order, the spins are ferromagnetic along a next-nearest-neighbor direction and the spin orientation of the ferromagnetic chains are modulated to form a structure with a period of six.
+As illustrated in Fig.~\ref{fig:ModulatedStripe}(b), the SSF of this classical six-chain stripe order shows clear peaks at the $\tilde{K}$ points in addition to those at the $\tilde{M}$ points, which is consistent with the characteristic of the SSF in Fig.~\ref{fig:StructureFactors}(e) calculated by the ED.
+We further perform a classical Monte Carlo simulations (see Sec.~\ref{subsec:MethodMC}) on a $24 \times24$ lattice to check the stability of the modulated stripe order in the large-size systems, and the ground-state spin configuration is shown in Fig.~\ref{fig:ModulatedStripe}(c).
+We find that the spin arrangement is still a modulated stripe order, but the spin orientations are also modulated along the ferromagnetic chains in addition to a larger modulated period perpendicular to the chains.
+Thus, we divide a transition region between the stipe-A and stripe-B phase and term it the modulated stripe order phase.
+
+For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively.
+Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-A and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
+We note that there are two special points with $J=K=0$ and $\Gamma=\pm1$ in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}.
+Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the numerical simulations by using the ``basin-hopping" global optimization and classical Monte Carlo methods.
+For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state.
+For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state also appear (see Appendix~\ref{apx:DegeneratedStates} for details).
+However, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states according to our ED calculations.
+This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
-    \caption{\label{fig:StructureFactors}(Color online) SSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice.}
+    \caption{\label{fig:StructureFactors}(Color online) SSF for different model paramters.
+The green dashed lines marks the first BZ corresponding to the triangular lattice.
+See Appendix~\ref{apx:SSF} for SSF profiles of other representative model parameters.}
 \end{figure}
 
-According the above analysis, we find that, unlike the case for the honeycomb lattice, the Kitaev interactions on the triangular lattice do not give rise to QSL states, so the quantum phase diagram is similar to its classic counterpart.
-Here, the large coordination number plays a key role to stabilize the classical magnetic order, although the geometric and exchange frustrations coexist in the triangular lattice $J$-$K$-$\Gamma$ model.
-Although we have basically determine the nature of each phase, there are still two problems should be explained: first, why there are phase transitions between the phases with the same type of classical order, suas the phase transitions between FM phases and stripe phases; second, what other important characteristics of the QSL phase in the phase diagram can be used to help us understand its properties more deeply.
+According to the above analysis, we find that, unlike the case for the honeycomb lattice, the Kitaev interactions on the triangular lattice do not give rise to QSL states, so the quantum phase diagram is similar to its classical counterpart~\cite{PhysRevB.92.165108}.
+Here, the large coordination number plays a key role to stabilize the classical magnetic orders, although the geometric and exchange frustrations coexist in the triangular lattice $J$-$K$-$\Gamma$ model.
+However, the SSF for the quantum phase in a small region around the point with $J=K=0$ and $\Gamma=1$ illustrated in Fig.~\ref{fig:StructureFactors}(h) exhibits high intensities at both $\tilde{\Gamma}$ and $\tilde{M}$ points, and it seems impossible for a classical magnetically ordering state to satisfy these two wave vectors simultaneously, so we infer that this quantum phase is a QSL candidate.
+
+Although we have basically determine the nature of each phase, there are still two problems should be explained: first, why there are phase transitions between the phases with the same type of classical orders, such as the phase transitions between FM phases or stripe phases, and why the FM and stripe phases of the HK model are the phase boundaries in the global phase diagram of $J$-$K$-$\Gamma$ model; second, what other important characteristics of the possible QSL phase in the phase diagram can be used to help us understand its properties more deeply.
 In the followings, we will address these problems.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
+    \caption{\label{fig:ModulatedStripe}(Color online) Illustration of the modulated stripe order.
+(a) The spin configuration obtained from basin-hopping optimization for a $12 \times 12$ cluster.
+(b) Classical spin structure factor corresponding to the spin configuration shown in (a).
+(c) The spin configuration obtained from classical Monte Carlo for a $24 \time 24$ cluster.}
+\end{figure}
 
@@
 
-To have a better understanding of the phase transitions between these FM phases, we first study the classical $J$-$K$-$\Gamma$ model where the spin operators are viewed as unit-vectors in three dimension.
-For classical FM states, all spins are aligned in parallel and the energy of the $J-K-\Gamma$ model per lattice site is given by
+To have a better understanding of the phase transitions between these FM phases, we first study the classical $J$-$K$-$\Gamma$ model where the spin operators are viewed as unit-vectors in the three dimension.
+For classical FM states, all spins are aligned in parallel and the energy per lattice site is given by
 \begin{equation}
@@
 \end{equation}
-where $v^x$, $v^y$, $v^z$ are the corresponding components of the classical moment vector.
-On this level, the moment direction of the classical FM state is determined solely by $\Gamma$ and the problem becomes finding the global minimum and maximum of the multi-variable function $f(v^x, v^y, v^z) = v^x v^y + v^y v^z + v^z v^x$ with the constraint $|\bm{v}| = 1$.
-$f(v^x, v^y, v^z)$ takes maximum value $f_{max}=1$ at $v^x=v^y=v^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $v^x + v^y + v^z = 0$ and $|\bm{v}| = 1$ are fulfilled.
-The condition $v^x + v^y + v^z = 0$ specifies a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction.
-Considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) this is actually the plane of the triangular lattice.
-That is to say, for $\Gamma > 0$ the ordered moment of the classcial FM state prefers to lie in the lattice plane and when $\Gamma$ is negative, the ordered moment would perpendicular to the lattice plane.
+where $v^x$, $v^y$, $v^z$ are the three components of the classical moment vector.
+On this level, the moment direction of the FM state is determined solely by $\Gamma$, so the problem becomes finding the global minimum and maximum of the multi-variable function $f(v^x, v^y, v^z) = v^x v^y + v^y v^z + v^z v^x$ with the constraint $|\bm{v}| = 1$.
+$f(v^x, v^y, v^z)$ takes the maximum value $f_{max}=1$ at $v^x=v^y=v^z=\pm 1/\sqrt{3}$ and minimum value $f_{min}=-0.5$ when the conditions $v^x + v^y + v^z = 0$ and $|\bm{v}| = 1$ are fulfilled.
+The condition $v^x + v^y + v^z = 0$ specifies a plane perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) it is actually the plane of the triangular lattice.
+That is to say, for $\Gamma > 0$ the ordered moment of the classical FM state prefers to lie in the lattice plane, while for $\Gamma<0$ the ordered moment would perpendicular to the lattice plane.
+This is the reason that there is a phase transition between the FM-A and FM-C phases, since the dependence of the ground state energy on the interaction parameters is different for the two FM phases, and the phase boundary is the line with $\Gamma=0$.
 
-Our classical Monte Carlo simulation found FM ordered states with the right moment direction for majority of the area marked as FM phase (see Fig.~\ref{fig:ClassicalPhaseDiagram}) except for the pure $\Gamma$ term.
-For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found.
-When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix~\ref{apx:AppendixA} for details).
-Based on these observation, it is reasonable to say that the GS of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions.
-For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM ordered state as the GS.
-On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS.
-
-In light of the classical analysis, we conjecture the main differences between these FM phases lies in the ordered moment direction.
-To further confirm our hypothesis, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435} to extract the moment direction of these FM phases from our ED cluster ground state.
-Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (such as FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
-The resulting probability maps for representive model parameters of FM-A and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(c) and (d).
-It is worth to note that the large overlap between the exact cluster GS and FM ordered cluster spin-coherent state again provides solid evidence that the corresponding areas are FM phases.
-For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction.
-The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction).
-In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis.
-However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction.
-For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(c)) with all directions degenerate.
-The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(d)).
-The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model.
-For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order.
-However, for the quantum model, quantum flucations select the FM ordered states lie in the lattice plane as GS out of an otherwise infinitely degenerate manifold of classical states.
-Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM state perpendicular to the lattice plane is selected as the GS.
-This selection of states among degenerate classical ground states is the so called \emph{order-from-disorder} mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.
-
-In the HK limit, the GS of the model near the $J=-1$ point is FM state and the ordered moment is fixed to the $x,y,z$-axis direction by the Kitaev interaction.
-When an infinitesimal $\Gamma$ interaction is introduced, positive couplings drive the ordered moment to the lattice plane and negative couplings pinning the ordered moment to be perpendicular to the lattice plane.
+The classical analysis suggests that the main difference between these FM phases lies in the ordered moment direction.
+To further confirm this, we use the spin coherent state to extract the moment direction of these FM phases from our ED cluster GS~\cite{PhysRevB.94.064435}.
+Since the cluster spin coherent state defined in Eq.~(\ref{eq:Spin-1/2CoherentState}) is captured only by a single pair of $(\theta, \phi)$ for the collinear states, it is easy to determine the direction of the FM orders by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
+The resulting probability maps for two representative interaction parameters of FM-A and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(a) and (b), where the large overlap between the exact cluster GS and FM cluster spin coherent state again provides solid evidence that the corresponding areas are FM phases.
+For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.
+The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in Fig.
+\ref{fig:Proabilities}(b)).
+Thus, the moment directions extracted from the ED cluster GS are consistent with the classical analysis.
+In the HK limit, for the pure FM Heisenberg model ($J=-1$), the FM state is spin rotational invariant and the ordered moment can point any direction.
+The Kitaev interaction breaks the spin rotational symmetry and pins the orderings to the axis direction (i.e., $x$, $y$ and $z$ directions) when the quantum fluctuations are included, although the classical energy in Eq.~(\ref{eq:EcFM}) is independent of the moment direction (see Appendix~\ref{apx:LSWOfFMA} for details).
+When the $\Gamma$ interactions are introduced, positive $\Gamma$ couplings drive the ordered moment to the lattice plane and negative $\Gamma$ couplings pin the ordered moment to be perpendicular to the lattice plane.
+Therefore, the line with $\Gamma=0$ is the phase boundary of the FM-A and FM-C phases.
 
@@
 
-Inspired by the previous discussion of those FM phases, we perform the same analysis for these stripe phases.
-For stripe order, there are three degenerated spin configurations in real-space, designated as \emph{config-x}, \emph{config-y} and \emph{config-z} respectively.
-For \emph{configx}, the spins on the chains along the $x$-bond direction form ferromagnetic chains and adjacent chains are anti-parallel.
-Similarly, the ferromagnetic chains along the $y$-bond and $z$-bond direction for \emph{config-y} and \emph{config-z} respectively.
-For \emph{config-x}, the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} per lattice site is
+Inspired by the previous discussion of FM phases, we here perform the same analysis for the stripe phases.
+For stripe order, there are three degenerated spin configurations in real-space, designated as stripe-$x$, stripe-$y$ and stripe-$z$, where the FM chains are along the $x$-bond, $y$-bond and $z$-bond directions, respectively.
+For simplicity, we take the stripe-$x$ configuration as an example, and the other two configurations can be obtained by analogy.
+The energy per lattice site is
 \begin{eqnarray}
-    E_{StripeX}^{c} & = & -(J + K) + 2 K v^x v^x \nonumber \\
-        & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y)
+    E_{stripe-x}^{c} & = & -(J + K) + 2 K v^x v^x \nonumber \\
+        & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y).
         \label{eq:EcStripeX}
 \end{eqnarray}
-and the energy for \emph{config-y} and \emph{config-z} can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$.
-The ordered moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$.
-In general ($K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has six extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ equal zero.
-Here we give three of them explicitly and the other three are opposite to the given ones
+The ordered moment direction of the classical stripe order is determined by the interaction parameters $K$ and $\Gamma$.
+In general ($K,\Gamma \neq 0$), $E_{stripe-x}^{c}$ has six extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ are equal to zero.
+Here we give three of them explicitly and the other three are opposite to the given ones,
 \begin{subequations}
@@
     \begin{eqnarray}
-        & \bm{v}_0:& \quad v_{0}^{y}=-v_{0}^{z} = 1/\sqrt{2}, \quad v_{0}^{x} = 0 \label{eq:v0} \\
-        & \bm{v}_1:& \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), \quad v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y} \label{eq:v1} \\
-        & \bm{v}_2:& \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), \quad v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y} \label{eq:v2}
+        & \bm{v}_0:& \quad v_{0}^{y}=-v_{0}^{z} = 1/\sqrt{2}, \quad v_{0}^{x} = 0, \label{eq:v0} \\
+        & \bm{v}_1:& \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), \quad v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y}, \label{eq:v1} \\
+        & \bm{v}_2:& \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), \quad v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y}, \label{eq:v2}
     \end{eqnarray}
 \end{subequations}
-see Appendix~\ref{apx:AppendixB} for their explicit expressions.
+where
+\begin{align}
+& f_{1,2}(K, \Gamma)= \frac{|\Gamma|}{\sqrt{4 \lambda_{1,2} (\lambda_{1,2} + \Gamma) + 3 \Gamma^{2}}}, \nonumber \\
+& g_{1,2}(K, \Gamma)= (2 \lambda_{1,2} + \Gamma) / \Gamma, \nonumber
+\end{align}
+with
+\begin{align}
+& \lambda_{1}=- (\Gamma +2 K - \sqrt{9\Gamma^2 - 4 \Gamma K + 4 K^2}) / 4, \nonumber \\
+& \lambda_{2}=-(\Gamma +2 K + \sqrt{9\Gamma^2 + 4 \Gamma K + 4 K^2}) / 4. \nonumber
+\end{align}
 
-For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $v^x = 0$ which means that \emph{config-x} prefers to lie in the $yz$ plane.
-An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction whereas negative $\Gamma$ drives it to the $\bm{v}_1$ direction.
-When $\Gamma=0, K<0$, the ordered moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\bm{v}_1$ direction.
-All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation.
-However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$ (see Appendix~\ref{apx:AppendixA} for details).
-The GS of the classical HK model near the antiferromagetic Kitaev point ($K=1$) is high degenerate and both positive and negative $\Gamma$ interactions select specific stripe ordered state as the GS.
+In the HK limit, for $K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{stripe-x}^{c}$ takes minimum value at $v^x = 0$ which means that stripe-$x$ prefers to lie in the $yz$ plane.
+An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction, whereas the negative $\Gamma$ drives it to the $\bm{v}_1$ direction.
+Thus, there is a phase transition between the stripe-A and stripe-B phases, as the ground state energies have different dependence on the interaction parameters for the two stripe phases, and the phase boundary is the line with $\Gamma=0$.
 
-To determined the ordered moment direction of those stripe phases in the quantum phase diagram, we construct stripe ordered cluster spin-coherent states and calculate their probabilities in the ED ground state.
-For brevity, we only construct cluster spin-coherent state based on \emph{config-x} and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(a), (e), (f), (b) for Stripe-A, Stripe-B, Stripe-C, Stripe-D respectively.
-The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction.
-The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for \emph{config-x} from classical considerations, our ED results show that this situation also applies at quantum limit.
-On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(b) indicates that the ordered moment pointing to the $y$ and $z$-axis direction.
-The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for \emph{config-x}, $\pm x$, $\pm z$ for \emph{config-y}, $\pm x$, $\pm y$ for \emph{config-z}), more importantly it is a signature of large quantum flucations in the GS.
-It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states.
-Stripe-D different from Stripe-A in the direction of the ordered moment direction.
-To be specific, for a certain spin configuration, the ordered moment would along only one of the $x, y, z$-axis direction in the Stripe-A phase and point to the other two axes directions for the Stripe-D phase.
-When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$ (See the green solid circle in \ref{fig:Proabilities}(e) and (f)).
-Considering the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the exact cluster GS, it is reasonable to say that the stripe ordered ground states for the classical $J-K-\Gamma$ model in these areas persist in the quantum limit and the ordered moments of the quantum states coincide with their classical analogue.
-The reduced probabilities $P_{max} < \frac{1}{6}$ may be attributed to quantum flucations.
+To confirm that the classical analysis is consistent with our ED calculations, we use the spin coherent states again to extract the ordered moment direction of the ED ground states in these stripe phases.
+For brevity, we here only construct cluster spin coherent state based on the stripe-$x$ and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(c) and (d) for stripe-A and stripe-B, respectively.
+We can see that there are large overlaps between the exact cluster GS and stripe cluster spin coherent state, which indicates that the results based on the ED calculation is consistent with the classical analysis.
 
-In the HK limit, there exist a stripe phase (i.e., Stripe-A) when $J>0, K<0$ and the ordered moment along the $x,y,z$-axis direction.
-When an infinitesimal $\Gamma$ interaction is included, both positive and negative couplings tilting the ordered moment orientation away from the cubic axes directions, yielding the Stripe-B phase.
-The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
-As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different.
-An infinitesimal positive $\Gamma$ interaction changes the ordered moment orientation from the cubic axes directions to the direction specified by Eq.~\eqref{eq:v0} and its equivalents (see Appendix~\ref{apx:AppendixB} for details).
-On the other hand, when an infinitesimal negative $\Gamma$ interaction is introduced, the ordered moment is rotated to the direction determined by Eq.~\eqref{eq:v1} and its equivalents.
+\subsection{\label{subsec:QSL}Possible QSL}
 
-\subsection{\label{subsec:QSL}Quantum Spin Liquid}
+Although the GSs of the pure Heisenberg, Kitaev and $\Gamma$ models are not QSL, the interplay of the Heisenberg, Kitaev and $\Gamma$ interactions may induce a possible QSL phase near the $\Gamma=1$ limit as discussed above according to the SSF.
+To have further understanding of the nature of this quantum phase that does not exist in the classical phase diagram~\cite{PhysRevB.92.165108}, we also calculate the DSF $A(\mathbf{k}, \omega)$, which in general can provide some critical information about the properties of a QSL.
+A typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}.
+We can find that a significant feature is that the whole spectrum is a broad continuum, which is a characteristic of QSL originating from the fractionalization of the $S=1$ spin excitations.
+Thus, the DSF gives another evidence that this quantum phase is a QSL.
+The DSF also shows another feature that the periodicity of its lower edge is doubled, which is a possible signature of the translational symmetry fractionalization of a $Z_{2}$ spin liquid~\cite{PhysRevB.90.121102,mei2015fractionalized,PhysRevB.99.205119}.
+Moreover, we also find that there is an obvious gap in the DSF.
+Thus, combined with all of the above results, we propose the GS of quantum $J$-$K$-$\Gamma$ model at the green area of the phase digram in Fig.~\ref{fig:QuantumPhaseDiagram} is a gapped $Z_{2}$ QSL.
 
-Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:QuantumPhaseDiagram}.
-For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ.
-Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase.
-To have further understanding of the characteristics of this phase, we also calculate the spin excitation spectrum and a typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}(b).
-The high intensities at both the center and M-points of the first BZ is consistent with the SMSF data.
-Moreover, there are continuum spectrum at high energy which is a characteristic of QSL.
-However, the $A(\mathbf{k}, \omega)$ does not have intensities at $\omega = 0$ which indicates the system described by the corresponding model Hamiltonian is gapped.
-Combined with all of the above results, we propose the GS of quantum $J-K-\Gamma$ model at the green area is a gapped QSL.
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
-    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$. $A(\bm{k}, \omega)$ is draw along the path $M-\Gamma-M-\Gamma$.}
+    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.1\pi$.
+$A(\bm{k}, \omega)$ is draw along the path $\tilde{M}-\tilde{\Gamma}-\tilde{M}-\tilde{\Gamma}$.}
 \end{figure}
@@
 \section{\label{sec:Summary}Summary}
-In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model.
-The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the antiferromagetic $\Gamma$ point.
-We propose the QSL to be gapped based on the spin excitation spectrum.
-Apart from this QSL phase, we also provide detailed description of the distinctions between those collinear phases.
-Especially, we propose the GS of the antiferromagetic Kitaev model to be a stripe ordered state and the ordered moment along the $x, y, z$-axis direction.
+
+In summary, by using exact diagnoalization calculations and classical analyses, we map out the global phase diagram of the $J$-$K$-$\Gamma$ model.
+The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the positive $\Gamma$ point, for which we propose the ground state to be a gapped $Z_{2}$ QSL based on its spin excitation spectrum.
+We also provide detailed descriptions of the phase transition between the classical magnetic phases.
+On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ and antiferromagnetic Kitaev models have specific orders, although the classical analyses suggest that the GSs are highly degenerate.
 
 \begin{acknowledgments}
-    \textcolor{red}{Acknowledgements.  To be accomplished $\cdots \cdots$}
+This work was supported by the National Natural Science Foundation of China (Grants No.
+11674158, No.
+11774152 and No.
+11774300) and National Key Projects for Research and Development of China (Grant No.
+2016YFA0300401).
 \end{acknowledgments}
@@
 % The following are the Appendixes of this article
-\newpage
+%\newpage
+
 \appendix
 
-\section{\label{apx:AppendixA}Classical ground states for some special model parameters}
+\section{\label{apx:PhaseBoundary}Phase boundaries in the quantum phase diagram}
 
-\subsection{$J=K=0, \Gamma=1$}
-For pure antiferromagetic $\Gamma$ model, the classical ground state is highly degenerate including FM state as well as states with no long range order.
-The ordered moment of the FM state lie in a plane that passes the coordinate origin and is perpendicular to the $[111]$ direction.
-Fig.~\ref{fig:GSForPositiveGamma} show a typical spin configuration of those disordered states that have the same energy as the FM state.
+As mentioned in the main text, the phase boundaries are determined by the location of singularities in $-\partial^{2} E_{2} / \partial \alpha^{2}$ and $-\partial^{2} E_{0} / \partial \beta^{2}$ based on the ED calculations.
+Some representative curves are shown in Fig.~\ref{fig:SecondDerivatives}.
+In Fig.~\ref{fig:SecondDerivatives}(a) for $\alpha=0.05\pi$, the second derivative of $E_0$ versus $\beta$ has two peaks located at $\beta=-0.01\pi$ and $\beta=0.81\pi$, which are the phase boundaries between the FM-A and QSL phases.
+As we increase $\alpha$ to $0.3\pi$, there are three singularities in the second derivatives (see Fig.~\ref{fig:SecondDerivatives}(b)).
+The small peak at $\beta=0.62\pi$ indicates the phase transition from modulated stripe to stripe-A, while the other two sharp peaks at $\beta=0.94\pi$ and $\beta=1.87\pi$ originate from the phase transitions from stripe-A to FM-A and from FM-A to stripe-B, respectively.
+Fig.~\ref{fig:SecondDerivatives}(c) show the case for $\alpha=0.75\pi$, where the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signify the phase transitions between stripe-A and FM-C.
+On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$ and the corresponding results are shown in Fig.~\ref{fig:SecondDerivatives}(d)-(f).
+In Fig.~\ref{fig:SecondDerivatives}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$ and $\alpha=0.097\pi$ reveal the phase transitions from FM-A to QSL and further to stripe-B.
+The peak at about $\alpha=0.5\pi$ is due to the phase transition from stripe-B to stripe-A.
+The last singularity at $\alpha=0.93\pi$ marks the phase boundary between stripe-A and FM-C.
+In Fig.~\ref{fig:SecondDerivatives}(e), we show the phase transition between modulated stripe and 120$^\circ$ N\'{e}el as well as the phase transition from 120$^\circ$ N\'{e}el to stripe-A.
+Here, $\beta$ is fixed to $0.5\pi$, and the transitions occur at $\alpha=0.32\pi$ and $\alpha=0.62\pi$, respectively.
+Last but not least, we show there are phase transitions between these different FM phases.
+In Fig.~\ref{fig:SecondDerivatives}(f) where $\beta=1.5\pi$, the sharp peak at $\alpha=0.5\pi$ shows that the FM-A phase for the HK model is a cirtical point, infinitesimal $\Gamma$ interaction will cause phase transition to other FM phases which have different moment direction from FM-A phase.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/SecondDerivatives.pdf}
+    \caption{\label{fig:SecondDerivatives}Second derivatives of ground state energies versus $\alpha$ or $\beta$.
+The blue lines are the ground state energies and the red lines are the second derivatives.
+(a)-(c) $-\partial^{2} E_{0} / \partial \beta^{2}$ with $\alpha$ fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively.
+(d)-(f) $-\partial^{2} E_{0} / \partial \alpha^{2}$ with $\beta$ fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively.}
+\end{figure}
+
+\section{\label{apx:SSF}Supplements of the SSF from the ED calculations}
+
+Here we provide additional SSF profiles as a supplement to these profiles shown in the main text.
+For classical 120$^\circ$ N\'{e}el state, the SSF has high intensity at the corner of the first BZ, i.e., $\tilde{K}$ points and the SSF peaked at the middle points of $\tilde{\Gamma}$ and $\tilde{K}$'s for the Dual N\'{e}el state.
+Fig.~\ref{fig:AppendixSSF}(a) and (b) show the SSF profiles calculated from our ED ground state at $\alpha=0.5\pi, \beta=0.5\pi$ and $\alpha=0.5\pi, \beta=1.85\pi$ which located at the 120$^\circ$ N\'{e}el phase and Dual N\'{e}el phase, respectively.
+For both profile, the points with highest intensity are consistent with the classical analyses.
+
+In the main text, we argue that the GSs of the pure $\Gamma$ models are FM ordered states.
+Here we provide the SSFs for $\Gamma = \pm 1$ in Fig.~\ref{fig:AppendixSSF}(c) and (d).
+Both SSFs have high intensities at the $\tilde{\Gamma}$ points, which is a typical characteristic of FM state.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/AppendixSSF.pdf}
+    \caption{\label{fig:AppendixSSF}(Color online) (a)-(b) Representative SSF profiles for 120$^\circ$ N\'{e}el and Dual N\'{e}el phase, respectively.
+(c)-(d) SSF profiles for $\Gamma = \pm 1$, respectively.}
+\end{figure}
+
+\section{\label{apx:DegeneratedStates}Classical GS configurations for some special interaction parameters}
+
+\subsection{$J=K=0$, $\Gamma=1$}
+
+For pure positive $\Gamma$ model, the classical GSs are highly degenerate including FM state as well as states with no long range order.
+The ordered moments of the FM state lie in the lattice plane.
+Fig.~\ref{fig:GSForPositiveGamma} shows a typical spin configuration of those disordered states that have the same energy as the FM state.
+
 \begin{figure}
@@
 
-\subsection{$J=K=0, \Gamma=-1$}
-For pure ferromagnetic $\Gamma$ model, we found several energetically degenerate states as the classcial ground state, including FM state, stripe states and a noncollinear state.
-The ordered moment of the FM state along the $[111]$ direction.
-As for the stripe states, there are three degenerate spin configurations as shown in Fig.~\ref{fig:GSForNegativeGamma}(a)-(c) and the directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively.
-Apart from these collinear states, a noncollinear state exist as the classical ground state.
-The magnetic unit-cell contains four lattice sites.
-The directions for the yellow, gray, pink, cyan arrows in Fig.~\ref{fig:GSForNegativeGamma}(d) are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.
+\subsection{$J=K=0$, $\Gamma=-1$}
+
+For pure negative $\Gamma$ model, we found several energetically degenerate states as the classcial GSs, including FM state, stripe states and a noncollinear state.
+The ordered moment of the FM state perpendicular to the lattice plane.
+As for the stripe states, there are three degenerate spin configurations as shown in Fig.~\ref{fig:GSForNegativeGamma}(a)-(c) and the moment directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively.
+Apart from these collinear states, a noncollinear state also exist as the classical ground state.
+The magnetic unit-cell contains four lattice sites, and the moment directions for the yellow, gray, pink, cyan arrows in Fig.~\ref{fig:GSForNegativeGamma}(d) are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.
 \begin{figure}
@@
 
-\subsection{$J=\Gamma=0, K=1$}
-The ground state for the classical antiferromagetic Kitaev model is also degenerate involving three nematic ordered states and three stripe ordered states.
-For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(a)-(c), the corresponding ordered moment lie in the $yz$, $xz$ and $xy$ plane, respectively.
-In addition to these stripe ordered states, there are nematic ordered states that have the same energy as the stripe ordered states.
-For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(d), the spins on the chains along the $x$-bond direction form antiferromagetic chains and the direction for the pink arrows are $[100]$.
+\subsection{$J=\Gamma=0$, $K=1$}
+
+The GSs for the classical antiferromagetic Kitaev model are also degenerate involving three types of nematic ordered states and three stripe ordered states.
+For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(a)-(c), the corresponding ordered moments lie in the $yz$, $xz$ and $xy$ plane, respectively.
+For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(d), the spins form antiferromagetic chains along the $x$-bond direction and the moment direction for the blue arrows are $[100]$.
 There are no association between different chains.
 Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(e) and Fig.~\ref{fig:GSForPositiveK}(f) respectively.
-The direction for the lightgreen arrows in Fig.~\ref{fig:GSForPositiveK}(e) and lightyellow arrows in Fig.~\ref{fig:GSForPositiveK}(f) are $[010]$ and $[001]$, respectively.
+The direction for the green arrows in Fig.~\ref{fig:GSForPositiveK}(e) and pink arrows in Fig.~\ref{fig:GSForPositiveK}(f) are $[010]$ and $[001]$, respectively.
 \begin{figure}
@@
 
-\section{\label{apx:AppendixB}Classical energy and moment direction of the stripe ordered states}
+\section{\label{apx:LSWOfFMA}Effects of Quantum fluctuations on FM phases}
 
-For classical stripe ordered states, all the spins are collinear and there are three degenerate spin configurations designated as \emph{config-x}, \emph{config-y} and \emph{config-z} respectively.
-The corresponding energies of the classical $J-K-\Gamma$ model for these spin configurations are
-\begin{subequations}
-    \begin{eqnarray}
-        E_{StripeX}^{c} & = & -(J + K) + 2 K v^x v^x \nonumber \\
-            & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y)
-            \label{eq:AEcStripeX} \\
-        E_{StripeY}^{c} & = & -(J + K) + 2 K v^y v^y \nonumber \\
-            & & +\: 2 \Gamma (v^z v^x - v^x v^y - v^y v^z)
-            \label{eq:AEcStripeY} \\
-        E_{StripeZ}^{c} & = & -(J + K) + 2 K v^z v^z \nonumber \\
-            & & +\: 2 \Gamma (v^x v^y - v^y v^z - v^z v^x)
-            \label{eq:AEcStripeZ}
-    \end{eqnarray}
-\end{subequations}
-where $v^x$, $v^y$, $v^z$ are the corresponding components of the classical spin vector.
-The ordered moment direction of the classical stripe order is determined by the anisotropic parameters $K$ and $\Gamma$ and can be obtained by finding the global minimum of $E_{StripeX}^{c}$, $E_{StripeY}^{c}$ and $E_{StripeZ}^{c}$ with the constraint $|\bm{v}|=1$.
-It is clear from Eq.~\eqref{eq:AEcStripeX}, Eq.~\eqref{eq:AEcStripeY} and Eq.~\eqref{eq:AEcStripeZ}, if $\bm{v}_{min}$ minimize the energy, then $-\bm{v}_{min}$ also minimize the energy.
-Here we only consider one of the direction.
-
-When $\Gamma=0$, it can be clearly seen from Eq.~\eqref{eq:AEcStripeX}, $E_{StripeX}^c$ takes minimum value at $v^x=0$ for positive $K$ and $v^x=1$ for negative $K$.
-When the $\Gamma$ interaction is included, the problem becomes a little more complex.
-To find the unit vector $\bm{v}_{min}$ that minimize $E_{StripeX}^{c}$, we use the Lagrange multiplier method.
-For $\Gamma>0, K=0$, $E_{StripeX}^{c}$ takes minimum value when the condition $v^x=v^y+v^z$ is fulfilled.
-On the other hand, when $\Gamma<0, K=0$, there are only two vectors that minimize $E_{StripeX}^{c}$, i.e., $v^y=v^z=-v^x=\pm 1/\sqrt{3}$.
-
-More generally, if both $K, \Gamma \neq 0$, $E_{StripeX}^{c}$ has six extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ equal zero.
-Here we give three of them explicitly and the other three are opposite to the given ones
-\begin{subequations}
-    \begin{eqnarray}
-        & \bm{v}_0: \quad v_{0}^{y}=-v_{0}^{z} = 1/\sqrt{2}, & v_{0}^{x} = 0 \\
-        & \bm{v}_1: \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), & v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y} \\
-        & \bm{v}_2: \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), & v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y}
-    \end{eqnarray}
-\end{subequations}
+According to Eq.~(\ref{eq:EcFM}), the spin directions in the FM state are independent of the Kitaev interactions, but here we demonstrate that the Kitaev interaction can make the spins point to some specific directions when the quantum fluctuations are included by a linear spin-wave analysis.
+Within the linear spin-wave theory, the GS energy per lattice site is given by $E_{SW}(\theta, \phi) = E^{c} + 1/(2N) \sum_{\bm{k}} \omega_{\bm{k}}(\theta, \phi)$, where $\omega_{\bm{k}}(\theta, \phi)$ is the spin-wave dispersion.
+The angles $\theta \in [0, \pi]$ and $\phi \in [0, 2\pi]$ are direction angles of the spins in spherical coordinate.
+The specific directions are selected if the minimum value of $E_{SW}(\theta, \phi)$ is arrived with some parameters $(\theta, \phi)$.
+For the FM states of the $J$-$K$-$\Gamma$ model, the dispersion of magnon $\omega_{\bm{k}}(\theta, \phi)$ is given by
+\begin{equation}
+    \omega_{\bm{k}}(\theta, \phi)= \frac{1}{2} \sqrt{A_{\bm{k}}^{2}(\theta, \phi) - |B_{\bm{k}}(\theta, \phi)|^{2}}
+    \label{eq:LSWDispersion}
+\end{equation}
+where
+\begin{equation}
+A_{\bm{k}}(\theta, \phi)=A_{0} + \eta_{1} A_{1} + \eta_{2} A_{2} + \eta_{3} A_{3}, \nonumber
+\end{equation}
+\begin{equation}
+A_{0}=-6J - 2K - 4 \Gamma (v_{x} v_{z} + v_{y} v_{z} + v_{x} v_{y}), \nonumber
+\end{equation}
+\begin{equation}
+A_{1}=2J + K (1-v_{x}^{2}) - 2 \Gamma v_{y} v_{z}, \nonumber
+\end{equation}
+\begin{equation}
+A_{2}=2J + K (1-v_{z}^{2}) - 2 \Gamma v_{x} v_{y}, \nonumber
+\end{equation}
+\begin{equation}
+A_{3}=2J + K (1-v_{y}^{2}) - 2 \Gamma v_{x} v_{z}, \nonumber
+\end{equation}
 and
-\begin{subequations}
-    \begin{eqnarray}
-        \lambda_{1} & = &- (\Gamma +2 K - \sqrt{9\Gamma^2 - 4 \Gamma K + 4 K^2}) / 4 \nonumber \\
-        \lambda_{2} & = & -(\Gamma +2 K + \sqrt{9\Gamma^2 + 4 \Gamma K + 4 K^2}) / 4 \nonumber \\
-        f_{1,2}(K, \Gamma) & = & \frac{|\Gamma|}{\sqrt{4 \lambda_{1,2} (\lambda_{1,2} + \Gamma) + 3 \Gamma^{2}}} \\
-        g_{1,2}(K, \Gamma) & = & (2 \lambda_{1,2} + \Gamma) / \Gamma
-    \end{eqnarray}
-\end{subequations}
-For a specific $K$ and $\Gamma$, by comparing the values of $E_{StripeX}^{c}$ at $\bm{v}_0$, $\bm{v}_1$ and $\bm{v}_2$ we can determine the global minimum of $E_{StripeX}^{c}$ and the corresponding $\bm{v}_{min}$.
-When both $\Gamma$ and $K$ are positive, $E_{StripeX}^{c}$ takes minimum value at the direction determined by $\bm{v}_0$.
-Otherwise, $\bm{v}_1$ specifies the direction where $E_{StripeX}^{c}$ has lowest energy.
-
-The similar analysis can be applied to $E_{StripeY}^{c}$ and $E_{StripeZ}^{c}$ and the ordered moment direction that minimize the classical energy can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$ of the results for $E_{StripeX}^{c}$.
-
-\newpage
+\begin{equation}
+B_{\bm{k}}(\theta, \phi)=\eta_{1} B_{1} + \eta_{2} B_{2} + \eta_{3} B_{3}, \nonumber
+\end{equation}
+\begin{align}
+B_{1}=K (1 - v_{x}^{2}) + 2\Gamma v_{y} v_{z}- 2\text{i} (K \frac{v_{x} v_{y} v_{z}}{1-v_{z}^{2}} + \Gamma v_{x}), \nonumber
+\end{align}
+\begin{align}
+B_{2}=K (1 - v_{z}^{2}) + 2 \Gamma \frac{1 + v_{z}^{2}}{1 - v_{z}^{2}} v_{x}v_{y}+ 2\text{i} \Gamma \frac{v_{z}}{1 - v_{z}^{2}}(v_{x}^2 - v_{y}^2), \nonumber
+\end{align}
+\begin{align}
+B_{3}=- K (1 - v_{y}^{2})- 2 \Gamma v_{x}v_{z}+ 2\text{i} (K \frac{v_{x} v_{y} v_{z}}{1-v_{z}^{2}} + \Gamma v_{y}). \nonumber
+\end{align}
+Here $\eta_{1,2,3} = \cos \bm{k} \cdot \bm{a}_{1,2,3}$ and $\bm{a}_{1,2,3}$ are the three nearest neighbor bonds, $v_x$, $v_y$, $v_z$ are the three components of the classical spin with $v_{x} = \sin \theta \cos \phi$, $v_{y} = \sin \theta \sin \phi$ and $v_{z} = \cos \theta$.
+In the HK limit ($\Gamma = 0$), the first derivative of $\omega_{\bm{k}}(\theta, \phi)$ versus $\theta$ and $\phi$ equals zero when $v_{x} = \pm1$, $v_{y} = \pm1$ or $v_{z} = \pm1$.
+Accordingly, $E_{SW}(\theta, \phi)$ takes extreme value at these special moment directions.
+Combined with numerical calculations, the minimum value of $E_{SW}(\theta, \phi)$ is obtained when the direction of the magnetic moment is along $x$, $y$, $z$ axis direction.
+Thus, quantum fluctuation lift the degeneracy of the classical ground state and select FM states with specific moment direction as the ground state.
 

### 2020-08-12 paper/paper.tex
20200812 9:10

@@
 The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins.
-In particular, the special case where spins are $S=1/2$ has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
+In particular, the spin-1/2 case has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
 When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}.
@@
 
-In fact, magnetic ions located at the center of edge-shared octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}.
-The HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}.
-All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types.
-Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,JPSJ.85.114710}.
-However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate.
-The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}.
-When the symmetric off-diagonal exchange interaction $\Gamma$ is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}.
-However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce.
-In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.
-
 \begin{figure}
     \centering
-    \begin{minipage}{0.6\columnwidth}
-        \includegraphics[width=\linewidth]{fig/EdgeSharingOctahedrons.pdf}
-    \end{minipage}\hspace{0pt}
-    \begin{minipage}{0.3\columnwidth}
-        \includegraphics[width=\linewidth]{fig/SingleOctahedron.pdf}\vspace{0pt}
-        \includegraphics[width=\linewidth]{fig/ModelDefinition.pdf}
-    \end{minipage}
+    \includegraphics[width=\columnwidth]{fig/ModelDefinition.pdf}
     \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron.
@@
 (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively.
-The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see the main text for detailed information.}
+The different colors of the lattice sites label the four sublattices realizing the four sublattice transformation ( see main text for details).}
 \end{figure}
-
+In fact, magnetic ions located at the center of edge-sharing octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}.
 On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments.
 In particular, due to their possible Kramers doublets and spin-orbital coupling, the $4f$ electrons can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbit entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms.
-A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614,PhysRevLett.117.267202,PhysRevLett.120.087201,PhysRevLett.122.137201,LiAdroja-398}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra~\cite{srep16419,PhysRevLett.115.167203}.
-At low temperatures, QSL states have been proposed due to its lack of long-range magnetic order and the observation of a continuum of magnetic excitations~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614}, but the exchange disorder induced by the intermixture of Mg$^{2+}$ and Ga$^{3+}$ may lead to a spin glass state~\cite{PhysRevLett.120.087201} or a random valence bond state~\cite{PhysRevLett.122.137201,LiAdroja-398}.
+A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203} and YbZnGaO$_{4}$~\cite{PhysRevLett.120.087201}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra.
 More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
@@
 
-In this paper, we study the global phase diagram and the phase transitions of the triangular-lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses.
+The phase diagram of the HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{PhysRevB.91.155135,KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}.
+All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types.
+Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,PhysRevB.91.155135,JPSJ.85.114710}.
+However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate.
+The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{PhysRevB.91.155135,JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}.
+When the symmetric off-diagonal $\Gamma$ interaction is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$ N\'{e}el, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}.
+However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce.
+In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.
+
+In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses.
 We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations.
@@
 
-The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK limit.
+%The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK limit.
 The ED and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}.
@@
 
-\section{\label{sec:Model}Model}
+\section{Model and Methods}
+
+\subsection{\label{sec:Model}Model}
 
@@
 
-In the followings, for convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchange interactions using spherical angles $\alpha$ and $\beta$
+In the followings, for convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchange parameters using spherical angles $\alpha$ and $\beta$
 \begin{equation}
@@
 \end{align*}
-This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the sublattices $1$, $2$, and $3$, respectively.
+This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the spin operators on the sublattices $1$, $2$, and $3$, respectively.
 The resulting Hamiltonian $H^{\prime}(\bm{S}^{\prime})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{\prime} = -J$ and $K^{\prime} = 2J + K$.
@@
 
-\section{\label{sec:Methods}Methods}
+%\section{\label{sec:Methods}Methods}
 
-\subsection{\label{subsec:MethodED}Exact Diagonalization}
+\subsection{\label{subsec:MethodED}Exact Diagonalization method}
 
@@
 To further determine the magnetic configurations of the magnetically ordered phases, we employ a method by studying the projections of the exact GSs of the finite cluster to the classical states~\cite{PhysRevB.94.064435}.
-The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin coherent states with varying moment directions.
+The basic idea of this method is to measure the probabilities of the cluster spin coherent states in the exact cluster GS with varying moment directions.
 The cluster spin coherent state is a direct product of spin-1/2 coherent states on each site $i$, i.e.,
@@
 \end{align}
-is fully polaried state along the $(\theta, \phi)$ direction.
+is fully polarized state along the $(\theta, \phi)$ direction.
 Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles.
@@
 \end{align}
-where $E_0$ is the ground state energy.
+where $E_0$ is the GS energy.
 
-\subsection{\label{subsec:MethodMC}Classical Monte Carlo}
+\subsection{\label{subsec:MethodMC}Classical Monte Carlo method}
 
@@
 \end{align}
-which is a key characterizes to identify magnetic phases.
+which is a key characteristic to identify magnetic phases.
 
@@
 The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
-There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, three different stripe phases designated as Stripe-A, Stripe-B and Stripe-C, Modulated Stripe, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase.
-The three FM phases different from each other in the direction of the ordered moment, and also the three stripe phases are distinguished by their moment directions, see main text for details.}
+There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases designated as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase.
+Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses.}
 \end{figure*}
@@
 Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-A and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
-We note that there are two special points with $J=K=0$ and $\Gamma=\pm1$ in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}.
+We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}.
 Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the numerical simulations by using the ``basin-hopping" global optimization and classical Monte Carlo methods.
@@
     \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
-    \caption{\label{fig:StructureFactors}(Color online) SSF for different model paramters.
+    \caption{\label{fig:StructureFactors}(Color online) (a)-(h) Representative SSFs from the ED calculations for different interaction parameters.
 The green dashed lines marks the first BZ corresponding to the triangular lattice.
-See Appendix~\ref{apx:SSF} for SSF profiles of other representative model parameters.}
+(i) Characteristic wave vectors for the FM and stipe phases.
+See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
 \end{figure}
@@
 
-Although we have basically determine the nature of each phase, there are still two problems should be explained: first, why there are phase transitions between the phases with the same type of classical orders, such as the phase transitions between FM phases or stripe phases, and why the FM and stripe phases of the HK model are the phase boundaries in the global phase diagram of $J$-$K$-$\Gamma$ model; second, what other important characteristics of the possible QSL phase in the phase diagram can be used to help us understand its properties more deeply.
+So far, we have basically determine the nature of each phase, but there are still two problems should be explained: first, why there are phase transitions between the phases with the same type of classical orders, such as the phase transitions between FM phases or stripe phases, and why the FM and stripe phases of the HK model are the phase boundaries in the global phase diagram of $J$-$K$-$\Gamma$ model; second, what other important characteristics of the possible QSL phase in the phase diagram can be used to help us understand its properties more deeply.
 In the followings, we will address these problems.
@@
     \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
-    \caption{\label{fig:ModulatedStripe}(Color online) Illustration of the modulated stripe order.
-(a) The spin configuration obtained from basin-hopping optimization for a $12 \times 12$ cluster.
-(b) Classical spin structure factor corresponding to the spin configuration shown in (a).
-(c) The spin configuration obtained from classical Monte Carlo for a $24 \time 24$ cluster.}
+    \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for a $12 \times 12$ cluster.
+(b) SSF corresponding to the spin configuration shown in (a).
+(c) Spin configuration obtained from the classical Monte Carlo calculations for a $24 \times 24$ cluster.}
 \end{figure}
@@
     \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
-    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS.
+    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in exact cluster GS for (a) FM-A, (b) FM-C, (c) stripe-A and (d) stripe-B phases.
 The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b).
-The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.}
+The green dashed lines and solid circles mark the ordered moment directions for the classical states.
+Note that the GSs are six-fold degenerate for the stripe-A and stripe-B phase, and two-fold degenerate for the FM-C phase, so the total probabilities for all of these phases are approximate to $1$.
+}
 \end{figure}
@@
     \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
-    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.1\pi$.
-$A(\bm{k}, \omega)$ is draw along the path $\tilde{M}-\tilde{\Gamma}-\tilde{M}-\tilde{\Gamma}$.}
+    \caption{\label{fig:Spectrum}(Color online) DSF $A(\bm{k}, \omega)$ for $\alpha=0.05\pi,\beta=0.1\pi$ in the QSL phase.
+The path $\tilde{M}-\tilde{\Gamma}-\tilde{M}-\tilde{\Gamma}$ is shown in Fig.~\ref{fig:StructureFactors}(i).}
 \end{figure}
@@
     \includegraphics[width=\columnwidth]{fig/SecondDerivatives.pdf}
-    \caption{\label{fig:SecondDerivatives}Second derivatives of ground state energies versus $\alpha$ or $\beta$.
-The blue lines are the ground state energies and the red lines are the second derivatives.
-(a)-(c) $-\partial^{2} E_{0} / \partial \beta^{2}$ with $\alpha$ fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively.
-(d)-(f) $-\partial^{2} E_{0} / \partial \alpha^{2}$ with $\beta$ fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively.}
+    \caption{\label{fig:SecondDerivatives} GS energies and their second derivatives versus $\alpha$ or $\beta$ for six representative path in the phase diagram.
+The blue lines are the GS energies and the red lines are the second derivatives.
+In (a)-(c) $\alpha$ is fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively.
+In (d)-(f), $\beta$ is fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively.}
 \end{figure}
@@
     \includegraphics[width=\columnwidth]{fig/AppendixSSF.pdf}
-    \caption{\label{fig:AppendixSSF}(Color online) (a)-(b) Representative SSF profiles for 120$^\circ$ N\'{e}el and Dual N\'{e}el phase, respectively.
-(c)-(d) SSF profiles for $\Gamma = \pm 1$, respectively.}
+    \caption{\label{fig:AppendixSSF}(Color online) (a) and (b) are the representative SSF profiles for 120$^\circ$ N\'{e}el and Dual N\'{e}el phase, respectively.
+(c) and (d) are the SSF profiles for the pure $\Gamma$ models with $\Gamma = \pm 1$, respectively.}
 \end{figure}
@@
     \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveGamma.pdf}
-    \caption{\label{fig:GSForPositiveGamma}(Color online) Typical disordered ground state for $J=K=0, \Gamma=1$.
+    \caption{\label{fig:GSForPositiveGamma}(Color online) Typical disordered GS for $J=K=0, \Gamma=1$.
 The 3D unit spin vectors were projected to the $xy$ plane and different vectors were represented by different colors.}
@@
     \includegraphics[width=\columnwidth]{fig/SpinConfigForNegativeGamma.pdf}
-    \caption{\label{fig:GSForNegativeGamma}(Color online) Typical ground state spin configurations for $J=K=0, \Gamma=-1$.
+    \caption{\label{fig:GSForNegativeGamma}(Color online) Typical classical GS spin configurations for $J=K=0, \Gamma=-1$.
 The 3D unit spin vectors were projected to the $xy$ plane and different vectors were represented by different colors.
@@
     \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveKitaev.pdf}
-    \caption{\label{fig:GSForPositiveK}(Color online) Nematic and stripe ground state spin configurations for $J=\Gamma=0, K=1$.}
+    \caption{\label{fig:GSForPositiveK}(Color online) Classical nematic and stripe GS spin configurations for $J=\Gamma=0, K=1$.}
 \end{figure}
@@
 Here $\eta_{1,2,3} = \cos \bm{k} \cdot \bm{a}_{1,2,3}$ and $\bm{a}_{1,2,3}$ are the three nearest neighbor bonds, $v_x$, $v_y$, $v_z$ are the three components of the classical spin with $v_{x} = \sin \theta \cos \phi$, $v_{y} = \sin \theta \sin \phi$ and $v_{z} = \cos \theta$.
-In the HK limit ($\Gamma = 0$), the first derivative of $\omega_{\bm{k}}(\theta, \phi)$ versus $\theta$ and $\phi$ equals zero when $v_{x} = \pm1$, $v_{y} = \pm1$ or $v_{z} = \pm1$.
+In the HK limit ($\Gamma = 0$), the first derivatives of $\omega_{\bm{k}}(\theta, \phi)$ versus $\theta$ and $\phi$ are equal to zero when $v_{x} = \pm1$, $v_{y} = \pm1$ or $v_{z} = \pm1$.
 Accordingly, $E_{SW}(\theta, \phi)$ takes extreme value at these special moment directions.
 Combined with numerical calculations, the minimum value of $E_{SW}(\theta, \phi)$ is obtained when the direction of the magnetic moment is along $x$, $y$, $z$ axis direction.
-Thus, quantum fluctuation lift the degeneracy of the classical ground state and select FM states with specific moment direction as the ground state.
+Thus, quantum fluctuation lift the degeneracy of the classical GS and select FM states with specific moment directions (i.e., $x$, $y$ and $z$ directions) as the quantum GSs.
 

### 2020-11-11 DualNeelED.py
Add `DualNeelED.py`.

@@ -1,0 +1,140 @@
+"""
+Exact diagonalization of the J-K-Gamma model on a 24-sites cluster that is
+compatible with 120 Neel order.
+"""
+
+
+import logging
+import sys
+from pathlib import Path
+from time import time
+
+import HamiltonianPy as HP
+import numpy as np
+from scipy.sparse import load_npz, save_npz
+from scipy.sparse.linalg import eigsh
+
+
+def BondsGenerator(cluster):
+    x_bonds = []
+    y_bonds = []
+    z_bonds = []
+    intra, inter = cluster.bonds(nth=1)
+    for bond in intra + inter:
+        p0, p1 = bond.endpoints
+        index0 = cluster.getIndex(site=p0, fold=True)
+        index1 = cluster.getIndex(site=p1, fold=True)
+        bond_index = (index0, index1)
+
+        azimuth = bond.getAzimuth(ndigits=0)
+        # The definition of x, y, z bond in a trio is counterclockwise.
+        if azimuth in (-180, 0, 180):
+            x_bonds.append(bond_index)
+        elif azimuth in (-120, 60):
+            z_bonds.append(bond_index)
+        elif azimuth in (-60, 120):
+            y_bonds.append(bond_index)
+        else:
+            raise RuntimeError("Invalid bond azimuth: {0}".format(azimuth))
+    return x_bonds, y_bonds, z_bonds
+
+
+def TermMatrix(cluster):
+    directory = Path("tmp/")
+    name_template = "TRIANGLE_DualNeel_H{0}.npz"
+    file_HJ = directory / name_template.format("J")
+    file_HK = directory / name_template.format("K")
+    file_HG = directory / name_template.format("G")
+
+    if file_HJ.exists() and file_HK.exists() and file_HG.exists():
+        t0 = time()
+        HJ = load_npz(file_HJ)
+        HK = load_npz(file_HK)
+        HG = load_npz(file_HG)
+        t1 = time()
+        logging.info("Load HJ, HK, HG, dt=%.3fs", t1 - t0)
+    else:
+        site_num = cluster.point_num
+        all_bonds = BondsGenerator(cluster)
+
+        HJ = HK = HG = 0.0
+        msg = "%s-bond: %2d/%2d, dt=%.3fs"
[…]

### 2020-11-11 run/ShowOptimizedSpinConfig.py
A new design of `ShowOptimizedSpinConfig.py`.

@@ -1,39 +1,74 @@
+import HamiltonianPy as HP
 import matplotlib.pyplot as plt
+import numpy as np
 import tables as tb
 
-from utilities import TriangularLattice
+from StructureFactor import ClassicalSpinStructureFactor
 
-data_path = "data/ClassicalSpinModel/OptimizedSpinConfig/"
-h5f_name_temp = "OSC_num1={0}_num2={1}_direction={2}_" \
-                "alpha={3:.4f}_beta={4:.4f}.h5"
+data_path = "C:/Users/swang/Desktop/Working/"
+data_path += "JKGModel/data/ClassicalSpinModel/OptimizedSpinConfig/"
+data_name_temp = "OSC_num0=12_num1=12_alpha={0:.4f}_beta={1:.4f}.h5"
 
-alpha = 0.50
-beta = 0.50
-num1 = num2 = 12
-direction = "xz"
-lattice = TriangularLattice(num1=num1, num2=num2, direction="xz")
-points = lattice.cluster.points
+step = 0.01
+ratios = np.arange(-0.7, 0.7 + step, step)
+kpoints = np.matmul(
+    np.stack(np.meshgrid(ratios, ratios, indexing="ij"), axis=-1),
+    4 * np.pi * np.identity(2) / np.sqrt(3)
+)
+BZBoundary = HP.TRIANGLE_CELL_KS[[*range(6), 0]]
+points = HP.lattice_generator("triangle", num0=12, num1=12).points
 
-h5f_name = h5f_name_temp.format(num1, num2, direction, alpha, beta)
-h5f = tb.open_file(data_path + h5f_name, mode="r")
-for carray in h5f.iter_nodes("/"):
-    spin_vectors = carray.read()
-    energy = h5f.get_node_attr(carray, "energy")
+axis = (np.pi * np.random.random(), 2 * np.pi * np.random.random())
+Rotation = HP.RotationGeneral(axis, 2 * np.pi * np.random.random())
 
-    fig, ax = plt.subplots(num=carray.name)
-    ax.plot(
-        points[:, 0], points[:, 1],
-        color="k", ls="", marker="o", ms=5
-    )
-    ax.quiver(
-        points[:, 0], points[:, 1],
-        spin_vectors[:, 0], spin_vectors[:, 1],
-        pivot="middle", color=0.5*spin_vectors+0.5,
-    )
-    ax.set_title("Energy = {0:.10f}".format(energy), fontsize="xx-large")
-    ax.set_axis_off()
-    ax.set_aspect("equal")
[…]

### 2020-11-11 FiguresForPaper/ShowStructureFactor.py
Minor changes to `ShowStructureFactor.py`.

@@ -22,8 +22,8 @@ SF_DATA_NAME_TEMP = "SF_num1=4_num2=6_direction=avg_" \
                     "alpha={0:.4f}_beta={1:.4f}.npz"
 
 params = [
-    (0.50, 0.00), (0.30, 0.80), (0.70, 0.66), (0.30, 0.00),
-    (0.00, 0.00), (1.00, 0.00), (0.05, 0.10), (0.30, 0.50),
+    (0.50, 0.00), (0.30, 0.75), (0.75, 0.25), (0.30, 0.00),
+    (0.30, 0.50), (0.30, 1.30), (0.70, 1.65), (0.05, 0.10),
 ]
 sub_fig_tags = ["(a)", "(b)", "(c)", "(d)", "(e)", "(f)", "(g)", "(h)"]
 for index in range(len(params)):
@@ -47,9 +47,9 @@ for index in range(len(params)):
     )
     im.set_edgecolor("face")
 
-    colorbar = fig.colorbar(im, ax=ax, pad=0.01, format="%.1f")
+    colorbar = fig.colorbar(im, ax=ax, pad=0.05, format="%.1f")
     colorbar.set_ticks(np.linspace(vmin, vmax, 5, endpoint=True))
-    colorbar.ax.tick_params(axis="y", labelsize=SMALL)
+    colorbar.ax.tick_params(axis="y", labelsize=MEDIUM)
 
     ax.plot(
         BZBoundary[:, 0], BZBoundary[:, 1], zorder=1,
@@ -57,58 +57,88 @@ for index in range(len(params)):
     )
     ax.text(
         0.02, 0.98, sub_fig_tag,
-        fontsize=LARGE, ha="left", va="top", transform=ax.transAxes,
+        fontsize=XLARGE, ha="left", va="top", transform=ax.transAxes,
     )
 
     ax.set_aspect("equal")
-    # ax.grid(True, ls="dashed", color="gray")
-    ax.set_title(title, fontsize=LARGE, loc="center")
+    ax.set_title(title, fontsize=XLARGE, loc="center")
     ticks = np.array([-1, 0, 1], dtype=np.int64)
     tick_labels = ["{0}".format(tick) for tick in ticks]
     ax.set_xticks(ticks * np.pi)
     ax.set_yticks(ticks * np.pi)
 
     if index in (0, 3, 6):
[…]

### 2020-11-11 FiguresForPaper/ShowSixSitesOrder.py
Minor changes to `ShowShowSixSitesOrder.py`.

@@ -11,15 +11,16 @@ from StructureFactor import ClassicalSpinStructureFactor
 
 POINTS = np.array(
     [
-        [0.0, 0.0], [1.0, 0.0], [0.5, np.sqrt(3) / 2],
-        [1.5, np.sqrt(3) / 2], [1.0, np.sqrt(3)], [2.0, np.sqrt(3)],
+        [0.0, 0.0], [0.5, 0.5 * np.sqrt(3)],
+        [1.0, 0.0], [1.5, 0.5 * np.sqrt(3)],
+        [2.0, 0.0], [2.5, 0.5 * np.sqrt(3)],
     ]
 )
-VECTORS = np.array([[1.5, -np.sqrt(3) / 2], [1.5, 1.5 * np.sqrt(3)]])
+VECTORS = np.array([[0.0, np.sqrt(3)], [3.0, 0.0]])
 CELL = HP.Lattice(POINTS, VECTORS)
 
-num0 = 7
-num1 = 4
+num0 = 5
+num1 = 3
 alpha = 0.30
 beta = 0.50
 
@@ -60,57 +61,68 @@ factors = factors.real
 vmin = np.min(factors)
 vmax = np.max(factors)
 
+angle = 4.705588762457632
+axis = (1.268856573288606, 5.486167665013975)
+Rotation = HP.RotationGeneral(axis, angle)
+
 fig_config, ax_config = plt.subplots(num="SpinConfig")
-ax_config.plot(
-    cluster.points[:, 0], cluster.points[:, 1],
-    color="k", ls="", marker="o", ms=5,
-)
+intra, inter = cluster.bonds(nth=1)
+for bond in intra:
+    (x0, y0), (x1, y1) = bond.endpoints
+    ax_config.plot(
+        [x0, x1], [y0, y1], ls="dashed", color="gray", lw=1.0, zorder=0
+    )
+
+cluster_vectors_temp = np.dot(cluster_vectors, Rotation.T)
 ax_config.quiver(
     cluster.points[:, 0], cluster.points[:, 1],
-    cluster_vectors[:, 0], cluster_vectors[:, 1],
-    units="xy", scale_units="xy", scale=1.45, width=0.08,
-    pivot="middle", color=0.5 * cluster_vectors + 0.5, clip_on=False,
+    cluster_vectors_temp[:, 0], cluster_vectors_temp[:, 1],
[…]

### 2020-11-11 FiguresForPaper/ShowProbabilities.py
Minor changes to `ShowProbabilities.py`.

@@ -17,22 +17,19 @@ INDICATOR_COLOR = "tab:green"
 PS_DATA_NAME_TEMP = "data/PS_num1=4_num2=6_direction=avg_" \
                     "alpha={0:.4f}_beta={1:.4f}.npz"
 
-params = [
-    (0.50, 0.75), (0.50, 0.00), (0.30, 1.30),
-    (0.70, 1.65), (0.70, 0.66), (0.30, 0.25),
-]
-sub_fig_tags = ["(a)", "(b)", "(c)", "(d)", "(e)", "(f)"]
+sub_fig_tags = ["(a)", "(b)", "(c)", "(d)"]
+params = [(0.30, 1.30), (0.70, 1.65), (0.70, 0.66), (0.30, 0.00)]
 
 theta_ticks = np.array([0.0, 0.25, 0.50])
 phi_ticks = np.array([0.0, 0.5, 1.0, 1.5])
 
 fig, axes = plt.subplots(
-    nrows=2, ncols=3, subplot_kw={"polar": True}, num="Probabilities",
+    nrows=2, ncols=2, subplot_kw={"polar": True}, num="Probabilities",
 )
 
 for index in range(len(params)):
     alpha, beta = params[index]
-    ax = axes[divmod(index, 3)]
+    ax = axes[divmod(index, 2)]
     sub_fig_tag = sub_fig_tags[index]
 
     ps_data_name = PS_DATA_NAME_TEMP.format(alpha, beta)
@@ -48,7 +45,7 @@ for index in range(len(params)):
     )
     im.set_edgecolor("face")
 
-    colorbar = fig.colorbar(im, ax=ax, pad=0.04)
+    colorbar = fig.colorbar(im, ax=ax, pad=0.03)
     colorbar_ticks = np.linspace(0.0, max_probs, 5, endpoint=True)
     colorbar.set_ticks(colorbar_ticks)
     colorbar.set_ticklabels(
@@ -91,55 +88,49 @@ tmp = [
     (1.0, "right", "center"), (1.5, "center", "top"),
 ]
 for phi, ha, va in tmp:
-    axes[0, 0].text(
+    axes[0, 1].text(
         phi * np.pi, 0.51 * np.pi,
         r"${0:.0f}^\circ$".format(phi * 180),
         fontsize=SMALL, ha=ha, va=va,
     )
[…]

### 2020-11-11 FiguresForPaper/ShowModulatedStripe.py
Add `ShowModulatedStripe.py`.

@@ -1,0 +1,88 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from scipy.spatial import cKDTree
+from FontSize import *
+
+
+def Rotation2D(theta=0.0, deg=True):
+    """
+    Rotation about the axis perpendicular to the plane by theta angle.
+
+    Parameters
+    ----------
+    theta : float, optional
+        The angle to rotate.
+        Default: 0.0.
+    deg : bool, optional
+        Whether the given theta is in degree or radian.
+        Default: True.
+
+    Returns
+    -------
+    RZ : array with shape (2, 2)
+        The corresponding rotation matrix.
+    """
+
+    if deg:
+        theta = np.pi * theta / 180
+    sin_theta = np.sin(theta)
+    cos_theta = np.cos(theta)
+    return np.array([[cos_theta, -sin_theta], [sin_theta, cos_theta]])
+
+
+LEFT = 10.0
+RIGHT = 30.0
+BOTTOM = -4.25
+TOP = 4.25
+
+with np.load("data/CMC_num0=24_num1=24_alpha=0.3000_beta=0.5000.npz") as ld:
+    all_points = ld["points"]
+    all_vectors = ld["vectors"]
+all_points = np.dot(all_points, Rotation2D(30))
+
+selected_points = []
+selected_vectors = []
+for index in range(all_points.shape[0]):
+    x, y = all_points[index]
+    if (LEFT < x < RIGHT) and (BOTTOM < y < TOP):
+        selected_points.append([x, y])
+        selected_vectors.append(all_vectors[index])
+selected_points = np.array(selected_points)
+selected_vectors = np.array(selected_vectors)
+# selected_points = all_points
+# selected_vectors = all_vectors
+
+tree = cKDTree(selected_points)
+pairs = tree.query_pairs(r=1.01)
+
+fig, ax = plt.subplots(num="CMCSpinConfig")
+for i, j in pairs:
+    x0, y0 = selected_points[i]
+    x1, y1 = selected_points[j]
+    ax.plot(
+        [x0, x1], [y0, y1], ls="dashed", color="gray", lw=1.0, zorder=0
+    )
+ax.quiver(
+    selected_points[:, 0], selected_points[:, 1],
+    selected_vectors[:, 0], selected_vectors[:, 1],
[…]

### 2020-11-11 FiguresForPaper/ShowAppendixSSF.py
Minor changes to `ShowAppendixSSF.py`.

@@ -5,18 +5,17 @@ parameters.
 
 import matplotlib.pyplot as plt
 import numpy as np
-from HamiltonianPy import TRIANGLE_CELL_MS as MS
 
 from FontSize import *
 
 BZLW = 5
 COLORMAP = "hot_r"
 BZCOLOR = "tab:green"
-SF_DATA_NAME_TEMP = "data/SF_num1=4_num2=6_which=avg_" \
-                    "alpha={0:.4f}_beta={1:.4f}.npz"
+SF_DATA_NAME_TEMP = "data/SF_num1=4_num2=6_" \
+                    "direction=avg_alpha={0:.4f}_beta={1:.4f}.npz"
 
 sub_fig_tags = ["(a)", "(b)", "(c)", "(d)"]
-params = [(0.50, 0.50), (0.50, 1.86), (0.30, 1.30), (0.7, 1.65)]
+params = [(0.50, 0.50), (0.50, 1.86), (0.00, 0.00), (1.00, 0.00)]
 
 fig, axes = plt.subplots(nrows=2, ncols=2, sharex="all", sharey="all")
 for index in range(len(params)):
@@ -39,8 +38,7 @@ for index in range(len(params)):
     )
     im.set_edgecolor("face")
 
-    colorbar = fig.colorbar(im, ax=ax, pad=0.01, format="%.1f")
-    colorbar.ax.tick_params(axis="y", labelsize="large")
+    colorbar = fig.colorbar(im, ax=ax, pad=0.02, format="%.1f")
     colorbar.set_ticks(np.linspace(vmin, vmax, 5, endpoint=True))
     colorbar.ax.tick_params(axis="y", labelsize=SMALL)
 
@@ -48,23 +46,17 @@ for index in range(len(params)):
         BZBoundary[:, 0], BZBoundary[:, 1], zorder=1,
         ls="dashed", lw=BZLW, color=BZCOLOR, alpha=1.0,
     )
+    ax.set_title(sub_fig_tag + " " + title, fontsize=LARGE, loc="center")
+    ax.set_aspect("equal")
+    ax.set_xlim(-4.5, 4.5)
+    ax.set_ylim(-4.5, 4.5)
 
-    ax.text(
-        0.0, 0.98, sub_fig_tag,
-        fontsize=LARGE, ha="left", va="top", transform=ax.transAxes,
-    )
-    ax.set_title(title, fontsize="xx-large", loc="center")
[…]

### 2020-11-11 FiguresForPaper/SecondDerivatives.py
Minor changes to `SecondDerivatives.py`.

@@ -3,6 +3,10 @@ import numpy as np
 
 from FontSize import *
 
+line_width = 4
+color_gses = "tab:blue"
+color_d2gses = "tab:red"
+
 
 def derivation(xs, ys, nth=1):
     """
@@ -42,90 +46,92 @@ def derivation(xs, ys, nth=1):
     return xs, ys
 
 
-name0 = "data/GEs_numx=4_numy=6_beta=1.5000.npz"
-name1 = "data/GEs_numx=4_numy=6_beta=0.0000.npz"
-name2 = "data/GEs_numx=4_numy=6_alpha=0.3000.npz"
-with np.load(name0) as ld:
-    gses0 = ld["gses"]
-    params0 = ld["params"]
-with np.load(name1) as ld:
-    gses1 = ld["gses"]
-    params1 = ld["params"]
-with np.load(name2) as ld:
-    gses2 = ld["gses"]
-    params2 = ld["params"]
-d2params0, d2gses0 = derivation(params0, gses0, nth=2)
-d2params1, d2gses1 = derivation(params1, gses1, nth=2)
-d2params2, d2gses2 = derivation(params2, gses2, nth=2)
+names = [
+    "data/GEs_numx=4_numy=6_alpha=0.0500.npz",
+    "data/GEs_numx=4_numy=6_alpha=0.3000.npz",
+    # "data/GEs_numx=4_numy=6_alpha=0.5000.npz",
+    "data/GEs_numx=4_numy=6_alpha=0.7500.npz",
+    "data/GEs_numx=4_numy=6_beta=0.0000.npz",
+    "data/GEs_numx=4_numy=6_beta=0.5000.npz",
+    # "data/GEs_numx=4_numy=6_beta=0.7500.npz",
+    "data/GEs_numx=4_numy=6_beta=1.5000.npz",
+]
+container = []
+for name in names:
+    with np.load(name) as ld:
+        gses = ld["gses"]
+        params = ld["params"]
+    d2params, d2gses = derivation(params, gses, nth=2)
+    container.append((params, gses, d2params, d2gses))
 
-line_width = 4
-color_gses = "tab:blue"
-color_d2gses = "tab:red"
+fig, axes_gses = plt.subplots(2, 3)
 
[…]

### 2020-11-11 FiguresForPaper/QuantumPhaseDiagramDataBase.py
Minor changes to `QuantumPhaseDiagramDataBase.py`.

@@ -31,77 +31,77 @@ PhaseTransitionPointsWithFixedAlpha = {
     "alpha=0.075": [0.845, 1.950],
     "alpha=0.080": [0.850, 1.940],
     "alpha=0.085": [0.854, 1.940],
-    "alpha=0.090": [0.500, 0.858, 1.940],
-    "alpha=0.095": [0.502, 0.862, 1.935],
-    "alpha=0.100": [0.504, 0.866, 1.930],
-    "alpha=0.105": [0.506, 0.870, 1.925],
-    "alpha=0.110": [0.508, 0.876, 1.923],
-    "alpha=0.115": [0.510, 0.882, 1.921],
-    "alpha=0.120": [0.512, 0.890, 1.919],
-    "alpha=0.125": [0.514, 0.893, 1.917],
-    "alpha=0.130": [0.516, 0.896, 1.916],
-    "alpha=0.135": [0.518, 0.899, 1.913],
-    "alpha=0.140": [0.520, 0.902, 1.910],
-    "alpha=0.145": [0.522, 0.905, 1.910],
-    "alpha=0.150": [0.524, 0.908, 1.910],
-    "alpha=0.155": [0.526, 0.911, 1.910],
-    "alpha=0.160": [0.528, 0.913, 1.908],
-    "alpha=0.165": [0.530, 0.915, 1.906],
-    "alpha=0.170": [0.532, 0.920, 1.904],
-    "alpha=0.175": [0.534, 0.920, 1.902],
-    "alpha=0.180": [0.536, 0.920, 1.900],
-    "alpha=0.185": [0.538, 0.923, 1.900],
-    "alpha=0.190": [0.540, 0.924, 1.900],
-    "alpha=0.195": [0.542, 0.924, 1.900],
-    "alpha=0.200": [0.544, 0.925, 1.900],
-    "alpha=0.205": [0.546, 0.925, 1.895],
-    "alpha=0.210": [0.548, 0.926, 1.890],
-    "alpha=0.215": [0.550, 0.926, 1.890],
-    "alpha=0.220": [0.552, 0.927, 1.890],
-    "alpha=0.225": [0.554, 0.928, 1.890],
-    "alpha=0.230": [0.556, 0.929, 1.888],
-    "alpha=0.235": [0.558, 0.929, 1.886],
-    "alpha=0.240": [0.560, 0.930, 1.884],
-    "alpha=0.245": [0.562, 0.931, 1.882],
[…]

### 2020-11-11 FiguresForPaper/QuantumGlobalPhaseDiagram.py
Minor changes to `QuantumGlobalPhaseDiagram.py`.

@@ -19,6 +19,10 @@ fig, (ax_north, ax_south) = plt.subplots(
     nrows=1, ncols=2, subplot_kw={"polar": True},
     num="QuantumGlobalPhaseDiagram",
 )
+# fig, (ax_south, ax_north) = plt.subplots(
+#     nrows=1, ncols=2, subplot_kw={"polar": True},
+#     num="QuantumGlobalPhaseDiagram",
+# )
 
 # Draw the north hemisphere
 radius = 0.00
@@ -107,24 +111,25 @@ ax_south.set_title(r"$\Gamma \leq 0$", fontsize=LARGE)
 
 # Annotate the different phases
 phase_annotate_north = [
-    (0.05 * np.pi, 0.35, "Stripe-B"),
+    (0.05 * np.pi, 0.35, "Stripe-C"),
     (0.49 * np.pi, 0.41, r"120$^\circ$ N$\mathsf{\acute e}$el"),
+    (0.40 * np.pi, 0.24, "Modulated\n Stripe"),
     (0.81 * np.pi, 0.30, "Stripe-A"),
-    (1.50 * np.pi, 0.35, "FM-A"),
+    (1.50 * np.pi, 0.35, "FM-B"),
     (0.45 * np.pi, 0.05, "QSL"),
 ]
 for annotate in phase_annotate_north:
     ax_north.text(*annotate, ha="center", va="center", fontsize=LARGE)
 
-ax_north.annotate(
-    "Stripe-C", xy=(0.07 * np.pi, 0.50), xytext=(0.10 * np.pi, 0.60),
-    ha="center", va="bottom", fontsize=LARGE,
-    arrowprops={
-        "arrowstyle": "fancy",
-        "connectionstyle": "angle3",
-        "color": PhaseNames2Colors["StripeC"],
-    },
-)
+# ax_north.annotate(
+#     "Stripe-C", xy=(0.07 * np.pi, 0.50), xytext=(0.10 * np.pi, 0.60),
+#     ha="center", va="bottom", fontsize=LARGE,
+#     arrowprops={
+#         "arrowstyle": "fancy",
+#         "connectionstyle": "angle3",
+#         "color": PhaseNames2Colors["StripeC"],
+#     },
+# )
 ax_north.annotate(
     r"Dual N$\mathsf{\acute e}$el",
     xy=(1.85 * np.pi, 0.50), xytext=(1.82 * np.pi, 0.62),
[…]

### 2020-11-11 FiguresForPaper/PhaseDiagramForHKModel.py
Add `PhaseDiagramForHKModel.py`.

@@ -1,0 +1,143 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+from FontSize import *
+from QuantumPhaseDiagramDataBase import *
+
+RADIUS = 1
+HEIGHT = 0.1
+
+alpha = 0.50
+key = "alpha={0:.3f}".format(alpha)
+edges = np.array(PhaseTransitionPointsWithFixedAlpha[key])
+colors = [PhaseNames2Colors[name] for name in PhaseNames[key]]
+widths = np.append(edges[1:] - edges[:-1], 2 + edges[0] - edges[-1])
+centers = np.pi * np.append(
+    edges[1:] + edges[:-1], 2 + edges[0] + edges[-1]
+) / 2
+
+fig, ax = plt.subplots(subplot_kw={"polar": True})
+ax.bar(
+    x=edges * np.pi, width=widths * np.pi,
+    bottom=RADIUS-HEIGHT/2, height=HEIGHT,
+    color=colors, align="edge",
+)
+
+# Parameter pairs connected by FST
+ax.annotate(
+    "", xy=(0.10 * np.pi, RADIUS - HEIGHT / 2),
+    xytext=(1.94 * np.pi, RADIUS - HEIGHT / 2),
+    arrowprops={
+        "linewidth": 1.2, "arrowstyle": "<->",
+        "connectionstyle": "arc3, rad=0.0",
+    },
+)
+ax.annotate(
+    "", xy=(0.23 * np.pi, RADIUS - HEIGHT / 2),
+    xytext=(1.90 * np.pi, RADIUS - HEIGHT / 2),
+    arrowprops={
+        "linewidth": 1.2, "arrowstyle": "<->",
+        "connectionstyle": "arc3, rad=0.0",
+    },
+)
+ax.annotate(
+    "", xy=(0.50 * np.pi, RADIUS - HEIGHT / 2),
+    xytext=(1.85 * np.pi, RADIUS - HEIGHT / 2),
+    arrowprops={
+        "linewidth": 1.2, "arrowstyle": "<->",
+        "connectionstyle": "arc3, rad=0.0",
+    },
+)
+ax.annotate(
+    "", xy=(0.64 * np.pi, RADIUS - HEIGHT / 2),
+    xytext=(1.82 * np.pi, RADIUS - HEIGHT / 2),
+    arrowprops={
[…]

### 2020-11-11 FiguresForPaper/ModelDefinition.py
Minor changes to `ModelDefinition.py`.

@@ -9,7 +9,7 @@ import numpy as np
 from FontSize import *
 
 LW = 6
-MS = 22
+MS = 25
 
 point0 = np.array([0.0, 0.0])
 point1 = np.array([1.0, 0.0])
@@ -61,25 +61,25 @@ for index, point in zip(
 ):
     ax.text(
         point[0], point[1], str(index),
-        fontsize=LARGE, ha="center", va="center", color="black",
+        fontsize=XXLARGE, ha="center", va="center", color="black",
     )
 
 ax.text(
     -0.50, 0.0, "x",
-    fontsize=LARGE, ha="center", va="bottom", color="tab:red",
+    fontsize=XXLARGE+8, ha="center", va="bottom", color="tab:red",
 )
 ax.text(
     0.25, -np.sqrt(3)/4, "y",
-    fontsize=LARGE, ha="left", va="bottom", color="tab:green",
+    fontsize=XXLARGE+8, ha="left", va="bottom", color="tab:green",
 )
 ax.text(
     0.25, np.sqrt(3)/4, "z",
-    fontsize=LARGE, ha="left", va="top", color="tab:blue",
+    fontsize=XXLARGE+8, ha="left", va="top", color="tab:blue",
 )
 
 ax.text(
     0, 1.0, "(c)",
-    fontsize=LARGE, ha="left", va="top", transform=ax.transAxes
+    fontsize=XXLARGE+8, ha="left", va="top", transform=ax.transAxes
 )
 
 ax.set_axis_off()

### 2020-11-11 FiguresForPaper/ClassicalGSForPositiveKitaev.py
Minor changes to `ClassicalGSForPositiveKitaev.py`.

@@ -4,8 +4,10 @@ Classical ground state spin configurations for pure positive Kitaev model.
 
 
 import matplotlib.pyplot as plt
+import matplotlib.colors as mcolors
 import numpy as np
 
+from scipy.spatial import cKDTree
 from FontSize import *
 
 POINTS = np.dot(
@@ -51,24 +53,33 @@ def StripeGenerator(config="StripeX"):
         chains = XCHAINS
         spin_up = [1.0, 0.0, 0.0]
         spin_down = [-1.0, 0.0, 0.0]
+        color_up = mcolors.to_rgba("tab:blue")
+        color_down = mcolors.to_rgba("tab:orange")
     elif config == "StripeY":
         chains = YCHAINS
         spin_up = [-0.5, np.sqrt(3) / 2, 0.0]
         spin_down = [0.5, -np.sqrt(3) / 2, 0.0]
+        color_up = mcolors.to_rgba("tab:green")
+        color_down = mcolors.to_rgba("tab:red")
     elif config == "StripeZ":
         chains = ZCHAINS
         spin_up = [0.5, np.sqrt(3) / 2, 0.0]
         spin_down = [-0.5, -np.sqrt(3) / 2, 0.0]
+        color_up = mcolors.to_rgba("tab:pink")
+        color_down = mcolors.to_rgba("tab:cyan")
     else:
         raise ValueError("Invalid `config`: {0}".format(config))
 
+    colors = np.empty((36, 4), dtype=np.float64)
     spin_vectors = np.empty((36, 3), dtype=np.float64)
     for index, chain in enumerate(chains):
         if index % 2 == 0:
+            colors[chain] = color_up
             spin_vectors[chain] = spin_up
         else:
+            colors[chain] = color_down
             spin_vectors[chain] = spin_down
-    return spin_vectors
+    return spin_vectors, colors
 
 
 def NematicGenerator(config="NematicX"):
@@ -76,60 +87,75 @@ def NematicGenerator(config="NematicX"):
         chains = XCHAINS
         spin_up = [1.0, 0.0, 0.0]
         spin_down = [-1.0, 0.0, 0.0]
+        color_up = mcolors.to_rgba("tab:blue")
+        color_down = mcolors.to_rgba("tab:orange")
     elif config == "NematicY":
         chains = YCHAINS
         spin_up = [-0.5, np.sqrt(3) / 2, 0.0]
[…]

### 2020-11-11 FiguresForPaper/ClassicalGSForPositiveGamma.py
Minor changes to `ClassicalGSForPositiveGamma.py`.

@@ -14,6 +14,7 @@ markersize = 12
 cluster = lattice_generator("triangle", num0=12, num1=12)
 xs = cluster.points[:, 0]
 ys = cluster.points[:, 1]
+intra, inter = cluster.bonds(nth=1)
 
 h5f_name = "data/OSC_num1=12_num1=12_alpha=0.0000_beta=0.0000.h5"
 h5f = tb.open_file(h5f_name, mode="r")
@@ -23,15 +24,19 @@ colors = 0.5 * spin_vectors + 0.5
 h5f.close()
 
 fig, ax = plt.subplots(num="Run{0:0>4d}".format(which))
-ax.plot(xs, ys, ls="", marker="o", ms=markersize, color="black", zorder=0)
+for bond in intra:
+    (x0, y0), (x1, y1) = bond.endpoints
+    ax.plot([x0, x1], [y0, y1], ls="dashed", color="gray", lw=1.0, zorder=0)
+ax.plot(xs, ys, ls="", marker="o", ms=markersize, color="black", zorder=1)
 ax.quiver(
     xs, ys, spin_vectors[:, 0], spin_vectors[:, 1], color=colors,
-    units="xy", scale_units="xy", scale=1, width=0.06, pivot="mid", zorder=1
+    units="xy", scale_units="xy", scale=1, width=0.06, pivot="mid", zorder=2
 )
 ax.set_axis_off()
 ax.set_aspect("equal")
-fig.set_size_inches(16, 9.26)
+fig.set_size_inches(9.8, 5.6)
 plt.tight_layout()
 plt.show()
+print(fig.get_size_inches())
 fig.savefig("figures/SpinConfigForPositiveGamma.pdf", transparent=True)
 plt.close("all")

### 2020-11-11 FiguresForPaper/ClassicalGSForNegativeGamma.py
Minor changes to `ClassicalGSForNegativeGamma.py`.

@@ -81,7 +81,7 @@ for index in range(4):
 
     for bond in INTRA_BONDS:
         (x0, y0), (x1, y1) = bond.endpoints
-        ax.plot([x0, x1], [y0, y1], ls="solid", lw=2, color="black", zorder=0)
+        ax.plot([x0, x1], [y0, y1], ls="dashed", lw=3, color="gray", zorder=0)
 
     colors = 0.5 * spin_vectors + 0.5
     ax.quiver(
@@ -89,10 +89,14 @@ for index in range(4):
         color=colors, units="xy", scale_units="xy", scale=1.45,
         width=0.06, pivot="mid", clip_on=False, zorder=1,
     )
+    ax.plot(
+        POINTS[:, 0], POINTS[:, 1],
+        color="k", ls="", marker="o", ms=15, zorder=2
+    )
 
     ax.text(
         1.0, 1.5 * SQRT3, sub_fig_tag,
-        ha="center", va="center", fontsize=LARGE,
+        ha="center", va="center", fontsize=XXLARGE+6,
     )
 
     ax.set_axis_off()

### 2020-11-11 paper/paper.tex
Paper 2020-08-11 16:10
Paper 2020-08-11 19:41

@@
 \end{figure}
-In fact, magnetic ions located at the center of edge-sharing octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}.
+In fact, magnetic ions located at the center of edge-shared octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}.
 On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments.
@@
 The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{PhysRevB.91.155135,JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}.
-When the symmetric off-diagonal $\Gamma$ interaction is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$ N\'{e}el, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}.
+When the symmetric off-diagonal exchange interaction $\Gamma$ is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}.
 However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce.
@@
 
-In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses.
+In this paper, we study the global phase diagram and the phase transitions of the triangular-lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses.
 We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations.
@@
 
-In the followings, for convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchange parameters using spherical angles $\alpha$ and $\beta$
+In the followings, for convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchange interactions using spherical angles $\alpha$ and $\beta$
 \begin{equation}
@@
 \end{align*}
-This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the spin operators on the sublattices $1$, $2$, and $3$, respectively.
+This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the sublattices $1$, $2$, and $3$, respectively.
 The resulting Hamiltonian $H^{\prime}(\bm{S}^{\prime})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{\prime} = -J$ and $K^{\prime} = 2J + K$.
@@
 Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-A and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
-We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}.
+We note that there are two special points with $J=K=0$ and $\Gamma=\pm1$ in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}.
 Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the numerical simulations by using the ``basin-hopping" global optimization and classical Monte Carlo methods.
@@
     \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
-    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in exact cluster GS for (a) FM-A, (b) FM-C, (c) stripe-A and (d) stripe-B phases.
+    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in exact cluster GS for (a) FM-A, (b) FM-B, (c) stripe-A and (d) stripe-B phases.
 The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b).
 The green dashed lines and solid circles mark the ordered moment directions for the classical states.
-Note that the GSs are six-fold degenerate for the stripe-A and stripe-B phase, and two-fold degenerate for the FM-C phase, so the total probabilities for all of these phases are approximate to $1$.
+Note that the GSs are six-fold degenerate for the FM-A, stripe-A and stripe-B phase, and two-fold degenerate for the FM-B phase, so the total probabilities for all of these phases are approximate to $1$.
 }

### 2020-11-11 paper/paper.tex
Paper 2020-08-12 14:51

--- 2020-08-12 paper/paper.tex
@@
 In particular, the spin-1/2 case has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
-When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}.
+When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.94.121111,PhysRevB.96.075116,PhysRevLett.120.207203,PhysRevLett.123.207203}.
 All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.
@@
 Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li).
-In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra.
+In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbital coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra.
 However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases.
@@
 In fact, magnetic ions located at the center of edge-sharing octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}.
-On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments.
-In particular, due to their possible Kramers doublets and spin-orbital coupling, the $4f$ electrons can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbit entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms.
-A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203} and YbZnGaO$_{4}$~\cite{PhysRevLett.120.087201}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra.
+On the experimental side, studies on several classes of  compounds containing localized $4d$, $5d$ or $4f$ electrons have recently shown that the quantum spin model on the triangular lattice can be formed by the localized moments~\cite{PhysRevB.86.140405,PhysRevB.94.174410,srep16419,PhysRevLett.115.167203,PhysRevLett.120.087201}.
+In particular, due to their possible Kramers doublets and spin-orbital coupling, these moments can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbital entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms.
+A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra.
 More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
 The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,PhysRevB.100.241116,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}.
-These triangluar magnets of rare-earth ions provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbit coupling.
+These triangluar magnets provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbital couplings.
 
@@
 All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types.
-Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,PhysRevB.91.155135,JPSJ.85.114710}.
+Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,PhysRevB.91.155135,JPSJ.85.114710,PhysRevResearch.1.013002}.
 However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate.
-The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{PhysRevB.91.155135,JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}.
+The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, the Schwinger-boson mean-field theory thought it to be a nematic phase~\cite{PhysRevB.95.024421}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{PhysRevB.91.155135,JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}.
 When the symmetric off-diagonal $\Gamma$ interaction is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$ N\'{e}el, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}.
@@
 There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases designated as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase.
-Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses.}
+Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses.
+The inset sub-figure(a) is the global phase diagram of the HK model.
+The two-way arrows indicate parameter pairs that can be connected by the FST.}
 \end{figure*}
@@
 Thus, by virtue of the FST, two more magnetic ordered phases can be identified.
-When $\beta=\pi - \arctan\frac{1}{2}$ in Eq.~\eqref{eq:FST}, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$, whose GS is a FM state.
+For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$.
+Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state of $\bm{S}$.
+Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$ and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$.
+However, for the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since it is mapped to itself under FST, we can not identify its magnetic properties with the FST.
+
+% When $\beta=\pi - \arctan\frac{1}{2}$ in Eq.~\eqref{eq:FST}, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$, whose GS is a FM state.
 Therefore, transformating back to the original spin basis, a collinear stripe order can be obtained.
@@
     \caption{\label{fig:GSForPositiveGamma}(Color online) Typical disordered GS for $J=K=0, \Gamma=1$.
-The 3D unit spin vectors were projected to the $xy$ plane and different vectors were represented by different colors.}
+For clarity, the equal spin vectors are marked with the same color, and the arrows denote the projections of the three-dimensional vectors to the $xy$ plane.}
 \end{figure}
@@
     \caption{\label{fig:GSForNegativeGamma}(Color online) Typical classical GS spin configurations for $J=K=0, \Gamma=-1$.
-The 3D unit spin vectors were projected to the $xy$ plane and different vectors were represented by different colors.
+The spin vectors were projected to the $xy$ plane and different vectors were represented by different colors.
 (a)-(c) Stripe ordered states.
@@
 For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(d), the spins form antiferromagetic chains along the $x$-bond direction and the moment direction for the blue arrows are $[100]$.
-There are no association between different chains.
+Different antiferromagnetic chains are decoupled in the nematic state.
 Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(e) and Fig.~\ref{fig:GSForPositiveK}(f) respectively.
@@
     \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveKitaev.pdf}
-    \caption{\label{fig:GSForPositiveK}(Color online) Classical nematic and stripe GS spin configurations for $J=\Gamma=0, K=1$.}
+    \caption{\label{fig:GSForPositiveK}(Color online) Classical stripe and nematic GS spin configurations for $J=\Gamma=0, K=1$. (a)-(c) Stripe states. (d)-(f) Nematic states.}
 \end{figure}

### 2020-11-11 paper/paper.tex
Paper 2020-08-17 21:53

@@
 
-In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses.
+In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model in detail using a combination of ED and classical analyses.
 We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations.
@@
 There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases designated as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase.
-Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses.
-The inset sub-figure(a) is the global phase diagram of the HK model.
-The two-way arrows indicate parameter pairs that can be connected by the FST.}
+Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses.}
 \end{figure*}
 
-The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}.
-The phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).
+The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).
+We find nine magnetically ordered phases and a possible QSL phase.
+The nine ordered magnetic phases consist of three stripe phases (dubbed as stripe-A, strip-B and stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}), three ferromagnetic phases (dubbed as FM-A, FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}), one 120$^\circ$ N\'{e}el phase, one dual N\'{e}el phase and one modulated stripe phase.
+In the followings, we will discuss the details on the natures of these phases and the corresponding phase transitions.
 
-In the HK limit ($\Gamma=0$), as with the previous study~\cite{KaiLi2015}, we find five quantum phases.
-For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{fig/HKModel.pdf}
+    \caption{\label{fig:HKModel}(Color online) Phase diagram in the HK limit ($\Gamma=0$). The double-arrow lines are the representative lines that connect the points exactly related by the FST.}
+\end{figure}
+Let's first discuss the the HK limit for $\Gamma=0$.
+As with the previous study~\cite{KaiLi2015}, we find five quantum phases (see Fig.~\ref{fig:HKModel}).
+For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state (denoted as FM-A) for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively.
 As mentioned in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions.
-Thus, by virtue of the FST, two more magnetic ordered phases can be identified.
+Thus, by virtue of the FST, we can identify other two magnetically ordered phases.
 For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$.
-Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state of $\bm{S}$.
-Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$ and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$.
-However, for the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since it is mapped to itself under FST, we can not identify its magnetic properties with the FST.
+Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state (denoted as stripe-A) of $\bm{S}$.
+Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$, and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$.
+Moreover, as indicated in Fig.~\ref{fig:HKModel}, the transition points $\beta=0.23\pi$ and $0.64\pi$ can also be well mapped to the transition points $\beta=1.90\pi$ and $1.82\pi$ through the FST.
+The isolated transition point $\beta=\pi$ is also consistent with the FST, as it is mapped to itself under the FST.
+
+For the phase near the AFM Kitaev point ($J=\Gamma=0$, $K=1$), which is between $\beta=1.90\pi$ and $0.23\pi$,  the points in this phase are still mapped to those in the same phase under the FST, so we can not identify its magnetic properties by the FST, and it was supposed to be a magnetically disordered phase in our previous study~\cite{KaiLi2015}.
+However, as shown in Fig.~\ref{fig:StructureFactors}(a), when we check the SSF in this phase, we find that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase.
+To find out, we further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters.
+We find that there are two types of degenerate classical GSs, one of which has the stripe order and the other is the nematic state, since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details).
+When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order.
+As shown in Fig.~\ref{fig:StructureFactors}(i), the peaks of SSF of the classical stripe orders are also consistent with the result calculated from ED [see Fig.~\ref{fig:StructureFactors}(a)].
+Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-B.
+Moreover, every stripe order in this phase (see Appendix~\ref{apx:DegeneratedStates} for details) can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.
+
+%The stripe orders are indeed possible GS spin configurations, but there are also many nematic states with the same energy as it at the classical level since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details).
+When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order.
+Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
+Moreover, every stripe order in this phase can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.
+
+%However, we can not identify the magnetic properties of the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since the points in this phase are still mapped to the points in the same phase under the FST.
 
@@
 
-The properties of each quantum phases, especially the spin configuration of the ordered phases, can be inferred from the SSF defined in Eq.~\eqref{eq:SSF}, so we calculate the SSF for the case of pure AFM Kitaev limit ($J=\Gamma=0$, $K=1$) and present the result in Fig.~\ref{fig:StructureFactors}(a).
+%The properties of each quantum phases, especially the spin configuration of the ordered phases, can be inferred from the SSF defined in Eq.~\eqref{eq:SSF}, so we calculate the SSF for the case of pure AFM Kitaev limit ($J=\Gamma=0$, $K=1$) and present the result in Fig.~\ref{fig:StructureFactors}(a).
 We find that the SSF shows obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i).
-For the sake of clarity, we further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters.
-The stripe orders are indeed possible GS spin configurations, but there are also many nematic states with the same energy as it at the classical level since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details).
-When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order.
-Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
-Moreover, every stripe order in this phase can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.
 
-When the $\Gamma$ term is included, we find that the FM phase and the stripe-C phase in the HK model are actually phase boundaries in the global phase diagram of the $J$-$K$-$\Gamma$ model.
-Moreover, except the 120$^\circ$ N\'{e}el state and the dual N\'{e}el state, which already exist in the HK limit, there are five other new phases according to the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
+Next, we will discuss the effects of the $\Gamma$ term on the phase diagram.
+A natural conjecture is that the phases in the HK limit ($\Gamma=0$) would extend to a larger region in the global phase diagram of the $J$-$K$-$\Gamma$ model.
+Our ED results do show that the stripe-A phase can extend to a large region from $\Gamma>0$ to $\Gamma<0$, which is consistent with the previous classical results~\cite{PhysRevB.92.165108}.
+The region of the dual N\'{e}el phase that was dubbed as a dual-$Z_{2}$ vortex crystal phase in Ref.~\onlinecite{PhysRevB.92.165108} is also consistent with the classical results.
+However, we find that an infinitesimal $\Gamma$ interaction can make the FM-A phase and the stripe-B phase unstable, so these two phases are actually phase boundaries in the global phase diagram.
+On the other hand, although the the 120$^\circ$ N\'{e}el phase can also extend to a certain region, its area in the phase diagram is much smaller than the classical results~\cite{PhysRevB.92.165108}.
+Besides these phases that already exist in the HK limit, there are five other new phases according to our ED calculations.
+Since the SSF is a key physical quantity to reveal the nature of each quantum phases, especially the spin configuration of the ordered phases, we will discuss the properties of the phases with $\Gamma\neq0$ in detail according to the SSFs.
 
-To reveal the natures of these new phases, we further study the SSFs in these new phases.
+In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e.
+$\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively.
+Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i).
+Thus, this further confirms that the stripe-A phase extents to a large region in the phase diagram.
+In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ in a new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.
+
+%To reveal the natures of these new phases, we further study the SSFs in these new phases.
 Since the stripe phase for $K<0$ in the HK limit is located inside a phase of the global phase diagram, we infer this phase to have a stripe order and denote it as the stripe-A phase in Fig.~\ref{fig:QuantumPhaseDiagram}.
@@
 We find that the spin arrangement is still a modulated stripe order, but the spin orientations are also modulated along the ferromagnetic chains in addition to a larger modulated period perpendicular to the chains.
-Thus, we divide a transition region between the stipe-A and stripe-B phase and term it the modulated stripe order phase.
+Thus, we divide a transition region between the stipe-A and stripe-C phase and term it the modulated stripe order phase.
 
 For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively.
-Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-A and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
+Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
 We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}.
@@
 That is to say, for $\Gamma > 0$ the ordered moment of the classical FM state prefers to lie in the lattice plane, while for $\Gamma<0$ the ordered moment would perpendicular to the lattice plane.
-This is the reason that there is a phase transition between the FM-A and FM-C phases, since the dependence of the ground state energy on the interaction parameters is different for the two FM phases, and the phase boundary is the line with $\Gamma=0$.
+This is the reason that there is a phase transition between the FM-B and FM-C phases, since the dependence of the ground state energy on the interaction parameters is different for the two FM phases, and the phase boundary is the line with $\Gamma=0$.
 
-The classical analysis suggests that the main difference between these FM phases lies in the ordered moment direction.
-To further confirm this, we use the spin coherent state to extract the moment direction of these FM phases from our ED cluster GS~\cite{PhysRevB.94.064435}.
+In order to confirm the consistency between the above classical analyses and the ED results, we use the spin coherent state to extract the moment direction of these FM phases from our ED cluster GS~\cite{PhysRevB.94.064435}.
 Since the cluster spin coherent state defined in Eq.~(\ref{eq:Spin-1/2CoherentState}) is captured only by a single pair of $(\theta, \phi)$ for the collinear states, it is easy to determine the direction of the FM orders by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
-The resulting probability maps for two representative interaction parameters of FM-A and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(a) and (b), where the large overlap between the exact cluster GS and FM cluster spin coherent state again provides solid evidence that the corresponding areas are FM phases.
-For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.
-The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in Fig.
-\ref{fig:Proabilities}(b)).
-Thus, the moment directions extracted from the ED cluster GS are consistent with the classical analysis.
-In the HK limit, for the pure FM Heisenberg model ($J=-1$), the FM state is spin rotational invariant and the ordered moment can point any direction.
+As shown in Fig.~\ref{fig:Proabilities}(a), for the FM-B phase, the peaks of the probability form a ring, which indicates that the moment being constrained to a plane with all directions degenerate.
+To compare with the classical results, we plot the classical magnetic moment directions with the green dashed line in Fig.~\ref{fig:Proabilities}(a), and we find that the the probability is concentrated near the classical magnetic moment directions.
+For the FM-C phase, the probability map is clearly peaked at specific directions, which are also consistent with the classical results marked by the green solid circle in Fig.
+\ref{fig:Proabilities}(b).
+Moreover, the large overlaps between the exact cluster GSs and FM cluster spin coherent states again provide solid evidences that the ED results are consistent with the classical analyses.
+
+%{\color{red}In the HK limit, for the pure FM Heisenberg model ($J=-1$), the FM state is spin rotational invariant and the ordered moment can point any direction.
 The Kitaev interaction breaks the spin rotational symmetry and pins the orderings to the axis direction (i.e., $x$, $y$ and $z$ directions) when the quantum fluctuations are included, although the classical energy in Eq.~(\ref{eq:EcFM}) is independent of the moment direction (see Appendix~\ref{apx:LSWOfFMA} for details).
 When the $\Gamma$ interactions are introduced, positive $\Gamma$ couplings drive the ordered moment to the lattice plane and negative $\Gamma$ couplings pin the ordered moment to be perpendicular to the lattice plane.
-Therefore, the line with $\Gamma=0$ is the phase boundary of the FM-A and FM-C phases.
+Therefore, the line with $\Gamma=0$ is the phase boundary of the FM-A and FM-C phases.}
+
+%The resulting probability maps for two representative interaction parameters of FM-B and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(a) and (b), form which we can see that both of the probabilities are concentrated near the classical magnetic moment directions.
+This large overlap between the exact cluster GS and FM cluster spin coherent state again provides solid evidence that the corresponding regions are FM phases.
+For the FM-B phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.
 
@@
 An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction, whereas the negative $\Gamma$ drives it to the $\bm{v}_1$ direction.
-Thus, there is a phase transition between the stripe-A and stripe-B phases, as the ground state energies have different dependence on the interaction parameters for the two stripe phases, and the phase boundary is the line with $\Gamma=0$.
+Thus, there is a phase transition between the stripe-A and stripe-C phases, as the ground state energies have different dependence on the interaction parameters for the two stripe phases, and the phase boundary is the line with $\Gamma=0$.
 
 To confirm that the classical analysis is consistent with our ED calculations, we use the spin coherent states again to extract the ordered moment direction of the ED ground states in these stripe phases.
-For brevity, we here only construct cluster spin coherent state based on the stripe-$x$ and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(c) and (d) for stripe-A and stripe-B, respectively.
+For brevity, we here only construct cluster spin coherent state based on the stripe-$x$ and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(c) and (d) for stripe-A and stripe-C, respectively.
 We can see that there are large overlaps between the exact cluster GS and stripe cluster spin coherent state, which indicates that the results based on the ED calculation is consistent with the classical analysis.
@@
 Thus, the DSF gives another evidence that this quantum phase is a QSL.
-The DSF also shows another feature that the periodicity of its lower edge is doubled, which is a possible signature of the translational symmetry fractionalization of a $Z_{2}$ spin liquid~\cite{PhysRevB.90.121102,mei2015fractionalized,PhysRevB.99.205119}.
+The DSF also shows another feature that the periodicity of its lower edge is doubled (i.e., $\tilde{M}$-$\tilde{\Gamma}$ forms a period instead of the usual $\tilde{M}$-$\tilde{M}$), which is a possible signature of the translational symmetry fractionalization of a $Z_{2}$ spin liquid~\cite{PhysRevB.90.121102,mei2015fractionalized,PhysRevB.99.205119}.
 Moreover, we also find that there is an obvious gap in the DSF.
@@
 Some representative curves are shown in Fig.~\ref{fig:SecondDerivatives}.
-In Fig.~\ref{fig:SecondDerivatives}(a) for $\alpha=0.05\pi$, the second derivative of $E_0$ versus $\beta$ has two peaks located at $\beta=-0.01\pi$ and $\beta=0.81\pi$, which are the phase boundaries between the FM-A and QSL phases.
+In Fig.~\ref{fig:SecondDerivatives}(a) for $\alpha=0.05\pi$, the second derivative of $E_0$ versus $\beta$ has two peaks located at $\beta=-0.01\pi$ and $\beta=0.81\pi$, which are the phase boundaries between the FM-B and QSL phases.
 As we increase $\alpha$ to $0.3\pi$, there are three singularities in the second derivatives (see Fig.~\ref{fig:SecondDerivatives}(b)).
-The small peak at $\beta=0.62\pi$ indicates the phase transition from modulated stripe to stripe-A, while the other two sharp peaks at $\beta=0.94\pi$ and $\beta=1.87\pi$ originate from the phase transitions from stripe-A to FM-A and from FM-A to stripe-B, respectively.
+The small peak at $\beta=0.62\pi$ indicates the phase transition from modulated stripe to stripe-A, while the other two sharp peaks at $\beta=0.94\pi$ and $\beta=1.87\pi$ originate from the phase transitions from stripe-A to FM-B and from FM-B to stripe-C, respectively.
 Fig.~\ref{fig:SecondDerivatives}(c) show the case for $\alpha=0.75\pi$, where the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signify the phase transitions between stripe-A and FM-C.
 On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$ and the corresponding results are shown in Fig.~\ref{fig:SecondDerivatives}(d)-(f).
-In Fig.~\ref{fig:SecondDerivatives}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$ and $\alpha=0.097\pi$ reveal the phase transitions from FM-A to QSL and further to stripe-B.
-The peak at about $\alpha=0.5\pi$ is due to the phase transition from stripe-B to stripe-A.
+In Fig.~\ref{fig:SecondDerivatives}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$ and $\alpha=0.097\pi$ reveal the phase transitions from FM-B to QSL and further to stripe-C.
+The peak at about $\alpha=0.5\pi$ is due to the phase transition from stripe-C to stripe-A.
 The last singularity at $\alpha=0.93\pi$ marks the phase boundary between stripe-A and FM-C.
@@
 
-\section{\label{apx:LSWOfFMA}Effects of Quantum fluctuations on FM phases}
+%\section{\label{apx:LSWOfFMA}Effects of Quantum fluctuations on FM phases}
 
-According to Eq.~(\ref{eq:EcFM}), the spin directions in the FM state are independent of the Kitaev interactions, but here we demonstrate that the Kitaev interaction can make the spins point to some specific directions when the quantum fluctuations are included by a linear spin-wave analysis.
+%According to Eq.~(\ref{eq:EcFM}), the spin directions in the FM state are independent of the Kitaev interactions, but here we demonstrate that the Kitaev interaction can make the spins point to some specific directions when the quantum fluctuations are included by a linear spin-wave analysis.
 Within the linear spin-wave theory, the GS energy per lattice site is given by $E_{SW}(\theta, \phi) = E^{c} + 1/(2N) \sum_{\bm{k}} \omega_{\bm{k}}(\theta, \phi)$, where $\omega_{\bm{k}}(\theta, \phi)$ is the spin-wave dispersion.
@@
 For the FM states of the $J$-$K$-$\Gamma$ model, the dispersion of magnon $\omega_{\bm{k}}(\theta, \phi)$ is given by
-\begin{equation}
-    \omega_{\bm{k}}(\theta, \phi)= \frac{1}{2} \sqrt{A_{\bm{k}}^{2}(\theta, \phi) - |B_{\bm{k}}(\theta, \phi)|^{2}}
-    \label{eq:LSWDispersion}
-\end{equation}
-where
-\begin{equation}
-A_{\bm{k}}(\theta, \phi)=A_{0} + \eta_{1} A_{1} + \eta_{2} A_{2} + \eta_{3} A_{3}, \nonumber
-\end{equation}
-\begin{equation}
-A_{0}=-6J - 2K - 4 \Gamma (v_{x} v_{z} + v_{y} v_{z} + v_{x} v_{y}), \nonumber
-\end{equation}
-\begin{equation}
-A_{1}=2J + K (1-v_{x}^{2}) - 2 \Gamma v_{y} v_{z}, \nonumber
-\end{equation}
-\begin{equation}
-A_{2}=2J + K (1-v_{z}^{2}) - 2 \Gamma v_{x} v_{y}, \nonumber
-\end{equation}
-\begin{equation}
-A_{3}=2J + K (1-v_{y}^{2}) - 2 \Gamma v_{x} v_{z}, \nonumber
-\end{equation}
-and
-\begin{equation}
-B_{\bm{k}}(\theta, \phi)=\eta_{1} B_{1} + \eta_{2} B_{2} + \eta_{3} B_{3}, \nonumber
-\end{equation}
-\begin{align}
-B_{1}=K (1 - v_{x}^{2}) + 2\Gamma v_{y} v_{z}- 2\text{i} (K \frac{v_{x} v_{y} v_{z}}{1-v_{z}^{2}} + \Gamma v_{x}), \nonumber
-\end{align}
-\begin{align}
-B_{2}=K (1 - v_{z}^{2}) + 2 \Gamma \frac{1 + v_{z}^{2}}{1 - v_{z}^{2}} v_{x}v_{y}+ 2\text{i} \Gamma \frac{v_{z}}{1 - v_{z}^{2}}(v_{x}^2 - v_{y}^2), \nonumber
-\end{align}
-\begin{align}
-B_{3}=- K (1 - v_{y}^{2})- 2 \Gamma v_{x}v_{z}+ 2\text{i} (K \frac{v_{x} v_{y} v_{z}}{1-v_{z}^{2}} + \Gamma v_{y}). \nonumber
-\end{align}
-Here $\eta_{1,2,3} = \cos \bm{k} \cdot \bm{a}_{1,2,3}$ and $\bm{a}_{1,2,3}$ are the three nearest neighbor bonds, $v_x$, $v_y$, $v_z$ are the three components of the classical spin with $v_{x} = \sin \theta \cos \phi$, $v_{y} = \sin \theta \sin \phi$ and $v_{z} = \cos \theta$.
+%\begin{equation}
+%    \omega_{\bm{k}}(\theta, \phi)= \frac{1}{2} \sqrt{A_{\bm{k}}^{2}(\theta, \phi) - |B_{\bm{k}}(\theta, \phi)|^{2}}
+%    \label{eq:LSWDispersion}
+%\end{equation}
+%where
+%\begin{equation}
+%A_{\bm{k}}(\theta, \phi)=A_{0} + \eta_{1} A_{1} + \eta_{2} A_{2} + \eta_{3} A_{3}, \nonumber
+%\end{equation}
+%\begin{equation}
+%A_{0}=-6J - 2K - 4 \Gamma (v_{x} v_{z} + v_{y} v_{z} + v_{x} v_{y}), \nonumber
+%\end{equation}
+%\begin{equation}
+%A_{1}=2J + K (1-v_{x}^{2}) - 2 \Gamma v_{y} v_{z}, \nonumber
+%\end{equation}
+%\begin{equation}
+%A_{2}=2J + K (1-v_{z}^{2}) - 2 \Gamma v_{x} v_{y}, \nonumber
+%\end{equation}
+%\begin{equation}
+%A_{3}=2J + K (1-v_{y}^{2}) - 2 \Gamma v_{x} v_{z}, \nonumber
+%\end{equation}
+%and
+%\begin{equation}
+%B_{\bm{k}}(\theta, \phi)=\eta_{1} B_{1} + \eta_{2} B_{2} + \eta_{3} B_{3}, \nonumber
+%\end{equation}
+%\begin{align}
+%B_{1}=K (1 - v_{x}^{2}) + 2\Gamma v_{y} v_{z}- 2\text{i} (K \frac{v_{x} v_{y} v_{z}}{1-v_{z}^{2}} + \Gamma v_{x}), \nonumber
+%\end{align}
+%\begin{align}
+%B_{2}=K (1 - v_{z}^{2}) + 2 \Gamma \frac{1 + v_{z}^{2}}{1 - v_{z}^{2}} v_{x}v_{y}+ 2\text{i} \Gamma \frac{v_{z}}{1 - v_{z}^{2}}(v_{x}^2 - v_{y}^2), \nonumber
+%\end{align}
+%\begin{align}
+%B_{3}=- K (1 - v_{y}^{2})- 2 \Gamma v_{x}v_{z}+ 2\text{i} (K \frac{v_{x} v_{y} v_{z}}{1-v_{z}^{2}} + \Gamma v_{y}). \nonumber
+%\end{align}
+%Here $\eta_{1,2,3} = \cos \bm{k} \cdot \bm{a}_{1,2,3}$ and $\bm{a}_{1,2,3}$ are the three nearest neighbor bonds, $v_x$, $v_y$, $v_z$ are the three components of the classical spin with $v_{x} = \sin \theta \cos \phi$, $v_{y} = \sin \theta \sin \phi$ and $v_{z} = \cos \theta$.
 In the HK limit ($\Gamma = 0$), the first derivatives of $\omega_{\bm{k}}(\theta, \phi)$ versus $\theta$ and $\phi$ are equal to zero when $v_{x} = \pm1$, $v_{y} = \pm1$ or $v_{z} = \pm1$.

### 2020-11-11 paper/paper.tex
Paper 2020-08-18 14:20

@@
 We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit.
-Near the antiferromagetic (AF) Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism.
-Around the AF $\Gamma$ point, we find a possible quantum spin liquid in a noticeable region with a continuum in spin excitations.
+Near the antiferromagetic Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism.
+Also, the order-by-disorder mechanism selects the ferromagnetic ordered states as the ground state out of the degenerate classical states for the pure $\Gamma$ models.
+Around the positive $\Gamma$ point, due to the interplay of the Heisenberg, Kiatev and $\Gamma$ interactions, we find a possible quantum spin liquid in a noticeable region with a continuum in spin excitations.
 \end{abstract}
@@
 
-In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model in detail using a combination of ED and classical analyses.
+In this paper, we comprehensively study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses.
 We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations.
@@
 When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases.
-With the aid of classical analysis, we determine the spin directions for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders.
+With the aid of classical analysis, we determine the spin configuration for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders.
 On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate.
 For the possible QSL phase, based on the investigation of the spin excitation spectrum, we find that the GS is probably a gapped $Z_{2}$ QSL.
-
-%The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK limit.
-The ED and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}.
-Section~\ref{sec:Results} gives the main results of this paper.
 
@@
 This special property of the model can help us to identify some exotic magnetically ordered phases from the well established simple counterparts.
-
-%\section{\label{sec:Methods}Methods}
 
@@
 The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
-There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases designated as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase.
-Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses.}
+There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases denoted as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase.
+Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-C phases given by the classical analyses.}
 \end{figure*}
@@
 
-%The stripe orders are indeed possible GS spin configurations, but there are also many nematic states with the same energy as it at the classical level since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details).
-When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order.
-Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
-Moreover, every stripe order in this phase can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.
-
-%However, we can not identify the magnetic properties of the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since the points in this phase are still mapped to the points in the same phase under the FST.
-
-% When $\beta=\pi - \arctan\frac{1}{2}$ in Eq.~\eqref{eq:FST}, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$, whose GS is a FM state.
-Therefore, transformating back to the original spin basis, a collinear stripe order can be obtained.
-Similarly, a noncollinear spiral order (Dual N\'{e}el) is obtained from the 120$^\circ$ N\'{e}el order for $\beta=-\arctan\frac{1}{2}$.
-However, for the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since it is mapped to itself under FST, we can not identify its magnetic properties with the FST.
-
-%The properties of each quantum phases, especially the spin configuration of the ordered phases, can be inferred from the SSF defined in Eq.~\eqref{eq:SSF}, so we calculate the SSF for the case of pure AFM Kitaev limit ($J=\Gamma=0$, $K=1$) and present the result in Fig.~\ref{fig:StructureFactors}(a).
-We find that the SSF shows obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i).
-
 Next, we will discuss the effects of the $\Gamma$ term on the phase diagram.
@@
 
-%To reveal the natures of these new phases, we further study the SSFs in these new phases.
-Since the stripe phase for $K<0$ in the HK limit is located inside a phase of the global phase diagram, we infer this phase to have a stripe order and denote it as the stripe-A phase in Fig.~\ref{fig:QuantumPhaseDiagram}.
-To confirm this, we present the SSFs for two typical points, i.e.
-$\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$, in the $\Gamma>0$ and $\Gamma<0$ regions in Fig.~\ref{fig:StructureFactors}(b) and (c), respectively.
-Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a signature feature of the stripe phase.
-In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-B in the phase diagram.
-
 When we carefully examine the SSF near $\beta=0.5\pi$, we find that the SSF is obviously different from those of the stripe phases.
@@
 We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}.
-Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the numerical simulations by using the ``basin-hopping" global optimization and classical Monte Carlo methods.
-For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state.
-For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state also appear (see Appendix~\ref{apx:DegeneratedStates} for details).
-However, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states according to our ED calculations.
+Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the classical analyses by using the ``basin-hopping" global optimization and classical Monte Carlo methods.
+For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state (see Appendix~\ref{apx:DegeneratedStates} for details).
+For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, there are also several noncollinear magnetic orders energetically degenerate with the FM state (see Appendix~\ref{apx:DegeneratedStates} for details).
+However, according to our ED calculations, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states.
 This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
@@
     \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
-    \caption{\label{fig:StructureFactors}(Color online) (a)-(h) Representative SSFs from the ED calculations for different interaction parameters.
-The green dashed lines marks the first BZ corresponding to the triangular lattice.
+    \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) strip-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL.
+The green dashed lines marks the first BZ of the triangular lattice.
 (i) Characteristic wave vectors for the FM and stipe phases.
@@
 Moreover, the large overlaps between the exact cluster GSs and FM cluster spin coherent states again provide solid evidences that the ED results are consistent with the classical analyses.
-
-%{\color{red}In the HK limit, for the pure FM Heisenberg model ($J=-1$), the FM state is spin rotational invariant and the ordered moment can point any direction.
-The Kitaev interaction breaks the spin rotational symmetry and pins the orderings to the axis direction (i.e., $x$, $y$ and $z$ directions) when the quantum fluctuations are included, although the classical energy in Eq.~(\ref{eq:EcFM}) is independent of the moment direction (see Appendix~\ref{apx:LSWOfFMA} for details).
-When the $\Gamma$ interactions are introduced, positive $\Gamma$ couplings drive the ordered moment to the lattice plane and negative $\Gamma$ couplings pin the ordered moment to be perpendicular to the lattice plane.
-Therefore, the line with $\Gamma=0$ is the phase boundary of the FM-A and FM-C phases.}
-
-%The resulting probability maps for two representative interaction parameters of FM-B and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(a) and (b), form which we can see that both of the probabilities are concentrated near the classical magnetic moment directions.
-This large overlap between the exact cluster GS and FM cluster spin coherent state again provides solid evidence that the corresponding regions are FM phases.
-For the FM-B phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate.
-
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
-    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in exact cluster GS for (a) FM-A, (b) FM-C, (c) stripe-A and (d) stripe-B phases.
+    \caption{\label{fig:Proabilities}(Color online) Maps of the probabilities of the cluster spin coherent states given by Eq.~\eqref{eq:Spin-1/2CoherentState} in exact cluster GS for (a) FM-B, (b) FM-C, (c) stripe-A and (d) stripe-C phases.
 The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b).
 The green dashed lines and solid circles mark the ordered moment directions for the classical states.
-Note that the GSs are six-fold degenerate for the stripe-A and stripe-B phase, and two-fold degenerate for the FM-C phase, so the total probabilities for all of these phases are approximate to $1$.
+Note that the GSs are two-fold degenerate for the FM-C phase, and six-fold degenerate for the stripe-A and stripe-C phases, so the total probabilities for all of these phases are approximate to $1$.
 }
@@
 \end{acknowledgments}
-
-% The following are the Appendixes of this article
-%\newpage
 
@@
 
-%\section{\label{apx:LSWOfFMA}Effects of Quantum fluctuations on FM phases}
-
-%According to Eq.~(\ref{eq:EcFM}), the spin directions in the FM state are independent of the Kitaev interactions, but here we demonstrate that the Kitaev interaction can make the spins point to some specific directions when the quantum fluctuations are included by a linear spin-wave analysis.
-Within the linear spin-wave theory, the GS energy per lattice site is given by $E_{SW}(\theta, \phi) = E^{c} + 1/(2N) \sum_{\bm{k}} \omega_{\bm{k}}(\theta, \phi)$, where $\omega_{\bm{k}}(\theta, \phi)$ is the spin-wave dispersion.
-The angles $\theta \in [0, \pi]$ and $\phi \in [0, 2\pi]$ are direction angles of the spins in spherical coordinate.
-The specific directions are selected if the minimum value of $E_{SW}(\theta, \phi)$ is arrived with some parameters $(\theta, \phi)$.
-For the FM states of the $J$-$K$-$\Gamma$ model, the dispersion of magnon $\omega_{\bm{k}}(\theta, \phi)$ is given by
-%\begin{equation}
-%    \omega_{\bm{k}}(\theta, \phi)= \frac{1}{2} \sqrt{A_{\bm{k}}^{2}(\theta, \phi) - |B_{\bm{k}}(\theta, \phi)|^{2}}
-%    \label{eq:LSWDispersion}
-%\end{equation}
-%where
-%\begin{equation}
-%A_{\bm{k}}(\theta, \phi)=A_{0} + \eta_{1} A_{1} + \eta_{2} A_{2} + \eta_{3} A_{3}, \nonumber
-%\end{equation}
-%\begin{equation}
-%A_{0}=-6J - 2K - 4 \Gamma (v_{x} v_{z} + v_{y} v_{z} + v_{x} v_{y}), \nonumber
-%\end{equation}
-%\begin{equation}
-%A_{1}=2J + K (1-v_{x}^{2}) - 2 \Gamma v_{y} v_{z}, \nonumber
-%\end{equation}
-%\begin{equation}
-%A_{2}=2J + K (1-v_{z}^{2}) - 2 \Gamma v_{x} v_{y}, \nonumber
-%\end{equation}
-%\begin{equation}
-%A_{3}=2J + K (1-v_{y}^{2}) - 2 \Gamma v_{x} v_{z}, \nonumber
-%\end{equation}
-%and
-%\begin{equation}
-%B_{\bm{k}}(\theta, \phi)=\eta_{1} B_{1} + \eta_{2} B_{2} + \eta_{3} B_{3}, \nonumber
-%\end{equation}
-%\begin{align}
-%B_{1}=K (1 - v_{x}^{2}) + 2\Gamma v_{y} v_{z}- 2\text{i} (K \frac{v_{x} v_{y} v_{z}}{1-v_{z}^{2}} + \Gamma v_{x}), \nonumber
-%\end{align}
-%\begin{align}
-%B_{2}=K (1 - v_{z}^{2}) + 2 \Gamma \frac{1 + v_{z}^{2}}{1 - v_{z}^{2}} v_{x}v_{y}+ 2\text{i} \Gamma \frac{v_{z}}{1 - v_{z}^{2}}(v_{x}^2 - v_{y}^2), \nonumber
-%\end{align}
-%\begin{align}
-%B_{3}=- K (1 - v_{y}^{2})- 2 \Gamma v_{x}v_{z}+ 2\text{i} (K \frac{v_{x} v_{y} v_{z}}{1-v_{z}^{2}} + \Gamma v_{y}). \nonumber
-%\end{align}
-%Here $\eta_{1,2,3} = \cos \bm{k} \cdot \bm{a}_{1,2,3}$ and $\bm{a}_{1,2,3}$ are the three nearest neighbor bonds, $v_x$, $v_y$, $v_z$ are the three components of the classical spin with $v_{x} = \sin \theta \cos \phi$, $v_{y} = \sin \theta \sin \phi$ and $v_{z} = \cos \theta$.
-In the HK limit ($\Gamma = 0$), the first derivatives of $\omega_{\bm{k}}(\theta, \phi)$ versus $\theta$ and $\phi$ are equal to zero when $v_{x} = \pm1$, $v_{y} = \pm1$ or $v_{z} = \pm1$.
-Accordingly, $E_{SW}(\theta, \phi)$ takes extreme value at these special moment directions.
-Combined with numerical calculations, the minimum value of $E_{SW}(\theta, \phi)$ is obtained when the direction of the magnetic moment is along $x$, $y$, $z$ axis direction.
-Thus, quantum fluctuation lift the degeneracy of the classical GS and select FM states with specific moment directions (i.e., $x$, $y$ and $z$ directions) as the quantum GSs.
-
 \bibliography{ref}

### 2020-11-11 paper/paper.tex
Paper 2020-08-21 15:55

--- 2020-11-11 paper/paper.tex
@@
 In particular, the spin-1/2 case has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
-When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.94.121111,PhysRevB.96.075116,PhysRevLett.120.207203,PhysRevLett.123.207203}.
+When the interactions beyond the NN Heisenberg type are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.94.121111,PhysRevB.96.075116,PhysRevLett.120.207203,PhysRevB.95.165110,PhysRevLett.123.207203,PhysRevX.9.031026}.
 All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.
@@
 However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases.
-The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204}, in which the NN Heisenberg interaction is also taken into account.
+The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204,10.1146/annurev-conmatphys-033117-053934}, in which the NN Heisenberg interaction is also taken into account.
 This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripe, and zigzag types, besides extended spin-liquid phases near the Kitaev limits.
@@
 Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included.
-Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204}.
+Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204,Winter_2017,10.1038/s42254-019-0038-2}.
 Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.
@@
 In fact, magnetic ions located at the center of edge-sharing octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}.
-On the experimental side, studies on several classes of  compounds containing localized $4d$, $5d$ or $4f$ electrons have recently shown that the quantum spin model on the triangular lattice can be formed by the localized moments~\cite{PhysRevB.86.140405,PhysRevB.94.174410,srep16419,PhysRevLett.115.167203,PhysRevLett.120.087201}.
+On the experimental side, studies on several classes of  compounds containing localized $4d$, $5d$ or $4f$ electrons have recently shown that the quantum spin model on the triangular lattice can be formed by the localized moments~\cite{PhysRevB.86.140405,PhysRevB.94.174410,srep16419,PhysRevLett.115.167203,PhysRevLett.120.087201,CEVALLOS2018154,10.1038/s41535-019-0151-6}.
 In particular, due to their possible Kramers doublets and spin-orbital coupling, these moments can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbital entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms.
-A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra.
+A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra, but due to the inherent disorder effect there are still controversies about the GS of this material~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.120.087201,PhysRevB.94.035107,Nature20614,nphys3971,PhysRevLett.117.267202,PhysRevX.8.031028,SciPostPhys.4.1.003,PhysRevB.97.184413}.
 More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored.
@@
 When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases.
-With the aid of classical analysis, we determine the spin directions for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders.
+With the aid of classical analysis, we determine the spin configuration for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders.
 On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate.
@@
 We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}.
-Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the numerical simulations by using the ``basin-hopping" global optimization and classical Monte Carlo methods.
-For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state.
-For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state also appear (see Appendix~\ref{apx:DegeneratedStates} for details).
-However, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states according to our ED calculations.
-This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
+Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the classical analyses by using the ``basin-hopping" global optimization and classical Monte Carlo methods.
+For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state (see Appendix~\ref{apx:DegeneratedStates} for details).
+For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, there are also several noncollinear magnetic orders energetically degenerate with the FM state (see Appendix~\ref{apx:DegeneratedStates} for details).
+However, according to our ED calculations, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states.
+This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevB.46.11137,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204,PhysRevX.5.041035}.
 \begin{figure}

### 2020-11-11 paper/paper.tex
Paper 2020-08-25 18:20

--- 2020-11-11 paper/paper.tex
@@
 
-\title{Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model}
+\title{Comprehensive study of the global phase diagram in the triangular $J$-$K$-$\Gamma$ model}
 
@@
 The celebrated Kitaev honeycomb model provides an analytically tractable example with an exact quantum spin liquid ground state.
-While in real materials, other types of interactions besides the Kitaev coupling are present and these models can also be generalized to a triangular lattice.
-Here, we study the classical and quantum Heisenberg-Kitaev-$\Gamma$ model on a triangular lattice using the classical Monte Carlo and exact diagonalization.
-We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit.
-Near the antiferromagetic Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism.
-Also, the order-by-disorder mechanism selects the ferromagnetic ordered states as the ground state out of the degenerate classical states for the pure $\Gamma$ models.
+While in real materials, other types of interactions besides the Kitaev coupling ($K$) are present, such as the Heisenberg ($J$) and symmetric off-diagonal ($\Gamma$) terms, and these interactions can also be generalized to a triangular lattice.
+Here, we carry out a comprehensive study of the $J$-$K$-$\Gamma$ model on the triangular lattice covering the full parameters region, using the combination of the exact diagonalization, classical Monte Carlo and analytic methods, with an emphasis on the effects of the $\Gamma$ term.
+In the HK limit ($\Gamma=0$), we find five quantum phases which is quite similar to its classical counterpart.
+Among them, the stripe-A and dual N\'{e}el phase are robust against the introduction of the $\Gamma$-term, in particular the stripe-A extends to the region connecting the $K=-1$ and $K=1$ for $\Gamma<0$.
+Though the 120$^\circ$ N\'{e}el phase also extends to a finite $\Gamma$, its region has been largely reduced compared to the previous classical result.
+Interestingly, the ferromagnetic (dubbed as FM-A) phase and the stripe-B phase are unstable in response to an infinitesimal $\Gamma$ interaction.
+Moreover, we find five new phases for $\Gamma\ne 0$ which are elaborated by both the quantum and classic numerical methods.
+Part of the space previously identified as 120$^\circ$ N\'{e}el phase in the previous classical study is found to give way to the modulated stripe phase.
+Depending on the sign of the $\Gamma$ term, the FM-A phase is transited into the FM-B ($\Gamma>0$) and FM-C ($\Gamma<0$) phase with different spin orientations.
+Similarly, the stripe-B p hase is transited into the stripe-C ($\Gamma>0$) and stripe-A ($\Gamma<0$).
 Around the positive $\Gamma$ point, due to the interplay of the Heisenberg, Kiatev and $\Gamma$ interactions, we find a possible quantum spin liquid in a noticeable region with a continuum in spin excitations.
+
+% Near the antiferromagetic Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism.
+Also, the order-by-disorder mechanism selects the ferromagnetic ordered states as the ground state out of the degenerate classical states for the pure $\Gamma$ models.We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit.
 \end{abstract}
@@
 
-In this paper, we comprehensively study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses.
-We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations.
+In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED, the classical simulation and analytical analyses.
 In the HK limit ($\Gamma=0$), there are five classical phases: one FM, two stripe, one $120^{\circ}$ N\'{e}el and its dual phases.
@@
 When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases.
-With the aid of classical analysis, we determine the spin configuration for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders.
+With the aid of classical analysis, we determine the spin configuration for each magnetically ordered phase and explain why there are phase transitions between the phases with the same type of classical orders.
 On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate.
-For the possible QSL phase, based on the investigation of the spin excitation spectrum, we find that the GS is probably a gapped $Z_{2}$ QSL.
+For the possible QSL phase, based on the investigation of the spin excitation spectrum, we suggest the GS is a gapped $Z_{2}$ QSL.
 
@@
 The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).
-We find nine magnetically ordered phases and a possible QSL phase.
+We find nine magnetically ordered phases and a phase ascribed to be a QSL.
 The nine ordered magnetic phases consist of three stripe phases (dubbed as stripe-A, strip-B and stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}), three ferromagnetic phases (dubbed as FM-A, FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}), one 120$^\circ$ N\'{e}el phase, one dual N\'{e}el phase and one modulated stripe phase.
@@
 \end{figure}
-Let's first discuss the the HK limit for $\Gamma=0$.
-As with the previous study~\cite{KaiLi2015}, we find five quantum phases (see Fig.~\ref{fig:HKModel}).
+Let's first discuss the HK limit for $\Gamma=0$.
+In accord with the previous study~\cite{KaiLi2015}, we find five quantum phases (see Fig.~\ref{fig:HKModel}).
 For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state (denoted as FM-A) for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively.
-As mentioned in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions.
+As noted in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions.
 Thus, by virtue of the FST, we can identify other two magnetically ordered phases.
@@
 
-For the phase near the AFM Kitaev point ($J=\Gamma=0$, $K=1$), which is between $\beta=1.90\pi$ and $0.23\pi$,  the points in this phase are still mapped to those in the same phase under the FST, so we can not identify its magnetic properties by the FST, and it was supposed to be a magnetically disordered phase in our previous study~\cite{KaiLi2015}.
-However, as shown in Fig.~\ref{fig:StructureFactors}(a), when we check the SSF in this phase, we find that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase.
-To find out, we further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters.
-We find that there are two types of degenerate classical GSs, one of which has the stripe order and the other is the nematic state, since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details).
+For the phase near the AFM Kitaev point ($J=\Gamma=0$, $K=1$), which is between $\beta=1.90\pi$ and $0.23\pi$,  the points in this phase are still mapped to those in the same phase under the FST, and it was supposed to be a magnetically disordered phase~\cite{KaiLi2015}.
+However, as shown in Fig.~\ref{fig:StructureFactors}(a), when we check the SSF in this phase, it is found that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase.
+We further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters.
+We find that there are two types of degenerate classical GSs, one of which has the stripe order and the other the nematic order, since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details).
 When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order.
@@
 
-Next, we will discuss the effects of the $\Gamma$ term on the phase diagram.
-A natural conjecture is that the phases in the HK limit ($\Gamma=0$) would extend to a larger region in the global phase diagram of the $J$-$K$-$\Gamma$ model.
-Our ED results do show that the stripe-A phase can extend to a large region from $\Gamma>0$ to $\Gamma<0$, which is consistent with the previous classical results~\cite{PhysRevB.92.165108}.
-The region of the dual N\'{e}el phase that was dubbed as a dual-$Z_{2}$ vortex crystal phase in Ref.~\onlinecite{PhysRevB.92.165108} is also consistent with the classical results.
+Then, let us study the effects of the $\Gamma$ term on the phase diagram.
+One may expect that the phases in the HK limit ($\Gamma=0$) would extend to a finite region in the global phase diagram of the $J$-$K$-$\Gamma$ model.
+Our ED results do show that the stripe-A phase can extend to a large region from $\Gamma>0$ to $\Gamma<0$, in particular it extends to the region connecting $K=-1$ to $K=1$ for $\Gamma<0$.
+The region of the dual N\'{e}el phase that was dubbed as a dual-$Z_{2}$ vortex crystal phase in Ref.~\onlinecite{PhysRevB.92.165108} also survives
+the introduction of the $\Gamma$ term, though the region is much smaller than the stripe-A phase. These results
+are consistent qualitatively with the classical results~\cite{PhysRevB.92.165108}.
 However, we find that an infinitesimal $\Gamma$ interaction can make the FM-A phase and the stripe-B phase unstable, so these two phases are actually phase boundaries in the global phase diagram.
-On the other hand, although the the 120$^\circ$ N\'{e}el phase can also extend to a certain region, its area in the phase diagram is much smaller than the classical results~\cite{PhysRevB.92.165108}.
+On the other hand, although the 120$^\circ$ N\'{e}el phase can also extend to a certain region, its area in the phase diagram is much smaller than the classical results~\cite{PhysRevB.92.165108}.
 Besides these phases that already exist in the HK limit, there are five other new phases according to our ED calculations.
@@
 Thus, this further confirms that the stripe-A phase extents to a large region in the phase diagram.
-In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ in a new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.
+In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ for one of the new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.
 
@@
 However, according to our ED calculations, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states.
-This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
+This selection of states among the degenerate classical ground states is the so called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
 \begin{figure}
@@
 
-According to the above analysis, we find that, unlike the case for the honeycomb lattice, the Kitaev interactions on the triangular lattice do not give rise to QSL states, so the quantum phase diagram is similar to its classical counterpart~\cite{PhysRevB.92.165108}.
+According to the above analysis, we find that, unlike the case for the honeycomb lattice, the Kitaev interactions on the triangular lattice do not give rise to QSL states.
 Here, the large coordination number plays a key role to stabilize the classical magnetic orders, although the geometric and exchange frustrations coexist in the triangular lattice $J$-$K$-$\Gamma$ model.
@@
     \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
-    \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for a $12 \times 12$ cluster.
+    \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for $\alpha=0.3\pi$, $\beta=0.5\pi$ in a $12 \times 12$ cluster.
 (b) SSF corresponding to the spin configuration shown in (a).
-(c) Spin configuration obtained from the classical Monte Carlo calculations for a $24 \times 24$ cluster.}
+(c) Spin configuration obtained from the classical Monte Carlo calculations in a $24 \times 24$ cluster.}
 \end{figure}
@@
 Thus, the DSF gives another evidence that this quantum phase is a QSL.
-The DSF also shows another feature that the periodicity of its lower edge is doubled (i.e., $\tilde{M}$-$\tilde{\Gamma}$ forms a period instead of the usual $\tilde{M}$-$\tilde{M}$), which is a possible signature of the translational symmetry fractionalization of a $Z_{2}$ spin liquid~\cite{PhysRevB.90.121102,mei2015fractionalized,PhysRevB.99.205119}.
+The DSF also shows another feature that the periodicity of its lower edge is doubled (i.e., $\tilde{M}$-$\tilde{\Gamma}$ forms a period instead of the usual $\tilde{M}$-$\tilde{M}$), which is a signature of the translational symmetry fractionalization of a $Z_{2}$ spin liquid~\cite{PhysRevB.90.121102,mei2015fractionalized,PhysRevB.99.205119}.
 Moreover, we also find that there is an obvious gap in the DSF.
@@
 
-In summary, by using exact diagnoalization calculations and classical analyses, we map out the global phase diagram of the $J$-$K$-$\Gamma$ model.
+%In summary, by using exact diagnoalization calculations and classical analyses, we map out the global phase diagram of the $J$-$K$-$\Gamma$ model.
 The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the positive $\Gamma$ point, for which we propose the ground state to be a gapped $Z_{2}$ QSL based on its spin excitation spectrum.
@@
 On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ and antiferromagnetic Kitaev models have specific orders, although the classical analyses suggest that the GSs are highly degenerate.
+
+In summary, we carry out a comprehensive study of the $J$-$K$-$\Gamma$ model on a triangular lattice in the full parameter space and map out its global phase diagram by use of a combination of the exact diagonalization, the classical Monte Carlo simulation and analytical analyses.
+We find that there are five quantum phases in the limit of $\Gamma=0$.
+Among them, the 120$^\circ$ N\'{e}el, the dual N\'{e}el and one of the stripe phases extend into the region with $\Gamma\ne 0$.
+However, the other stripe and the ferromagnetic phases are unstable in response to an infinitesimal $\Gamma$ interaction.
+Due to the introduction of the $\Gamma$ term, five new phases emerge including two ferromagnetic phases, one stripe, one modulated stripe and a possible quantum spin liquid.
+We also elaborate that the pure $\Gamma$ model has a ferromagnetic ground state and the antiferromagnetic Kitaev model a stripe ground state, which are selected by the order-by-disorder mechanism from the degenerate classic ground states.
 

### 2020-11-11 paper/paper.tex
Paper 2020-09-05 12:44

@@
 
-\title{Comprehensive study of the global phase diagram in the triangular $J$-$K$-$\Gamma$ model}
+\title{Comprehensive study of the global phase diagram of the $J$-$K$-$\Gamma$ model on a triangular lattice}
 
@@
 Here, we carry out a comprehensive study of the $J$-$K$-$\Gamma$ model on the triangular lattice covering the full parameters region, using the combination of the exact diagonalization, classical Monte Carlo and analytic methods, with an emphasis on the effects of the $\Gamma$ term.
-In the HK limit ($\Gamma=0$), we find five quantum phases which is quite similar to its classical counterpart.
-Among them, the stripe-A and dual N\'{e}el phase are robust against the introduction of the $\Gamma$-term, in particular the stripe-A extends to the region connecting the $K=-1$ and $K=1$ for $\Gamma<0$.
+In the HK limit ($\Gamma=0$), we find five quantum phases which are quite similar to their classical counterparts.
+Among them, the stripe-A and dual N\'{e}el phase are robust against the introduction of the $\Gamma$ term, in particular the stripe-A extends to the region connecting the $K=-1$ and $K=1$ for $\Gamma<0$.
 Though the 120$^\circ$ N\'{e}el phase also extends to a finite $\Gamma$, its region has been largely reduced compared to the previous classical result.
 Interestingly, the ferromagnetic (dubbed as FM-A) phase and the stripe-B phase are unstable in response to an infinitesimal $\Gamma$ interaction.
-Moreover, we find five new phases for $\Gamma\ne 0$ which are elaborated by both the quantum and classic numerical methods.
-Part of the space previously identified as 120$^\circ$ N\'{e}el phase in the previous classical study is found to give way to the modulated stripe phase.
-Depending on the sign of the $\Gamma$ term, the FM-A phase is transited into the FM-B ($\Gamma>0$) and FM-C ($\Gamma<0$) phase with different spin orientations.
-Similarly, the stripe-B p hase is transited into the stripe-C ($\Gamma>0$) and stripe-A ($\Gamma<0$).
+Moreover, we find five new phases for $\Gamma\ne 0$ which are elaborated by both the quantum and classical numerical methods.
+Part of the parameter space previously identified as 120$^\circ$ N\'{e}el phase in the classical study is found to give way to the modulated stripe phase.
+Depending on the sign of the $\Gamma$ term, the FM-A phase transits into the FM-B ($\Gamma>0$) and FM-C ($\Gamma<0$) phase with different spin orientations.
+Similarly, the stripe-B phase transits into the stripe-C ($\Gamma>0$) and stripe-A ($\Gamma<0$).
 Around the positive $\Gamma$ point, due to the interplay of the Heisenberg, Kiatev and $\Gamma$ interactions, we find a possible quantum spin liquid in a noticeable region with a continuum in spin excitations.
@@
 % Near the antiferromagetic Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism.
-Also, the order-by-disorder mechanism selects the ferromagnetic ordered states as the ground state out of the degenerate classical states for the pure $\Gamma$ models.We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit.
+Also, the order-by-disorder mechanism selects the ferromagnetic ordered states as the ground state out of the degenerate classical states for the pure $\Gamma$ models.
+% We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit.
 \end{abstract}
@@
 In particular, the spin-1/2 case has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
-When the interactions beyond the NN Heisenberg type are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.94.121111,PhysRevB.96.075116,PhysRevLett.120.207203,PhysRevB.95.165110,PhysRevLett.123.207203,PhysRevX.9.031026}.
+When the interactions beyond the NN Heisenberg type are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, stripe states and QSL states~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.94.121111,PhysRevB.96.075116,PhysRevLett.120.207203,PhysRevB.95.165110,PhysRevLett.123.207203,PhysRevX.9.031026,wu2020exact}.
 All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.
@@
 Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204,Winter_2017,10.1038/s42254-019-0038-2}.
-Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.
+Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevB.93.214431,PhysRevB.96.115103}.
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/ModelDefinition.pdf}
+    \includegraphics[width=\columnwidth]{ModelDefinition.pdf}
     \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron.
@@
 
-The phase diagram of the HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{PhysRevB.91.155135,KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}.
+The phase diagram of the HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{KaiLi2015,PhysRevB.91.155135}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}.
 All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types.
@@
 where $\langle i,j \rangle$ denotes the NN bonds, $\gamma$ takes value $x$, $y$, or $z$ depending on the direction of the NN bond as shown in Fig.~\ref{fig:ModelDefinition}(c), and $\alpha$, $\beta$ are the remaining directions.
-$J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions, and $\Gamma$ the symmetric off-diagonal exchanges.
+$J$ and $K$ are the magnitude of the Heisenberg and Kitaev interactions, and $\Gamma$ the symmetric off-diagonal exchange.
 
@@
 The FST is a spin rotation transformation which divides the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and performs the following rotations of the spins on the four sublattices to map the spin $\bm{S}_{i}$ to $\bm{S}_{i}^{\prime}$,
-\begin{align*}
-    & \bm{S}_{0}^{\prime} = \bm{S}_{0}& \quad \text{for sublattice 0}, \\
-    & \bm{S}_{1}^{\prime} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1}, \\
-    & \bm{S}_{2}^{\prime} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2}, \\
+\begin{align}
+    & \bm{S}_{0}^{\prime} = \bm{S}_{0}& \quad \text{for sublattice 0}, \nonumber \\
+    & \bm{S}_{1}^{\prime} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1}, \nonumber \\
+    & \bm{S}_{2}^{\prime} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2},  \nonumber \\
     & \bm{S}_{3}^{\prime} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}.
-\end{align*}
+    \label{eq:FST}
+\end{align}
 This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the spin operators on the sublattices $1$, $2$, and $3$, respectively.
-The resulting Hamiltonian $H^{\prime}(\bm{S}^{\prime})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{\prime} = -J$ and $K^{\prime} = 2J + K$.
+The resulting Hamiltonian $H^{\prime}(\bm{S}^{\prime})$ has the same form as the original Hamiltonian albeit with different model parameters,
+\begin{equation}
+J^{\prime} = -J, \ \ K^{\prime} = 2J + K.
+ \label{eq:JK}
+\end{equation}
 For the spherical angles defined in Eq.~\eqref{eq:Parameters}, the mapping takes the form
@@
     \tan\beta^{\prime} = -\sin\beta / (2\sin\beta + \cos\beta).
-    \label{eq:FST}
+    \label{eq:angle}
 \end{align}
@@
 
-\subsection{\label{subsec:MethodED}Exact Diagonalization method}
+\subsection{\label{subsec:MethodED}Exact Diagonalization Method}
 
@@
 
-\subsection{\label{subsec:MethodMC}Classical Monte Carlo method}
+\subsection{\label{subsec:MethodMC}Classical Monte Carlo Method}
 
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
+    \includegraphics[width=0.95\textwidth]{QuantumGlobalPhaseDiagram.pdf}
     \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/HKModel.pdf}
+    \includegraphics[width=\columnwidth]{HKModel.pdf}
     \caption{\label{fig:HKModel}(Color online) Phase diagram in the HK limit ($\Gamma=0$). The double-arrow lines are the representative lines that connect the points exactly related by the FST.}
@@
 In accord with the previous study~\cite{KaiLi2015}, we find five quantum phases (see Fig.~\ref{fig:HKModel}).
-For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state (denoted as FM-A) for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively.
-As noted in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions.
+For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively.
+So, the phase in the region between $\beta=1.00\pi$ and $1.82\pi$ is identified as FM-A, and that between $\beta=0.23\pi$ and $0.64\pi$ the 120$^\circ$ N\'{e}el state.
+As introduced in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under FST, which is in fact a spin-rotation transformation~\cite{PhysRevB.89.014414}.
+The transformed model has different exchange interactions related to the original ones via Eq.~\eqref{eq:JK} and the mapping angle is given by Eq.~\eqref{eq:angle}.
 Thus, by virtue of the FST, we can identify other two magnetically ordered phases.
-For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$.
+Starting from the FM-A phase, it will be transformed to the phase between $\beta=1.00\pi$ and $0.64\pi$ via the mapping angle Eq.~\eqref{eq:angle}.
+Then, using the spin rotation transformation Eq.~\eqref{eq:FST}, one can identify the phase between $\beta=1.00\pi$ and $0.64\pi$ as a collinear stripe state (denoted as stripe-A).
+Similarly, the 120$^\circ$ N\'{e}el state is transformed to a noncollinear spiral order (Dual N\'{e}el) in the region from $\beta=1.82\pi$ to $\beta=1.90\pi$.
+We also note that, as indicated in Fig.~\ref{fig:HKModel}, the transition points $\beta=0.23\pi$ and $0.64\pi$ are indeed mapped to the transition points $\beta=1.90\pi$ and $1.82\pi$ through the FST.
+However, the transition point $\beta=\pi$ is mapped to itself under the FST, so it the isolated transition point.
+
+%For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$.
 Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state (denoted as stripe-A) of $\bm{S}$.
 Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$, and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$.
-Moreover, as indicated in Fig.~\ref{fig:HKModel}, the transition points $\beta=0.23\pi$ and $0.64\pi$ can also be well mapped to the transition points $\beta=1.90\pi$ and $1.82\pi$ through the FST.
-The isolated transition point $\beta=\pi$ is also consistent with the FST, as it is mapped to itself under the FST.
 
-For the phase near the AFM Kitaev point ($J=\Gamma=0$, $K=1$), which is between $\beta=1.90\pi$ and $0.23\pi$,  the points in this phase are still mapped to those in the same phase under the FST, and it was supposed to be a magnetically disordered phase~\cite{KaiLi2015}.
-However, as shown in Fig.~\ref{fig:StructureFactors}(a), when we check the SSF in this phase, it is found that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase.
+For the phase near the AFM Kitaev point ($J=\Gamma=0$, $K=1$), which is between $\beta=1.90\pi$ and $0.23\pi$, the points in this phase are mapped to those in the same phase under the FST, so it was supposed to be a magnetically disordered phase~\cite{KaiLi2015}.
+However, as shown in Fig.~\ref{fig:StructureFactors}(a), when check the SSF in this phase, we find that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase.
 We further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters.
@@
 As shown in Fig.~\ref{fig:StructureFactors}(i), the peaks of SSF of the classical stripe orders are also consistent with the result calculated from ED [see Fig.~\ref{fig:StructureFactors}(a)].
-Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-B.
-Moreover, every stripe order in this phase (see Appendix~\ref{apx:DegeneratedStates} for details) can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.
+Moreover, every stripe order in this phase (see Appendix~\ref{apx:DegeneratedStates} for details) can be transformed to another degenerate stripe pattern in the same phase by the spin rotation transformation of FST.
+Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model (between $\beta=1.90\pi$ and $0.23\pi$) is a stripe phase, which we label the stripe-B.
 
@@
 On the other hand, although the 120$^\circ$ N\'{e}el phase can also extend to a certain region, its area in the phase diagram is much smaller than the classical results~\cite{PhysRevB.92.165108}.
-Besides these phases that already exist in the HK limit, there are five other new phases according to our ED calculations.
+Besides these phases that already exist in the HK limit, there are five new phases according to our ED calculations.
 Since the SSF is a key physical quantity to reveal the nature of each quantum phases, especially the spin configuration of the ordered phases, we will discuss the properties of the phases with $\Gamma\neq0$ in detail according to the SSFs.
@@
 We further perform a classical Monte Carlo simulations (see Sec.~\ref{subsec:MethodMC}) on a $24 \times24$ lattice to check the stability of the modulated stripe order in the large-size systems, and the ground-state spin configuration is shown in Fig.~\ref{fig:ModulatedStripe}(c).
-We find that the spin arrangement is still a modulated stripe order, but the spin orientations are also modulated along the ferromagnetic chains in addition to a larger modulated period perpendicular to the chains.
-Thus, we divide a transition region between the stipe-A and stripe-C phase and term it the modulated stripe order phase.
+We find that the spin arrangement is still a modulated stripe order, although the spin orientations are also modulated along the ferromagnetic chains in addition to a larger modulated period perpendicular to the chains.
+Thus, we unveil an unnoticed phase in the region between the stipe-A and stripe-C phase and term it the modulated stripe order phase.
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
+    \includegraphics[width=\columnwidth]{StructureFactors.pdf}
     \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) strip-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL.
@@
 
-According to the above analysis, we find that, unlike the case for the honeycomb lattice, the Kitaev interactions on the triangular lattice do not give rise to QSL states.
+According to the above analyses, we find that, unlike the case for the honeycomb lattice, the Kitaev interactions on the triangular lattice do not give rise to QSL states.
 Here, the large coordination number plays a key role to stabilize the classical magnetic orders, although the geometric and exchange frustrations coexist in the triangular lattice $J$-$K$-$\Gamma$ model.
@@
 
-So far, we have basically determine the nature of each phase, but there are still two problems should be explained: first, why there are phase transitions between the phases with the same type of classical orders, such as the phase transitions between FM phases or stripe phases, and why the FM and stripe phases of the HK model are the phase boundaries in the global phase diagram of $J$-$K$-$\Gamma$ model; second, what other important characteristics of the possible QSL phase in the phase diagram can be used to help us understand its properties more deeply.
+So far, we have determined each phase in the parameter space, but there are still two problems should be addressed: first, why there are phase transitions between the phases with the same type of classical orders, such as the phase transitions between FM phases or stripe phases, and why the FM and stripe phases of the HK model are the phase boundaries in the global phase diagram of $J$-$K$-$\Gamma$ model; second, what other important characteristics of the possible QSL phase in the phase diagram can be used to help us understand its properties more deeply.
 In the followings, we will address these problems.
@@
     \centering
-    \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
+    \includegraphics[width=0.95\columnwidth]{ModulatedStripe.pdf}
     \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for $\alpha=0.3\pi$, $\beta=0.5\pi$ in a $12 \times 12$ cluster.
@@
 Since the cluster spin coherent state defined in Eq.~(\ref{eq:Spin-1/2CoherentState}) is captured only by a single pair of $(\theta, \phi)$ for the collinear states, it is easy to determine the direction of the FM orders by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
-As shown in Fig.~\ref{fig:Proabilities}(a), for the FM-B phase, the peaks of the probability form a ring, which indicates that the moment being constrained to a plane with all directions degenerate.
-To compare with the classical results, we plot the classical magnetic moment directions with the green dashed line in Fig.~\ref{fig:Proabilities}(a), and we find that the the probability is concentrated near the classical magnetic moment directions.
+As shown in Fig.~\ref{fig:Proabilities}(a), for the FM-B phase, the peaks of the probability form a ring, indicating that the moment is constrained to a plane with all directions degenerate.
+To compare with the classical results, we plot the classical magnetic moment directions with the green dashed line in Fig.~\ref{fig:Proabilities}(a), and find that the probability centers on the classical magnetic moment directions.
 For the FM-C phase, the probability map is clearly peaked at specific directions, which are also consistent with the classical results marked by the green solid circle in Fig.
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
+    \includegraphics[width=\columnwidth]{Probabilities.pdf}
     \caption{\label{fig:Proabilities}(Color online) Maps of the probabilities of the cluster spin coherent states given by Eq.~\eqref{eq:Spin-1/2CoherentState} in exact cluster GS for (a) FM-B, (b) FM-C, (c) stripe-A and (d) stripe-C phases.
-The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b).
+The radial and polar coordinate give the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b).
 The green dashed lines and solid circles mark the ordered moment directions for the classical states.
@@
 
-Inspired by the previous discussion of FM phases, we here perform the same analysis for the stripe phases.
-For stripe order, there are three degenerated spin configurations in real-space, designated as stripe-$x$, stripe-$y$ and stripe-$z$, where the FM chains are along the $x$-bond, $y$-bond and $z$-bond directions, respectively.
+Inspired by the above discussion of the FM phases, we here perform the same analysis for the stripe phases.
+For the stripe order, there are three degenerated spin configurations in the real space, designated as stripe-$x$, stripe-$y$ and stripe-$z$, where the FM chains are along the $x$-bond, $y$-bond and $z$-bond directions, respectively.
 For simplicity, we take the stripe-$x$ configuration as an example, and the other two configurations can be obtained by analogy.
-The energy per lattice site is
+The energy per lattice site for the stripe-$x$ configuration is
 \begin{eqnarray}
@@
 A typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}.
-We can find that a significant feature is that the whole spectrum is a broad continuum, which is a characteristic of QSL originating from the fractionalization of the $S=1$ spin excitations.
+A significant feature one can see is that the whole spectrum is a broad continuum, which is a characteristic of QSL originating from the fractionalization of the $S=1$ spin excitations.
 Thus, the DSF gives another evidence that this quantum phase is a QSL.
 The DSF also shows another feature that the periodicity of its lower edge is doubled (i.e., $\tilde{M}$-$\tilde{\Gamma}$ forms a period instead of the usual $\tilde{M}$-$\tilde{M}$), which is a signature of the translational symmetry fractionalization of a $Z_{2}$ spin liquid~\cite{PhysRevB.90.121102,mei2015fractionalized,PhysRevB.99.205119}.
-Moreover, we also find that there is an obvious gap in the DSF.
+Moreover, we find that there is an obvious gap in the DSF.
 Thus, combined with all of the above results, we propose the GS of quantum $J$-$K$-$\Gamma$ model at the green area of the phase digram in Fig.~\ref{fig:QuantumPhaseDiagram} is a gapped $Z_{2}$ QSL.
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
+    \includegraphics[width=\columnwidth]{Spectrum.pdf}
     \caption{\label{fig:Spectrum}(Color online) DSF $A(\bm{k}, \omega)$ for $\alpha=0.05\pi,\beta=0.1\pi$ in the QSL phase.
@@
 Due to the introduction of the $\Gamma$ term, five new phases emerge including two ferromagnetic phases, one stripe, one modulated stripe and a possible quantum spin liquid.
-We also elaborate that the pure $\Gamma$ model has a ferromagnetic ground state and the antiferromagnetic Kitaev model a stripe ground state, which are selected by the order-by-disorder mechanism from the degenerate classic ground states.
+We also elaborate that the pure $\Gamma$ model has a ferromagnetic ground state and the antiferromagnetic Kitaev model a stripe ground state, which are selected by the order-by-disorder mechanism from the degenerate classical ground states.
+Our study of the global phase diagram on a generic spin model paves the way for future studies of a large group of triangular transition-metal materials with an appreciable spin-orbit coupling and electronic correlations.
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/SecondDerivatives.pdf}
+    \includegraphics[width=\columnwidth]{SecondDerivatives.pdf}
     \caption{\label{fig:SecondDerivatives} GS energies and their second derivatives versus $\alpha$ or $\beta$ for six representative path in the phase diagram.
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/AppendixSSF.pdf}
+    \includegraphics[width=\columnwidth]{AppendixSSF.pdf}
     \caption{\label{fig:AppendixSSF}(Color online) (a) and (b) are the representative SSF profiles for 120$^\circ$ N\'{e}el and Dual N\'{e}el phase, respectively.
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveGamma.pdf}
+    \includegraphics[width=\columnwidth]{SpinConfigForPositiveGamma.pdf}
     \caption{\label{fig:GSForPositiveGamma}(Color online) Typical disordered GS for $J=K=0, \Gamma=1$.
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{fig/SpinConfigForNegativeGamma.pdf}
+    \includegraphics[width=\columnwidth]{SpinConfigForNegativeGamma.pdf}
     \caption{\label{fig:GSForNegativeGamma}(Color online) Typical classical GS spin configurations for $J=K=0, \Gamma=-1$.
@@
 The direction for the green arrows in Fig.~\ref{fig:GSForPositiveK}(e) and pink arrows in Fig.~\ref{fig:GSForPositiveK}(f) are $[010]$ and $[001]$, respectively.
+
 \begin{figure}
-    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveKitaev.pdf}
+    \includegraphics[width=\columnwidth]{SpinConfigForPositiveKitaev.pdf}
     \caption{\label{fig:GSForPositiveK}(Color online) Classical stripe and nematic GS spin configurations for $J=\Gamma=0, K=1$. (a)-(c) Stripe states. (d)-(f) Nematic states.}

### 2020-11-11 paper/paper.tex
Paper 2020-11-11 15:30

@@
 While in real materials, other types of interactions besides the Kitaev coupling ($K$) are present, such as the Heisenberg ($J$) and symmetric off-diagonal ($\Gamma$) terms, and these interactions can also be generalized to a triangular lattice.
-Here, we carry out a comprehensive study of the $J$-$K$-$\Gamma$ model on the triangular lattice covering the full parameters region, using the combination of the exact diagonalization, classical Monte Carlo and analytic methods, with an emphasis on the effects of the $\Gamma$ term.
+Here, we carry out a comprehensive study of the $J$-$K$-$\Gamma$ model on the triangular lattice covering the whole parameter region, using the combination of the exact diagonalization, classical Monte Carlo and analytic methods, with an emphasis on the effects of the $\Gamma$ term.
 In the HK limit ($\Gamma=0$), we find five quantum phases which are quite similar to their classical counterparts.
 Among them, the stripe-A and dual N\'{e}el phase are robust against the introduction of the $\Gamma$ term, in particular the stripe-A extends to the region connecting the $K=-1$ and $K=1$ for $\Gamma<0$.
-Though the 120$^\circ$ N\'{e}el phase also extends to a finite $\Gamma$, its region has been largely reduced compared to the previous classical result.
+Though the 120$^\circ$ N\'{e}el phase also extends to a finite $\Gamma$, its region is largely reduced compared to the previous classical result.
 Interestingly, the ferromagnetic (dubbed as FM-A) phase and the stripe-B phase are unstable in response to an infinitesimal $\Gamma$ interaction.
@@
 Part of the parameter space previously identified as 120$^\circ$ N\'{e}el phase in the classical study is found to give way to the modulated stripe phase.
-Depending on the sign of the $\Gamma$ term, the FM-A phase transits into the FM-B ($\Gamma>0$) and FM-C ($\Gamma<0$) phase with different spin orientations.
-Similarly, the stripe-B phase transits into the stripe-C ($\Gamma>0$) and stripe-A ($\Gamma<0$).
+Depending on the sign of the $\Gamma$ term, the FM-A phase transits into the FM-B ($\Gamma>0$) and FM-C ($\Gamma<0$) phases with different spin orientations.
+Similarly, the stripe-B phase transits into the stripe-C ($\Gamma>0$) and stripe-A ($\Gamma<0$) phases.
 Around the positive $\Gamma$ point, due to the interplay of the Heisenberg, Kiatev and $\Gamma$ interactions, we find a possible quantum spin liquid in a noticeable region with a continuum in spin excitations.
-
-% Near the antiferromagetic Kitaev point, we show that the stripe order is selected out of the classic nematic order via the order-by-disorder mechanism.
-Also, the order-by-disorder mechanism selects the ferromagnetic ordered states as the ground state out of the degenerate classical states for the pure $\Gamma$ models.
-% We find that the quantum phase diagram is quite similar to its classical counterpart in the large region, suggesting that the Kitaev physics would have emerged largely in the classical limit.
 \end{abstract}
@@
 Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems.
-The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins.
+The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their AFM interaction, the third one can no longer point in a direction opposite to both other spins.
 In particular, the spin-1/2 case has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}.
@@
 On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states.
-Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy.
+Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual GS entropy.
 The spin-$1/2$ Kitaev model~\cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless QSL states supporting fractionalized excitations, is a celebrated example of a model with exchange frustration.
@@
 Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li).
-In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbital coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra.
+In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbital coupling, electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra.
 However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases.
@@
 All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types.
-Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,PhysRevB.91.155135,JPSJ.85.114710,PhysRevResearch.1.013002}.
-However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate.
+Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,PhysRevB.91.155135,JPSJ.85.114710,PhysRevResearch.1.013002,PhysRevResearch.2.013205}.
+However, the nature of the phase around the AFM Kitaev point is still under debate.
 The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, the Schwinger-boson mean-field theory thought it to be a nematic phase~\cite{PhysRevB.95.024421}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{PhysRevB.91.155135,JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}.
-When the symmetric off-diagonal $\Gamma$ interaction is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$ N\'{e}el, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}.
+When the symmetric off-diagonal $\Gamma$ interaction is included, a classical analysis reveals that the stripe and FM phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$ N\'{e}el, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}.
 However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce.
@@
 The FST is a spin rotation transformation which divides the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and performs the following rotations of the spins on the four sublattices to map the spin $\bm{S}_{i}$ to $\bm{S}_{i}^{\prime}$,
-\begin{align}
-    & \bm{S}_{0}^{\prime} = \bm{S}_{0}& \quad \text{for sublattice 0}, \nonumber \\
-    & \bm{S}_{1}^{\prime} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1}, \nonumber \\
-    & \bm{S}_{2}^{\prime} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2},  \nonumber \\
-    & \bm{S}_{3}^{\prime} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}.
-    \label{eq:FST}
-\end{align}
+\begin{eqnarray} \label{eq:FST}
+  \begin{split}
+  \bm{S}_{0}^{\prime} &= \bm{S}_{0} \quad &\text{for sublattice 0}, \\
+  \bm{S}_{1}^{\prime} &= (S_1^x, -S_1^y, -S_1^z) \quad &\text{for sublattice 1}, \\
+  \bm{S}_{2}^{\prime} &= (-S_2^x, S_2^y, -S_2^z) \quad &\text{for sublattice 2}, \\
+  \bm{S}_{3}^{\prime} &= (-S_3^x, -S_3^y, S_3^z) \quad &\text{for sublattice 3}.
+  \end{split}
+\end{eqnarray}
 This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the spin operators on the sublattices $1$, $2$, and $3$, respectively.
@@
 
-To identify the ground-state properties, we first examine the static structure factor (SSF),
+To identify the GS properties, we first examine the static structure factor (SSF),
 \begin{align}
@@
 We find nine magnetically ordered phases and a phase ascribed to be a QSL.
-The nine ordered magnetic phases consist of three stripe phases (dubbed as stripe-A, strip-B and stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}), three ferromagnetic phases (dubbed as FM-A, FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}), one 120$^\circ$ N\'{e}el phase, one dual N\'{e}el phase and one modulated stripe phase.
+The nine ordered magnetic phases consist of three stripe phases (dubbed as stripe-A, strip-B and stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}), three FM phases (dubbed as FM-A, FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}), one 120$^\circ$ N\'{e}el phase, one dual N\'{e}el phase and one modulated stripe phase.
 In the followings, we will discuss the details on the natures of these phases and the corresponding phase transitions.
@@
 So, the phase in the region between $\beta=1.00\pi$ and $1.82\pi$ is identified as FM-A, and that between $\beta=0.23\pi$ and $0.64\pi$ the 120$^\circ$ N\'{e}el state.
-As introduced in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under FST, which is in fact a spin-rotation transformation~\cite{PhysRevB.89.014414}.
+As introduced in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST, which is in fact a spin-rotation transformation~\cite{PhysRevB.89.014414}.
 The transformed model has different exchange interactions related to the original ones via Eq.~\eqref{eq:JK} and the mapping angle is given by Eq.~\eqref{eq:angle}.
 Thus, by virtue of the FST, we can identify other two magnetically ordered phases.
-Starting from the FM-A phase, it will be transformed to the phase between $\beta=1.00\pi$ and $0.64\pi$ via the mapping angle Eq.~\eqref{eq:angle}.
+Starting from the FM-A phase, it will be transformed to the phase between $\beta=1.00\pi$ and $0.64\pi$ via the angle mapping Eq.~\eqref{eq:angle}.
 Then, using the spin rotation transformation Eq.~\eqref{eq:FST}, one can identify the phase between $\beta=1.00\pi$ and $0.64\pi$ as a collinear stripe state (denoted as stripe-A).
@@
 
-%For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$.
-Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state (denoted as stripe-A) of $\bm{S}$.
-Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$, and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$.
-
 For the phase near the AFM Kitaev point ($J=\Gamma=0$, $K=1$), which is between $\beta=1.90\pi$ and $0.23\pi$, the points in this phase are mapped to those in the same phase under the FST, so it was supposed to be a magnetically disordered phase~\cite{KaiLi2015}.
-However, as shown in Fig.~\ref{fig:StructureFactors}(a), when check the SSF in this phase, we find that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase.
+However, as shown in Fig.~\ref{fig:StructureFactors}(a), when checking the SSF in this phase, we find that the SSF shows obvious peaks at the $\tilde{M}$ points, which implies that it is likely to be a magnetically ordered phase.
 We further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters.
@@
 As shown in Fig.~\ref{fig:StructureFactors}(e) for $\alpha=0.3\pi$ and $\beta=0.5\pi$, besides the peaks at the $\tilde{M}$ points, the SSF also shows significant intensities along the boundary of the BZ.
-In order to clarify whether there is another magnetic ordering phase near $\beta=0.5\pi$, we use the ``basin-hopping" technique again to search for the possible spin order for $\alpha=0.3\pi$ and $\beta=0.5\pi$ on a $12 \times 12$ lattice.
+In order to clarify whether there is another magnetically ordered phase near $\beta=0.5\pi$, we use the ``basin-hopping" technique again to search for the possible spin order for $\alpha=0.3\pi$ and $\beta=0.5\pi$ on a $12 \times 12$ lattice.
 The spin configuration is depicted in Fig.~\ref{fig:ModulatedStripe}(a), which exhibits a modulated stripe order.
-For this modulated stripe order, the spins are ferromagnetic along a next-nearest-neighbor direction and the spin orientation of the ferromagnetic chains are modulated to form a structure with a period of six.
+For this modulated stripe order, the spins are FM along a next-nearest-neighbor direction and the spin orientation of the FM chains are modulated along the direction perpendicular to the FM chains to form a structure with a period of six.
 As illustrated in Fig.~\ref{fig:ModulatedStripe}(b), the SSF of this classical six-chain stripe order shows clear peaks at the $\tilde{K}$ points in addition to those at the $\tilde{M}$ points, which is consistent with the characteristic of the SSF in Fig.~\ref{fig:StructureFactors}(e) calculated by the ED.
-We further perform a classical Monte Carlo simulations (see Sec.~\ref{subsec:MethodMC}) on a $24 \times24$ lattice to check the stability of the modulated stripe order in the large-size systems, and the ground-state spin configuration is shown in Fig.~\ref{fig:ModulatedStripe}(c).
-We find that the spin arrangement is still a modulated stripe order, although the spin orientations are also modulated along the ferromagnetic chains in addition to a larger modulated period perpendicular to the chains.
+We further perform a classical Monte Carlo simulations (see Sec.~\ref{subsec:MethodMC}) on a $24 \times24$ lattice to check the stability of the modulated stripe order in the large-size systems, and the GS spin configuration is shown in Fig.~\ref{fig:ModulatedStripe}(c).
+We find that the spin arrangement is still a modulated stripe order, although the spin orientations are also modulated along the FM chains in addition to a larger modulated period perpendicular to the chains.
 Thus, we unveil an unnoticed phase in the region between the stipe-A and stripe-C phase and term it the modulated stripe order phase.
@@
 For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively.
-Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
+The SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have FM orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}.
 We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}.
-Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the classical analyses by using the ``basin-hopping" global optimization and classical Monte Carlo methods.
+Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform an analysis based on the ``basin-hopping" global optimization and classical Monte Carlo methods.
 For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state (see Appendix~\ref{apx:DegeneratedStates} for details).
 For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, there are also several noncollinear magnetic orders energetically degenerate with the FM state (see Appendix~\ref{apx:DegeneratedStates} for details).
-However, according to our ED calculations, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states.
-This selection of states among the degenerate classical ground states is the so called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
+However, according to our ED calculations, for the quantum model, quantum fluctuations select the FM ordered states as the GS out of the degenerate manifolds of classical states.
+This selection of states among the degenerate classical GSs is the so called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical GS configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
 \begin{figure}
@@
     \includegraphics[width=\columnwidth]{StructureFactors.pdf}
-    \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) strip-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL.
-The green dashed lines marks the first BZ of the triangular lattice.
-(i) Characteristic wave vectors for the FM and stipe phases.
+    \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) stripe-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL.
+The green dashed lines mark the first BZ of the triangular lattice.
+(i) Characteristic wave vectors for the FM and stripe phases.
 See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
@@
 Here, the large coordination number plays a key role to stabilize the classical magnetic orders, although the geometric and exchange frustrations coexist in the triangular lattice $J$-$K$-$\Gamma$ model.
-However, the SSF for the quantum phase in a small region around the point with $J=K=0$ and $\Gamma=1$ illustrated in Fig.~\ref{fig:StructureFactors}(h) exhibits high intensities at both $\tilde{\Gamma}$ and $\tilde{M}$ points, and it seems impossible for a classical magnetically ordering state to satisfy these two wave vectors simultaneously, so we infer that this quantum phase is a QSL candidate.
+However, the SSF for the quantum phase in a small region around the point with $J=K=0$ and $\Gamma=1$ illustrated in Fig.~\ref{fig:StructureFactors}(h) exhibits high intensities at both $\tilde{\Gamma}$ and $\tilde{M}$ points, and it seems impossible for a classical magnetically ordered state to satisfy these two wave vectors simultaneously, so we infer that this quantum phase is a QSL candidate.
 
-So far, we have determined each phase in the parameter space, but there are still two problems should be addressed: first, why there are phase transitions between the phases with the same type of classical orders, such as the phase transitions between FM phases or stripe phases, and why the FM and stripe phases of the HK model are the phase boundaries in the global phase diagram of $J$-$K$-$\Gamma$ model; second, what other important characteristics of the possible QSL phase in the phase diagram can be used to help us understand its properties more deeply.
+So far, we have determined every phase in the parameter space, but there are still two problems should be addressed: first, why there are phase transitions between the phases with the same type of classical orders, such as the phase transitions between FM phases or stripe phases, and why the FM and stripe phases of the HK model are the phase boundaries in the global phase diagram of $J$-$K$-$\Gamma$ model; second, what other important characteristics of the possible QSL phase in the phase diagram can be used to help us understand its properties more deeply.
 In the followings, we will address these problems.
@@
 The condition $v^x + v^y + v^z = 0$ specifies a plane perpendicular to the $[111]$ direction, and considering the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b) it is actually the plane of the triangular lattice.
-That is to say, for $\Gamma > 0$ the ordered moment of the classical FM state prefers to lie in the lattice plane, while for $\Gamma<0$ the ordered moment would perpendicular to the lattice plane.
-This is the reason that there is a phase transition between the FM-B and FM-C phases, since the dependence of the ground state energy on the interaction parameters is different for the two FM phases, and the phase boundary is the line with $\Gamma=0$.
+That is to say, for $\Gamma > 0$ the ordered moment of the classical FM state prefers to lie in the lattice plane, while for $\Gamma<0$ the ordered moment would be perpendicular to the lattice plane.
+This is the reason that there is a phase transition between the FM-B and FM-C phases, since the dependence of the GS energy on the interaction parameters is different for the two FM phases, and the phase boundary is the line with $\Gamma=0$.
 
-In order to confirm the consistency between the above classical analyses and the ED results, we use the spin coherent state to extract the moment direction of these FM phases from our ED cluster GS~\cite{PhysRevB.94.064435}.
-Since the cluster spin coherent state defined in Eq.~(\ref{eq:Spin-1/2CoherentState}) is captured only by a single pair of $(\theta, \phi)$ for the collinear states, it is easy to determine the direction of the FM orders by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
+In order to confirm the consistency between the above classical analyses and the ED results, we use the spin coherent state to extract the moment directions of these FM phases from our ED cluster GSs~\cite{PhysRevB.94.064435}.
+Since the cluster spin coherent state defined in Eq.~(\ref{eq:Spin-1/2CoherentState}) is captured only by a single pair of $(\theta, \phi)$ for the collinear states, it is easy to determine the directions of the FM orders by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$.
 As shown in Fig.~\ref{fig:Proabilities}(a), for the FM-B phase, the peaks of the probability form a ring, indicating that the moment is constrained to a plane with all directions degenerate.
@@
 The radial and polar coordinate give the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b).
-The green dashed lines and solid circles mark the ordered moment directions for the classical states.
+The green dashed line and solid circles mark the ordered moment directions for the classical states.
 Note that the GSs are two-fold degenerate for the FM-C phase, and six-fold degenerate for the stripe-A and stripe-C phases, so the total probabilities for all of these phases are approximate to $1$.
@@
 
-In the HK limit, for $K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{stripe-x}^{c}$ takes minimum value at $v^x = 0$ which means that stripe-$x$ prefers to lie in the $yz$ plane.
+In the HK limit, for $K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{stripe-x}^{c}$ takes minimum value at $v^x = 0$ which means that the moments of the stripe-$x$ configuration prefer to lie in the $yz$ plane.
 An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction, whereas the negative $\Gamma$ drives it to the $\bm{v}_1$ direction.
-Thus, there is a phase transition between the stripe-A and stripe-C phases, as the ground state energies have different dependence on the interaction parameters for the two stripe phases, and the phase boundary is the line with $\Gamma=0$.
+Thus, there is a phase transition between the stripe-A and stripe-C phases, as the GS energies have different dependence on the interaction parameters for the two stripe phases, and the phase boundary is the line with $\Gamma=0$.
 
-To confirm that the classical analysis is consistent with our ED calculations, we use the spin coherent states again to extract the ordered moment direction of the ED ground states in these stripe phases.
-For brevity, we here only construct cluster spin coherent state based on the stripe-$x$ and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(c) and (d) for stripe-A and stripe-C, respectively.
-We can see that there are large overlaps between the exact cluster GS and stripe cluster spin coherent state, which indicates that the results based on the ED calculation is consistent with the classical analysis.
+To confirm that the classical analysis is consistent with our ED calculations, we use the spin coherent states again to extract the ordered moment directions of the ED GSs in these stripe phases.
+For brevity, we here only construct cluster spin coherent state based on the stripe-$x$ configuration and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(c) and (d) for the stripe-A and stripe-C phases, respectively.
+We can see that there are large overlaps between the exact cluster GS and stripe cluster spin coherent state, which indicates that the results based on the ED calculation are consistent with the classical analysis.
 
@@
 
-%In summary, by using exact diagnoalization calculations and classical analyses, we map out the global phase diagram of the $J$-$K$-$\Gamma$ model.
-The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the positive $\Gamma$ point, for which we propose the ground state to be a gapped $Z_{2}$ QSL based on its spin excitation spectrum.
-We also provide detailed descriptions of the phase transition between the classical magnetic phases.
-On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ and antiferromagnetic Kitaev models have specific orders, although the classical analyses suggest that the GSs are highly degenerate.
-
 In summary, we carry out a comprehensive study of the $J$-$K$-$\Gamma$ model on a triangular lattice in the full parameter space and map out its global phase diagram by use of a combination of the exact diagonalization, the classical Monte Carlo simulation and analytical analyses.
@@
 
-As mentioned in the main text, the phase boundaries are determined by the location of singularities in $-\partial^{2} E_{2} / \partial \alpha^{2}$ and $-\partial^{2} E_{0} / \partial \beta^{2}$ based on the ED calculations.
+As mentioned in the main text, the phase boundaries are determined by the locations of singularities in $-\partial^{2} E_{2} / \partial \alpha^{2}$ and $-\partial^{2} E_{0} / \partial \beta^{2}$ based on the ED calculations.
 Some representative curves are shown in Fig.~\ref{fig:SecondDerivatives}.
@@
 The small peak at $\beta=0.62\pi$ indicates the phase transition from modulated stripe to stripe-A, while the other two sharp peaks at $\beta=0.94\pi$ and $\beta=1.87\pi$ originate from the phase transitions from stripe-A to FM-B and from FM-B to stripe-C, respectively.
-Fig.~\ref{fig:SecondDerivatives}(c) show the case for $\alpha=0.75\pi$, where the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signify the phase transitions between stripe-A and FM-C.
-On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$ and the corresponding results are shown in Fig.~\ref{fig:SecondDerivatives}(d)-(f).
+Fig.~\ref{fig:SecondDerivatives}(c) shows the case for $\alpha=0.75\pi$, where the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signify the phase transitions between stripe-A and FM-C.
+On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$ and the corresponding results are shown in Figs.~\ref{fig:SecondDerivatives}(d)-(f).
 In Fig.~\ref{fig:SecondDerivatives}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$ and $\alpha=0.097\pi$ reveal the phase transitions from FM-B to QSL and further to stripe-C.
@@
 Last but not least, we show there are phase transitions between these different FM phases.
-In Fig.~\ref{fig:SecondDerivatives}(f) where $\beta=1.5\pi$, the sharp peak at $\alpha=0.5\pi$ shows that the FM-A phase for the HK model is a cirtical point, infinitesimal $\Gamma$ interaction will cause phase transition to other FM phases which have different moment direction from FM-A phase.
+In Fig.~\ref{fig:SecondDerivatives}(f) where $\beta=1.5\pi$, the sharp peak at $\alpha=0.5\pi$ shows that the FM-A phase for the HK model is a phase-transition boundary, infinitesimal $\Gamma$ interaction will cause phase transitions to other FM phases which have different moment directions from the FM-A phase.
 
@@
     \includegraphics[width=\columnwidth]{SecondDerivatives.pdf}
-    \caption{\label{fig:SecondDerivatives} GS energies and their second derivatives versus $\alpha$ or $\beta$ for six representative path in the phase diagram.
+    \caption{\label{fig:SecondDerivatives} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ for six representative paths in the phase diagram.
 The blue lines are the GS energies and the red lines are the second derivatives.
@@
 Here we provide additional SSF profiles as a supplement to these profiles shown in the main text.
-For classical 120$^\circ$ N\'{e}el state, the SSF has high intensity at the corner of the first BZ, i.e., $\tilde{K}$ points and the SSF peaked at the middle points of $\tilde{\Gamma}$ and $\tilde{K}$'s for the Dual N\'{e}el state.
-Fig.~\ref{fig:AppendixSSF}(a) and (b) show the SSF profiles calculated from our ED ground state at $\alpha=0.5\pi, \beta=0.5\pi$ and $\alpha=0.5\pi, \beta=1.85\pi$ which located at the 120$^\circ$ N\'{e}el phase and Dual N\'{e}el phase, respectively.
+For classical 120$^\circ$ N\'{e}el state, the SSF has high intensity at the corner of the first BZ, i.e., $\tilde{K}$ points and the SSF peaked at the middle points of $\tilde{\Gamma}$ and $\tilde{K}$'s for the dual N\'{e}el state.
+Fig.~\ref{fig:AppendixSSF}(a) and (b) show the SSF profiles calculated from our ED GS at $\alpha=0.5\pi, \beta=0.5\pi$ and $\alpha=0.5\pi, \beta=1.85\pi$ which located at the 120$^\circ$ N\'{e}el phase and dual N\'{e}el phase, respectively.
 For both profile, the points with highest intensity are consistent with the classical analyses.
@@
 Here we provide the SSFs for $\Gamma = \pm 1$ in Fig.~\ref{fig:AppendixSSF}(c) and (d).
-Both SSFs have high intensities at the $\tilde{\Gamma}$ points, which is a typical characteristic of FM state.
+Both SSFs have high intensities at the $\tilde{\Gamma}$ points, which is a typical characteristic of FM states.
 
@@
     \includegraphics[width=\columnwidth]{AppendixSSF.pdf}
-    \caption{\label{fig:AppendixSSF}(Color online) (a) and (b) are the representative SSF profiles for 120$^\circ$ N\'{e}el and Dual N\'{e}el phase, respectively.
+    \caption{\label{fig:AppendixSSF}(Color online) (a) and (b) are the representative SSF profiles for 120$^\circ$ N\'{e}el and dual N\'{e}el phase, respectively.
 (c) and (d) are the SSF profiles for the pure $\Gamma$ models with $\Gamma = \pm 1$, respectively.}
@@
 As for the stripe states, there are three degenerate spin configurations as shown in Fig.~\ref{fig:GSForNegativeGamma}(a)-(c) and the moment directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively.
-Apart from these collinear states, a noncollinear state also exist as the classical ground state.
+Apart from these collinear states, a noncollinear state also exist as the classical GS.
 The magnetic unit-cell contains four lattice sites, and the moment directions for the yellow, gray, pink, cyan arrows in Fig.~\ref{fig:GSForNegativeGamma}(d) are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.
@@
     \caption{\label{fig:GSForNegativeGamma}(Color online) Typical classical GS spin configurations for $J=K=0, \Gamma=-1$.
-The spin vectors were projected to the $xy$ plane and different vectors were represented by different colors.
+The spin vectors are projected to the $xy$ plane and different vectors are represented by different colors.
 (a)-(c) Stripe ordered states.
@@
 \end{figure}
-
-\subsection{$J=\Gamma=0$, $K=1$}
-
-The GSs for the classical antiferromagetic Kitaev model are also degenerate involving three types of nematic ordered states and three stripe ordered states.
-For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(a)-(c), the corresponding ordered moments lie in the $yz$, $xz$ and $xy$ plane, respectively.
-For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(d), the spins form antiferromagetic chains along the $x$-bond direction and the moment direction for the blue arrows are $[100]$.
-Different antiferromagnetic chains are decoupled in the nematic state.
-Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(e) and Fig.~\ref{fig:GSForPositiveK}(f) respectively.
-The direction for the green arrows in Fig.~\ref{fig:GSForPositiveK}(e) and pink arrows in Fig.~\ref{fig:GSForPositiveK}(f) are $[010]$ and $[001]$, respectively.
-
 \begin{figure}
@@
 
+\subsection{$J=\Gamma=0$, $K=1$}
+
+The GSs for the classical AFM Kitaev model are also degenerate involving three types of nematically ordered states and three stripe ordered states.
+For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(a)-(c), the corresponding ordered moments lie in the $yz$, $xz$ and $xy$ plane, respectively.
+For the nematically ordered state shown in Fig.~\ref{fig:GSForPositiveK}(d), the spins form AFM chains along the $x$-bond direction and the moment direction for the blue arrows are $[100]$.
+Different AFM chains are decoupled in the nematic state.
+Similarly, the AFM chains are along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(e) and Fig.~\ref{fig:GSForPositiveK}(f), respectively.
+The direction for the green arrows in Fig.~\ref{fig:GSForPositiveK}(e) and pink arrows in Fig.~\ref{fig:GSForPositiveK}(f) are $[010]$ and $[001]$, respectively.
+
 \bibliography{ref}

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 13:55

@@
 \usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}
+\usepackage{changes}
+    \definechangesauthor[name={Shi Wang}, color=red]{swang}
+    \setauthormarkup{}
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{ModelDefinition.pdf}
+    \includegraphics[width=\columnwidth]{fig/ModelDefinition.pdf}
     \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron.
@@
 \begin{align}
-    \bm{S}_{i} = \frac{\bm{h}_{i}^{loc}}{|\bm{h}_{i}^{loc}|} S,
+    \vec{S}_{i} = \frac{\vec{h}_{i}^{loc}}{|\vec{h}_{i}^{loc}|} S,
 \end{align}
@@
 \begin{align}
-    \bm{h}_{i}^{loc} = \sum_{\langle j \rangle} J \bm{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
+    \vec{h}_{i}^{loc} = \sum_{\langle j \rangle} J \vec{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
 \end{align}
+\added[swang]{
+    and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
+    \begin{eqnarray}
+        \vec{S}_i^{new} & = &\frac{2 (\vec{S}_i^{old} \cdot \vec{h}_i^{loc}) \vec{h}_i^{loc}}{|\vec{h}_i^{loc}|^2}-\vec{S}_i^{old}.
+    \end{eqnarray}
+}
 For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.
@@
     \centering
-    \includegraphics[width=0.95\textwidth]{QuantumGlobalPhaseDiagram.pdf}
-    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
+    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
+    \caption{\label{fig:QuantumPhaseDiagram}(Color online) \replaced[swang]{Zero-temperature global}{Global} phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
 The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
@@
 
-The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).
+The \added[swang]{zero-temperature} quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).
 We find nine magnetically ordered phases and a phase ascribed to be a QSL.
@@
     \centering
-    \includegraphics[width=\columnwidth]{HKModel.pdf}
+    \includegraphics[width=\columnwidth]{fig/HKModel.pdf}
     \caption{\label{fig:HKModel}(Color online) Phase diagram in the HK limit ($\Gamma=0$). The double-arrow lines are the representative lines that connect the points exactly related by the FST.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{StructureFactors.pdf}
+    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
     \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) stripe-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL.
 The green dashed lines mark the first BZ of the triangular lattice.
-(i) Characteristic wave vectors for the FM and stripe phases.
+(i) Characteristic wave vectors for the \replaced[swang]{FM (blue circle), stripe (orange square), 120$^\circ$ N\'{e}el (red up-triangle) and dual N\'{e}el (purple down-triangle)}{FM and stripe} phases.
 See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
@@
     \centering
-    \includegraphics[width=0.95\columnwidth]{ModulatedStripe.pdf}
+    \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
     \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for $\alpha=0.3\pi$, $\beta=0.5\pi$ in a $12 \times 12$ cluster.
@@
     \centering
-    \includegraphics[width=\columnwidth]{Probabilities.pdf}
+    \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
     \caption{\label{fig:Proabilities}(Color online) Maps of the probabilities of the cluster spin coherent states given by Eq.~\eqref{eq:Spin-1/2CoherentState} in exact cluster GS for (a) FM-B, (b) FM-C, (c) stripe-A and (d) stripe-C phases.
@@
     \centering
-    \includegraphics[width=\columnwidth]{Spectrum.pdf}
+    \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
     \caption{\label{fig:Spectrum}(Color online) DSF $A(\bm{k}, \omega)$ for $\alpha=0.05\pi,\beta=0.1\pi$ in the QSL phase.
@@
 11674158, No.
-11774152 and No.
-11774300) and National Key Projects for Research and Development of China (Grant No.
-2016YFA0300401).
+11774152\replaced[swang]{, No.
+11774300 and No.
+12004191}{ and No.
+11774300})\replaced[swang]{,}{ and} National Key Projects for Research and Development of China (Grant No.
+2016YFA0300401) \added[swang]{and Natural Science Foundation of Jiangsu Province, China (Grant No.
+BK20200738)}.
 \end{acknowledgments}
@@
 
-\section{\label{apx:PhaseBoundary}Phase boundaries in the quantum phase diagram}
+\section{\label{apx:PhaseBoundary}Phase boundaries in the \added[swang]{zero-temperature} quantum phase diagram}
 
-As mentioned in the main text, the phase boundaries are determined by the locations of singularities in $-\partial^{2} E_{2} / \partial \alpha^{2}$ and $-\partial^{2} E_{0} / \partial \beta^{2}$ based on the ED calculations.
-Some representative curves are shown in Fig.~\ref{fig:SecondDerivatives}.
-In Fig.~\ref{fig:SecondDerivatives}(a) for $\alpha=0.05\pi$, the second derivative of $E_0$ versus $\beta$ has two peaks located at $\beta=-0.01\pi$ and $\beta=0.81\pi$, which are the phase boundaries between the FM-B and QSL phases.
-As we increase $\alpha$ to $0.3\pi$, there are three singularities in the second derivatives (see Fig.~\ref{fig:SecondDerivatives}(b)).
+As mentioned in the main text, the phase boundaries are determined by the locations of singularities in $-\partial^{2} E_{0} / \partial \alpha^{2}$ and $-\partial^{2} E_{0} / \partial \beta^{2}$ based on the ED calculations.
+Some representative curves are shown in Fig.~\ref{fig:SecondDerivatives46}.
+In Fig.~\ref{fig:SecondDerivatives46}(a) for $\alpha=0.05\pi$, the second derivative of $E_0$ versus $\beta$ has two peaks located at $\beta=-0.01\pi$ and $\beta=0.81\pi$, which are the phase boundaries between the FM-B and QSL phases.
+As we increase $\alpha$ to $0.3\pi$, there are three singularities in the second derivatives (see Fig.~\ref{fig:SecondDerivatives46}(b)).
 The small peak at $\beta=0.62\pi$ indicates the phase transition from modulated stripe to stripe-A, while the other two sharp peaks at $\beta=0.94\pi$ and $\beta=1.87\pi$ originate from the phase transitions from stripe-A to FM-B and from FM-B to stripe-C, respectively.
-Fig.~\ref{fig:SecondDerivatives}(c) shows the case for $\alpha=0.75\pi$, where the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signify the phase transitions between stripe-A and FM-C.
-On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$ and the corresponding results are shown in Figs.~\ref{fig:SecondDerivatives}(d)-(f).
-In Fig.~\ref{fig:SecondDerivatives}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$ and $\alpha=0.097\pi$ reveal the phase transitions from FM-B to QSL and further to stripe-C.
+Fig.~\ref{fig:SecondDerivatives46}(c) shows the case for $\alpha=0.75\pi$, where the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signify the phase transitions between stripe-A and FM-C.
+On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$ and the corresponding results are shown in Figs.~\ref{fig:SecondDerivatives46}(d)-(f).
+In Fig.~\ref{fig:SecondDerivatives46}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$ and $\alpha=0.097\pi$ reveal the phase transitions from FM-B to QSL and further to stripe-C.
 The peak at about $\alpha=0.5\pi$ is due to the phase transition from stripe-C to stripe-A.
 The last singularity at $\alpha=0.93\pi$ marks the phase boundary between stripe-A and FM-C.
-In Fig.~\ref{fig:SecondDerivatives}(e), we show the phase transition between modulated stripe and 120$^\circ$ N\'{e}el as well as the phase transition from 120$^\circ$ N\'{e}el to stripe-A.
+In Fig.~\ref{fig:SecondDerivatives46}(e), we show the phase transition between modulated stripe and 120$^\circ$ N\'{e}el as well as the phase transition from 120$^\circ$ N\'{e}el to stripe-A.
 Here, $\beta$ is fixed to $0.5\pi$, and the transitions occur at $\alpha=0.32\pi$ and $\alpha=0.62\pi$, respectively.
 Last but not least, we show there are phase transitions between these different FM phases.
-In Fig.~\ref{fig:SecondDerivatives}(f) where $\beta=1.5\pi$, the sharp peak at $\alpha=0.5\pi$ shows that the FM-A phase for the HK model is a phase-transition boundary, infinitesimal $\Gamma$ interaction will cause phase transitions to other FM phases which have different moment directions from the FM-A phase.
+In Fig.~\ref{fig:SecondDerivatives46}(f) where $\beta=1.5\pi$, the sharp peak at $\alpha=0.5\pi$ shows that the FM-A phase for the HK model is a phase-transition boundary, infinitesimal $\Gamma$ interaction will cause phase transitions to other FM phases which have different moment directions from the FM-A phase.
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{SecondDerivatives.pdf}
-    \caption{\label{fig:SecondDerivatives} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ for six representative paths in the phase diagram.
-The blue lines are the GS energies and the red lines are the second derivatives.
+    \includegraphics[width=\columnwidth]{fig/SecondDerivatives46.pdf}
+    \caption{\label{fig:SecondDerivatives46} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ for six representative paths in the phase diagram.
+\added[swang]{The ED calculations are performed on a $4 \times 6$ cluster with periodic boundary condition.} The blue lines are the GS energies and the red lines are the second derivatives.
 In (a)-(c) $\alpha$ is fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively.
@@
 \end{figure}
+
+\added[swang]{
+    \section{\label{apx:SizeEffect}The effects of system size on the phase boundaries}
+    To study the effects of system size on the zero-temperature quantum phase diagram, we carry out ED calculations on a $2 \times 6$ cluster with periodic boundary condition, see Fig.~\ref{fig:SecondDerivatives26}(g) for the cluster as well as the periodic boundary condition.
+This cluster is compatible with most of the magnetic orders, such as FM, stripe, 120$^\circ$ N\'{e}el, dual N\'{e}el and modulated stripe shown in Fig.~\ref{fig:ModulatedStripe}(a).
+
+    In Fig.~\ref{fig:SecondDerivatives26}(a)-(c), the $\alpha$ parameter is fixed to $0.05\pi$, $0.2\pi$ and $0.75\pi$, respectively.
+In Fig.~\ref{fig:SecondDerivatives26}(d)-(f), the $\beta$ parameter is fixed to 0, $0.5\pi$ and $1.5\pi$, respectively.
+The singularities in Fig.~\ref{fig:SecondDerivatives26}(a)-(f) are consistent with the results of the $4 \times 6$ cluster shown in Fig.~\ref{fig:SecondDerivatives46}(a)-(f) even though the positions of the phase boundaries are slightly shifted.
+It is worth to note that, in Fig.~\ref{fig:SecondDerivatives26}(b) the $\beta$ parameter is fixed to $0.2\pi$ while in Fig.~\ref{fig:SecondDerivatives46}(b) $\beta = 0.3\pi$.
+The reason to take different $\beta$ parameter is that for $2 \times 6$ cluster the region of the 120$^\circ$ N\'eel phase would extend to larger area.
+If we continue take $\beta = 0.3\pi$, the singularities in -$\partial^2E_0 / \partial \alpha^2$ would not correspond to the peaks shown in Fig.~\ref{fig:SecondDerivatives46}(b).
+In a word, different system size only has effects on the positions of the phase boundaries but not these quantum phases.
+
+    \begin{figure}
+        \centering
+        \includegraphics[width=\columnwidth]{fig/SecondDerivatives26.pdf}
+        \includegraphics[width=\columnwidth]{fig/Cluster26.pdf}
+        \added[swang]{
+            \caption{\label{fig:SecondDerivatives26} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ along the same paths shown in Fig.~\ref{fig:SecondDerivatives46}.
+The blue lines are the GS energies and the red lines are the second derivatives.
+In (a)-(c) $\alpha$ is fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively.
+In (d)-(f), $\beta$ is fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively.
+(g) The $2 \times 6$ cluster as well as the periodic boundary condition that is used to perform the ED calculations.}
+        }
+    \end{figure}
+}
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{AppendixSSF.pdf}
+    \includegraphics[width=\columnwidth]{fig/AppendixSSF.pdf}
     \caption{\label{fig:AppendixSSF}(Color online) (a) and (b) are the representative SSF profiles for 120$^\circ$ N\'{e}el and dual N\'{e}el phase, respectively.
@@
     \centering
-    \includegraphics[width=\columnwidth]{SpinConfigForPositiveGamma.pdf}
+    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveGamma.pdf}
     \caption{\label{fig:GSForPositiveGamma}(Color online) Typical disordered GS for $J=K=0, \Gamma=1$.
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{SpinConfigForNegativeGamma.pdf}
+    \includegraphics[width=\columnwidth]{fig/SpinConfigForNegativeGamma.pdf}
     \caption{\label{fig:GSForNegativeGamma}(Color online) Typical classical GS spin configurations for $J=K=0, \Gamma=-1$.
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{SpinConfigForPositiveKitaev.pdf}
+    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveKitaev.pdf}
     \caption{\label{fig:GSForPositiveK}(Color online) Classical stripe and nematic GS spin configurations for $J=\Gamma=0, K=1$. (a)-(c) Stripe states. (d)-(f) Nematic states.}

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 13:57

@@
 This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripe, and zigzag types, besides extended spin-liquid phases near the Kitaev limits.
-Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e.
-bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.
+Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e., bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.
 Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included.
@@
     \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
-    \caption{\label{fig:QuantumPhaseDiagram}(Color online) \replaced[swang]{Zero-temperature global}{Global} phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
+    \caption{\label{fig:QuantumPhaseDiagram}(Color online) \added[swang]{Zero-temperature global} phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
 The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
@@
 
-In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e.
-$\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively.
+In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e., $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively.
 Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i).
@@
 In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ for one of the new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.
+\added[swang]{The difference between stripe-A, stripe-B and stripe-C lies in that they have different moment directions, which we will discuss in detail later.}
 
@@
 We find that the spin arrangement is still a modulated stripe order, although the spin orientations are also modulated along the FM chains in addition to a larger modulated period perpendicular to the chains.
-Thus, we unveil an unnoticed phase in the region between the stipe-A and stripe-C phase and term it the modulated stripe order phase.
+Thus, we unveil an unnoticed phase in the region between the stripe-A and stripe-C phase and term it the modulated stripe order phase.
 
@@
 The green dashed lines mark the first BZ of the triangular lattice.
-(i) Characteristic wave vectors for the \replaced[swang]{FM (blue circle), stripe (orange square), 120$^\circ$ N\'{e}el (red up-triangle) and dual N\'{e}el (purple down-triangle)}{FM and stripe} phases.
+(i) Characteristic wave vectors for the \added[swang]{FM (blue circle), stripe (orange square), 120$^\circ$ N\'{e}el (red up-triangle) and dual N\'{e}el (purple down-triangle)} phases.
 See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
@@
 \subsection{\label{subsec:FMPhases}FM Phases}
+
+\added[swang]{The most commonly used physcial quantity to distinguish different quantum phases is the order parameter.
+The order parameter of FM, stripe, 120$^\circ$ N\'eel and dual N\'eel states can be defined as $\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector of these magnetically ordered states.
+However since the cluster ground state does not spontaneously break the symmetry and corresponds to a superposition of all possible degenerate orderings, the calculated ground state average may give no useful information.}
 
@@
 11674158, No.
-11774152\replaced[swang]{, No.
-11774300 and No.
-12004191}{ and No.
-11774300})\replaced[swang]{,}{ and} National Key Projects for Research and Development of China (Grant No.
+11774152, No.
+11774300, \added[swang]{No.
+12004191 and No.
+12074175}, National Key Projects for Research and Development of China (Grant No.
 2016YFA0300401) \added[swang]{and Natural Science Foundation of Jiangsu Province, China (Grant No.
@@
 \section{\label{apx:SizeEffect}The effects of system size on the phase boundaries}
-    To study the effects of system size on the zero-temperature quantum phase diagram, we carry out ED calculations on a $2 \times 6$ cluster with periodic boundary condition, see Fig.~\ref{fig:SecondDerivatives26}(g) for the cluster as well as the periodic boundary condition.
-This cluster is compatible with most of the magnetic orders, such as FM, stripe, 120$^\circ$ N\'{e}el, dual N\'{e}el and modulated stripe shown in Fig.~\ref{fig:ModulatedStripe}(a).
+To study the effects of system size on the zero-temperature quantum phase diagram, we also carry out ED calculations on a $2 \times 6$ cluster with periodic boundary condition, see Fig.~\ref{fig:SecondDerivatives26}(g) for the shape of the cluster as well as the form of the boundary condition.
+This cluster and the boundary condition are compatible with most of the magnetic orders, such as FM, stripe, 120$^\circ$ N\'{e}el, dual N\'{e}el and six-chain modulated stripe shown in Fig.~\ref{fig:ModulatedStripe}(a).
 
@@
 The singularities in Fig.~\ref{fig:SecondDerivatives26}(a)-(f) are consistent with the results of the $4 \times 6$ cluster shown in Fig.~\ref{fig:SecondDerivatives46}(a)-(f) even though the positions of the phase boundaries are slightly shifted.
-It is worth to note that, in Fig.~\ref{fig:SecondDerivatives26}(b) the $\beta$ parameter is fixed to $0.2\pi$ while in Fig.~\ref{fig:SecondDerivatives46}(b) $\beta = 0.3\pi$.
-The reason to take different $\beta$ parameter is that for $2 \times 6$ cluster the region of the 120$^\circ$ N\'eel phase would extend to larger area.
-If we continue take $\beta = 0.3\pi$, the singularities in -$\partial^2E_0 / \partial \alpha^2$ would not correspond to the peaks shown in Fig.~\ref{fig:SecondDerivatives46}(b).
-In a word, different system size only has effects on the positions of the phase boundaries but not these quantum phases.
+It is worth to note that, in Fig.~\ref{fig:SecondDerivatives26}(b) the $\beta$ parameter is fixed to $0.2\pi$ while in Fig.~\ref{fig:SecondDerivatives46}(b) $\beta = 0.3\pi$, since the region of the 120$^\circ$ N\'eel phase extends to a larger area for the $2 \times 6$ cluster, which leads to that $\beta = 0.3\pi$ is still in the 120$^\circ$ N\'eel phase.
+Thus, in comparison with the results for the $4 \times 6$ cluster, we find that different system sizes do not change the phase diagram qualitatively and only affect the locations of the phase boundaries.
 
@@
 The blue lines are the GS energies and the red lines are the second derivatives.
-In (a)-(c) $\alpha$ is fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively.
+In (a)-(c) $\alpha$ is fixed to $0.05\pi$, $0.2\pi$ and $0.75\pi$, respectively.
 In (d)-(f), $\beta$ is fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively.

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 14:01

@@
 \end{align}
-\added[swang]{
-    and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
+\added[swang]{and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
 \begin{eqnarray}
@@
 \end{eqnarray}
-}
-For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.
+}For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.
 
@@
 In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ for one of the new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.
-\added[swang]{The difference between stripe-A, stripe-B and stripe-C lies in that they have different moment directions, which we will discuss in detail later.}
+
+\added[swang]{Although the singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ show that there are phase transitions between stripe-A, stripe-B and stripe-C (see Appendix \ref{apx:PhaseBoundary} for details), the differences between these phases cannot be seen from the SSFs, which show the same characteristic wave vector [Fig.~\ref{fig:StructureFactors}(a), (b), (c) and (d)].
+In fact, the most commonly used physcial quantity to distinguish different quantum phases is the order parameter.
+For the magnetically ordered phases, such as the stripe phases discussed here, the order parameter can be defined as $\bm{m}(\bm{Q})=\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector.
+Thus, both the ordering vector and the moment direction are the defining characteristic.
+The difference between the stripe-A, stripe-B and stripe-C phases lies in that they have different moment directions, which we will discuss in detail later in the paper.}
 
@@
 \subsection{\label{subsec:FMPhases}FM Phases}
-
-\added[swang]{The most commonly used physcial quantity to distinguish different quantum phases is the order parameter.
-The order parameter of FM, stripe, 120$^\circ$ N\'eel and dual N\'eel states can be defined as $\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector of these magnetically ordered states.
-However since the cluster ground state does not spontaneously break the symmetry and corresponds to a superposition of all possible degenerate orderings, the calculated ground state average may give no useful information.}
 

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 14:02

@@
 \end{align}
-\added[swang]{and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
+\added[swang]{
+    and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
     \begin{eqnarray}
@@
     \end{eqnarray}
-}For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.
+}
+For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.
 

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 14:04

@@
 For the magnetically ordered phases, such as the stripe phases discussed here, the order parameter can be defined as $\bm{m}(\bm{Q})=\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector.
-Thus, both the ordering vector and the moment direction are the defining characteristic.
-The difference between the stripe-A, stripe-B and stripe-C phases lies in that they have different moment directions, which we will discuss in detail later in the paper.}
+Thus, both the ordering vector and the moment direction are the defining characteristics.
+The difference between the stripe-A, stripe-B and stripe-C phases lies in that they have different moment directions, which we will discuss in detail later.}
 
@@
 \added[swang]{
-\section{\label{apx:SizeEffect}The effects of system size on the phase boundaries}
+\section{\label{apx:SizeEffect}Effects of system size on the phase boundaries}
 To study the effects of system size on the zero-temperature quantum phase diagram, we also carry out ED calculations on a $2 \times 6$ cluster with periodic boundary condition, see Fig.~\ref{fig:SecondDerivatives26}(g) for the shape of the cluster as well as the form of the boundary condition.
@@
 
-In Fig.~\ref{fig:SecondDerivatives26}(a)-(c), the $\alpha$ parameter is fixed to $0.05\pi$, $0.2\pi$ and $0.75\pi$, respectively.
-In Fig.~\ref{fig:SecondDerivatives26}(d)-(f), the $\beta$ parameter is fixed to 0, $0.5\pi$ and $1.5\pi$, respectively.
+In Fig.~\ref{fig:SecondDerivatives26}(a)-(c), the $\alpha$ parameter is fixed to be $0.05\pi$, $0.2\pi$ and $0.75\pi$, respectively.
+In Fig.~\ref{fig:SecondDerivatives26}(d)-(f), the $\beta$ parameter is fixed to be 0, $0.5\pi$ and $1.5\pi$, respectively.
 The singularities in Fig.~\ref{fig:SecondDerivatives26}(a)-(f) are consistent with the results of the $4 \times 6$ cluster shown in Fig.~\ref{fig:SecondDerivatives46}(a)-(f) even though the positions of the phase boundaries are slightly shifted.

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 14:11

@@
     \centering
-    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
+    \includegraphics[width=0.95\textwidth]{QuantumGlobalPhaseDiagram.pdf}
     \caption{\label{fig:QuantumPhaseDiagram}(Color online) \added[swang]{Zero-temperature global} phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
@@
 For the magnetically ordered phases, such as the stripe phases discussed here, the order parameter can be defined as $\bm{m}(\bm{Q})=\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector.
-Thus, both the ordering vector and the moment direction are the defining characteristics.
+Thus, both the ordering wave vector and the moment direction are the defining characteristics.
 The difference between the stripe-A, stripe-B and stripe-C phases lies in that they have different moment directions, which we will discuss in detail later.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
+    \includegraphics[width=\columnwidth]{StructureFactors.pdf}
     \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) stripe-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL.
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
+    \includegraphics[width=\columnwidth]{Probabilities.pdf}
     \caption{\label{fig:Proabilities}(Color online) Maps of the probabilities of the cluster spin coherent states given by Eq.~\eqref{eq:Spin-1/2CoherentState} in exact cluster GS for (a) FM-B, (b) FM-C, (c) stripe-A and (d) stripe-C phases.
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/SecondDerivatives46.pdf}
+    \includegraphics[width=\columnwidth]{SecondDerivatives46.pdf}
     \caption{\label{fig:SecondDerivatives46} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ for six representative paths in the phase diagram.
@@
   \centering
-  \includegraphics[width=\columnwidth]{fig/SecondDerivatives26.pdf}
-  \includegraphics[width=\columnwidth]{fig/Cluster26.pdf}
+  \includegraphics[width=\columnwidth]{SecondDerivatives26.pdf}
+  \includegraphics[width=\columnwidth]{Cluster26.pdf}
   \added[swang]{
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig/AppendixSSF.pdf}
+    \includegraphics[width=\columnwidth]{AppendixSSF.pdf}
     \caption{\label{fig:AppendixSSF}(Color online) (a) and (b) are the representative SSF profiles for 120$^\circ$ N\'{e}el and dual N\'{e}el phase, respectively.
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveKitaev.pdf}
+    \includegraphics[width=\columnwidth]{SpinConfigForPositiveKitaev.pdf}
     \caption{\label{fig:GSForPositiveK}(Color online) Classical stripe and nematic GS spin configurations for $J=\Gamma=0, K=1$. (a)-(c) Stripe states. (d)-(f) Nematic states.}

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 14:17

@@
 \usepackage[colorlinks,urlcolor=blue,linkcolor=blue,anchorcolor=blue,citecolor=blue,bookmarks]{hyperref}
-\usepackage{changes}
-    \definechangesauthor[name={Shi Wang}, color=red]{swang}
-    \setauthormarkup{}
 
@@
 \end{align}
-\added[swang]{and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
+{\color{red}and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
 \begin{eqnarray}
@@
     \includegraphics[width=0.95\textwidth]{QuantumGlobalPhaseDiagram.pdf}
-    \caption{\label{fig:QuantumPhaseDiagram}(Color online) \added[swang]{Zero-temperature global} phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
+    \caption{\label{fig:QuantumPhaseDiagram}(Color online){ \color{red}Zero-temperature global} phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model.
 The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively.
@@
 
-The \added[swang]{zero-temperature} quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).
+The {\color{red}zero-temperature} quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}, where the phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).
 We find nine magnetically ordered phases and a phase ascribed to be a QSL.
@@
 
-\added[swang]{Although the singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ show that there are phase transitions between stripe-A, stripe-B and stripe-C (see Appendix \ref{apx:PhaseBoundary} for details), the differences between these phases cannot be seen from the SSFs, which show the same characteristic wave vector [Fig.~\ref{fig:StructureFactors}(a), (b), (c) and (d)].
+{\color{red}Although the singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ show that there are phase transitions between stripe-A, stripe-B and stripe-C (see Appendix \ref{apx:PhaseBoundary} for details), the differences between these phases cannot be seen from the SSFs, which show the same characteristic wave vector [Fig.~\ref{fig:StructureFactors}(a), (b), (c) and (d)].
 In fact, the most commonly used physcial quantity to distinguish different quantum phases is the order parameter.
@@
 The green dashed lines mark the first BZ of the triangular lattice.
-(i) Characteristic wave vectors for the \added[swang]{FM (blue circle), stripe (orange square), 120$^\circ$ N\'{e}el (red up-triangle) and dual N\'{e}el (purple down-triangle)} phases.
+(i) Characteristic wave vectors for the {\color{red}FM (blue circle), stripe (orange square), 120$^\circ$ N\'{e}el (red up-triangle) and dual N\'{e}el (purple down-triangle)} phases.
 See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
@@
 11774152, No.
-11774300, \added[swang]{No.
+11774300, {\color{red}No.
 12004191 and No.
 12074175}, National Key Projects for Research and Development of China (Grant No.
-2016YFA0300401) \added[swang]{and Natural Science Foundation of Jiangsu Province, China (Grant No.
+2016YFA0300401) {\color{red}and Natural Science Foundation of Jiangsu Province, China (Grant No.
 BK20200738)}.
@@
 
-\section{\label{apx:PhaseBoundary}Phase boundaries in the \added[swang]{zero-temperature} quantum phase diagram}
+\section{\label{apx:PhaseBoundary}Phase boundaries in the {\color{red}zero-temperature} quantum phase diagram}
 
@@
     \caption{\label{fig:SecondDerivatives46} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ for six representative paths in the phase diagram.
-\added[swang]{The ED calculations are performed on a $4 \times 6$ cluster with periodic boundary condition.} The blue lines are the GS energies and the red lines are the second derivatives.
+{\color{red}The ED calculations are performed on a $4 \times 6$ cluster with periodic boundary condition.} The blue lines are the GS energies and the red lines are the second derivatives.
 In (a)-(c) $\alpha$ is fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively.
@@
 
-\added[swang]{
+{\color{red}
 \section{\label{apx:SizeEffect}Effects of system size on the phase boundaries}
@@
   \includegraphics[width=\columnwidth]{SecondDerivatives26.pdf}
-  \includegraphics[width=\columnwidth]{Cluster26.pdf}
-  \added[swang]{
+  {\color{red}
   \caption{\label{fig:SecondDerivatives26} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ along the same paths shown in Fig.~\ref{fig:SecondDerivatives46}.
